### 2013-02-14 writeup/paper.tex
initial commit

%
% File acl2012.tex
%
% Contact: Maggie Li (cswjli@comp.polyu.edu.hk), Michael White (mwhite@ling.osu.edu)
%%
%% Based on the style files for ACL2008 by Joakim Nivre and Noah Smith
%% and that of ACL2010 by Jing-Shin Chang and Philipp Koehn

\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage[numbers]{natbib}
\usepackage[fit]{truncate}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{multirow}
\usepackage{dblfloatfix}
\usepackage{float}
\usepackage{subfigure}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

\title{Some Negativity Results for Moduli}

\author{Ellie Pavlick \\
  {\tt elliepavlick@gmail.com} \\\And
  Chris Callison-Burch \\
  {\tt ccb@cs.jhu.edu} \\\And
  Dmitry Kachaev \\
  {\tt dmitry.kachaev@gmail.com } \\}

\date{}

\begin{document}
\maketitle

\begin{abstract}
 Let $\hat{F} < \pi$.  A central problem in elliptic model theory is the characterization of Noetherian functions.  We show that \begin{align*} Y' \left( \mathscr{{O}} \emptyset, \dots, \pi \emptyset \right) & \sim \sup \iiint_{{\eta_{\lambda,\Xi}}} t \left( \hat{Z}, \dots, \bar{h} + e \right) \,d R \\ & \ne \sum  \tilde{\Omega} \left( \| K \|^{-1}, N \wedge \pi \right) \vee \dots + L''  .\end{align*}  It would be interesting to apply the techniques of \cite{cite:0} to quasi-Gaussian vectors. This leaves open the question of uniqueness.
\end{abstract}

\section{Overview}
Crowdsourcing environments have become a key source of data for natural language processing research. Access to a fast, cheap, and flexible workforce has changed the way we collect data, and holds a great deal of promise for the future development of language technologies. Crowdsourced work has proven effective for collecting massive amounts of simple data annotations, such as annotating data for face recognition software and labeling sentiment in twitter data. As the demands and expectations of automated systems progress, and the complexity of the data required for training increases, however, it becomes natural to ask about the strengths and limitations of the crowd as annotators for natural language data.\\\\
We evaluate the language skills of bilingual workers on Amazon's Mechanical Turk, and their ability to provide translated data for statistical machine translation. Collecting parallel translated texts has traditionally been assumed to require a higher level of expertise than what is available from non-professional crowd workers. However, with an increasing number of active crowd workers located outside of the United States, the potential to access fluent speakers of lower resource languages makes crowdsourcing an attractive resource for translation.\\\\
We construct a task in which we aim to build bilingual dictionaries for over 100 languages, containing over 10,000 words each, using only translators available on Mechanical Turk. We collect demographic data relevant to the workers' language skills, and evaluate the quality of the translations submitted from workers across varying backgrounds and locations. Based on the data collected, we identify the strengths of Mechanical Turk as a source of multilingual data, and discuss best practices for ensuring high data quality from non-professional translators.

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/natlang-pie}
\caption{Self-reported native language of 2651 bilingual turkers}
\label{lang-pie}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Mechanical Turk}
Amazon's Mechanical Turk (MTurk) is an online crowdsourcing marketplace which gives employers and researchers access to a large, low-cost, human workforce. MTurk advertises `artificial artificial intelligence'; it provides a simple interface for accessing human skill, allowing small tasks, which are too difficult for computers, to be completed with the speed and scale of an automated process. When Amazon first introduced MTurk, payment was offered only in Amazon credits. As the service grew, payment switched to US dollars, and more recently has expanded to include foreign currencies, such as the rupee. Currently, MTurk claims over half a million workers from 190 countries, making it a compelling source of data for diverse natural language applications.\\\\
Within MTurk, those who need work completed (`requesters') post individual `Human Intelligence Tasks,' or just `HITs'. A typical HIT  requires a few minutes of work and pays a few cents, although there is significant variation across HITs. Once a HIT is posted, MTurk workers (`Turkers') are free to choose to complete the HITs which interest them. Worker identities remain anonymous to requesters, and all payment occurs through Amazon. Requesters are able to accept submitted work or reject work that they do not feel meets their standards, and only pay workers from whom they accepted tasks. \\\\
The convenience and low cost of using MTurk has made it popular among researchers. Because of the lack of oversight and the high potential for spam, however, most of the data collected from MTurk has been limited to simple tasks for which inter-annotator agreement is expected to be high (see Related Work section below). We explore the idea that MTurk's machinery is flexible enough to support more complex tasks requiring more nuanced quality control mechanisms, which could allow it to be a competitive alternative to professional data annotations.

\section{Related Work}
Crowdsourced data has been used in a variety of machine learning applications, including computer vision (Sorokin et al.), paraphrasing (Nakov et al.) and sentiment analysis (Snow et al.). More recently, in 2010, NAACL hosted a workshop on Creating Speech and Language Data with MTurk, in which MTurk was used to generate data for 24 different natural language tasks (CCB).\\\\
Typically, researchers rely on large amounts of MTurk data in order to compensate for the high likelihood of low quality labels. Snow et al. describes the success of using redundant non-expert labels to substitute for professional annotations, achieving comparable quality for much lower cost. The tasks from which these conclusions were drawn, however, were kept simple and easily-verifiable, with annotations restricted to either multiple choice or bounded numeric inputs. As NLP research advances, the level of expertise required from annotators advances as well. Callison-Burch et al. report success using MTurk to build parallel corpora for Machine Translation, a task which requires Turkers to speak two languages with a high level of proficiency.\\\\
As the use of MTurk has grown, researchers have become interested in who exactly makes up the Turker population. Early demographic studies by Ipeirotis revealed that Turkers are typically younger and more educated than the population as a whole. The study found that while most Turkers cite money as a motivation for working on MTurk, few cite it as their only motivation. A follow-up study by Ross et al. found that the majority of Turkers were located in the US, 30\% of Turkers were located in India, and that Indian Turkers tend to have lower incomes than US-based Turkers. Ross et al. also suggested that the international presence on MTurk has been growing over time. While there has not yet been a thorough investigation of Turkers' language abilities, Munro compiled survey responses of 2,000 Turkers, revealing that four of the six most represented languages come from India (the top six being Hindi, Malayalam, Tamil, Spanish, French, and Telugu). No study has yet been conducted to comprehensively assess the language skills of the growing number of international and bilingual Turkers or to analyze the potential of MTurk to support work in low-resource languages. \\\\

%%%%%%%%%%%%%%% HIT UIs %%%%%%%%%%%
\begin{figure}[h]
\centering
\includegraphics[width=3in]{figures/vocabulary_hit_mturk}
\caption{Translation HIT UI}
\label{tranhit}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=3in]{figures/synonyms_hit_mturk}
\caption{Evaluation HIT UI}
\label{synhit}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
\begin{table*}[h]
\centering
\begin{tabular}{lc}\hline\hline\\
Is [HIT language/English] your native language? &129,049\\
How many years have you spoken [HIT language]?&159,807\\
How many years have you spoken English?&159,808\\
What country do you live in?&329,033\\\\
Current location (collected automatically)& 329,033\\\\
\hline\\
Total assignments& 329,033\\
Total unique workers& 6,034\\\\
\hline\hline
\end{tabular}
\caption{Demographic survey questions and number of assignments with valid responses for each}
\label{survey-tab}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Task Design}
The central task in this study was to use Mechanical Turk to create low cost, high quality bilingual dictionaries for over 100 languages in order to test the reliability and breadth of the knowledge of Mechanical Turk's bilingual population. \\\\
We chose the languages which were highly used on Wikipedia, in terms of the number of available articles. We compiled a list of all languages for which there existed at least 10,000 Wikipedia articles; we also included a small number of low resource languages for which there were approximately 1,000 available articles, giving a total of 119 languages to use in our task. For each of the languages, we chose the 1,000 most popular articles, and from these selected the 10,000 most frequent words. The resulting vocabularies served as the source side of our dictionaries.\\\\
The dictionary creation task was broken into two steps: a translation HIT and an evaluation HIT. Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.  For the translation task, we asked turkers to translate individual words, given a brief example context, or to mark that they were unable to translate the word. Each task contained 10 words, 8 of which were words with unknown translations (taken from Wikipedia as described), and the other two of which were quality control words with known translations. The task paid one million dollars for the translation of 10 words. \\\\
For the evaluation task, Turkers were shown a pair of words, one which was a Turker's translation of one of the embedded quality control words, and the other which was a known gold-standard translation of the same word. Evaluators were asked whether the two words were synonyms, and chose between three answers: `Yes', `No', or `Related but not synonyms'. The last category was intended for word pairs such as `clouds' and `sky', which may be confusable to a non-native speaker but are not acceptable as dictionary translations. Turkers in the evaluation task could also flag the translated word as misspelled. Each HIT included 10 word pairs to be compared, and paid next to nothing. We describe the evaluation process further in the Measuring Quality section of this paper.\\\\
Quality control for the evalutation HIT consisted of embedded word pairs which were either known to be synonyms or were known to be unrelated. Whether the evaluators correctly labeled the known word pairs could be assessed automatically, allowing the evaluation HIT to be the final step of the dictionary creation pipeline.\\\\

\section{Turker Demographics}
At the start of each HIT, Turkers were asked to complete a brief survey about their language abilities. Valid responses to all survey questions were not required in order to complete the HIT; survey questions and the number of valid responses received for each are listed in table \ref{survey-tab}. Although it was not required, Turkers who completed multiple HIT assignments could fill out the survey multiple times. This enabled some Turkers to report multiple native languages (see figure \ref{numlangs-tab}). While most results presented are calculated across all Turkers, figures given for distributions across native languages are calculated only from Turkers who reported a single native language.\\

%%%%%%%%%%%%%%% NUM LANGUAGES TABLE %%%%%%%%%%%
\begin{figure}[h]
\begin{tabular}{ccc}\hline\hline
&\# languages&\# Turkers\\
\hline
No languages&0&2555\\\\
One language&1&2651\\\\
Multiple languages&2&684\\
&3&94\\
&4&23\\
&5&7\\
&6&8\\
&7&4\\
&8&1\\
&9&2\\
&10&3\\
&15&1\\
\hline\hline
\end{tabular}
\label{numlangs-tab}\\
\caption{Number of native languages reported during demographic survey.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% ASSIGNMENT SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/assign-turk-scatter}
\caption{Number of assignments and number of turkers for each language. Each dot represents a language.}
\label{ass-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Figure \ref{ass-scatter} shows the volume of HITs completed and the number of workers participating for each language. While the bulk (22\%) of bilingual turkers report English as their native language (see figure \ref{lang-pie}), Mechanical Turk's capacity to support the Indian languages is apparent. Hindi, Tamil, and Malayalam are especially well represented in terms of number of active translators, and Urdu, Telugu, and Macedonian are particularly productive in terms of number of assignments completed. As shown in figure \ref{langgeo-bar}, 11 of the top 25 languages, in terms of number of assignments submitted, were Indian languages, and the assignments for 15 of the top 25 were completed mostly or entirely by turkers located in India.

%%%%%%%%%%%%%%% LOCATION BAR %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/assign-langgeo-sorted}
\caption{Geolocation of turkers speaking 40 most represented languages, in terms of number of assignments submitted}
\label{langgeo-bar}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Measuring Data Quality}
The primary challenge of using crowdsourced language data is the widely variable quality of the collected annotations. While it is possible to strengthen the signal by collecting redundant labels, this strategy becomes difficult in practice for more complex data annotation. In the case of translation, even professional translations can be expected to vary significantly, and fully automatic comparison of free form text is itself an open research question.\\\\ 
In order to address the quality of the translations we received on the dictionary task, we constructed a pipeline in which the output of the translation HIT was reviewed by humans in a second evaluation HIT, described above. We quantified the quality of each translation assignment based on the output of the evaluation HIT. The quality of an assignment was scored as the fraction of known words which were acceptably translated: i.e, the supplied translation was judged to be synonymous with the gold standard translation. Since each assignment had either one or two known words embedded, each assignment was assigned a score of either 0, 0.5, or 1.\\\\

%%%%%%%%%%%%%%% MISREPORT TABLE %%%%%%%%%%%
\begin{figure}[h]
\centering
\begin{tabular}{cccc}\hline\hline\\
&Avg. & 99\%&\\
&Quality & Conf. Int.&n\\
Misreport&0.252&(0.244, 0.260)&10,479\\
Correct&0.282&(0.280, 0.283)&296,911\\
Overall&0.281&(0.279, 0.282)&307,390\\\\
\hline\hline
\end{tabular}
\label{mism-tab}
\caption{Quality of translations recieved from truthful versus misreporting Turkers.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-hitlang}
\caption{Translation quality of by source language}
\label{hitlangqual-bar}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Measured in this way, the average quality score across all HITs was just under 0.3. In general, countries which produced more translations did not produce lower quality translations, with India, Macedonia, and the US falling very close to average quality (figure \ref{quality-scatter}). In fact, likely as a result of the large number of India-based Turkers, most of the Indian languages fall above average quality, including Hindi, Telugu, Malayalam, Marathis, Tamil, Gujarati, Kannada, Bengali, and Punjabi, shown in figure \ref{hitlangqual-bar}. The notable exception is Urdu, which produced below average translations, likely due to the relatively low number of unique translators, making quality more susceptible to individual careless workers (see figure \ref{ass-scatter}). \\\\

%%%%%%%%%%%%%%% NATIVE LANGUAGE QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-natlang-sorted}
\caption{Translation quality of native and non-native speakers}
\label{natlangqual-bar}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Interestingly, native speakers do not consistently outperform non-native speakers (see figure \ref{natlangqual-bar}). In certain unique cases, such as Vietnam, non-native speakers produce significantly better translations than native speakers, possibly due to a large population of fluent US-based workers (figure \ref{langgeo-bar}). In general, the quality difference between native and non-native speakers is not significant.	\\\\

%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-scatter-avgturkers-country-labeled}
\caption{Quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country.}
\label{quality-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Self-reported country information is typically reliable. Three quarters of Turkers who reported their native language reported a single native language consistantly across all assignments (table \ref{numlangs-tab}), and of those reporting multiple native languages, the majority listed English in addition to the HIT's source language, meaning less than 5\% of Turkers gave unreasonable responses. Across all assignments, 96\% of reported locations agreed with automatically reported locations, although assignments in which Turkers misreported their location averaged 10\% lower in quality than those in which the reported location was accurate, shown in table \ref{mism-tab}.\\\\

\section{Discussion}
MTurk has a strong and diverse presence of bilingual workers, making it a promising resource for researchers and developers of multilingual systems. Although unfiltered data can contain large amounts of noise, crowdsourced pipelines, which contain human oversight as a means of evaluation, offer a feasible way of ensuring high quality data, even on tasks which require more complex labels. While MTurk does offer the ability to restrict workers based on country, embedded per-task controls which are checked either automatically when possible, or manually in a second-pass HIT, are likely to provide higher quality data than naive demographic filters. \\\\
Also, with intelligent quality control techniques, MTurk can prove that $P = NP$, solve the problems in the Middle East, and allow you to eat carbs and still lose weight.

%\begin{thebibliography}{}

%\bibitem[\protect\citename{}yrs]{name}
%name
%\newblock year
%\newblock title
%\newblock In {\em journal}.

%\end{thebibliography}

\end{document}

### 2013-02-16 writeup/paper.tex
fixing numlangs table
table with counts of dictionaries

@@
 \begin{tabular}{ccc}\hline\hline
+IGNORE TABLE& WILL FIX SOON&\\
 &\# languages&\# Turkers\\
@@
 
+%%%%%%%%%%%%%%% MISREPORT TABLE %%%%%%%%%%%
+\begin{figure}[h]
+\centering
+\begin{tabular}{cccc}
+Language&Total&Quality $\geq$ 0.5& Quality $>$ 0.5\\\hline\hline
+af&9983.0&7199.0&1679.0\\
+am&8341.0&6646.0&2489.0\\
+an&3080.0&938.0&228.0\\
+ar&9994.0&9638.0&5024.0\\
+ast&9968.0&9035.0&3808.0\\
+az&9975.0&7034.0&1983.0\\
+bcl&9940.0&4718.0&384.0\\
+be&9964.0&7008.0&2039.0\\
+bg&9982.0&8389.0&2622.0\\
+bn&9984.0&8915.0&3761.0\\
+bo&9920.0&1744.0&64.0\\
+bpy&9854.0&6439.0&2604.0\\
+br&9978.0&6188.0&1722.0\\
+bs&9860.0&7110.0&1913.0\\
+ca&9993.0&7318.0&1533.0\\
+ceb&9445.0&5394.0&1202.0\\
+cs&9957.0&6844.0&1342.0\\
+cy&9971.0&5369.0&942.0\\
+da&9983.0&8827.0&2843.0\\
+de&9921.0&8594.0&2609.0\\
+diq&33.0&8.0&0\\
+el&9994.0&8150.0&2630.0\\
+eo&9962.0&7261.0&1574.0\\
+es&9835.0&8127.0&2265.0\\
+eu&9993.0&9031.0&3365.0\\
+fa&5565.0&3527.0&1070.0\\
+fi&9968.0&8527.0&2499.0\\
+fr&9900.0&8472.0&2859.0\\
+fy&9962.0&6840.0&1618.0\\
+ga&9914.0&8421.0&2711.0\\
+gl&9987.0&7843.0&2606.0\\
+gu&9982.0&9916.0&9294.0\\
+he&8271.0&5807.0&1854.0\\
+hi&9949.0&9519.0&6066.0\\
+hr&9949.0&8723.0&2589.0\\
+ht&9938.0&8874.0&3323.0\\
+hu&9885.0&8304.0&2246.0\\
+hy&1758.0&1314.0&613.0\\
+id&9770.0&7090.0&1363.0\\
+ilo&9705.0&7510.0&1303.0\\
+io&147.0&58.0&41.0\\
+is&9913.0&6163.0&1907.0\\
+it&9755.0&8270.0&2312.0\\
+ja&8053.0&4204.0&1501.0\\
+jv&9883.0&7126.0&1404.0\\
+ka&5557.0&3837.0&1437.0\\
+kk&40.0&8.0&8.0\\
+kn&9993.0&9928.0&8591.0\\
+\end{tabular}
+\label{mism-tab}
+\end{figure}
+\clearpage
+\begin{figure}[h]
+\centering
+\begin{tabular}{cccc}
+ko&7159.0&3244.0&1094.0\\
+ku&149.0&70.0&0\\
+lb&9965.0&6786.0&1498.0\\
+lt&9975.0&8044.0&2197.0\\
+lv&9981.0&7343.0&2008.0\\
+mg&201.0&46.0&5.0\\
+mk&9845.0&9373.0&5138.0\\
+ml&9991.0&9795.0&7047.0\\
+mr&9993.0&9840.0&7540.0\\
+ms&9766.0&8348.0&2810.0\\
+nap&6540.0&2171.0&462.0\\
+nds&7324.0&3179.0&615.0\\
+ne&9972.0&9570.0&6100.0\\
+new&9976.0&6530.0&1018.0\\
+nl&9932.0&8924.0&3106.0\\
+nn&9994.0&8355.0&2529.0\\
+no&9941.0&8965.0&3070.0\\
+pa&9881.0&9464.0&6611.0\\
+pam&9909.0&6960.0&1384.0\\
+pl&9813.0&7207.0&1367.0\\
+pms&9285.0&4104.0&688.0\\
+ps&9727.0&5309.0&794.0\\
+pt&9857.0&7638.0&1554.0\\
+qu&67.0&0&0\\
+ro&9875.0&8849.0&2804.0\\
+ru&9977.0&0&0\\
+scn&9983.0&8446.0&3476.0\\
+sd&9357.0&3866.0&139.0\\
+sh&9930.0&8120.0&2043.0\\
+sk&9977.0&6039.0&1435.0\\
+sl&9889.0&5871.0&1092.0\\
+so&9908.0&2925.0&263.0\\
+sq&9924.0&8237.0&2468.0\\
+sr&9890.0&9005.0&3428.0\\
+su&9947.0&5818.0&891.0\\
+sv&9856.0&8127.0&2241.0\\
+sw&9770.0&8148.0&2186.0\\
+ta&9979.0&9687.0&6948.0\\
+te&9933.0&9085.0&5265.0\\
+th&4252.0&2381.0&883.0\\
+tl&9280.0&7173.0&2475.0\\
+tr&9941.0&8011.0&1896.0\\
+tt&40.0&8.0&8.0\\
+uk&9787.0&6349.0&2208.0\\
+ur&9864.0&3076.0&1033.0\\
+uz&9874.0&6643.0&1122.0\\
+vi&8276.0&7027.0&2935.0\\
+wa&49.0&28.0&11.0\\
+war&8579.0&5273.0&874.0\\
+wo&9759.0&5691.0&0\\
+yo&2367.0&2119.0&1245.0\\
+zh&3647.0&2812.0&1037.0\\
+\hline\hline
+\end{tabular}
+\label{mism-tab}
+\caption{Quality of translations recieved from truthful versus misreporting Turkers.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Measured in this way, the average quality score across all HITs was just under 0.3.

### 2013-02-17 writeup/paper.tex
Updated title, abstract, author order

@@
-%
-% File acl2012.tex
-%
-% Contact: Maggie Li (cswjli@comp.polyu.edu.hk), Michael White (mwhite@ling.osu.edu)
-%%
-%% Based on the style files for ACL2008 by Joakim Nivre and Noah Smith
-%% and that of ACL2010 by Jing-Shin Chang and Philipp Koehn
-
 \documentclass[11pt]{article}
@@
 
-\title{Some Negativity Results for Moduli}
+\title{A large scale study of the languages spoken (by bilinguals) on Mechanical Turk}
+\title{The Language Demographics of  Amazon Mechanical Turk}
 
 \author{Ellie Pavlick  \\
-  {\tt elliepavlick@gmail.com} \\\And
+  \small {\tt elliepavlick@gmail.com} \normalsize \\
+  \And
+  Dmitry Kachaev  \\
+ \small  {\tt dmitry.kachaev@gmail.com } \normalsize \\
+  \And
   Chris Callison-Burch \\
-  {\tt ccb@cs.jhu.edu} \\\And
-  Dmitry Kachaev \\
-  {\tt dmitry.kachaev@gmail.com } \\}
+ \small  {\tt ccb@seas.upenn.edu} \normalsize \\
+  }
 
@@
 \begin{abstract}
- Let $\hat{F} < \pi$.
-A central problem in elliptic model theory is the characterization of Noetherian functions.
-We show that \begin{align*} Y' \left( \mathscr{{O}} \emptyset, \dots, \pi \emptyset \right) & \sim \sup \iiint_{{\eta_{\lambda,\Xi}}} t \left( \hat{Z}, \dots, \bar{h} + e \right) \,d R \\ & \ne \sum  \tilde{\Omega} \left( \| K \|^{-1}, N \wedge \pi \right) \vee \dots + L''  .\end{align*}  It would be interesting to apply the techniques of \cite{cite:0} to quasi-Gaussian vectors.
-This leaves open the question of uniqueness.
+We present a large scale study of the languages spoken by bilingual workers on Mechanical Turk (MTurk).  
+We establish a  methodology for determining the language skills of anonymous crowd workers that is more robust than simple surveying.
+We validate workers' self-reported language skills claims by measuring their ability to correct translate words, and performing geolocation to see if they come from a country where the language is spoken.
+Moreover, rather than posting a one-off survey, we posted large, paid tasks consisting of 1,000 assignment to translate a total of 10,000 words in each of 100 languages.
+Our study ran for weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilinguals workers would have seen.
+Our study resulted in the creation of bilingual dictionaries for a wide variety of languages, and acted as census of the bilingual speakers on MTurk.
+We use this to recommend languages with the largest speaker populations that are good candidates for other researchers who want to  develop crowdsourced, multilingual technologies.
+
 \end{abstract}

### 2013-02-17 writeup/paper.tex
Minor changes to abstract

@@
 We establish a  methodology for determining the language skills of anonymous crowd workers that is more robust than simple surveying.
-We validate workers' self-reported language skills claims by measuring their ability to correct translate words, and performing geolocation to see if they come from a country where the language is spoken.
-Moreover, rather than posting a one-off survey, we posted large, paid tasks consisting of 1,000 assignment to translate a total of 10,000 words in each of 100 languages.
+We validate workers' self-reported language skills claims by measuring their ability to correctly translate words, and by geolocating workers to see if they come from a country where the language is spoken.
+Rather than posting a one-off survey, we posted large-scale, paid tasks consisting of 1,000 assignment to translate a total of 10,000 words in each of 100 languages.
 Our study ran for weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilinguals workers would have seen.

### 2013-02-17 writeup/paper.tex
Minor tweaks to abstract, author info

@@
 
-\author{Ellie Pavlick  \\
-  \small {\tt elliepavlick@gmail.com} \normalsize \\
-  \And
-  Dmitry Kachaev  \\
- \small  {\tt dmitry.kachaev@gmail.com } \normalsize \\
-  \And
-  Chris Callison-Burch \\
- \small  {\tt ccb@seas.upenn.edu} \normalsize \\
+\author{Ellie Pavlick \ \ \ \ \ \ \ \ \ \ Dmitry Kachaev \ \ \ \ \ \ \ \ \ \  Chris Callison-Burch \\
+Computer and Information Science Department, University of Pennsylvania \\
+Human Language Technology Center of Excellence, Johns Hopkins University \\
   }
@@
 We establish a  methodology for determining the language skills of anonymous crowd workers that is more robust than simple surveying.
-We validate workers' self-reported language skills claims by measuring their ability to correctly translate words, and by geolocating workers to see if they come from a country where the language is spoken.
-Rather than posting a one-off survey, we posted large-scale, paid tasks consisting of 1,000 assignment to translate a total of 10,000 words in each of 100 languages.
-Our study ran for weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilinguals workers would have seen.
-Our study resulted in the creation of bilingual dictionaries for a wide variety of languages, and acted as census of the bilingual speakers on MTurk.
-We use this to recommend languages with the largest speaker populations that are good candidates for other researchers who want to  develop crowdsourced, multilingual technologies.
+We validate workers' self-reported language skill claims by measuring their ability to correctly translate words, and by geolocating workers to see if they reside in countries where the languages are likely to be spoken.
+Rather than posting a one-off survey, we posted paid tasks consisting of 1,000 assignments to translate a total of 10,000 words in each of 100 languages.
+Our study ran for weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilinguals workers would have seen it.
+Our study was useful both to create bilingual dictionaries and to act as census of the bilingual speakers on MTurk.
+We use this data to recommend languages with the largest speaker populations as good candidates for other researchers who want to  develop crowdsourced, multilingual technologies.
 

### 2013-02-17 writeup/paper.tex
Fixed paragraph breaks

@@
 \section{Overview}
-Crowdsourcing environments have become a key source of data for natural language processing research.
-Access to a fast, cheap, and flexible workforce has changed the way we collect data, and holds a great deal of promise for the future development of language technologies.
+Crowdsourcing has become a key source of data for natural language processing research.
+Access to a fast, cheap, and flexible workforce has changed the way we collect data, and holds a great deal of promise for developing future language technologies.
 Crowdsourced work has proven effective for collecting massive amounts of simple data annotations, such as annotating data for face recognition software and labeling sentiment in twitter data.
-As the demands and expectations of automated systems progress, and the complexity of the data required for training increases, however, it becomes natural to ask about the strengths and limitations of the crowd as annotators for natural language data.\\\\
+As the demands and expectations of automated systems progress, and the complexity of the data required for training increases, however, it becomes natural to ask about the strengths and limitations of the crowd as annotators for natural language data.
+
 We evaluate the language skills of bilingual workers on Amazon's Mechanical Turk, and their ability to provide translated data for statistical machine translation.
 Collecting parallel translated texts has traditionally been assumed to require a higher level of expertise than what is available from non-professional crowd workers.
-However, with an increasing number of active crowd workers located outside of the United States, the potential to access fluent speakers of lower resource languages makes crowdsourcing an attractive resource for translation.\\\\
+However, with an increasing number of active crowd workers located outside of the United States, the potential to access fluent speakers of lower resource languages makes crowdsourcing an attractive resource for translation.
+
 We construct a task in which we aim to build bilingual dictionaries for over 100 languages, containing over 10,000 words each, using only translators available on Mechanical Turk.
@@
 As the service grew, payment switched to US dollars, and more recently has expanded to include foreign currencies, such as the rupee.
-Currently, MTurk claims over half a million workers from 190 countries, making it a compelling source of data for diverse natural language applications.\\\\
+Currently, MTurk claims over half a million workers from 190 countries, making it a compelling source of data for diverse natural language applications.
+
 Within MTurk, those who need work completed (`requesters') post individual `Human Intelligence Tasks,' or just `HITs'.
@@
 Requesters are able to accept submitted work or reject work that they do not feel meets their standards, and only pay workers from whom they accepted tasks.
-\\\\
+
 The convenience and low cost of using MTurk has made it popular among researchers.
@@
 Crowdsourced data has been used in a variety of machine learning applications, including computer vision (Sorokin et al.), paraphrasing (Nakov et al.) and sentiment analysis (Snow et al.).
-More recently, in 2010, NAACL hosted a workshop on Creating Speech and Language Data with MTurk, in which MTurk was used to generate data for 24 different natural language tasks (CCB).\\\\
+More recently, in 2010, NAACL hosted a workshop on Creating Speech and Language Data with MTurk, in which MTurk was used to generate data for 24 different natural language tasks (CCB).
+
 Typically, researchers rely on large amounts of MTurk data in order to compensate for the high likelihood of low quality labels.
@@
 Callison-Burch et al.
-report success using MTurk to build parallel corpora for Machine Translation, a task which requires Turkers to speak two languages with a high level of proficiency.\\\\
+report success using MTurk to build parallel corpora for Machine Translation, a task which requires Turkers to speak two languages with a high level of proficiency.
+
 As the use of MTurk has grown, researchers have become interested in who exactly makes up the Turker population.
@@
 No study has yet been conducted to comprehensively assess the language skills of the growing number of international and bilingual Turkers or to analyze the potential of MTurk to support work in low-resource languages.
-\\\\
 
@@
 How many years have you spoken English?&159,808\\
-What country do you live in?&329,033\\\\
-Current location (collected automatically)& 329,033\\\\
+What country do you live in?&329,033
+
+Current location (collected automatically)& 329,033
+
 \hline\\
 Total assignments& 329,033\\
-Total unique workers& 6,034\\\\
+Total unique workers& 6,034
+
 \hline\hline
@@
 The central task in this study was to use Mechanical Turk to create low cost, high quality bilingual dictionaries for over 100 languages in order to test the reliability and breadth of the knowledge of Mechanical Turk's bilingual population.
-\\\\
+
 We chose the languages which were highly used on Wikipedia, in terms of the number of available articles.
@@
 For each of the languages, we chose the 1,000 most popular articles, and from these selected the 10,000 most frequent words.
-The resulting vocabularies served as the source side of our dictionaries.\\\\
+The resulting vocabularies served as the source side of our dictionaries.
+
 The dictionary creation task was broken into two steps: a translation HIT and an evaluation HIT.
@@
 The task paid one million dollars for the translation of 10 words.
-\\\\
+
 For the evaluation task, Turkers were shown a pair of words, one which was a Turker's translation of one of the embedded quality control words, and the other which was a known gold-standard translation of the same word.
@@
 Each HIT included 10 word pairs to be compared, and paid next to nothing.
-We describe the evaluation process further in the Measuring Quality section of this paper.\\\\
+We describe the evaluation process further in the Measuring Quality section of this paper.
+
 Quality control for the evalutation HIT consisted of embedded word pairs which were either known to be synonyms or were known to be unrelated.
-Whether the evaluators correctly labeled the known word pairs could be assessed automatically, allowing the evaluation HIT to be the final step of the dictionary creation pipeline.\\\\
+Whether the evaluators correctly labeled the known word pairs could be assessed automatically, allowing the evaluation HIT to be the final step of the dictionary creation pipeline.
 
@@
 \hline
-No languages&0&2555\\\\
-One language&1&2651\\\\
+No languages&0&2555
+
+One language&1&2651
+
 Multiple languages&2&684\\
@@
 While it is possible to strengthen the signal by collecting redundant labels, this strategy becomes difficult in practice for more complex data annotation.
-In the case of translation, even professional translations can be expected to vary significantly, and fully automatic comparison of free form text is itself an open research question.\\\\
+In the case of translation, even professional translations can be expected to vary significantly, and fully automatic comparison of free form text is itself an open research question.
+
 In order to address the quality of the translations we received on the dictionary task, we constructed a pipeline in which the output of the translation HIT was reviewed by humans in a second evaluation HIT, described above.
@@
 The quality of an assignment was scored as the fraction of known words which were acceptably translated: i.e, the supplied translation was judged to be synonymous with the gold standard translation.
-Since each assignment had either one or two known words embedded, each assignment was assigned a score of either 0, 0.5, or 1.\\\\
+Since each assignment had either one or two known words embedded, each assignment was assigned a score of either 0, 0.5, or 1.
 
@@
 Correct&0.282&(0.280, 0.283)&296,911\\
-Overall&0.281&(0.279, 0.282)&307,390\\\\
+Overall&0.281&(0.279, 0.282)&307,390
+
 \hline\hline
@@
 The notable exception is Urdu, which produced below average translations, likely due to the relatively low number of unique translators, making quality more susceptible to individual careless workers (see figure \ref{ass-scatter}).
-\\\\
 
@@
 In certain unique cases, such as Vietnam, non-native speakers produce significantly better translations than native speakers, possibly due to a large population of fluent US-based workers (figure \ref{langgeo-bar}).
-In general, the quality difference between native and non-native speakers is not significant.	\\\\
+In general, the quality difference between native and non-native speakers is not significant.
 
@@
 Three quarters of Turkers who reported their native language reported a single native language consistantly across all assignments (table \ref{numlangs-tab}), and of those reporting multiple native languages, the majority listed English in addition to the HIT's source language, meaning less than 5\% of Turkers gave unreasonable responses.
-Across all assignments, 96\% of reported locations agreed with automatically reported locations, although assignments in which Turkers misreported their location averaged 10\% lower in quality than those in which the reported location was accurate, shown in table \ref{mism-tab}.\\\\
+Across all assignments, 96\% of reported locations agreed with automatically reported locations, although assignments in which Turkers misreported their location averaged 10\% lower in quality than those in which the reported location was accurate, shown in table \ref{mism-tab}.
 
@@
 While MTurk does offer the ability to restrict workers based on country, embedded per-task controls which are checked either automatically when possible, or manually in a second-pass HIT, are likely to provide higher quality data than naive demographic filters.
-\\\\
+
 Also, with intelligent quality control techniques, MTurk can prove that $P = NP$, solve the problems in the Middle East, and allow you to eat carbs and still lose weight.

### 2013-02-17 writeup/paper.tex

@@
 How many years have you spoken English?&159,808\\
-What country do you live in?&329,033
-
-Current location (collected automatically)& 329,033
-
+What country do you live in?&329,033\\
+Current location (collected automatically)& 329,033\\
 \hline\\
 Total assignments& 329,033\\
-Total unique workers& 6,034
-
+Total unique workers& 6,034\\
 \hline\hline
@@
 \hline
-No languages&0&2555
-
-One language&1&2651
-
+No languages&0&2555\\
+One language&1&2651\\
 Multiple languages&2&684\\
@@
 Correct&0.282&(0.280, 0.283)&296,911\\
-Overall&0.281&(0.279, 0.282)&307,390
-
+Overall&0.281&(0.279, 0.282)&307,390\\
 \hline\hline

### 2013-02-17 writeup/paper.tex
Editing Intro.

@@
 \section{Overview}
-Crowdsourcing has become a key source of data for natural language processing research.
-Access to a fast, cheap, and flexible workforce has changed the way we collect data, and holds a great deal of promise for developing future language technologies.
+Crowdsourcing has become a key mechanism for collecting data for natural language processing research.
+Access to a fast, cheap, and flexible workforce has changed the way we collect data, and holds promise for enabling future language technologies.
 Crowdsourced work has proven effective for collecting massive amounts of simple data annotations, such as annotating data for face recognition software and labeling sentiment in twitter data.

### 2013-02-18 writeup/paper.tex
counts of turkers per language

--- 2013-02-17 writeup/paper.tex
@@
 
-%%%%%%%%%%%%%%% MISREPORT TABLE %%%%%%%%%%%
-\begin{figure}[h]
-\centering
-\begin{tabular}{cccc}
-Language&Total&Quality $\geq$ 0.5& Quality $>$ 0.5\\\hline\hline
-af&9983.0&7199.0&1679.0\\
-am&8341.0&6646.0&2489.0\\
-an&3080.0&938.0&228.0\\
-ar&9994.0&9638.0&5024.0\\
-ast&9968.0&9035.0&3808.0\\
-az&9975.0&7034.0&1983.0\\
-bcl&9940.0&4718.0&384.0\\
-be&9964.0&7008.0&2039.0\\
-bg&9982.0&8389.0&2622.0\\
-bn&9984.0&8915.0&3761.0\\
-bo&9920.0&1744.0&64.0\\
-bpy&9854.0&6439.0&2604.0\\
-br&9978.0&6188.0&1722.0\\
-bs&9860.0&7110.0&1913.0\\
-ca&9993.0&7318.0&1533.0\\
-ceb&9445.0&5394.0&1202.0\\
-cs&9957.0&6844.0&1342.0\\
-cy&9971.0&5369.0&942.0\\
-da&9983.0&8827.0&2843.0\\
-de&9921.0&8594.0&2609.0\\
-diq&33.0&8.0&0\\
-el&9994.0&8150.0&2630.0\\
-eo&9962.0&7261.0&1574.0\\
-es&9835.0&8127.0&2265.0\\
-eu&9993.0&9031.0&3365.0\\
-fa&5565.0&3527.0&1070.0\\
-fi&9968.0&8527.0&2499.0\\
-fr&9900.0&8472.0&2859.0\\
-fy&9962.0&6840.0&1618.0\\
-ga&9914.0&8421.0&2711.0\\
-gl&9987.0&7843.0&2606.0\\
-gu&9982.0&9916.0&9294.0\\
-he&8271.0&5807.0&1854.0\\
-hi&9949.0&9519.0&6066.0\\
-hr&9949.0&8723.0&2589.0\\
-ht&9938.0&8874.0&3323.0\\
-hu&9885.0&8304.0&2246.0\\
-hy&1758.0&1314.0&613.0\\
-id&9770.0&7090.0&1363.0\\
-ilo&9705.0&7510.0&1303.0\\
-io&147.0&58.0&41.0\\
-is&9913.0&6163.0&1907.0\\
-it&9755.0&8270.0&2312.0\\
-ja&8053.0&4204.0&1501.0\\
-jv&9883.0&7126.0&1404.0\\
-ka&5557.0&3837.0&1437.0\\
-kk&40.0&8.0&8.0\\
-kn&9993.0&9928.0&8591.0\\
-\end{tabular}
-\label{mism-tab}
-\end{figure}
-\clearpage
-\begin{figure}[h]
-\centering
-\begin{tabular}{cccc}
-ko&7159.0&3244.0&1094.0\\
-ku&149.0&70.0&0\\
-lb&9965.0&6786.0&1498.0\\
-lt&9975.0&8044.0&2197.0\\
-lv&9981.0&7343.0&2008.0\\
-mg&201.0&46.0&5.0\\
-mk&9845.0&9373.0&5138.0\\
-ml&9991.0&9795.0&7047.0\\
-mr&9993.0&9840.0&7540.0\\
-ms&9766.0&8348.0&2810.0\\
-nap&6540.0&2171.0&462.0\\
-nds&7324.0&3179.0&615.0\\
-ne&9972.0&9570.0&6100.0\\
-new&9976.0&6530.0&1018.0\\
-nl&9932.0&8924.0&3106.0\\
-nn&9994.0&8355.0&2529.0\\
-no&9941.0&8965.0&3070.0\\
-pa&9881.0&9464.0&6611.0\\
-pam&9909.0&6960.0&1384.0\\
-pl&9813.0&7207.0&1367.0\\
-pms&9285.0&4104.0&688.0\\
-ps&9727.0&5309.0&794.0\\
-pt&9857.0&7638.0&1554.0\\
-qu&67.0&0&0\\
-ro&9875.0&8849.0&2804.0\\
-ru&9977.0&0&0\\
-scn&9983.0&8446.0&3476.0\\
-sd&9357.0&3866.0&139.0\\
-sh&9930.0&8120.0&2043.0\\
-sk&9977.0&6039.0&1435.0\\
-sl&9889.0&5871.0&1092.0\\
-so&9908.0&2925.0&263.0\\
-sq&9924.0&8237.0&2468.0\\
-sr&9890.0&9005.0&3428.0\\
-su&9947.0&5818.0&891.0\\
-sv&9856.0&8127.0&2241.0\\
-sw&9770.0&8148.0&2186.0\\
-ta&9979.0&9687.0&6948.0\\
-te&9933.0&9085.0&5265.0\\
-th&4252.0&2381.0&883.0\\
-tl&9280.0&7173.0&2475.0\\
-tr&9941.0&8011.0&1896.0\\
-tt&40.0&8.0&8.0\\
-uk&9787.0&6349.0&2208.0\\
-ur&9864.0&3076.0&1033.0\\
-uz&9874.0&6643.0&1122.0\\
-vi&8276.0&7027.0&2935.0\\
-wa&49.0&28.0&11.0\\
-war&8579.0&5273.0&874.0\\
-wo&9759.0&5691.0&0\\
-yo&2367.0&2119.0&1245.0\\
-zh&3647.0&2812.0&1037.0\\
-\hline\hline
-\end{tabular}
-\label{mism-tab}
-\caption{Quality of translations recieved from truthful versus misreporting Turkers.}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 Measured in this way, the average quality score across all HITs was just under 0.3.

### 2013-02-18 writeup/paper.tex
updated language counts and pie chart

@@
 \includegraphics[width=7in]{figures/natlang-pie}
-\caption{Self-reported native language of 2651 bilingual turkers}
+\caption{Self-reported native language of 3154 bilingual turkers}
 \label{lang-pie}
@@
 \begin{tabular}{ccc}\hline\hline
-IGNORE TABLE& WILL FIX SOON&\\
-&\# languages&\# Turkers\\
-\hline
-No languages&0&2555\\
-One language&1&2651\\
-Multiple languages&2&684\\
-&3&94\\
-&4&23\\
-&5&7\\
-&6&8\\
-&7&4\\
+&\# languages&\# Turkers\\ \hline
+No languages&0&1801\\
+One language&1&3154\\
+Multiple languages&2&243	\\
+&3&49\\
+&4&12\\
+&5&9\\
+&6&5\\
+&7&2\\
 &8&1\\
 &9&2\\
-&10&3\\
+&10&2\\
 &15&1\\
-\hline\hline
+\hline\\hline
 \end{tabular}
-\label{numlangs-tab}\\
+\label{numlangs-tab}
 \caption{Number of native languages reported during demographic survey.}

### 2013-02-18 writeup/paper.tex
turker map
Making changes to the intro

@@
 We validate workers' self-reported language skill claims by measuring their ability to correctly translate words, and by geolocating workers to see if they reside in countries where the languages are likely to be spoken.
-Rather than posting a one-off survey, we posted paid tasks consisting of 1,000 assignments to translate a total of 10,000 words in each of 100 languages.
-Our study ran for weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilinguals workers would have seen it.
+Rather than posting a one-off survey, we posted paid tasks consisting of 1,000 assignments to translate a total of 10,000 words in each of 119 languages.
+Our study ran for weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilinguals workers would complete it.
 Our study was useful both to create bilingual dictionaries and to act as census of the bilingual speakers on MTurk.
@@
 
-\section{Overview}
-Crowdsourcing has become a key mechanism for collecting data for natural language processing research.
-Access to a fast, cheap, and flexible workforce has changed the way we collect data, and holds promise for enabling future language technologies.
+\section{Introduction}
+Crowdsourcing is a promising new mechanism for collecting data for natural language processing research.
+Access to a fast, cheap, and flexible workforce allows us to collect new types of data, potentially enabling new language technologies.
+% ccb - todo - combine these sentences:
+Because crowdsourcing platforms like Amazon Mechanical Turk (MTurk) give researchers access to a worldwide workforce, one obvious application of crowdsourcing is the creation of multilingual technologies.
+With an increasing number of active crowd workers located outside of the United States, there is even the potential to reach fluent speakers of lower resource languages.
+In this paper, we present the first large-scale demographic study of the languages spoken by workers on MTurk.
+
+%Access to a fast, cheap, and flexible workforce has changed the way we collect data, and holds promise for enabling future language technologies.
 Crowdsourced work has proven effective for collecting massive amounts of simple data annotations, such as annotating data for face recognition software and labeling sentiment in twitter data.
 As the demands and expectations of automated systems progress, and the complexity of the data required for training increases, however, it becomes natural to ask about the strengths and limitations of the crowd as annotators for natural language data.
-
-We evaluate the language skills of bilingual workers on Amazon's Mechanical Turk, and their ability to provide translated data for statistical machine translation.
+%We evaluate the language skills of bilingual workers on Amazon's Mechanical Turk, and their ability to provide translated data for statistical machine translation.
 Collecting parallel translated texts has traditionally been assumed to require a higher level of expertise than what is available from non-professional crowd workers.
@@
 \label{lang-pie}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
+\begin{figure*}[h]
+\centering
+\includegraphics[width=7in]{figures/turkermap}
+\caption{}
+\label{map}
 \end{figure*}

### 2013-02-18 writeup/paper.tex
Finished updating the Overview

@@
 
-\section{Introduction}
+\section{Overview}
 Crowdsourcing is a promising new mechanism for collecting data for natural language processing research.
 Access to a fast, cheap, and flexible workforce allows us to collect new types of data, potentially enabling new language technologies.
-% ccb - todo - combine these sentences:
 Because crowdsourcing platforms like Amazon Mechanical Turk (MTurk) give researchers access to a worldwide workforce, one obvious application of crowdsourcing is the creation of multilingual technologies.
 With an increasing number of active crowd workers located outside of the United States, there is even the potential to reach fluent speakers of lower resource languages.
-In this paper, we present the first large-scale demographic study of the languages spoken by workers on MTurk.
+In this paper, we investigate the feasibility of hiring language informants on MTurk by conducting the first large-scale demographic study of the languages spoken by workers on the platform.
 
@@
 
-We construct a task in which we aim to build bilingual dictionaries for over 100 languages, containing over 10,000 words each, using only translators available on Mechanical Turk.
+There are several complicating factors when trying to take a census of workers on MTurk.
+The workers identities are anonymized, and Amazon provides no information about their countries of origin nor their language abilities.
+Posting a simple survey to have workers self-report this information may be inadequate, since (a) many worker may never see the survey, (b) many opt not to do one-off surveys since potential payment is low, and (c) validating the answers of respondents is not straightforward.
+
+Our study establishes a methodology for determining the language demographics of anonymous crowd workers that is more robust than simple surveying.
+We ask workers what languages they speak and what country they reside in, and validate their claims by measuring their ability to correctly translate words, and by geolocating them.
+To increase the visibility and the desirability of our tasks, we post 1,000 assignments in each of 119 languages.
+These tasks each consist of translating 12 foreign words into English.
+Two of the 12 words have known translations, allowing us to validate the the workers' translations are accurate, while constructing bilingual dictionaries with up to 10,000 new entries.
+
+%We construct a task in which we aim to build bilingual dictionaries for over 100 languages, containing over 10,000 words each, using only translators available on Mechanical Turk.
 We collect demographic data relevant to the workers' language skills, and evaluate the quality of the translations submitted from workers across varying backgrounds and locations.
 Based on the data collected, we identify the strengths of Mechanical Turk as a source of multilingual data, and discuss best practices for ensuring high data quality from non-professional translators.
+
+The demographic data allows us to analyze current speaker populations for more than 100 languages.
+Our survey also allows us to report on other information like how quickly translations were completed for each language, how often workers misrepresented their language abilities to try to obtain financial rewards, and what the estimated accuracy is for the bilingual dictionaries that we construct.
 
@@
 
-\section{Mechanical Turk}
+\section{Background and Related Work}
+%\section{Mechanical Turk}
 Amazon's Mechanical Turk (MTurk) is an online crowdsourcing marketplace which gives employers and researchers access to a large, low-cost, human workforce.

### 2013-02-18 writeup/paper.tex
Modified Overview
Rephrased the last paragraph as questions to make it a little more
interesting.

@@
 \DeclareMathOperator*{\argmax}{arg\,max}
-\setlength\titlebox{6.5cm}    % Expanding the titlebox
+\setlength\titlebox{5.4cm}    % Expanding the titlebox
 
@@
 
-%We construct a task in which we aim to build bilingual dictionaries for over 100 languages, containing over 10,000 words each, using only translators available on Mechanical Turk.
-We collect demographic data relevant to the workers' language skills, and evaluate the quality of the translations submitted from workers across varying backgrounds and locations.
-Based on the data collected, we identify the strengths of Mechanical Turk as a source of multilingual data, and discuss best practices for ensuring high data quality from non-professional translators.
-
-The demographic data allows us to analyze current speaker populations for more than 100 languages.
-Our survey also allows us to report on other information like how quickly translations were completed for each language, how often workers misrepresented their language abilities to try to obtain financial rewards, and what the estimated accuracy is for the bilingual dictionaries that we construct.
+The survey data allows us to analyze current speaker populations for more than 100 languages.  The data also allows us to answer questions like: 
+How quickly is work completed in a given language? 
+Are crowdsourced translations reliably good? 
+How often do workers misrepresented their language abilities to falsely obtain financial rewards?
 

### 2013-02-18 writeup/paper.tex
Added markers to show affliations.

@@
 
+\newcommand{\affliationPenn}{\ensuremath{{}^\text{1}}}
+\newcommand{\affliationJHU}{\ensuremath{{}^\text{2}}}
+
 \title{A large scale study of the languages spoken (by bilinguals) on Mechanical Turk}
@@
 
-\author{Ellie Pavlick \ \ \ \ \ \ \ \ \ \ Dmitry Kachaev \ \ \ \ \ \ \ \ \ \  Chris Callison-Burch \\
-Computer and Information Science Department, University of Pennsylvania \\
-Human Language Technology Center of Excellence, Johns Hopkins University \\
+\author{Ellie Pavlick\affliationPenn \ \ \ \ \ \ \ \ \ \ Dmitry Kachaev\affliationJHU \ \ \ \ \ \ \ \ \ \  Chris Callison-Burch\affliationPenn$^{,}$\affliationJHU \\
+\affliationPenn Computer and Information Science Department, University of Pennsylvania \\
+\affliationJHU Human Language Technology Center of Excellence, Johns Hopkins University \\
   }

### 2013-02-18 writeup/paper.tex
Added paragraph to Discssion
Added a description about the fact that we sampled bilinguals rather
than monolinguals.  Might move this to some other place in the paper.

@@
 
+Although our research targeted bilingual workers on Mechanical Turk, and neglected monolingual workers, we believe our results reliably represent the current speaker populations, since the vast majority of the work available on the crowdsourced platform is currently English-only.
+We therefore assume the number of non-English speakers is small.
+In the future, it may be desirable to recruit monolingual foreign workers.
+In such cases, we recommend other tests to validate their language abilities in place of our translation test.
+These could include performing narrative cloze, or listening to audio files containing speech in different language and identifying their language.
+
 Also, with intelligent quality control techniques, MTurk can prove that $P = NP$, solve the problems in the Middle East, and allow you to eat carbs and still lose weight.

### 2013-02-18 writeup/paper.tex
Adding bibliography

@@
 
-The survey data allows us to analyze current speaker populations for more than 100 languages.  The data also allows us to answer questions like: 
+Surveying thousands of workers allows us to analyze current speaker populations for more than 100 languages.  The data also allows us to answer questions like: 
 How quickly is work completed in a given language? 
 Are crowdsourced translations reliably good? 
-How often do workers misrepresented their language abilities to falsely obtain financial rewards?
+How often do workers misrepresented their language abilities to 
+%falsely
+obtain financial rewards?
 
@@
 \section{Related Work}
-Crowdsourced data has been used in a variety of machine learning applications, including computer vision (Sorokin et al.), paraphrasing (Nakov et al.) and sentiment analysis (Snow et al.).
-More recently, in 2010, NAACL hosted a workshop on Creating Speech and Language Data with MTurk, in which MTurk was used to generate data for 24 different natural language tasks (CCB).
+Crowdsourced data has been used in a variety of machine learning applications, including computer vision (Sorokin et al.), paraphrasing (Nakov et al.) and sentiment analysis \cite{Snow2008}.
+More recently, in 2010, NAACL hosted a workshop on Creating Speech and Language Data with MTurk, in which MTurk was used to generate data for 24 different natural language tasks \cite{callisonburch-dredze:2010:MTURK}.
 
@@
 As the use of MTurk has grown, researchers have become interested in who exactly makes up the Turker population.
-Early demographic studies by Ipeirotis revealed that Turkers are typically younger and more educated than the population as a whole.
+Early demographic studies by \newcite{ipeirotis:2010:demographics} revealed that Turkers are typically younger and more educated than the population as a whole.
 The study found that while most Turkers cite money as a motivation for working on MTurk, few cite it as their only motivation.
@@
 
-Also, with intelligent quality control techniques, MTurk can prove that $P = NP$, solve the problems in the Middle East, and allow you to eat carbs and still lose weight.
-
-%\begin{thebibliography}{}
-
-%\bibitem[\protect\citename{}yrs]{name}
-%name
-%\newblock year
-%\newblock title
-%\newblock In {\em journal}.
-
-%\end{thebibliography}
+\bibliographystyle{acl2012}
+\bibliography{mturk}
 

### 2013-02-18 writeup/paper.tex
Removed natbib

@@
 \usepackage{mathrsfs}
-\usepackage[numbers]{natbib}
 \usepackage[fit]{truncate}
@@
 also suggested that the international presence on MTurk has been growing over time.
-While there has not yet been a thorough investigation of Turkers' language abilities, Munro compiled survey responses of 2,000 Turkers, revealing that four of the six most represented languages come from India (the top six being Hindi, Malayalam, Tamil, Spanish, French, and Telugu).
+While there has not yet been a thorough investigation of Turkers' language abilities, \newcite{munro-tily:2011} compiled survey responses of 2,000 Turkers, revealing that four of the six most represented languages come from India (the top six being Hindi, Malayalam, Tamil, Spanish, French, and Telugu).
 No study has yet been conducted to comprehensively assess the language skills of the growing number of international and bilingual Turkers or to analyze the potential of MTurk to support work in low-resource languages.

### 2013-02-18 writeup/paper.tex
new map
Editing related work

@@
 \centering
-\includegraphics[width=7in]{figures/turkermap}
+\includegraphics[width=7in]{figures/turkermap-color}
 \caption{}
@@
 \section{Background and Related Work}
+%\section{Background on Mechanical Turk and Related Work}
 %\section{Mechanical Turk}
-Amazon's Mechanical Turk (MTurk) is an online crowdsourcing marketplace which gives employers and researchers access to a large, low-cost, human workforce.
-MTurk advertises `artificial artificial intelligence'; it provides a simple interface for accessing human skill, allowing small tasks, which are too difficult for computers, to be completed with the speed and scale of an automated process.
-When Amazon first introduced MTurk, payment was offered only in Amazon credits.
-As the service grew, payment switched to US dollars, and more recently has expanded to include foreign currencies, such as the rupee.
-Currently, MTurk claims over half a million workers from 190 countries, making it a compelling source of data for diverse natural language applications.
+Amazon's Mechanical Turk (MTurk) is an online marketplace for work which gives employers and researchers access to a large, low-cost, human workforce.
+MTurk provides a simple interface for accessing human skill, allowing requesters to provide micro-payments in return for workers completing micro-tasks.
+The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs), which suggests that it was designed to accommodate tasks that are difficult for computers, but simple for people.
+This allows for research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}, as well as for large-scale annotation of training data for machine learning applications, including computer vision \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10} and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK}.
+%In 2010, NAACL hosted a workshop on Creating Speech and Language Data with MTurk, in which MTurk was used to generate data for 24 different natural language tasks \cite{callisonburch-dredze:2010:MTURK}.
 
-Within MTurk, those who need work completed (`requesters') post individual `Human Intelligence Tasks,' or just `HITs'.
+Several reports examine Mechanical Turk as a marketplace \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.
+When Amazon introduced MTurk, it first offered payment only in Amazon credits, and later offered direct payment in US dollars.
+More recently has expanded to include one foreign currency, the Indian rupee.
+Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries.\footnote{https://requester.mturk.com/tour}  This suggest that it has a diverse worker population that should represent a wide variety of languages.
+
+%Within MTurk, those who need work completed (`requesters') post individual HITs.
 A typical HIT  requires a few minutes of work and pays a few cents, although there is significant variation across HITs.
@@
 
-The convenience and low cost of using MTurk has made it popular among researchers.
+%The convenience and low cost of using MTurk has made it popular among researchers.
 Because of the lack of oversight and the high potential for spam, however, most of the data collected from MTurk has been limited to simple tasks for which inter-annotator agreement is expected to be high (see Related Work section below).
@@
 
-\section{Related Work}
-Crowdsourced data has been used in a variety of machine learning applications, including computer vision (Sorokin et al.), paraphrasing (Nakov et al.) and sentiment analysis \cite{Snow2008}.
-More recently, in 2010, NAACL hosted a workshop on Creating Speech and Language Data with MTurk, in which MTurk was used to generate data for 24 different natural language tasks \cite{callisonburch-dredze:2010:MTURK}.
+%\section{Related Work}
 

### 2013-02-18 writeup/paper.tex
small edits

--- 2013-02-18 writeup/paper.tex
@@
 Our study establishes a methodology for determining the language demographics of anonymous crowd workers that is more robust than simple surveying.
-We ask workers what languages they speak and what country they reside in, and validate their claims by measuring their ability to correctly translate words, and by geolocating them.
+We ask workers what languages they speak and in what country they reside, and validate their claims by measuring their ability to correctly translate words and by geolocating them.
 To increase the visibility and the desirability of our tasks, we post 1,000 assignments in each of 119 languages.
-These tasks each consist of translating 12 foreign words into English.
-Two of the 12 words have known translations, allowing us to validate the the workers' translations are accurate, while constructing bilingual dictionaries with up to 10,000 new entries.
+These tasks each consist of translating 10 foreign words into English.
+Two of the 10 words have known translations, allowing us to validate the the workers' translations are accurate, while constructing bilingual dictionaries with up to 10,000 new entries.
+
+\textbf{***Is this right? I think most of our tasks have 10 words per HIT.***}
 
@@
 Worker identities remain anonymous to requesters, and all payment occurs through Amazon.
-Requesters are able to accept submitted work or reject work that they do not feel meets their standards, and only pay workers from whom they accepted tasks.
+Requesters are able to accept submitted work or reject work that they do not feel meets their standards, and only pay workers from whom they accept tasks.
 
@@
 &15&1\\
-\hline\\hline
+\hline\hline
 \end{tabular}

### 2013-02-18 writeup/paper.tex

--- 2013-02-18 writeup/paper.tex
@@
 
+Within MTurk, those who need work completed (`requesters') post individual `Human Intelligence Tasks,' or just `HITs'.
+A typical HIT  requires a few minutes of work and pays a few cents, although there is significant variation across HITs.
+Once a HIT is posted, MTurk workers (`Turkers') are free to choose to complete the HITs which interest them.
+Worker identities remain anonymous to requesters, and all payment occurs through Amazon.
+Requesters are able to accept submitted work or reject work that they do not feel meets their standards, and only pay workers from whom they accept tasks.
 Several reports examine Mechanical Turk as a marketplace \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.

### 2013-02-18 writeup/paper.tex
Corrected Intro to address Ellie's comment

@@
 \DeclareMathOperator*{\argmax}{arg\,max}
-\setlength\titlebox{5.4cm}    % Expanding the titlebox
+\setlength\titlebox{5.2cm}    % Expanding the titlebox
 
@@
 These tasks each consist of translating 10 foreign words into English.
-Two of the 10 words have known translations, allowing us to validate the the workers' translations are accurate, while constructing bilingual dictionaries with up to 10,000 new entries.
-
-\textbf{***Is this right? I think most of our tasks have 10 words per HIT.***}
+Two of the 10 words have known translations, allowing us to validate the the workers' translations are accurate, while constructing bilingual dictionaries with up to 10,000 entries, with the majority of entries being new.
 

### 2013-02-18 writeup/paper.tex
Editing background

@@
 This allows for research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}, as well as for large-scale annotation of training data for machine learning applications, including computer vision \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10} and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK}.
-%In 2010, NAACL hosted a workshop on Creating Speech and Language Data with MTurk, in which MTurk was used to generate data for 24 different natural language tasks \cite{callisonburch-dredze:2010:MTURK}.
 
-Within MTurk, those who need work completed (`requesters') post individual `Human Intelligence Tasks,' or just `HITs'.
-A typical HIT  requires a few minutes of work and pays a few cents, although there is significant variation across HITs.
-Once a HIT is posted, MTurk workers (`Turkers') are free to choose to complete the HITs which interest them.
-Worker identities remain anonymous to requesters, and all payment occurs through Amazon.
-Requesters are able to accept submitted work or reject work that they do not feel meets their standards, and only pay workers from whom they accept tasks.
+On MTurk researchers who need work completed are called `Requesters', workers are often referred to as `Turkers', and micro tasks are called `HITs'.
+MTurk is a true market, meaning that Turkers are free to choose to complete the HITs which interest them, and Requesters can price their tasks competitively to try to attract workers and complete have their tasks done quickly \cite{faridani-et-al:2011,singer-mittal:2011}.
+Turkers' identities remain anonymous to Requesters, and all payment occurs through Amazon.
+Requesters are able to accept submitted work or reject work that they do not feel meets their standards.
+Turkers are only pay if a Requester accepts their work.
+
 Several reports examine Mechanical Turk as a marketplace \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.

### 2013-02-18 writeup/paper.tex
Cropped the map and added a caption

@@
 
-%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
+%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
 \begin{figure*}[h]
 \centering
-\includegraphics[width=7in]{figures/turkermap-color}
-\caption{}
+\includegraphics[width=\linewidth]{figures/turkermap-color-cropped}
+\caption{A map of the number of workers per country.
+This is map is generated based on ((the self-reported location / geolocation of IP address)) of the XXXX workers in our study.
+The size of the circles represents the number of worker from each country.
+The largest are India (1082 workers), the United States (XXX), XXX (XXX) and XXX (XXX).
+To calibrate the sizes: the Philippines has XXX workers, Egypt has XXX, and Russia has XXX.}
 \label{map}

### 2013-02-18 writeup/paper.tex
Edited caption

--- 2013-02-18 writeup/paper.tex
@@
 
-%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
+%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
 \begin{figure*}[h]
 \centering
-\includegraphics[width=7in]{figures/turkermap-color}
-\caption{}
+\includegraphics[width=\linewidth]{figures/turkermap-color-cropped}
+\caption{The number of workers per country.
+This map was generated based on ((the self-reported location / geolocation of IP address)) of the XXXX workers in our study.
+The size of the circles represents the number of worker from each country.
+The two largest are India (1082 workers) and the United States (XXX).
+To calibrate the sizes: the Philippines has XXX workers, Egypt has XXX, Russia has XXX, and Sri Lanka has XXX.}
 \label{map}

### 2013-02-19 writeup/paper.tex
updated map and caption

--- 2013-02-18 writeup/paper.tex
@@
 
-%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
+%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
 \begin{figure*}[h]
 \centering
-\includegraphics[width=7in]{figures/turkermap-color}
-\caption{}
+\includegraphics[width=\linewidth]{figures/turkermap-full}
+\caption{The number of workers per country.
+This map was generated based on geolocation of IP address of the 5284 workers in our study.
+The size of the circles represents the number of worker from each country.
+The two largest are India (2022 workers) and the United States (904).
+To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
 \label{map}

### 2013-02-19 writeup/paper.tex

@@
 \centering
-\includegraphics[width=\linewidth]{figures/turkermap-full}
+\includegraphics[width=\linewidth]{figures/turkermap-color-cropped}
 \caption{The number of workers per country.
-This map was generated based on geolocation of IP address of the 5284 workers in our study.
+This map was generated based on geolocating the IP address of the 5,284 workers in our study.
 The size of the circles represents the number of worker from each country.
-The two largest are India (2022 workers) and the United States (904).
+The two largest are India (2,022 workers) and the United States (904).
 To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
@@
 %\section{Mechanical Turk}
-Amazon's Mechanical Turk (MTurk) is an online marketplace for work which gives employers and researchers access to a large, low-cost, human workforce.
-MTurk provides a simple interface for accessing human skill, allowing requesters to provide micro-payments in return for workers completing micro-tasks.
-The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs), which suggests that it was designed to accommodate tasks that are difficult for computers, but simple for people.
-This allows for research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}, as well as for large-scale annotation of training data for machine learning applications, including computer vision \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10} and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK}.
+Amazon's Mechanical Turk (MTurk) is an online marketplace for work which gives employers and researchers access to a large, low-cost, workforce.
+MTurk provides a simple interface for accessing human skills, allowing employers to provide micro-payments in return for workers completing micro-tasks.
+The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs).
+MTurk was designed to accommodate tasks that are difficult for computers, but simple for people.
+This facilitates research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}.
+It has application to other fields like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{novotney-callisonburch:2010:NAACLHLT,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK}.
 
-On MTurk researchers who need work completed are called `Requesters', workers are often referred to as `Turkers', and micro tasks are called `HITs'.
+On MTurk, researchers who need work completed are called `Requesters', workers are often referred to as `Turkers', and micro tasks are called `HITs'.
 MTurk is a true market, meaning that Turkers are free to choose to complete the HITs which interest them, and Requesters can price their tasks competitively to try to attract workers and complete have their tasks done quickly \cite{faridani-et-al:2011,singer-mittal:2011}.
@@
 
-Several reports examine Mechanical Turk as a marketplace \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.
+Several reports examine Mechanical Turk as an economic market \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.
 When Amazon introduced MTurk, it first offered payment only in Amazon credits, and later offered direct payment in US dollars.
 More recently has expanded to include one foreign currency, the Indian rupee.
-Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries.\footnote{https://requester.mturk.com/tour}  This suggest that it has a diverse worker population that should represent a wide variety of languages.
+Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries.\footnote{https://requester.mturk.com/tour}  This suggest that its worker population that should represent a diverse set of languages.
 
@@
 
-Typically, researchers rely on large amounts of MTurk data in order to compensate for the high likelihood of low quality labels.
+%Typically, researchers rely on large amounts of MTurk data in order to compensate for the high likelihood of low quality labels.
 Snow et al.
@@
 No study has yet been conducted to comprehensively assess the language skills of the growing number of international and bilingual Turkers or to analyze the potential of MTurk to support work in low-resource languages.
+
+\newcite{irvine:10} Using Mechanical Turk to annotate lexicons for less commonly used languages
+
+ MTurk to build parallel corpora for Machine Translation, a task which requires Turkers to speak two languages with a high level of proficiency.
+\cite{ambati_act,ambati_naacl,bloodgood-callisonburch:2010:ACL,zaidan-callisonburch:2011:ACL-HLT2011a,Zbib-etal:2012:NAACL,post-callisonburch-osborne:2012:WMT}
 

### 2013-02-19 writeup/paper.tex
Finished revising the Related Work section

@@
 MTurk provides a simple interface for accessing human skills, allowing employers to provide micro-payments in return for workers completing micro-tasks.
-The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs).
+The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs),which hints at its origins.
 MTurk was designed to accommodate tasks that are difficult for computers, but simple for people.
 This facilitates research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}.
-It has application to other fields like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{novotney-callisonburch:2010:NAACLHLT,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK}.
+It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge-banerjee-rudnicky:2010:MTURK,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.
+
+\nocite{novotney-callisonburch:2010:NAACLHLT}
 
@@
 
-As the use of MTurk has grown, researchers have become interested in who exactly makes up the Turker population.
-Early demographic studies by \newcite{ipeirotis:2010:demographics} revealed that Turkers are typically younger and more educated than the population as a whole.
-The study found that while most Turkers cite money as a motivation for working on MTurk, few cite it as their only motivation.
-A follow-up study by Ross et al.
-found that the majority of Turkers were located in the US, 30\% of Turkers were located in India, and that Indian Turkers tend to have lower incomes than US-based Turkers.
-Ross et al.
-also suggested that the international presence on MTurk has been growing over time.
-While there has not yet been a thorough investigation of Turkers' language abilities, \newcite{munro-tily:2011} compiled survey responses of 2,000 Turkers, revealing that four of the six most represented languages come from India (the top six being Hindi, Malayalam, Tamil, Spanish, French, and Telugu).
-No study has yet been conducted to comprehensively assess the language skills of the growing number of international and bilingual Turkers or to analyze the potential of MTurk to support work in low-resource languages.
+A demographic study by \newcite{ipeirotis:2010:demographics} focused on age, gender, martial status, income levels, motivation for working on MTurk, and whether workers used it as a primary or supplemental form of income.
+The study contrasted Indian and US workers.
+A number of other studies have informally investigated Turkers' language abilities.
+\newcite{munro-tily:2011} compiled survey responses of 2,000 Turkers, revealing that four of the six most represented languages come from India (the top six being Hindi, Malayalam, Tamil, Spanish, French, and Telugu).
+\newcite{irvine:10} had Turkers evaluate the accuracy of translations that had been automatically inducted from monolingual texts.
+They examined translations of 100 words in 42 low-resource languages, reported geolocated countries for their workers (India, the US, Romania, Pakistan, Macedonia, Latvia, Bangladesh and the Philippines).
+Irvine and Klementiev discussed the difficulty of quality control and assessing the plausibility of workers' language skills for rare languages, which we address in this paper.
 
-\newcite{irvine:10} Using Mechanical Turk to annotate lexicons for less commonly used languages
+%No study has yet been conducted to comprehensively assess the language skills of the growing number of international and bilingual Turkers or to analyze the potential of MTurk to support work in low-resource languages.
 
- MTurk to build parallel corpora for Machine Translation, a task which requires Turkers to speak two languages with a high level of proficiency.
-\cite{ambati_act,ambati_naacl,bloodgood-callisonburch:2010:ACL,zaidan-callisonburch:2011:ACL-HLT2011a,Zbib-etal:2012:NAACL,post-callisonburch-osborne:2012:WMT}
+Several researchers have investigated using MTurk to build parallel corpora for machine translation, a task which stands to directly benefit from the availability of large volumes of low-cost translations \cite{Germann2001}.
+\newcite{ambati_act} conducted a pilot study by posting 25 sentences to MTurk for Spanish, Chinese Hindi, Telugu, Urdu, and Haitian Creole.
+In a study of 2000 Urdu sentences,
+\newcite{zaidan-callisonburch:2011:ACL-HLT2011a} presented methods for achieving professional-level translation quality from Turkers by soliciting multiple English translations of each foreign sentence.
+\newcite{Zbib-etal:2012:NAACL} used crowdsourcing to construct a 1.5 million word parallel corpus of dialect Arabic and English, training a statistical machine translation system that produced higher quality translations of dialect Arabic than a system a trained on 100x more Modern Standard Arabic-English parallel data.
+\newcite{post-callisonburch-osborne:2012:WMT} used MTurk to build parallel corpora between English and six Indian languages, ranging from .5M to 1.5M words, and use them to demonstrate the efficacy of syntactic approaches to machine translation on verb-final languages.
+Several researchers have examined cost optimization through using active learning techniques to select which sentences or fragments to translate \cite{ambati_naacl,bloodgood-callisonburch:2010:ACL,AmbatiThesis}.
 

### 2013-02-19 writeup/paper.tex
Added paragraph to related work that re-states our contributions

@@
 
-%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
-\begin{figure*}[h]
-\centering
-\includegraphics[width=7in]{figures/natlang-pie}
-\caption{Self-reported native language of 3154 bilingual turkers}
-\label{lang-pie}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
@@
 \caption{The number of workers per country.
-This map was generated based on geolocating the IP address of the 5,284 workers in our study.
+This map was generated based on geolocating the IP address of  5,284 workers in our study.
 The size of the circles represents the number of worker from each country.
@@
 \label{map}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
+\begin{figure*}[h]
+\centering
+\includegraphics[width=7in]{figures/natlang-pie}
+\caption{Self-reported native language of 3,154 bilingual turkers}
+\label{lang-pie}
 \end{figure*}
@@
 
-%Within MTurk, those who need work completed (`requesters') post individual HITs.
-A typical HIT  requires a few minutes of work and pays a few cents, although there is significant variation across HITs.
-Once a HIT is posted, MTurk workers (`Turkers') are free to choose to complete the HITs which interest them.
-Worker identities remain anonymous to requesters, and all payment occurs through Amazon.
-Requesters are able to accept submitted work or reject work that they do not feel meets their standards, and only pay workers from whom they accepted tasks.
-
-%The convenience and low cost of using MTurk has made it popular among researchers.
-Because of the lack of oversight and the high potential for spam, however, most of the data collected from MTurk has been limited to simple tasks for which inter-annotator agreement is expected to be high (see Related Work section below).
-We explore the idea that MTurk's machinery is flexible enough to support more complex tasks requiring more nuanced quality control mechanisms, which could allow it to be a competitive alternative to professional data annotations.
-
-%\section{Related Work}
-
-%Typically, researchers rely on large amounts of MTurk data in order to compensate for the high likelihood of low quality labels.
-Snow et al.
-describes the success of using redundant non-expert labels to substitute for professional annotations, achieving comparable quality for much lower cost.
-The tasks from which these conclusions were drawn, however, were kept simple and easily-verifiable, with annotations restricted to either multiple choice or bounded numeric inputs.
-As NLP research advances, the level of expertise required from annotators advances as well.
-Callison-Burch et al.
-report success using MTurk to build parallel corpora for Machine Translation, a task which requires Turkers to speak two languages with a high level of proficiency.
-
 A demographic study by \newcite{ipeirotis:2010:demographics} focused on age, gender, martial status, income levels, motivation for working on MTurk, and whether workers used it as a primary or supplemental form of income.
@@
 
-%No study has yet been conducted to comprehensively assess the language skills of the growing number of international and bilingual Turkers or to analyze the potential of MTurk to support work in low-resource languages.
-
 Several researchers have investigated using MTurk to build parallel corpora for machine translation, a task which stands to directly benefit from the availability of large volumes of low-cost translations \cite{Germann2001}.
@@
 Several researchers have examined cost optimization through using active learning techniques to select which sentences or fragments to translate \cite{ambati_naacl,bloodgood-callisonburch:2010:ACL,AmbatiThesis}.
+
+To contrast our research with previous work, the main contributions of this paper are: (1) a robust methodology for assessing the bilingual  skills of anonymous crowdworkers, (2) the largest-scale census to date of language skills of workers on MTurk, and (3) a detailed analysis of the data gathered in our study, including the quality of the translations and recommendations for  languages that are feasible for near-term creation of multi-lingual technologies.
 

### 2013-02-19 writeup/paper.tex

@@
 %\section{Mechanical Turk}
-Amazon's Mechanical Turk (MTurk) is an online marketplace for work which gives employers and researchers access to a large, low-cost, workforce.
+Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost, workforce.
 MTurk provides a simple interface for accessing human skills, allowing employers to provide micro-payments in return for workers completing micro-tasks.
@@
 This facilitates research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}.
-It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge-banerjee-rudnicky:2010:MTURK,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.
+It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge:10,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.
 

### 2013-02-19 code/compile_data_from_raw.py
code for extracting byassign and byturker data and quality metrics

@@ -1,0 +1,274 @@
+import re
+import sys
+import csv
+import json
+import string
+import codecs
+
+RAW_DIR = '../data/dictionary-data-dump-2012-11-13_15:11/'
+OUTPUT_DIR = 'output'
+
+def hits_language():
+	hit_path = '%s/hits'%RAW_DIR
+	language_path = '%s/languages'%RAW_DIR
+        lang_data = {}
+        for line in csv.DictReader(open(language_path)):
+                lang = line['id']
+                if(lang not in lang_data):
+                        lang_data[lang] = lang
+        hit_data = {}
+        for line in csv.DictReader(open(hit_path)):
+                hit = line['id']
+                if(hit not in hit_data):
+                        l =  line['language_id']
+                        hit_data[hit] = lang_data[line['language_id']]
+        return hit_data
+
+def lang_map():
+        lang_data = {}
+        num_data = {}
+        for line in csv.DictReader(open('%s/languages'%RAW_DIR)):
+                lang = line['name'].lower()
+                id = line['id']
+                if(lang not in lang_data):
+                        lang_data[lang] = line['prefix']
+                if(id not in num_data):
+                        num_data[id] = line['prefix']
+        return num_data, lang_data
+
+def country_map():
+	ret = dict()
+	for l in open('data-files/countrymap').readlines():
+		ll = l.split('\t')
+		ret[ll[0]] = ll[1].strip()
+	return ret
+
+def code_map():
+	ret = dict()
+	for l in open('data-files/countrycodemap').readlines():
+		ll = l.split('\t')
+		ret[ll[0]] = ll[1].strip()
+	return ret
+
+def map_country(c, countrymap, codemap):
+	c = clean(c)
+	if c in countrymap:
+		c = countrymap[c]
+	if c in codemap:
+		return codemap[c]
+	return 'N/A'
+
+def list2str(lst):
+	s = ''
+	if len(lst) == 0:
+		s = 'N/A;'
+	for l in lst:
+		s+=l+';'
+	return s
+
+def assign_workers(path, langs, idlist=None):
+	countrymap = country_map()
+        codemap = code_map()
+        numlangmap, langmap = lang_map()
+        data = {}
[…]

### 2013-02-19 code/qc.py

@@ -1,0 +1,163 @@
+import sys
+import csv
+import math
+import numpy
+import scipy
+import operator
+import itertools
+from scipy import stats
+from scipy.stats import norm
+import matplotlib.pyplot as plt
+
+RAW_DIR = '../data/dictionary-data-dump-2012-11-13_15:11/'
+OUTPUT_DIR = 'output'
+
+def turker_map():
+        tmap = dict()
+        for line in open('%s/byassign.workerids.voc'%OUTPUT_DIR).readlines()[1:]:
+                assign, worker = line.split()
+                tmap[assign.strip()] = worker.strip()
+        return tmap
+
+def qual_map():
+        qual_data = {}
+        for line in csv.DictReader(open('%s/byassign.voc.quality'%OUTPUT_DIR), delimiter='\t'):
+                assign = line['id']
+                qual = line['avg']
+                if(assign not in qual_data):
+                        if qual == 'N/A':
+                                qual_data[assign] = qual
+                        else:
+                                qual_data[assign] = float(qual)
+        return qual_data
+
+#map of word id to word
+def word_map():
+	words = dict()
+        for line in csv.DictReader(open('%s/dictionary'%RAW_DIR)):
+		wid = line['id']
+		word = line['translation']
+		if wid not in words:
+			words[wid] = word
+	return words
+
+#map of pair id to word pair
+def pair_map():
+	pairs = dict()
+        for line in csv.DictReader(open('%s/syn_hits_data'%RAW_DIR)):
+		pid = line['id']
+		word = line['translation']
+		syn = line['synonym']
+		if pid not in pairs:
+			pairs[pid] = (word,syn)
+	return pairs
+
+#return (list of pair ids that are know synonyms, list of pair ids that are known nonsynonyms)
+def get_syn_lists():
+	syns = list()
+	nonsyns = list()
+        for line in csv.DictReader(open('%s/synonyms'%RAW_DIR)):
+		syns.append(line['id'])
+        for line in csv.DictReader(open('%s/non_synonyms'%RAW_DIR)):
+		nonsyns.append(line['id'])
+	return (syns, nonsyns)
+
+#get a dictionary of word: list of acceptable synonyms. filter list of assignment ids used to restrict list of synonyms to come only from certain assignments
[…]

### 2013-02-19 writeup/paper.tex
Updating survey design section

@@
 
-To contrast our research with previous work, the main contributions of this paper are: (1) a robust methodology for assessing the bilingual  skills of anonymous crowdworkers, (2) the largest-scale census to date of language skills of workers on MTurk, and (3) a detailed analysis of the data gathered in our study, including the quality of the translations and recommendations for  languages that are feasible for near-term creation of multi-lingual technologies.
+To contrast our research with previous work, the main contributions of this paper are: (1) a robust methodology for assessing the bilingual  skills of anonymous workers, (2) the largest-scale census to date of language skills of workers on MTurk, and (3) a detailed analysis of the data gathered in our study.
+%, including the quality of the translations and recommendations for  languages that are feasible for near-term creation of multi-lingual technologies.
 
@@
 
-\section{Task Design}
+\section{Survey Design}
 The central task in this study was to use Mechanical Turk to create low cost, high quality bilingual dictionaries for over 100 languages in order to test the reliability and breadth of the knowledge of Mechanical Turk's bilingual population.
@@
 Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.
-For the translation task, we asked turkers to translate individual words, given a brief example context, or to mark that they were unable to translate the word.
-Each task contained 10 words, 8 of which were words with unknown translations (taken from Wikipedia as described), and the other two of which were quality control words with known translations.
+For the translation task, we asked turkers to translate individual words, showing each word used in the context of three sentences.
+Turkers were allowed to mark that they were unable to translate a word.
+Each task contained 10 words, 8 of which were words with unknown translations, and the other two of which were quality control words with known translations.
+The known translations were harvested from the titles of English and foreign articles that were linked via Wikipedia's inter-language links.
 The task paid one million dollars for the translation of 10 words.

### 2013-02-19 code/compile_data_from_raw.py
adding readme

@@ -113,6 +113,11 @@ def assign_langs(path, langs, idlist=None):
 		if('survey_is_native_foreign_speaker' in data): 
 			if(data['survey_is_native_foreign_speaker']=='yes'): 
 				survey_data[assign]['lang'] = numlangmap[langs[hit]] 
+
+		## ** assignments that don't trigger one of the above ifs end up as N/A in the final output. there are 1801 of these. ** #
+		## ** i checked a few, and they are mostly because the question 'is xx your native language' doesn't appear in the ** #
+		## ** data, not because they answer no to both questions. ** #
+
 		if(survey_data[assign]['lang'] == None):
 			survey_data[assign]['lang'] = 'N/A'
 		if('survey_years_speaking_english' in data): 

### 2013-02-20 writeup/paper.tex
Added external dictionaries
Collapsed Figure 5 (number native languages) into the caption on the native language pie chart.

@@
 \centering
-\includegraphics[width=\linewidth]{figures/turkermap-color-cropped}
+\includegraphics[width=\linewidth]{figures/Turkermap-color-cropped}
 \caption{The number of workers per country.
@@
 \includegraphics[width=7in]{figures/natlang-pie}
-\caption{Self-reported native language of 3,154 bilingual turkers}
+\caption{Self-reported native language of 3,154 bilingual Turkers.
+Not shown are the languages of 243 Turkers who reported two native languages, 83 who reported $\geq$3 native languages, and 1.801 who failed to answer the language survey component of our translation HITs.}
 \label{lang-pie}
@@
 Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.
-For the translation task, we asked turkers to translate individual words, showing each word used in the context of three sentences.
+For the translation task, we asked Turkers to translate individual words, showing each word used in the context of three sentences.
 Turkers were allowed to mark that they were unable to translate a word.
@@
 The known translations were harvested from the titles of English and foreign articles that were linked via Wikipedia's inter-language links.
-The task paid one million dollars for the translation of 10 words.
+The task paid \$0.15 for the translation of 10 words.
+Each set of 10 words was independently translated by three separate workers.
 
@@
 %%%%%%%%%%%%%%% NUM LANGUAGES TABLE %%%%%%%%%%%
-\begin{figure}[h]
-\begin{tabular}{ccc}\hline\hline
-&\# languages&\# Turkers\\ \hline
-No languages&0&1801\\
-One language&1&3154\\
-Multiple languages&2&243	\\
-&3&49\\
-&4&12\\
-&5&9\\
-&6&5\\
-&7&2\\
-&8&1\\
-&9&2\\
-&10&2\\
-&15&1\\
-\hline\hline
-\end{tabular}
-\label{numlangs-tab}
-\caption{Number of native languages reported during demographic survey.}
-\end{figure}
+%\begin{figure}[h]
+%\begin{tabular}{ccc}\hline\hline
+%&\# languages&\# Turkers\\ \hline
+%No languages&0&1801\\
+%One language&1&3154\\
+%Multiple languages&2&243	\\
+%&3&49\\
+%&4&12\\
+%&5&9\\
+%&6&5\\
+%&7&2\\
+%&8&1\\
+%&9&2\\
+%&10&2\\
+%&15&1\\
+%\hline\hline
+%\end{tabular}
+%\label{numlangs-tab}
+%\caption{Number of native languages reported during demographic survey.}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \includegraphics[width=6in]{figures/assign-turk-scatter}
-\caption{Number of assignments and number of turkers for each language. Each dot represents a language.}
+\caption{Number of assignments and number of Turkers for each language. Each dot represents a language.}
 \label{ass-scatter}
@@
 Figure \ref{ass-scatter} shows the volume of HITs completed and the number of workers participating for each language.
-While the bulk (22\%) of bilingual turkers report English as their native language (see figure \ref{lang-pie}), Mechanical Turk's capacity to support the Indian languages is apparent.
+While the bulk (22\%) of bilingual Turkers report English as their native language (see figure \ref{lang-pie}), Mechanical Turk's capacity to support the Indian languages is apparent.
 Hindi, Tamil, and Malayalam are especially well represented in terms of number of active translators, and Urdu, Telugu, and Macedonian are particularly productive in terms of number of assignments completed.
-As shown in figure \ref{langgeo-bar}, 11 of the top 25 languages, in terms of number of assignments submitted, were Indian languages, and the assignments for 15 of the top 25 were completed mostly or entirely by turkers located in India.
+As shown in figure \ref{langgeo-bar}, 11 of the top 25 languages, in terms of number of assignments submitted, were Indian languages, and the assignments for 15 of the top 25 were completed mostly or entirely by Turkers located in India.
 
@@
 \includegraphics[width=6in]{figures/assign-langgeo-sorted}
-\caption{Geolocation of turkers speaking 40 most represented languages, in terms of number of assignments submitted}
+\caption{Geolocation of Turkers speaking 40 most represented languages, in terms of number of assignments submitted}
 \label{langgeo-bar}
@@
 \centering
-\includegraphics[width=6in]{figures/quality-scatter-avgturkers-country-labeled}
+\includegraphics[width=6in]{figures/quality-scatter-avgTurkers-country-labeled}
 \caption{Quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country.}
@@
 Self-reported country information is typically reliable.
-Three quarters of Turkers who reported their native language reported a single native language consistantly across all assignments (table \ref{numlangs-tab}), and of those reporting multiple native languages, the majority listed English in addition to the HIT's source language, meaning less than 5\% of Turkers gave unreasonable responses.
+Three quarters of Turkers who reported their native language reported a single native language consistently across all assignments, and of those reporting multiple native languages, the majority listed English in addition to the HIT's source language.
+Less than 5\% of Turkers gave unreasonable responses with 3 or more native languages.
 Across all assignments, 96\% of reported locations agreed with automatically reported locations, although assignments in which Turkers misreported their location averaged 10\% lower in quality than those in which the reported location was accurate, shown in table \ref{mism-tab}.

### 2013-02-20 code/turk_external_comparison.py
script to calculate match between turk and external dictionaries

@@ -1,0 +1,86 @@
+langs=[]
+ext_langs=[]
+
+import os
+
+import codecs
+
+
+for dirname, dirnames, filenames in os.walk('../dictionaries/all/'):
+    # print path to all filenames.
+    for filename in filenames:
+        #print os.path.join(dirname, filename)
+		#print filename.split(".")[1]
+		langs.append(filename.split(".")[1])
+
+
+for dirname, dirnames, filenames in os.walk('../dictionaries/external_dictionaries/'):
+    # print path to all subdirectories first.
+    for subdirname in dirnames:
+		#print os.path.join(dirname, subdirname)
+		#print subdirname
+		ext_langs.append(subdirname)
+
+print langs
+print ext_langs
+
+for lang in langs:
+	print "---"
+	print "processing: "+lang
+	turk_dict={}
+	ext_dict={}
+	overlap=0
+	match=0
+
+	if not os.path.exists("../dictionaries/external_dictionaries/"+lang+"/"+lang+"-en"):
+		print "no external dictionary, skipping"
+		continue
+
+	f = codecs.open("../dictionaries/all/dictionary."+lang, encoding='utf-8')
+	for line in f:
+		line=line.strip()
+		#print line.split("	")[0], line.split("	")[1].strip(",").split(",")
+		#print line
+		if line == "no word is shown!!!," or line=="error in display," or line=="?," or line=="no word written to translate,":
+			continue
+		try:
+			word, translations =line.split("	") 
+			word=word.upper()
+			turk_dict[word]=translations.strip(",").split(",")
+		except:
+			#glith in turk dictionary, skipping
+			#print "glitch: ",line
+			pass
+		
+	f = codecs.open("../dictionaries/external_dictionaries/"+lang+"/"+lang+"-en", encoding='utf-8')
+	for line in f:
+		line=line.strip()
+		#print line.split("	")[0], line.split("	")[1].strip(",").split(",")
+		#print line
+		try:
+			word, translations =line.split("	") 
+			word=word.upper()
+			ext_dict[word.strip()]=translations.strip(",").split(",")
+		except:
+			#glith in external dictionary, skipping
+			#print "glitch: ",line
+			pass
+	
+	for word in turk_dict.keys():
+		if ext_dict.has_key(word):
+			overlap=overlap+1
+			for translation in turk_dict[word]:
+				if translation==ext_dict[word][0]:
+					match=match+1
+		
[…]

### 2013-02-20 writeup/paper.tex
Converted languages piechart into one column figure.  Fonts need to be bigger.
Moving figures.

@@
 
-%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
-\begin{figure*}[h]
-\centering
-\includegraphics[width=\linewidth]{figures/Turkermap-color-cropped}
-\caption{The number of workers per country.
-This map was generated based on geolocating the IP address of  5,284 workers in our study.
-The size of the circles represents the number of worker from each country.
-The two largest are India (2,022 workers) and the United States (904).
-To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
-\label{map}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Background and Related Work}
 
-%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
-\begin{figure*}[h]
-\centering
-\includegraphics[width=7in]{figures/natlang-pie}
-\caption{Self-reported native language of 3,154 bilingual Turkers.
-Not shown are the languages of 243 Turkers who reported two native languages, 83 who reported $\geq$3 native languages, and 1.801 who failed to answer the language survey component of our translation HITs.}
-\label{lang-pie}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Background and Related Work}
-%\section{Background on Mechanical Turk and Related Work}
-%\section{Mechanical Turk}
 Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost, workforce.
@@
 More recently has expanded to include one foreign currency, the Indian rupee.
-Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries.\footnote{https://requester.mturk.com/tour}  This suggest that its worker population that should represent a diverse set of languages.
+Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries \cite{AmazonRequesterTour}.
+This suggest that its worker population that should represent a diverse set of languages.
 
@@
 
+%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
+\begin{figure*}[h]
+\centering
+\includegraphics[width=\linewidth]{figures/Turkermap-color-cropped}
+\caption{The number of workers per country.
+This map was generated based on geolocating the IP address of  5,284 workers in our study.
+The size of the circles represents the number of worker from each country.
+The two largest are India (2,022 workers) and the United States (904).
+To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
+\label{map}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%% HIT UIs %%%%%%%%%%%
-\begin{figure}[h]
-\centering
-\includegraphics[width=3in]{figures/vocabulary_hit_mturk}
-\caption{Translation HIT UI}
-\label{tranhit}
-\end{figure}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=3in]{figures/synonyms_hit_mturk}
-\caption{Evaluation HIT UI}
-\label{synhit}
-\end{figure}
+%\begin{figure}[h]
+%\centering
+%\includegraphics[width=3in]{figures/vocabulary_hit_mturk}
+%\caption{Translation HIT UI}
+%\label{tranhit}
+%\end{figure}
+%
+%\begin{figure}[h]
+%\centering
+%\includegraphics[width=3in]{figures/synonyms_hit_mturk}
+%\caption{Evaluation HIT UI}
+%\label{synhit}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
+\begin{figure}[h]
+\centering
+\includegraphics[width=\linewidth]{figures/natlang-pie}
+\caption{Self-reported native language of 3,154 bilingual Turkers.
+Not shown are the languages of 243 Turkers who reported two native languages, 83 who reported $\geq$3 native languages, and 1.801 who failed to answer the language survey component of our translation HITs.}
+\label{lang-pie}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Survey Design}
-The central task in this study was to use Mechanical Turk to create low cost, high quality bilingual dictionaries for over 100 languages in order to test the reliability and breadth of the knowledge of Mechanical Turk's bilingual population.
+The central task in this study was to use Mechanical Turk to create bilingual dictionaries for over 100 languages in order to test Mechanical Turk's bilingual population.
 
@@
 The dictionary creation task was broken into two steps: a translation HIT and an evaluation HIT. 
-Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.
+%Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.  
 For the translation task, we asked Turkers to translate individual words, showing each word used in the context of three sentences.
@@
 Each task contained 10 words, 8 of which were words with unknown translations, and the other two of which were quality control words with known translations.
-The known translations were harvested from the titles of English and foreign articles that were linked via Wikipedia's inter-language links.
+.
 The task paid \$0.15 for the translation of 10 words.
 Each set of 10 words was independently translated by three separate workers.
+
+The known translations were harvested from the titles of English and foreign articles that were linked via Wikipedia's inter-language links.
+Keeping only pairs such that (1) the English word is present in the WordNet ontology, (2) the article titles were a single word in both English and the foreign language, (3) the English wikipedia page was not a subcategory of person, and (4) the English and the foreign titles were not identical and were not contained as a substring in the other.
 
@@
 Whether the evaluators correctly labeled the known word pairs could be assessed automatically, allowing the evaluation HIT to be the final step of the dictionary creation pipeline.
+
+That was method for building gold pairs for english-foreign dictionaries for Vocabulary HIT controls.
+
+We used Brown corpus for building synonyms and non-synonyms pairs for Synonyms HIT controls.
+It was built using random words from Brown corpora and if it had any synonyms we added them as pair.
+For non-synonyms we took two random words from Brown and if they were not in each others synonyms lists we added them as non-synonyms pair.
 

### 2013-02-20 writeup/paper.tex
table instead of pie chart

--- 2013-02-19 writeup/paper.tex
@@
 
+%%%%%%%%%%%%%%% NAT LANG PIE TABLE %%%%%%%%%%%
+\begin{figure}[h]
+\begin{tabular}{cc}\hline\hline
+Language&\# Turkers\\
+\hline
+English&591\\
+Tamil&253\\
+Malayalam&219\\
+Hindi&149\\
+Spanish&131\\
+Telugu&87\\
+Chinese&86\\
+Romanian&85\\
+Portuguese&82\\
+Arabic&74\\
+Kannada&72\\
+German&66\\
+French&63\\
+Polish&61\\
+Urdu&56\\
+Tagalog&54\\
+Marathi&48\\
+Russian&44\\
+Italian&43\\
+Bengali&41\\
+Gujarati&39\\
+Hebrew&38\\
+Dutch&37\\
+Turkish&35\\
+Vietnamese&34\\
+Macedonian&31\\
+Cebuano&29\\
+Swedish&26\\
+Bulgarian&25\\
+Hungarian&23\\
+Swahili&23\\
+Thai&22\\
+Catalan&22\\
+Lithuanian&21\\
+Punjabi&21\\
+Other($\leq$ 20 per language)&423\\
+\hline\hline
+\end{tabular}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
-\begin{figure*}[h]
-\centering
-\includegraphics[width=7in]{figures/natlang-pie}
-\caption{Self-reported native language of 3,154 bilingual turkers}
-\label{lang-pie}
-\end{figure*}
+%\begin{figure*}[h]
+%\centering
+%\includegraphics[width=7in]{figures/natlang-pie}
+%\caption{Self-reported native language of 3,154 bilingual turkers}
+%\label{lang-pie}
+%\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The quality of an assignment was scored as the fraction of known words which were acceptably translated: i.e, the supplied translation was judged to be synonymous with the gold standard translation.
-Since each assignment had either one or two known words embedded, each assignment was assigned a score of either 0, 0.5, or 1.
+Since most assignments had two known words embedded, most assignments had scores of either 0, 0.5, or 1.
 
 %%%%%%%%%%%%%%% MISREPORT TABLE %%%%%%%%%%%
-\begin{figure}[h]
-\centering
-\begin{tabular}{cccc}\hline\hline\\
-&Avg. & 99\%&\\
-&Quality & Conf. Int.&n\\
-Misreport&0.252&(0.244, 0.260)&10,479\\
-Correct&0.282&(0.280, 0.283)&296,911\\
-Overall&0.281&(0.279, 0.282)&307,390\\
-\hline\hline
-\end{tabular}
-\label{mism-tab}
-\caption{Quality of translations recieved from truthful versus misreporting Turkers.}
-\end{figure}
+%\begin{figure}[h]
+%\centering
+%\begin{tabular}{cccc}\hline\hline\\
+%&Avg. & 99\%&\\
+%&Quality & Conf. Int.&n\\
+%Misreport&0.252&(0.244, 0.260)&10,479\\
+%Correct&0.282&(0.280, 0.283)&296,911\\
+%Overall&0.281&(0.279, 0.282)&307,390\\
+%\hline\hline
+%\end{tabular}
+%\label{mism-tab}
+%\caption{Quality of translations recieved from truthful versus misreporting Turkers.}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Self-reported country information is typically reliable.
+Self-reported country information is typically reliable; about 96\% of self-reported locations agreed with automatically reported locations, 
 Three quarters of Turkers who reported their native language reported a single native language consistantly across all assignments (table \ref{numlangs-tab}), and of those reporting multiple native languages, the majority listed English in addition to the HIT's source language, meaning less than 5\% of Turkers gave unreasonable responses.
-Across all assignments, 96\% of reported locations agreed with automatically reported locations, although assignments in which Turkers misreported their location averaged 10\% lower in quality than those in which the reported location was accurate, shown in table \ref{mism-tab}.
+
+%Across all assignments, 96\% of reported locations agreed with automatically reported locations, although assignments in which Turkers misreported their location averaged 10\% lower in quality than those in which the reported location was accurate, shown in table \ref{mism-tab}.
 

### 2013-02-20 writeup/paper.tex
completion time data

@@
 
+%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
+\begin{figure*}[h]
+\centering
+\includegraphics[width=7in]{figures/completiontime}
+\caption{Time (in days) to complete all HITs in each language.
+Red bar shows time until first HIT was started, relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu).
+Blue bar shows time until all HITs in each language were completed.}
+\label{completion-time}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Background and Related Work}
 %%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%

### 2013-02-20 writeup/summary.tex
summary table template

\begin{figure}[h]
\centering
\begin{tabular}{llcclccc}
\multicolumn{8}{c}{Number of Turkers per language}\\
\hline\hline
&&All&\multicolumn{2}{c}{cl match}&\multicolumn{2}{c}{quality (dict size)}\\
&&&total&by country&in region&out of region\\
\hline\hline
hi&Hindi&312&300&India(285) Uae(5) &\textbf{0.5387} (9908)&0.4728 (41) \\
&&&&Scotland (5) Other (5) &&&\\
&&&&&&&\\
ta&Tamil&294&278&India(271) US(3) &\textbf{0.5528} (9974)&0.54 (5) \\
&&&&Canada (2) Other (2) &&&\\
&&&&&&&\\
ml&Malayalam&245&235&India(224) Uae(6) &0.4759 (9966)&\textbf{0.5523} (25)\\
&&&&US (3) Other (2) &&&\\
&&&&&&&\\
es&Spanish&235&206&US(131) Mexico(18) &\textbf{0.2711} (9768)&0.2677 (67) \\
&&&&Westspain (14) Other (43) &&&\\
&&&&&&&\\
fr&French&202&183&India(68) US(48) &0.2907 (9514)&\textbf{0.3063} (386)\\
&&&&France (25) Other (42) &&&\\
&&&&&&&\\
de&German&163&100&Germany(51) US(29) &\textbf{0.3527} (8892)&0.306 (1029) \\
&&&&Austria (9) Other (11) &&&\\
&&&&&&&\\
it&Italian&159&98&Italy(44) US(32) &\textbf{0.3221} (7885)&0.2734 (1870) \\
&&&&Romania (9) Other (13) &&&\\
&&&&&&&\\
zh&Chinese&150&130&US(80) Singapore(15) &0.1821 (3510)&\textbf{0.4113} (137)\\
&&&&China (14) Other (21) &&&\\
&&&&&&&\\
ms&Malay&128&15&Malaysia(8) Singapore(4) &\textbf{0.2946} (6143)&0.2755 (3623) \\
&&&&US (2) Other (1) &&&\\
&&&&&&&\\
ga&Irish&121&58&US(41) Ireland(13) &\textbf{0.3201} (3775)&0.2612 (6139) \\
&&&&Scotland (4) &&&\\
&&&&&&&\\
\hline\hline
\end{tabular}
\end{figure}

### 2013-02-20 writeup/paper.tex
Made the native lang table more compact by doing 3 columns

--- 2013-02-20 writeup/paper.tex
@@
 
+%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
+\begin{figure*}[h]
+\centering
+\includegraphics[width=\linewidth]{figures/turkermap-color-cropped}
+\caption{The number of workers per country.
+This map was generated based on geolocating the IP address of  5,284 workers in our study.
+The size of the circles represents the number of worker from each country.
+The two largest are India (2,022 workers) and the United States (904).
+To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
+\label{map}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%% NAT LANG PIE TABLE %%%%%%%%%%%
+\begin{figure}[h]
+\footnotesize
+\begin{tabular}{lrlrlr}\hline\hline
+%Language&\# Turkers\\
+\hline
+English&591&	French&63&	Vietnamese&34\\
+Tamil&253&	Polish&61&	Macedonian&31\\
+Malayalam&219&	Urdu&56&	Cebuano&29\\
+Hindi&149&	Tagalog&54&	Swedish&26\\
+Spanish&131&	Marathi&48&	Bulgarian&25\\
+Telugu&87&	Russian&44&	Hungarian&23\\
+Chinese&86&	Italian&43&	Swahili&23\\
+Romanian&85&	Bengali&41&	Thai&22\\
+Portuguese&82&	Gujarati&39&	Catalan&22\\
+Arabic&74&	Hebrew&38&	Lithuanian&21\\
+Kannada&72&	Dutch&37&	Punjabi&21\\
+German&66&	Turkish&35&	Others &$\leq$20\\
+\hline\hline
+\end{tabular}
+\normalsize
+\caption{XXX}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
+\begin{figure*}[h]
+\centering
+\includegraphics[width=7in]{figures/completiontime}
+\caption{Time (in days) to complete all HITs in each language.
+Red bar shows time until first HIT was started, relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu).
+Blue bar shows time until all HITs in each language were completed.}
+\label{completion-time}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
+%\begin{figure}[h]
+%\centering
+%\includegraphics[width=\linewidth]{figures/natlang-pie}
+%\caption{Self-reported native language of 3,154 bilingual turkers}
+%\label{lang-pie}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Background and Related Work}
-
 Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost, workforce.
@@
 
-Self-reported country information is typically reliable.
+Self-reported country information is typically reliable; about 96\% of self-reported locations agreed with automatically reported locations, 
+Three quarters of Turkers who reported their native language reported a single native language consistantly across all assignments (table \ref{numlangs-tab}), and of those reporting multiple native languages, the majority listed English in addition to the HIT's source language, meaning less than 5\% of Turkers gave unreasonable responses.
+
+%Across all assignments, 96\% of reported locations agreed with automatically reported locations, although assignments in which Turkers misreported their location averaged 10\% lower in quality than those in which the reported location was accurate, shown in table \ref{mism-tab}.
+%Self-reported country information is typically reliable.
 Three quarters of Turkers who reported their native language reported a single native language consistently across all assignments, and of those reporting multiple native languages, the majority listed English in addition to the HIT's source language.

### 2013-02-20 writeup/paper.tex
turker quality summary table

@@
 \begin{figure}[h]
-\footnotesize
-\begin{tabular}{lrlrlr}\hline\hline
-%Language&\# Turkers\\
+\begin{tabular}{cc}\hline\hline
+Language&\# Turkers\\
 \hline
-English&591&	French&63&	Vietnamese&34\\
-Tamil&253&	Polish&61&	Macedonian&31\\
-Malayalam&219&	Urdu&56&	Cebuano&29\\
-Hindi&149&	Tagalog&54&	Swedish&26\\
-Spanish&131&	Marathi&48&	Bulgarian&25\\
-Telugu&87&	Russian&44&	Hungarian&23\\
-Chinese&86&	Italian&43&	Swahili&23\\
-Romanian&85&	Bengali&41&	Thai&22\\
-Portuguese&82&	Gujarati&39&	Catalan&22\\
-Arabic&74&	Hebrew&38&	Lithuanian&21\\
-Kannada&72&	Dutch&37&	Punjabi&21\\
-German&66&	Turkish&35&	Others &$\leq$20\\
+English&591\\
+Tamil&253\\
+Malayalam&219\\
+Hindi&149\\
+Spanish&131\\
+Telugu&87\\
+Chinese&86\\
+Romanian&85\\
+Portuguese&82\\
+Arabic&74\\
+Kannada&72\\
+German&66\\
+French&63\\
+Polish&61\\
+Urdu&56\\
+Tagalog&54\\
+Marathi&48\\
+Russian&44\\
+Italian&43\\
+Bengali&41\\
+Gujarati&39\\
+Hebrew&38\\
+Dutch&37\\
+Turkish&35\\
+Vietnamese&34\\
+Macedonian&31\\
+Cebuano&29\\
+Swedish&26\\
+Bulgarian&25\\
+Hungarian&23\\
+Swahili&23\\
+Thai&22\\
+Catalan&22\\
+Lithuanian&21\\
+Punjabi&21\\
+Other($\leq$ 20 per language)&423\\
 \hline\hline
 \end{tabular}
-\normalsize
-\caption{XXX}
 \end{figure}
@@
 
+%\section{Background and Related Work}
 %%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
-%\begin{figure}[h]
+%\begin{figure*}[h]
 %\centering
-%\includegraphics[width=\linewidth]{figures/natlang-pie}
+%\includegraphics[width=7in]{figures/natlang-pie}
 %\caption{Self-reported native language of 3,154 bilingual turkers}
 %\label{lang-pie}
-%\end{figure}
+%\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Background and Related Work}
+%\section{Background on Mechanical Turk and Related Work}
+%\section{Mechanical Turk}
 Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost, workforce.
@@
 \centering
-\includegraphics[width=\linewidth]{figures/Turkermap-color-cropped}
+\includegraphics[width=\linewidth]{figures/turkermap-color-cropped}
 \caption{The number of workers per country.
@@
 
+%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
+\centering
+\include{summary}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
@@
 \centering
-\includegraphics[width=6in]{figures/quality-scatter-avgTurkers-country-labeled}
+\includegraphics[width=6in]{figures/quality-scatter-avgturkers-country-labeled}
 \caption{Quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country.}
@@
 Three quarters of Turkers who reported their native language reported a single native language consistantly across all assignments (table \ref{numlangs-tab}), and of those reporting multiple native languages, the majority listed English in addition to the HIT's source language, meaning less than 5\% of Turkers gave unreasonable responses.
-
-%Across all assignments, 96\% of reported locations agreed with automatically reported locations, although assignments in which Turkers misreported their location averaged 10\% lower in quality than those in which the reported location was accurate, shown in table \ref{mism-tab}.
-%Self-reported country information is typically reliable.
-Three quarters of Turkers who reported their native language reported a single native language consistently across all assignments, and of those reporting multiple native languages, the majority listed English in addition to the HIT's source language.
-Less than 5\% of Turkers gave unreasonable responses with 3 or more native languages.
-Across all assignments, 96\% of reported locations agreed with automatically reported locations, although assignments in which Turkers misreported their location averaged 10\% lower in quality than those in which the reported location was accurate, shown in table \ref{mism-tab}.
 

### 2013-02-20 writeup/summary.tex
turker quality summary table

@@
 \centering
-\begin{tabular}{llcclccc}
+*** PLACE HOLDER NUMBERS; NUMBERS WITH ACCPETED HITS ONLY STILL RUNNING ***
+\begin{tabular}{llcccccc}
 \multicolumn{8}{c}{Number of Turkers per language}\\
 \hline\hline
-&&All&\multicolumn{2}{c}{cl match}&\multicolumn{2}{c}{quality (dict size)}\\
-&&&total&by country&in region&out of region\\
+&&Total \# Turkers&\multicolumn{2}{c}{\# Turkers in language region}&\multicolumn{2}{c}{Avg. Turker quality (Dictionary size)}\\
+&&&Overall&By country&In region&Out of region\\
 \hline\hline
-hi&Hindi&312&300&India(285) Uae(5) &\textbf{0.5387} (9908)&0.4728 (41) \\
+hi&Hindi&312&300&India (285) Uae (5) &\textbf{0.5387} (9908)&0.4728 (41) \\
 &&&&Scotland (5) Other (5) &&&\\
 &&&&&&&\\
-ta&Tamil&294&278&India(271) US(3) &\textbf{0.5528} (9974)&0.54 (5) \\
+ta&Tamil&294&278&India (271) US (3) &\textbf{0.5528} (9974)&0.54 (5) \\
 &&&&Canada (2) Other (2) &&&\\
 &&&&&&&\\
-ml&Malayalam&245&235&India(224) Uae(6) &0.4759 (9966)&\textbf{0.5523} (25)\\
+ml&Malayalam&245&235&India (224) Uae (6) &0.4759 (9966)&\textbf{0.5523} (25)\\
 &&&&US (3) Other (2) &&&\\
 &&&&&&&\\
-es&Spanish&235&206&US(131) Mexico(18) &\textbf{0.2711} (9768)&0.2677 (67) \\
+es&Spanish&235&206&US (131) Mexico (18) &\textbf{0.2711} (9768)&0.2677 (67) \\
 &&&&Westspain (14) Other (43) &&&\\
 &&&&&&&\\
-fr&French&202&183&India(68) US(48) &0.2907 (9514)&\textbf{0.3063} (386)\\
+fr&French&202&183&India (68) US (48) &0.2907 (9514)&\textbf{0.3063} (386)\\
 &&&&France (25) Other (42) &&&\\
 &&&&&&&\\
-de&German&163&100&Germany(51) US(29) &\textbf{0.3527} (8892)&0.306 (1029) \\
+de&German&163&100&Germany (51) US (29) &\textbf{0.3527} (8892)&0.306 (1029) \\
 &&&&Austria (9) Other (11) &&&\\
 &&&&&&&\\
-it&Italian&159&98&Italy(44) US(32) &\textbf{0.3221} (7885)&0.2734 (1870) \\
+it&Italian&159&98&Italy (44) US (32) &\textbf{0.3221} (7885)&0.2734 (1870) \\
 &&&&Romania (9) Other (13) &&&\\
 &&&&&&&\\
-zh&Chinese&150&130&US(80) Singapore(15) &0.1821 (3510)&\textbf{0.4113} (137)\\
+zh&Chinese&150&130&US (80) Singapore (15) &0.1821 (3510)&\textbf{0.4113} (137)\\
 &&&&China (14) Other (21) &&&\\
 &&&&&&&\\
-ms&Malay&128&15&Malaysia(8) Singapore(4) &\textbf{0.2946} (6143)&0.2755 (3623) \\
+ms&Malay&128&15&Malaysia (8) Singapore (4) &\textbf{0.2946} (6147)&0.2755 (3619) \\
 &&&&US (2) Other (1) &&&\\
 &&&&&&&\\
-ga&Irish&121&58&US(41) Ireland(13) &\textbf{0.3201} (3775)&0.2612 (6139) \\
+ga&Irish&121&58&US (41) Ireland (13) &\textbf{0.3201} (3775)&0.2612 (6139) \\
 &&&&Scotland (4) &&&\\

### 2013-02-20 writeup/paper.tex
minor changes

--- 2013-02-20 writeup/paper.tex
@@
 On MTurk, researchers who need work completed are called `Requesters', workers are often referred to as `Turkers', and micro tasks are called `HITs'.
-MTurk is a true market, meaning that Turkers are free to choose to complete the HITs which interest them, and Requesters can price their tasks competitively to try to attract workers and complete have their tasks done quickly \cite{faridani-et-al:2011,singer-mittal:2011}.
+MTurk is a true market, meaning that Turkers are free to choose to complete the HITs which interest them, and Requesters can price their tasks competitively to try to attract workers and have their tasks done quickly \cite{faridani-et-al:2011,singer-mittal:2011}.
 Turkers' identities remain anonymous to Requesters, and all payment occurs through Amazon.
@@
 When Amazon introduced MTurk, it first offered payment only in Amazon credits, and later offered direct payment in US dollars.
-More recently has expanded to include one foreign currency, the Indian rupee.
+More recently, it has expanded to include one foreign currency, the Indian rupee.
 Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries \cite{AmazonRequesterTour}.

### 2013-02-20 writeup/paper.tex
Munging figures

@@
 \normalsize
-\caption{XXX}
+\caption{Self-reported native language of 3,154 bilingual Turkers.
+Not shown are 54 langs with $\leq$20 speakers  each for a total of 423 remaining speakers.
+We omit Turkers did not self-report their native languages (1,801), 243 who reported two native languages, 83 who reported $\geq$3 native languages.}\label{lang-pie}
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
-\begin{figure*}[h]
-\centering
-\includegraphics[width=7in]{figures/completiontime}
-\caption{Time (in days) to complete all HITs in each language.
-Red bar shows time until first HIT was started, relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu).
-Blue bar shows time until all HITs in each language were completed.}
-\label{completion-time}
-\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
-\begin{figure*}[h]
-\centering
-\includegraphics[width=\linewidth]{figures/turkermap-color-cropped}
-\caption{The number of workers per country.
-This map was generated based on geolocating the IP address of  5,284 workers in our study.
-The size of the circles represents the number of worker from each country.
-The two largest are India (2,022 workers) and the United States (904).
-To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
-\label{map}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%% HIT UIs %%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
-\begin{figure}[h]
-\centering
-\includegraphics[width=\linewidth]{figures/natlang-pie}
-\caption{Self-reported native language of 3,154 bilingual Turkers.
+%
+%%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
+%\begin{figure}[h]
+%\centering
+%\includegraphics[width=\linewidth]{figures/natlang-pie}
+%\caption{Self-reported native language of 3,154 bilingual Turkers.
 Not shown are the languages of 243 Turkers who reported two native languages, 83 who reported $\geq$3 native languages, and 1.801 who failed to answer the language survey component of our translation HITs.}
-\label{lang-pie}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%\label{lang-pie}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
 \section{Survey Design}
@@
 Keeping only pairs such that (1) the English word is present in the WordNet ontology, (2) the article titles were a single word in both English and the foreign language, (3) the English wikipedia page was not a subcategory of person, and (4) the English and the foreign titles were not identical and were not contained as a substring in the other.
+
+%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
+\begin{figure}[h]
+\centering
+\includegraphics[height=\linewidth,angle=270]{figures/completiontime}
+\caption{Time (in days) to complete all HITs in each language. Red bar shows time until first HIT was started,
+% relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu). 
+ blue bar shows time until all HITs in each language were completed.}
+\label{completion-time}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2013-02-20 writeup/paper.tex
Cropped completion time figure
Anonymized for submission

@@
   }
+
+% Anonymized for submission
+\author{}
 
@@
 \normalsize
-\caption{Self-reported native language of 3,154 bilingual Turkers.
-Not shown are 54 langs with $\leq$20 speakers  each for a total of 423 remaining speakers.
-We omit Turkers did not self-report their native languages (1,801), 243 who reported two native languages, 83 who reported $\geq$3 native languages.}\label{lang-pie}
+\caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 langs with $\leq$20 speakers  each. 
+%(for a total of 423 remaining speakers).  
+We omit 1,801 Turkers did not report their native language, 243 who reported 2 native languages, and 83 who reported $\geq$3 native languages.}\label{lang-pie}
 \end{figure}
@@
 
-We chose the languages which were highly used on Wikipedia, in terms of the number of available articles.
-We compiled a list of all languages for which there existed at least 10,000 Wikipedia articles; we also included a small number of low resource languages for which there were approximately 1,000 available articles, giving a total of 119 languages to use in our task.
+We chose the languages which were highly used on Wikipedia, in terms of the number of available articles.\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} We compiled a list of all languages for which there existed at least 10,000 Wikipedia articles; we also included a small number of low resource languages for which there were approximately 1,000 available articles, giving a total of 119 languages to use in our task.
 For each of the languages, we chose the 1,000 most popular articles, and from these selected the 10,000 most frequent words.
-The resulting vocabularies served as the source side of our dictionaries.
+The resulting vocabulariesserved as the source side of our dictionaries.
 
@@
 \includegraphics[height=\linewidth,angle=270]{figures/completiontime}
-\caption{Time (in days) to complete all HITs in each language. Red bar shows time until first HIT was started,
+\caption{Time (in days) to complete all HITs in each language. Red bars show time until first HIT was started,
 % relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu). 
- blue bar shows time until all HITs in each language were completed.}
+ blue bars show time until all HITs in each language were completed.}
 \label{completion-time}

### 2013-02-20 writeup/paper.tex
Minor edits

@@
 MTurk was designed to accommodate tasks that are difficult for computers, but simple for people.
-This facilitates research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}.
+This facilitates research into human computation, where people can be treated as a function call \cite{vonAhnThesis,Little2009,quinn-bederson:2011}.
 It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge:10,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.
@@
 
-On MTurk, researchers who need work completed are called `Requesters', workers are often referred to as `Turkers', and micro tasks are called `HITs'.
+On MTurk, researchers who need work completed are called `Requesters', workers are often referred to as `Turkers', and micro-tasks are called `HITs'.
 MTurk is a true market, meaning that Turkers are free to choose to complete the HITs which interest them, and Requesters can price their tasks competitively to try to attract workers and have their tasks done quickly \cite{faridani-et-al:2011,singer-mittal:2011}.
 Turkers' identities remain anonymous to Requesters, and all payment occurs through Amazon.
-Requesters are able to accept submitted work or reject work that they do not feel meets their standards.
+Requesters are able to accept submitted work or reject work that they does not meet their standards.
 Turkers are only pay if a Requester accepts their work.
@@
 
-Several researchers have investigated using MTurk to build parallel corpora for machine translation, a task which stands to directly benefit from the availability of large volumes of low-cost translations \cite{Germann2001}.
+Several researchers have investigated using MTurk to build parallel corpora for machine translation, a task which stands to benefit low cost, high volume  translation on demand \cite{Germann2001}.
 \newcite{ambati_act} conducted a pilot study by posting 25 sentences to MTurk for Spanish, Chinese Hindi, Telugu, Urdu, and Haitian Creole.
@@
 \newcite{zaidan-callisonburch:2011:ACL-HLT2011a} presented methods for achieving professional-level translation quality from Turkers by soliciting multiple English translations of each foreign sentence.
-\newcite{Zbib-etal:2012:NAACL} used crowdsourcing to construct a 1.5 million word parallel corpus of dialect Arabic and English, training a statistical machine translation system that produced higher quality translations of dialect Arabic than a system a trained on 100x more Modern Standard Arabic-English parallel data.
-\newcite{post-callisonburch-osborne:2012:WMT} used MTurk to build parallel corpora between English and six Indian languages, ranging from .5M to 1.5M words, and use them to demonstrate the efficacy of syntactic approaches to machine translation on verb-final languages.
-Several researchers have examined cost optimization through using active learning techniques to select which sentences or fragments to translate \cite{ambati_naacl,bloodgood-callisonburch:2010:ACL,AmbatiThesis}.
+\newcite{Zbib-etal:2012:NAACL} used crowdsourcing to construct a 1.5 million word parallel corpus of dialect Arabic and English, training a statistical machine translation system that produced higher quality translations of dialect Arabic than a system a trained on 100 times more Modern Standard Arabic-English parallel data.
+\newcite{post-callisonburch-osborne:2012:WMT} used MTurk to build parallel corpora between English and six Indian languages, ranging from .5M to 1.5M words, and use them to demonstrate the efficacy of syntactic machine translation on verb-final languages.
+Several researchers have examined cost optimization using active learning techniques to select the most useful sentences or fragments to translate \cite{ambati_naacl,bloodgood-callisonburch:2010:ACL,AmbatiThesis}.
 
@@
 
-The dictionary creation task was broken into two steps: a translation HIT and an evaluation HIT. 
+Our experiments consist of two task types: a translation HIT and an evaluation HIT. 
 %Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.  
@@
 Each task contained 10 words, 8 of which were words with unknown translations, and the other two of which were quality control words with known translations.
-.
+
 The task paid \$0.15 for the translation of 10 words.
 Each set of 10 words was independently translated by three separate workers.
+In total, XXXXXX translation tasks were completed by YYYY workers over a period of ZZZ months.
 

### 2013-02-20 writeup/paper.tex
Bib changes
summary table for turker quality

--- 2013-02-20 writeup/paper.tex
@@
 \normalsize
-\caption{Self-reported native language of 3,154 bilingual Turkers.
-Not shown are 54 langs with $\leq$20 speakers  each for a total of 423 remaining speakers.
-We omit Turkers did not self-report their native languages (1,801), 243 who reported two native languages, 83 who reported $\geq$3 native languages.}\label{lang-pie}
+\caption{XXX}
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
+\begin{figure*}[h]
+\centering
+\includegraphics[width=7in]{figures/completiontime}
+\caption{Time (in days) to complete all HITs in each language.
+Red bar shows time until first HIT was started, relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu).
+Blue bar shows time until all HITs in each language were completed.}
+\label{completion-time}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries \cite{AmazonRequesterTour}.
-This suggest that its worker population that should represent a diverse set of languages.
+This suggests that its worker population should represent a diverse set of languages.
 
@@
 %, including the quality of the translations and recommendations for  languages that are feasible for near-term creation of multi-lingual technologies.
+
+%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
+\begin{figure*}[h]
+\centering
+\includegraphics[width=\linewidth]{figures/turkermap-color-cropped}
+\caption{The number of workers per country.
+This map was generated based on geolocating the IP address of  5,284 workers in our study.
+The size of the circles represents the number of worker from each country.
+The two largest are India (2,022 workers) and the United States (904).
+To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
+\label{map}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{tabular}{lc}\hline\hline\\
-Is [HIT language/English] your native language? &129,049\\
-How many years have you spoken [HIT language]?&159,807\\
-How many years have you spoken English?&159,808\\
-What country do you live in?&329,033\\
-Current location (collected automatically)& 329,033\\
+Is [HIT language/English] your native language? &NUM\\
+How many years have you spoken [HIT language]?&NUM\\
+How many years have you spoken English?&NUM\\
+What country do you live in?&308,079\\
+Current location (collected automatically)& 308,079\\
 \hline\\
-Total assignments& 329,033\\
-Total unique workers& 6,034\\
+Total assignments& 308,079\\
+Total unique workers& 5,271\\
 \hline\hline
@@
 
-%
-%%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
-%\begin{figure}[h]
-%\centering
-%\includegraphics[width=\linewidth]{figures/natlang-pie}
-%\caption{Self-reported native language of 3,154 bilingual Turkers.
+%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
+\begin{figure}[h]
+\centering
+\includegraphics[width=\linewidth]{figures/natlang-pie}
+\caption{Self-reported native language of 3,154 bilingual Turkers.
 Not shown are the languages of 243 Turkers who reported two native languages, 83 who reported $\geq$3 native languages, and 1.801 who failed to answer the language survey component of our translation HITs.}
-%\label{lang-pie}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
+\label{lang-pie}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Survey Design}
@@
 Keeping only pairs such that (1) the English word is present in the WordNet ontology, (2) the article titles were a single word in both English and the foreign language, (3) the English wikipedia page was not a subcategory of person, and (4) the English and the foreign titles were not identical and were not contained as a substring in the other.
-
-%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
-\begin{figure}[h]
-\centering
-\includegraphics[height=\linewidth,angle=270]{figures/completiontime}
-\caption{Time (in days) to complete all HITs in each language. Red bar shows time until first HIT was started,
-% relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu). 
- blue bar shows time until all HITs in each language were completed.}
-\label{completion-time}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2013-02-20 writeup/summary.tex
summary table for turker quality

@@
 \centering
-*** PLACE HOLDER NUMBERS; NUMBERS WITH ACCPETED HITS ONLY STILL RUNNING ***
 \begin{tabular}{llcccccc}
@@
 \hline\hline
-&&Total \# Turkers&\multicolumn{2}{c}{\# Turkers in language region}&\multicolumn{2}{c}{Avg. Turker quality (Dictionary size)}\\
+&&Total \# Turkers&\multicolumn{2}{c}{\# Turkers in language region}&\multicolumn{2}{c}{Avg. Turker quality}\\
 &&&Overall&By country&In region&Out of region\\
 \hline\hline
-hi&Hindi&312&300&India (285) Uae (5) &\textbf{0.5387} (9908)&0.4728 (41) \\
-&&&&Scotland (5) Other (5) &&&\\
+hi&Hindi&362&299&India (285) Uae (5) &\textbf{0.5395}&0.474\\
+&&&&Uk (5) Other (5) &&&\\
 &&&&&&&\\
-ta&Tamil&294&278&India (271) US (3) &\textbf{0.5528} (9974)&0.54 (5) \\
+ta&Tamil&304&278&India (271) US (3) &\textbf{0.5528}&0.54\\
 &&&&Canada (2) Other (2) &&&\\
 &&&&&&&\\
-ml&Malayalam&245&235&India (224) Uae (6) &0.4759 (9966)&\textbf{0.5523} (25)\\
+ml&Malayalam&284&235&India (224) Uae (6) &0.4759&\textbf{0.5523}\\
 &&&&US (3) Other (2) &&&\\
 &&&&&&&\\
-es&Spanish&235&206&US (131) Mexico (18) &\textbf{0.2711} (9768)&0.2677 (67) \\
+es&Spanish&244&205&US (131) Mexico (18) &\textbf{0.2723}&0.2675\\
 &&&&Westspain (14) Other (43) &&&\\
 &&&&&&&\\
-fr&French&202&183&India (68) US (48) &0.2907 (9514)&\textbf{0.3063} (386)\\
+fr&French&217&183&India (68) US (48) &0.2907&\textbf{0.307}\\
 &&&&France (25) Other (42) &&&\\
 &&&&&&&\\
-de&German&163&100&Germany (51) US (29) &\textbf{0.3527} (8892)&0.306 (1029) \\
+de&German&170&99&Germany (51) US (29) &\textbf{0.3529}&0.306\\
 &&&&Austria (9) Other (11) &&&\\
 &&&&&&&\\
-it&Italian&159&98&Italy (44) US (32) &\textbf{0.3221} (7885)&0.2734 (1870) \\
+it&Italian&166&98&Italy (44) US (32) &\textbf{0.3223}&0.2733\\
 &&&&Romania (9) Other (13) &&&\\
 &&&&&&&\\
-zh&Chinese&150&130&US (80) Singapore (15) &0.1821 (3510)&\textbf{0.4113} (137)\\
+zh&Chinese&151&123&US (80) Singapore (15) &\textbf{0.4171}&0.4123\\
 &&&&China (14) Other (21) &&&\\
 &&&&&&&\\
-ms&Malay&128&15&Malaysia (8) Singapore (4) &\textbf{0.2946} (6147)&0.2755 (3619) \\
+te&Telugu&137&102&India (98) US (3) &\textbf{0.4793}&0.4051\\
+&&&&Uae (1) &&&\\
+&&&&&&&\\
+ms&Malay&131&15&Malaysia (8) Singapore (4) &\textbf{0.2964}&0.276\\
 &&&&US (2) Other (1) &&&\\
-&&&&&&&\\
-ga&Irish&121&58&US (41) Ireland (13) &\textbf{0.3201} (3775)&0.2612 (6139) \\
-&&&&Scotland (4) &&&\\
 &&&&&&&\\

### 2013-02-20 writeup/paper.tex

--- 2013-02-20 writeup/paper.tex
@@
 The study contrasted Indian and US workers.
+\newcite{Ross2010} completed a longitudinal follow-on study.
 A number of other studies have informally investigated Turkers' language abilities.

### 2013-02-20 writeup/paper.tex
Added list of wikipedia langauges

@@
 % Anonymized for submission
-\author{}
+%\author{}
 
@@
 
+\begin{table}[htdp]
+\scriptsize 
+\begin{center}
+\begin{tabular}{|p{0.95\linewidth}|}
+\hline
+{\sc 500k+ articles:}
+Dutch (nl), English (en), French (fr), German (de), Italian (it), Japanese (ja), Polish (pl), Portuguese (pt), Russian (ru), Spanish (es)\\
+\hline
+{\sc 100k-500k articles:} Arabic (ar), Basque (eu), Bulgarian (bg), Catalan (ca), Chinese (zh), Croatian (hr), Czech (cs), Danish (da), Esperanto (eo), Finnish (fi), Hebrew (he), Hindi (hi), Hungarian (hu), Indonesian (id), Kazakh (kk), Korean (ko), Lithuanian (lt), Malay (ms), Norwegian (Bokmal) (no), Persian (fa), Romanian (ro), Serbian (sr), Slovak (sk), Slovenian (sl), Swedish (sv), Turkish (tr), Ukrainian (uk), Vietnamese (vi), Waray-Waray (war)\\
+\hline
+{\sc 10k-100k articles:}
+Azerbaijani (az), Afrikaans (af), Albanian (sq), Amharic (am), Aragonese (an), Armenian (hy), Asturian (ast), Belarusian (be), Bengali (bn), Bishnupriya Manipuri (bpy), Bosnian (bs), Breton (br), Cebuano (ceb), Galician (gl), Georgian (ka), Greek (el), Gujarati (gu), Haitian (ht), Icelandic (is), Ido (io), Irish (ga), Javanese (jv), Kannada (kn), Kurdish (ku), Latvian (lv), Low Saxon (nds), Luxembourgish (lb), Macedonian (mk), Malagasy (mg), Malayalam (ml), Marathi (mr), Neapolitan (nap), Nepali (ne), Newar / Nepal Bhasa (new), Norwegian (Nynorsk) (nn), Piedmontese (pms), Quechua (qu), Serbo-Croatian (sh), Sicilian (scn), Sundanese (su), Swahili (sw), Tagalog (tl), Tamil (ta), Tatar (tt), Telugu (te), Thai (th), Urdu (ur), Walloon (wa), Welsh (cy), West Frisian (fy), Yoruba (yo), Zazaki (diq)\\
+\hline
+{\sc $<$10k articles:} Central Bicolano (bcl), Ilokano (ilo), Kapampangan (pam), Pashto (ps), Punjabi (pa), Sindhi (sd), Somali (so), Tibetan (bo), Uzbek (uz), Wolof (wo)\\
+\hline
+\end{tabular}
+\end{center}
+\normalsize
+\caption{A list of the languages that were used in our study, grouped by the number of Wikipedia articles in the language.
+Each language's code is given in parentheses.
+These language codes are used in other figures in this paper.}\label{wikipedia-buckets}
+\end{table}%
+
 Our experiments consist of two task types: a translation HIT and an evaluation HIT. 
@@
 Each set of 10 words was independently translated by three separate workers.
-In total, XXXXXX translation tasks were completed by YYYY workers over a period of ZZZ months.
+In total, 308079 translation tasks were completed by 5271 workers over
+a period of three and a half months.
+20955 synonym tasks were used to judge the submitted translations, and
+were completed by an additional 1006 workers.
 

### 2013-02-20 writeup/paper.tex
fixed weird formatting thing I caused
fixed survey response table

@@
 \begin{tabular}{lc}\hline\hline\\
-Is [HIT language/English] your native language? &NUM\\
-How many years have you spoken [HIT language]?&NUM\\
-How many years have you spoken English?&NUM\\
-What country do you live in?&308,079\\
-Current location (collected automatically)& 308,079\\
+Is [HIT language/English] your native language? &3,480\\
+How many years have you spoken [HIT language]?&3,767\\
+How many years have you spoken English?&3,840\\
+What country do you live in?&3,890\\
+Current location (collected automatically)& 5,054\\
 \hline\\
-Total assignments& 308,079\\
-Total unique workers& 5,271\\
+Total unique workers& 5,281\\
 \hline\hline
 \end{tabular}
-\caption{Demographic survey questions and number of assignments with valid responses for each}
+\caption{Demographic survey questions and number of Turkers with valid responses for each}
 \label{survey-tab}
@@
 Each set of 10 words was independently translated by three separate workers.
-In total, 308079 translation tasks were completed by 5271 workers over
+In total, 308079 translation tasks were completed by 5281 workers over
 a period of three and a half months.
@@
 %%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
-\centering
 \include{summary}

### 2013-02-20 writeup/summary.tex
compressed summary table

@@
 \centering
-\begin{tabular}{llcccccc}
-\multicolumn{8}{c}{Number of Turkers per language}\\
+\begin{tabular}{lccc}
+\multicolumn{4}{c}{Number of turkers per language}\\
 \hline\hline
-&&Total \# Turkers&\multicolumn{2}{c}{\# Turkers in language region}&\multicolumn{2}{c}{Avg. Turker quality}\\
-&&&Overall&By country&In region&Out of region\\
+&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&In-region turker locations\\
+&In region&Out of region\\
 \hline\hline
-hi&Hindi&362&299&India (285) Uae (5) &\textbf{0.5395}&0.474\\
-&&&&Uk (5) Other (5) &&&\\
-&&&&&&&\\
-ta&Tamil&304&278&India (271) US (3) &\textbf{0.5528}&0.54\\
-&&&&Canada (2) Other (2) &&&\\
-&&&&&&&\\
-ml&Malayalam&284&235&India (224) Uae (6) &0.4759&\textbf{0.5523}\\
-&&&&US (3) Other (2) &&&\\
-&&&&&&&\\
-es&Spanish&244&205&US (131) Mexico (18) &\textbf{0.2723}&0.2675\\
-&&&&Westspain (14) Other (43) &&&\\
-&&&&&&&\\
-fr&French&217&183&India (68) US (48) &0.2907&\textbf{0.307}\\
-&&&&France (25) Other (42) &&&\\
-&&&&&&&\\
-de&German&170&99&Germany (51) US (29) &\textbf{0.3529}&0.306\\
-&&&&Austria (9) Other (11) &&&\\
-&&&&&&&\\
-it&Italian&166&98&Italy (44) US (32) &\textbf{0.3223}&0.2733\\
-&&&&Romania (9) Other (13) &&&\\
-&&&&&&&\\
-zh&Chinese&151&123&US (80) Singapore (15) &\textbf{0.4171}&0.4123\\
-&&&&China (14) Other (21) &&&\\
-&&&&&&&\\
-te&Telugu&137&102&India (98) US (3) &\textbf{0.4793}&0.4051\\
-&&&&Uae (1) &&&\\
-&&&&&&&\\
-ms&Malay&131&15&Malaysia (8) Singapore (4) &\textbf{0.2964}&0.276\\
-&&&&US (2) Other (1) &&&\\
-&&&&&&&\\
+Hindi&\textbf{0.54 (299)}&0.47 (63)&India (285) UAE (5) UK (5) Other (5) \\
+Tamil&\textbf{0.55 (278)}&0.54 (26)&India (271) US (3) Canada (2) Other (2) \\
+Malayalam&0.48 (235) &\textbf{0.55} (49)&India (224) UAE (6) US (3) Other (2) \\
+Spanish&\textbf{0.27 (205)}&0.27 (39)&US (131) Mexico (18) Spain (14) Other (43) \\
+French&0.29 (183) &\textbf{0.31} (34)&India (68) US (48) France (25) Other (42) \\
+German&\textbf{0.35 (99)}&0.31 (71)&Germany (51) US (29) Austria (9) Other (11) \\
+Italian&\textbf{0.32 (98)}&0.27 (68)&Italy (44) US (32) Romania (9) Other (13) \\
+Chinese&\textbf{0.42 (123)}&0.41 (28)&US (80) Singapore (15) China (14) Other (21) \\
+Telugu&\textbf{0.48 (102)}&0.41 (35)&India (98) US (3) UAE (1) \\
+Malay&\textbf{0.30 (15)}&0.28 (116)&Malaysia (8) Singapore (4) US (2) Other (1) \\
 \hline\hline

### 2013-02-20 writeup/summary.tex
compressed summary table

@@
 \hline\hline
-Hindi&\textbf{0.54 (299)}&0.47 (63)&India (285) UAE (5) UK (5) Other (5) \\
-Tamil&\textbf{0.55 (278)}&0.54 (26)&India (271) US (3) Canada (2) Other (2) \\
+Hindi&\textbf{0.54} (299)&0.47 (63)&India (285) UAE (5) UK (5) Other (5) \\
+Tamil&\textbf{0.55} (278)&0.54 (26)&India (271) US (3) Canada (2) Other (2) \\
 Malayalam&0.48 (235) &\textbf{0.55} (49)&India (224) UAE (6) US (3) Other (2) \\
-Spanish&\textbf{0.27 (205)}&0.27 (39)&US (131) Mexico (18) Spain (14) Other (43) \\
+Spanish&\textbf{0.27} (205)&0.27 (39)&US (131) Mexico (18) Spain (14) Other (43) \\
 French&0.29 (183) &\textbf{0.31} (34)&India (68) US (48) France (25) Other (42) \\
-German&\textbf{0.35 (99)}&0.31 (71)&Germany (51) US (29) Austria (9) Other (11) \\
-Italian&\textbf{0.32 (98)}&0.27 (68)&Italy (44) US (32) Romania (9) Other (13) \\
-Chinese&\textbf{0.42 (123)}&0.41 (28)&US (80) Singapore (15) China (14) Other (21) \\
-Telugu&\textbf{0.48 (102)}&0.41 (35)&India (98) US (3) UAE (1) \\
-Malay&\textbf{0.30 (15)}&0.28 (116)&Malaysia (8) Singapore (4) US (2) Other (1) \\
+German&\textbf{0.35} (99)&0.31 (71)&Germany (51) US (29) Austria (9) Other (11) \\
+Italian&\textbf{0.32} (98)&0.27 (68)&Italy (44) US (32) Romania (9) Other (13) \\
+Chinese&\textbf{0.42} (123)&0.41 (28)&US (80) Singapore (15) China (14) Other (21) \\
+Telugu&\textbf{0.48} (102)&0.41 (35)&India (98) US (3) UAE (1) \\
+Malay&\textbf{0.30} (15)&0.28 (116)&Malaysia (8) Singapore (4) US (2) Other (1) \\
+Turkish&\textbf{0.30} (83)&0.27 (47)&Turkey (39) US (20) Macedonia (12) Other (13) \\
+Kannada&0.64 (106) &\textbf{0.65} (21)&India (106) US (1) \\
+Portuguese&0.20 (107) &\textbf{0.24} (19)&Brazil (46) Portugal (32) US (15) Other (14) \\
+Arabic&0.45 (62) &\textbf{0.45} (64)&Egypt (19) Jordan (17) Morocco (9) Other (17) \\
+Romanian&0.29 (87) &\textbf{0.33} (37)&Romania (77) US (6) Moldova (3) Other (2) \\
+Swedish&\textbf{0.30} (58)&0.29 (66)&US (28) Sweden (23) Finland (3) Other (4) \\
+Czech&0.24 (52) &\textbf{0.25} (71)&US (19) Czechrepublic (15) Serbia (5) Other (13) \\
+Irish&\textbf{0.32} (58)&0.26 (64)&US (41) Ireland (13) UK (4) \\
+Amharic&0.21 (17) &\textbf{0.42} (105)&US (14) Ethiopia (3) \\
+Russian&0.15 (72) &\textbf{0.16} (49)&US (38) Russia (8) Moldova (7) Other (19) \\
 \hline\hline

### 2013-02-20 writeup/summary.tex
compressed summary table

--- 2013-02-20 writeup/summary.tex
@@
 \begin{figure}[h]
-\centering
-\begin{tabular}{lccc}
+\footnotesize
+\begin{tabular}{lccl}
 \multicolumn{4}{c}{Number of turkers per language}\\
 \hline\hline
-&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&In-region turker locations\\
-&In region&Out of region\\
+&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&Primary locations\\
+&In region&Out of region&of turkers in region\\
 \hline\hline
-Hindi&\textbf{0.54 (299)}&0.47 (63)&India (285) UAE (5) UK (5) Other (5) \\
-Tamil&\textbf{0.55 (278)}&0.54 (26)&India (271) US (3) Canada (2) Other (2) \\
-Malayalam&0.48 (235) &\textbf{0.55} (49)&India (224) UAE (6) US (3) Other (2) \\
-Spanish&\textbf{0.27 (205)}&0.27 (39)&US (131) Mexico (18) Spain (14) Other (43) \\
-French&0.29 (183) &\textbf{0.31} (34)&India (68) US (48) France (25) Other (42) \\
-German&\textbf{0.35 (99)}&0.31 (71)&Germany (51) US (29) Austria (9) Other (11) \\
-Italian&\textbf{0.32 (98)}&0.27 (68)&Italy (44) US (32) Romania (9) Other (13) \\
-Chinese&\textbf{0.42 (123)}&0.41 (28)&US (80) Singapore (15) China (14) Other (21) \\
-Telugu&\textbf{0.48 (102)}&0.41 (35)&India (98) US (3) UAE (1) \\
-Malay&\textbf{0.30 (15)}&0.28 (116)&Malaysia (8) Singapore (4) US (2) Other (1) \\
+Hindi&\textbf{0.54} (299)&0.47 (63)&India (285) UAE (5) UK (5) \\
+Tamil&\textbf{0.55} (278)&0.54 (26)&India (271) US (3) Canada (2) \\
+Malayalam&0.48 (235) &\textbf{0.55} (49)&India (224) UAE (6) US (3) \\
+Spanish&\textbf{0.27} (205)&0.27 (39)&US (131) Mexico (18) Spain (14) \\
+French&0.29 (183) &\textbf{0.31} (34)&India (68) US (48) France (25) \\
+German&\textbf{0.35} (99)&0.31 (71)&Germany (51) US (29) Austria (9) \\
+Italian&\textbf{0.32} (98)&0.27 (68)&Italy (44) US (32) Romania (9) \\
+Chinese&\textbf{0.42} (123)&0.41 (28)&US (80) Singapore (15) China (14) \\
+Telugu&\textbf{0.48} (102)&0.41 (35)&India (98) US (3) UAE (1) \\
+Malay&\textbf{0.30} (15)&0.28 (116)&Malaysia (8) Singapore (4) US (2) \\
+Turkish&\textbf{0.30} (83)&0.27 (47)&Turkey (39) US (20) Macedonia (12) \\
+Kannada&0.64 (106) &\textbf{0.65} (21)&India (106) US (1) \\
+Portuguese&0.20 (107) &\textbf{0.24} (19)&Brazil (46) Portugal (32) US (15) \\
+Arabic&0.45 (62) &\textbf{0.45} (64)&Egypt (19) Jordan (17) Morocco (9) \\
+Romanian&0.29 (87) &\textbf{0.33} (37)&Romania (77) US (6) Moldova (3) \\
+Swedish&\textbf{0.30} (58)&0.29 (66)&US (28) Sweden (23) Finland (3) \\
+Czech&0.24 (52) &\textbf{0.25} (71)&US (19) Czechrepublic (15) Serbia (5) \\
+Irish&\textbf{0.32} (58)&0.26 (64)&US (41) Ireland (13) UK (4) \\
+Amharic&0.21 (17) &\textbf{0.42} (105)&US (14) Ethiopia (3) \\
+Russian&0.15 (72) &\textbf{0.16} (49)&US (38) Russia (8) Moldova (7) \\
 \hline\hline

### 2013-02-20 writeup/paper.tex
compressed summary table
Modifying the Survey Design section

@@
 
-%%%%%%%%%%%%%%% NAT LANG PIE TABLE %%%%%%%%%%%
-\begin{figure}[h]
-\footnotesize
-\begin{tabular}{lrlrlr}\hline\hline
-%Language&\# Turkers\\
-\hline
-English&591&	French&63&	Vietnamese&34\\
-Tamil&253&	Polish&61&	Macedonian&31\\
-Malayalam&219&	Urdu&56&	Cebuano&29\\
-Hindi&149&	Tagalog&54&	Swedish&26\\
-Spanish&131&	Marathi&48&	Bulgarian&25\\
-Telugu&87&	Russian&44&	Hungarian&23\\
-Chinese&86&	Italian&43&	Swahili&23\\
-Romanian&85&	Bengali&41&	Thai&22\\
-Portuguese&82&	Gujarati&39&	Catalan&22\\
-Arabic&74&	Hebrew&38&	Lithuanian&21\\
-Kannada&72&	Dutch&37&	Punjabi&21\\
-German&66&	Turkish&35&	Others &$\leq$20\\
-\hline\hline
-\end{tabular}
-\normalsize
-\caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 langs with $\leq$20 speakers  each. 
-%(for a total of 423 remaining speakers).  
-We omit 1,801 Turkers did not report their native language, 243 who reported 2 native languages, and 83 who reported $\geq$3 native languages.}\label{lang-pie}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
-%\begin{figure}[h]
-%\centering
-%\includegraphics[width=\linewidth]{figures/natlang-pie}
-%\caption{Self-reported native language of 3,154 bilingual turkers}
-%\label{lang-pie}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Background and Related Work}
@@
 %%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
-\begin{table*}[h]
-\centering
-\begin{tabular}{lc}\hline\hline\\
-Is [HIT language/English] your native language? &3,480\\
-How many years have you spoken [HIT language]?&3,767\\
-How many years have you spoken English?&3,840\\
-What country do you live in?&3,890\\
-Current location (collected automatically)& 5,054\\
-\hline\\
-Total unique workers& 5,281\\
-\hline\hline
-\end{tabular}
-\caption{Demographic survey questions and number of Turkers with valid responses for each}
-\label{survey-tab}
-\end{table*}
+%\begin{table*}[h]
+%\centering
+%\begin{tabular}{lc}\hline\hline\\
+%Is [HIT language/English] your native language? &3,480\\
+%How many years have you spoken [HIT language]?&3,767\\
+%How many years have you spoken English?&3,840\\
+%What country do you live in?&3,890\\
+%Current location (collected automatically)& 5,054\\
+%\hline\\
+%Total unique workers& 5,281\\
+%\hline\hline
+%\end{tabular}
+%\caption{Demographic survey questions and number of Turkers with valid responses for each}
+%\label{survey-tab}
+%\end{table*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Survey Design}
-The central task in this study was to use Mechanical Turk to create bilingual dictionaries for over 100 languages in order to test Mechanical Turk's bilingual population.
+The central task in this study was to study Mechanical Turk's bilingual population.
+We accomplished this through self-reported surveys combined with a HIT to translate individual words for over 100 languages.
+We evaluate the accuracy of the workers' translations against known translations.
+In cases where these were not exact matches, we used a second pass monolingual HIT, which asked English speakers to evaluate if a worker-provided translation was a synonym of the known translation.
+
+\paragraph{Demographic Survey}
+
+At the start of each HIT, Turkers were asked to complete a brief survey about their language abilities. The survey asked the following questions:
+\begin{itemize}
+\item Is [HIT language] your native language? 
+\item How many years have you spoken [language]? 
+\item Is English your native language? 
+\item How many years have you spoken English?
+\item What country do you live in?
+\end{itemize}
+We automatically collected each worker's current location by geolocating their IP address.
+A total of 5,281 unique workers completed our HITs.
+Among those, 3,890 provided valid responses to our survey questions, and we were able to geolocate 5,054.
+Figure \ref{map} plots the location of workers across XXX countries.
+
+% were not required in order to complete the HIT; survey questions and the number of valid responses received for each are listed in table \ref{survey-tab}.
+Although it was not required, Turkers who completed multiple HIT assignments could fill out the survey multiple times.
+This enabled some Turkers to report multiple native languages (see figure \ref{numlangs-tab}).
+While most results presented are calculated across all Turkers, figures given for distributions across native languages are calculated only from Turkers who reported a single native language.\\
+
+%%%%%%%%%%%%%%% NAT LANG PIE TABLE %%%%%%%%%%%
+\begin{figure}[h]
+\footnotesize
+\begin{tabular}{lrlrlr}\hline\hline
+%Language&\# Turkers\\
+\hline
+English&591&	French&63&	Vietnamese&34\\
+Tamil&253&	Polish&61&	Macedonian&31\\
+Malayalam&219&	Urdu&56&	Cebuano&29\\
+Hindi&149&	Tagalog&54&	Swedish&26\\
+Spanish&131&	Marathi&48&	Bulgarian&25\\
+Telugu&87&	Russian&44&	Hungarian&23\\
+Chinese&86&	Italian&43&	Swahili&23\\
+Romanian&85&	Bengali&41&	Thai&22\\
+Portuguese&82&	Gujarati&39&	Catalan&22\\
+Arabic&74&	Hebrew&38&	Lithuanian&21\\
+Kannada&72&	Dutch&37&	Punjabi&21\\
+German&66&	Turkish&35&	Others &$\leq$20\\
+\hline\hline
+\end{tabular}
+\normalsize
+\caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 langs with $\leq$20 speakers  each. 
+%(for a total of 423 remaining speakers).  
+We omit 1,801 Turkers did not report their native language, 243 who reported 2 native languages, and 83 who reported $\geq$3 native languages.}\label{lang-pie}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\paragraph{Selection of languages}
 
@@
 
-\begin{table}[htdp]
+\begin{table}[h]
 \scriptsize 
@@
 
-Our experiments consist of two task types: a translation HIT and an evaluation HIT. 
+\paragraph{Translation HIT}
+
+%Our experiments consist of two task types: a translation HIT and an evaluation HIT. 
 %Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.  
@@
 Each set of 10 words was independently translated by three separate workers.
-In total, 308079 translation tasks were completed by 5281 workers over
+In total, 308,079 translation tasks were completed by 5,281 workers over
 a period of three and a half months.
-20955 synonym tasks were used to judge the submitted translations, and
-were completed by an additional 1006 workers.
+
+\paragraph{Evaluating translation accuracy}
 
@@
 Keeping only pairs such that (1) the English word is present in the WordNet ontology, (2) the article titles were a single word in both English and the foreign language, (3) the English wikipedia page was not a subcategory of person, and (4) the English and the foreign titles were not identical and were not contained as a substring in the other.
+20,955 synonym tasks were used to judge the submitted translations, and
+were completed by an additional 1,006 workers.
 
@@
 For non-synonyms we took two random words from Brown and if they were not in each others synonyms lists we added them as non-synonyms pair.
-
-\section{Turker Demographics}
-At the start of each HIT, Turkers were asked to complete a brief survey about their language abilities.
-Valid responses to all survey questions were not required in order to complete the HIT; survey questions and the number of valid responses received for each are listed in table \ref{survey-tab}.
-Although it was not required, Turkers who completed multiple HIT assignments could fill out the survey multiple times.
-This enabled some Turkers to report multiple native languages (see figure \ref{numlangs-tab}).
-While most results presented are calculated across all Turkers, figures given for distributions across native languages are calculated only from Turkers who reported a single native language.\\
 
@@
 %%%%%%%%%%%%%%% LOCATION BAR %%%%%%%%%%%
-\begin{figure*}[h]
-\centering
-\includegraphics[width=6in]{figures/assign-langgeo-sorted}
-\caption{Geolocation of Turkers speaking 40 most represented languages, in terms of number of assignments submitted}
-\label{langgeo-bar}
-\end{figure*}
+%\begin{figure*}[h]
+%\centering
+%\includegraphics[width=6in]{figures/assign-langgeo-sorted}
+%\caption{Geolocation of Turkers speaking 40 most represented languages, in terms of number of assignments submitted}
+%\label{langgeo-bar}
+%\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
+\include{summary}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
-\include{summary}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%

### 2013-02-20 writeup/paper.tex
compressing survey table

--- 2013-02-20 writeup/paper.tex
@@
 %%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
-\begin{table*}[h]
-\centering
+\begin{figure}[h]
 \begin{tabular}{lc}\hline\hline\\
-Is [HIT language/English] your native language? &3,480\\
-How many years have you spoken [HIT language]?&3,767\\
-How many years have you spoken English?&3,840\\
+Is [HIT language/English]&\multirow{2}{*}{3,480}\\
+your native language? &\\
+How many years have you&\multirow{2}{*}{3,767}\\
+spoken [HIT language]?&\\
+How many years have you&\multirow{2}{*}{3,840}\\
+spoken English?&\\
 What country do you live in?&3,890\\
-Current location (collected automatically)& 5,054\\
+Geolocation (collected automatically)& 5,054\\
 \hline\\
-Total unique workers& 5,281\\
+Total workers& 5,281\\
 \hline\hline
@@
 \label{survey-tab}
-\end{table*}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-02-20 writeup/paper.tex

--- 2013-02-20 writeup/paper.tex
@@
 %%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
+\begin{figure}[h]
+\begin{tabular}{lc}\hline\hline\\
+Is [HIT language/English]&\multirow{2}{*}{3,480}\\
+your native language? &\\
+How many years have you&\multirow{2}{*}{3,767}\\
+spoken [HIT language]?&\\
+How many years have you&\multirow{2}{*}{3,840}\\
+spoken English?&\\
+What country do you live in?&3,890\\
+Geolocation (collected automatically)& 5,054\\
+\hline\\
+Total workers& 5,281\\
+\hline\hline
+\end{tabular}
+\caption{Demographic survey questions and number of Turkers with valid responses for each}
+\label{survey-tab}
+\end{figure}
 %\begin{table*}[h]

### 2013-02-20 writeup/paper.tex
Minor edits and reorderings.
Finished revising the Survey Design section.

--- 2013-02-20 writeup/paper.tex
@@
 % Anonymized for submission
-%\author{}
+\author{}
 
@@
 Requesters are able to accept submitted work or reject work that they does not meet their standards.
-Turkers are only pay if a Requester accepts their work.
+Turkers are only paid if a Requester accepts their work.
 
@@
 
-%%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
+%%%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
+%\begin{figure}[h]
+%\begin{tabular}{lc}\hline\hline\\
+%Is [HIT language/English]&\multirow{2}{*}{3,480}\\
+%your native language? &\\
+%How many years have you&\multirow{2}{*}{3,767}\\
+%spoken [HIT language]?&\\
+%How many years have you&\multirow{2}{*}{3,840}\\
+%spoken English?&\\
+%What country do you live in?&3,890\\
+%Geolocation (collected automatically)& 5,054\\
+%\hline\\
+%Total workers& 5,281\\
+%\hline\hline
+%\end{tabular}
+%\caption{Demographic survey questions and number of Turkers with valid responses for each}
+%\label{survey-tab}
+%\end{figure}
+
 %\begin{table*}[h]
@@
 Among those, 3,890 provided valid responses to our survey questions, and we were able to geolocate 5,054.
-Figure \ref{map} plots the location of workers across XXX countries.
+Figure \ref{map} plots the location of workers across 111 countries.
 
@@
 \normalsize
-\caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 langs with $\leq$20 speakers  each. 
+\caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 languages with $\leq$20 speakers . 
 %(for a total of 423 remaining speakers).  
@@
 
-We chose the languages which were highly used on Wikipedia, in terms of the number of available articles.\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} We compiled a list of all languages for which there existed at least 10,000 Wikipedia articles; we also included a small number of low resource languages for which there were approximately 1,000 available articles, giving a total of 119 languages to use in our task.
-For each of the languages, we chose the 1,000 most popular articles, and from these selected the 10,000 most frequent words.
-The resulting vocabulariesserved as the source side of our dictionaries.
+We drew our data from the different language versions of Wikipedia.
+We selected all of the  in terms of the number of available articles.
+We selected the 100 languages with the largest number of articles\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}}, and then selected an additional 19 languages low resource languages with $<$10,000 articles, giving a total of 119 languages (Table \ref{wikipedia-buckets}).
+For each language, we chose the 1,000 most viewed articles,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and used these to extract the 10,000 most frequent words.
+The resulting vocabularies served as the input to our translation HIT.
 
@@
 Each language's code is given in parentheses.
-These language codes are used in other figures in this paper.}\label{wikipedia-buckets}
+These language codes are used in other figures throughout this paper.}\label{wikipedia-buckets}
 \end{table}%
@@
 %Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.  
-For the translation task, we asked Turkers to translate individual words, showing each word used in the context of three sentences.
+For the translation task, we asked Turkers to translate individual words.
+We showed each word in the context of three sentences that were drawn from Wikipedia.
+Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems.
+%
 Turkers were allowed to mark that they were unable to translate a word.
 Each task contained 10 words, 8 of which were words with unknown translations, and the other two of which were quality control words with known translations.
+%
+The task paid \$0.15 for the translation of 10 words.  
+% 
+%Assignments which had less than XXX items translated was rejected, as were workers who failed the quality control measures more than XXX\% of the time.
+Each set of 10 words was independently translated by three separate workers.
+5,281 workers completed 308,079 translations assignments, totally more than 3 million words, over a period of three and a half months.
 
-The task paid \$0.15 for the translation of 10 words.
-Each set of 10 words was independently translated by three separate workers.
-In total, 308,079 translation tasks were completed by 5,281 workers over
-a period of three and a half months.
+\paragraph{Gold standard translations} 
+Gold standard translation controls for every language were automatically harvested from Wikipedia.
+We use Wikipedia's inter-language links to pair titles of English articles with their corresponding foreign articles title.
+To get a more translatable set of pairs, we excluded any pairs where: (1) the English word was not present in the WordNet ontology, (2) either article title was longer than a single word, (3) the English wikipedia page was a subcategory of person or place, or (4) the English and the foreign titles were identical or a substring of the other.
 
-\paragraph{Evaluating translation accuracy}
+\paragraph{Manual evaluation of non-identical translations}
+We counted all translations that exactly matched the gold standard translation as correct.  For non-exact matches we created a second-pass quality assurance HIT.  
+For the evaluation task, Turkers were shown a pair of English words, one which was a Turker's translation of the foreign word used for quality control, and the other was the gold-standard translation the foreign word.
+Evaluators were asked whether the two words had the same meaning, and chose between three answers: `Yes', `No', or `Related but not synonymous'.
+Examples of meaning equivalent pairs include: $<${\it petroglyphs, rock paintings}$>$, $<${\it demo, show}$>$ and  $<${\it loam, loam: soil rich in decaying matter}$>$.
+Non-meaning equivalents included: $<${\it assorted, minutes}$>$, and $<${\it major,} URL of image$>$.
+Related items were things like $<${\it sky, clouds}$>$.
+Misspellings like $<${\it lactation, lactiation} $>$ were judged to have same meaning, and were marked as misspelled.
 
-The known translations were harvested from the titles of English and foreign articles that were linked via Wikipedia's inter-language links.
-Keeping only pairs such that (1) the English word is present in the WordNet ontology, (2) the article titles were a single word in both English and the foreign language, (3) the English wikipedia page was not a subcategory of person, and (4) the English and the foreign titles were not identical and were not contained as a substring in the other.
-20,955 synonym tasks were used to judge the submitted translations, and
+We checked Turkers who were working on this task by embedding pairs which were either known to be synonyms or were known to be unrelated. 
+We drew known synonyms from WordNet, and non-synonyms by pairing random words from a corpus of English (including them after they were determined to be unrelated according to WordNet).
+Automating the evaluation in this way allowed the whole pipeline to be run automatically.
+
+We cached the judgments collected in the evaluation HIT, and did not present pairs that were identical.  We ultimately needed only 
+20,955 synonym tasks to judge all of the submitted translations.  These
 were completed by an additional 1,006 workers.
+Each of these assignments included 10 word pairs, paid \$0.10, and was completed by 3 separate Turkers to allow majority votes in the cases of difficult judgments.
+%We describe the evaluation process further in the Measuring Quality section of this paper
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-For the evaluation task, Turkers were shown a pair of words, one which was a Turker's translation of one of the embedded quality control words, and the other which was a known gold-standard translation of the same word.
-Evaluators were asked whether the two words were synonyms, and chose between three answers: `Yes', `No', or `Related but not synonyms'.
-The last category was intended for word pairs such as `clouds' and `sky', which may be confusable to a non-native speaker but are not acceptable as dictionary translations.
-Turkers in the evaluation task could also flag the translated word as misspelled.
-Each HIT included 10 word pairs to be compared, and paid next to nothing.
-We describe the evaluation process further in the Measuring Quality section of this paper.
-
-Quality control for the evalutation HIT consisted of embedded word pairs which were either known to be synonyms or were known to be unrelated.
-Whether the evaluators correctly labeled the known word pairs could be assessed automatically, allowing the evaluation HIT to be the final step of the dictionary creation pipeline.
-
-That was method for building gold pairs for english-foreign dictionaries for Vocabulary HIT controls.
-
-We used Brown corpus for building synonyms and non-synonyms pairs for Synonyms HIT controls.
-It was built using random words from Brown corpora and if it had any synonyms we added them as pair.
-For non-synonyms we took two random words from Brown and if they were not in each others synonyms lists we added them as non-synonyms pair.
 

### 2013-02-20 writeup/paper.tex
new quality scores

--- 2013-02-20 writeup/paper.tex
@@
 While it is possible to strengthen the signal by collecting redundant labels, this strategy becomes difficult in practice for more complex data annotation.
-In the case of translation, even professional translations can be expected to vary significantly, and fully automatic comparison of free form text is itself an open research question.
+In the case of translation, low quality translations may have a high level of agreement (for example, when many workers use google translate) while high quality, even professional translations, can be expected to vary significantly.
 
@@
 
-Measured in this way, the average quality score across all HITs was just under 0.3.
+Measured in this way, the average quality score across all HITs was just under \textbf{XXXX}.
 In general, countries which produced more translations did not produce lower quality translations, with India, Macedonia, and the US falling very close to average quality (figure \ref{quality-scatter}).

### 2013-02-20 writeup/summary.tex
new quality scores

--- 2013-02-20 writeup/summary.tex
@@
 \begin{figure}[h]
-\centering
-\begin{tabular}{lccc}
+\footnotesize
+\begin{tabular}{llll}
 \multicolumn{4}{c}{Number of turkers per language}\\
 \hline\hline
-&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&In-region turker locations\\
-&In region&Out of region\\
+&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&Primary locations\\
+&In region&Out of region&of turkers in region\\
 \hline\hline
-Hindi&\textbf{0.54 (299)}&0.47 (63)&India (285) UAE (5) UK (5) Other (5) \\
-Tamil&\textbf{0.55 (278)}&0.54 (26)&India (271) US (3) Canada (2) Other (2) \\
-Malayalam&0.48 (235) &\textbf{0.55} (49)&India (224) UAE (6) US (3) Other (2) \\
-Spanish&\textbf{0.27 (205)}&0.27 (39)&US (131) Mexico (18) Spain (14) Other (43) \\
-French&0.29 (183) &\textbf{0.31} (34)&India (68) US (48) France (25) Other (42) \\
-German&\textbf{0.35 (99)}&0.31 (71)&Germany (51) US (29) Austria (9) Other (11) \\
-Italian&\textbf{0.32 (98)}&0.27 (68)&Italy (44) US (32) Romania (9) Other (13) \\
-Chinese&\textbf{0.42 (123)}&0.41 (28)&US (80) Singapore (15) China (14) Other (21) \\
-Telugu&\textbf{0.48 (102)}&0.41 (35)&India (98) US (3) UAE (1) \\
-Malay&\textbf{0.30 (15)}&0.28 (116)&Malaysia (8) Singapore (4) US (2) Other (1) \\
+Hindi&\textbf{0.410} (299)&0.406 (63)&India (285) UAE (5) UK (5) \\
+Tamil&0.339 (278) &\textbf{0.482} (26)&India (271) US (3) Canada (2) \\
+Malayalam&\textbf{0.534} (235)&0.505 (49)&India (224) UAE (6) US (3) \\
+Spanish&0.561 (205) &\textbf{0.682} (39)&US (131) Mexico (18) Spain (14) \\
+French&\textbf{0.636} (183)&0.541 (34)&India (68) US (48) France (25) \\
+German&\textbf{0.691} (99)&0.678 (71)&Germany (51) US (29) Austria (9) \\
+Italian&0.650 (98) &\textbf{0.716} (68)&Italy (44) US (32) Romania (9) \\
+Chinese&0.165 (123) &\textbf{0.207} (28)&US (80) Singapore (15) China (14) \\
+Telugu&\textbf{0.582} (102)&0.582 (35)&India (98) US (3) UAE (1) \\
+Malay&0.630 (15) &\textbf{0.649} (116)&Malaysia (8) Singapore (4) US (2) \\
+Turkish&0.593 (83) &\textbf{0.634} (47)&Turkey (39) US (20) Macedonia (12) \\
+Kannada&0.155 (106) &\textbf{0.284} (21)&India (106) US (1) \\
+Portuguese&0.599 (107) &\textbf{0.651} (19)&Brazil (46) Portugal (32) US (15) \\
+Arabic&\textbf{0.278} (62)&0.217 (64)&Egypt (19) Jordan (17) Morocco (9) \\
+Romanian&0.653 (87) &\textbf{0.668} (37)&Romania (77) US (6) Moldova (3) \\
+Swedish&0.497 (58) &\textbf{0.504} (66)&US (28) Sweden (23) Finland (3) \\
+Czech&0.536 (52) &\textbf{0.571} (71)&US (19) Czechrepublic (15) Serbia (5) \\
+Irish&\textbf{0.645} (58)&0.605 (64)&US (41) Ireland (13) UK (4) \\
+Amharic&0.080 (17) &\textbf{0.138} (105)&US (14) Ethiopia (3) \\
+Russian&0.202 (72) &\textbf{0.275} (49)&US (38) Russia (8) Moldova (7) \\
 \hline\hline

### 2013-02-20 writeup/paper.tex
Minor edits

--- 2013-02-20 writeup/paper.tex
@@
 
-\paragraph{Demographic Survey}
+\paragraph{Demographic questionnaire}
 
@@
 Figure \ref{map} plots the location of workers across 111 countries.
+Table \ref{lang-pie} gives the most common self-reported native languages.
 
@@
 %%%%%%%%%%%%%%% NAT LANG PIE TABLE %%%%%%%%%%%
-\begin{figure}[h]
+\begin{table}[h]
 \footnotesize
@@
 We omit 1,801 Turkers did not report their native language, 243 who reported 2 native languages, and 83 who reported $\geq$3 native languages.}\label{lang-pie}
-\end{figure}
+\end{table}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Each set of 10 words was independently translated by three separate workers.
-5,281 workers completed 308,079 translations assignments, totally more than 3 million words, over a period of three and a half months.
+5,281 workers completed 308,079 translations assignments, totaling more than 3 million words, over a period of three and a half months.
 
@@
 Misspellings like $<${\it lactation, lactiation} $>$ were judged to have same meaning, and were marked as misspelled.
+3 separate Turkers judged each pair, allowing majority votes in the cases of difficult cases.
 
-We checked Turkers who were working on this task by embedding pairs which were either known to be synonyms or were known to be unrelated. 
-We drew known synonyms from WordNet, and non-synonyms by pairing random words from a corpus of English (including them after they were determined to be unrelated according to WordNet).
-Automating the evaluation in this way allowed the whole pipeline to be run automatically.
-
-We cached the judgments collected in the evaluation HIT, and did not present pairs that were identical.  We ultimately needed only 
-20,955 synonym tasks to judge all of the submitted translations.  These
-were completed by an additional 1,006 workers.
-Each of these assignments included 10 word pairs, paid \$0.10, and was completed by 3 separate Turkers to allow majority votes in the cases of difficult judgments.
-%We describe the evaluation process further in the Measuring Quality section of this paper
+We checked Turkers who were working on this task by embedding pairs word which were either known to be synonyms (drawn from WordNet) or were known to be unrelated (randomly chosen from a corpus). 
+%We drew known synonyms from WordNet, and non-synonyms by pairing random words from a corpus of English (including them after they were determined to be unrelated according to WordNet).
+Automating the evaluation in this way allowed the whole pipeline to be run automatically.  Caching judgments meant that we ultimately needed only 
+20,955 synonym tasks to judge all of the submitted translations (a total of 55,880 unique word pairs).
+These were completed by an additional 1,006 workers.
+Each of these assignments included 10 word pairs and paid \$0.10.
+\section{Data Analysis}
 

### 2013-02-20 writeup/paper.tex
Edits to survey design, introduction of research questions

@@
 \paragraph{Gold standard translations} 
-Gold standard translation controls for every language were automatically harvested from Wikipedia.
-We use Wikipedia's inter-language links to pair titles of English articles with their corresponding foreign articles title.
+A set of gold standard translations were automatically harvested from Wikipedia  for every language to use as embedded controls.
+We used Wikipedia's inter-language links to pair titles of English articles with their corresponding foreign articles title.
 To get a more translatable set of pairs, we excluded any pairs where: (1) the English word was not present in the WordNet ontology, (2) either article title was longer than a single word, (3) the English wikipedia page was a subcategory of person or place, or (4) the English and the foreign titles were identical or a substring of the other.
@@
 For the evaluation task, Turkers were shown a pair of English words, one which was a Turker's translation of the foreign word used for quality control, and the other was the gold-standard translation the foreign word.
-Evaluators were asked whether the two words had the same meaning, and chose between three answers: `Yes', `No', or `Related but not synonymous'.
-Examples of meaning equivalent pairs include: $<${\it petroglyphs, rock paintings}$>$, $<${\it demo, show}$>$ and  $<${\it loam, loam: soil rich in decaying matter}$>$.
+Evaluators were asked whether the two words had the same meaning, and chose between three answers: `Yes', `No', or `Related but not synonymous.'  Examples of meaning equivalent pairs include: $<${\it petroglyphs, rock paintings}$>$, $<${\it demo, show}$>$ and  $<${\it loam, loam: soil rich in decaying matter}$>$.
 Non-meaning equivalents included: $<${\it assorted, minutes}$>$, and $<${\it major,} URL of image$>$.
@@
 Each of these assignments included 10 word pairs and paid \$0.10.
+
 \section{Data Analysis}
+
+We performed an analysis of our data to address the following questions:
+\begin{itemize}
+\item How quickly is work completed in each language? 
+\item What is the quality of crowdsourced translations? 
+\item Do workers accurately represent their language abilities? 
+\end{itemize}
 

### 2013-02-21 writeup/paper.tex
new quality data

@@
 \centering
-\includegraphics[width=6in]{figures/quality-hitlang}
+\includegraphics[width=6in]{figures/quality-hitlang-new}
 \caption{Translation quality of by source language}
@@
 \centering
-\includegraphics[width=6in]{figures/quality-scatter-avgturkers-country-labeled}
+\includegraphics[width=6in]{figures/quality-scatter-avgturkers-country-labeled-new}
 \caption{Quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country.}

### 2013-02-21 writeup/paper.tex
Updating data analysis questions
Minor edits

@@
 There are several complicating factors when trying to take a census of workers on MTurk.
-The workers identities are anonymized, and Amazon provides no information about their countries of origin nor their language abilities.
+The workers' identities are anonymized, and Amazon provides no information about their countries of origin or their language abilities.
 Posting a simple survey to have workers self-report this information may be inadequate, since (a) many worker may never see the survey, (b) many opt not to do one-off surveys since potential payment is low, and (c) validating the answers of respondents is not straightforward.
@@
 Our study establishes a methodology for determining the language demographics of anonymous crowd workers that is more robust than simple surveying.
-We ask workers what languages they speak and in what country they reside, and validate their claims by measuring their ability to correctly translate words and by geolocating them.
+We ask workers what languages they speak and what country they live in, and validate their claims by measuring their ability to correctly translate words and by geolocating them.
 To increase the visibility and the desirability of our tasks, we post 1,000 assignments in each of 119 languages.
 These tasks each consist of translating 10 foreign words into English.
-Two of the 10 words have known translations, allowing us to validate the the workers' translations are accurate, while constructing bilingual dictionaries with up to 10,000 entries, with the majority of entries being new.
+Two of the 10 words have known translations, allowing us to validate the the workers' translations are accurate.
+We construct bilingual dictionaries with up to 10,000 entries, with the majority of entries being new.
 
@@
 Are crowdsourced translations reliably good? 
-How often do workers misrepresented their language abilities to 
-%falsely
-obtain financial rewards?
+How often do workers misrepresent their language abilities to obtain financial rewards?
 
@@
 Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost, workforce.
-MTurk provides a simple interface for accessing human skills, allowing employers to provide micro-payments in return for workers completing micro-tasks.
-The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs),which hints at its origins.
+MTurk allows employers to provide micro-payments in return for workers completing micro-tasks.
+The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs).
 MTurk was designed to accommodate tasks that are difficult for computers, but simple for people.
@@
 
-On MTurk, researchers who need work completed are called `Requesters', workers are often referred to as `Turkers', and micro-tasks are called `HITs'.
+On MTurk, researchers who need work completed are called `Requesters', and workers are often referred to as `Turkers'.
 MTurk is a true market, meaning that Turkers are free to choose to complete the HITs which interest them, and Requesters can price their tasks competitively to try to attract workers and have their tasks done quickly \cite{faridani-et-al:2011,singer-mittal:2011}.
-Turkers' identities remain anonymous to Requesters, and all payment occurs through Amazon.
+Turkers remain anonymous to Requesters, and all payment occurs through Amazon.
 Requesters are able to accept submitted work or reject work that they does not meet their standards.
@@
 \begin{itemize}
-\item Is [HIT language] your native language? 
+\item Is [language] your native language? 
 \item How many years have you spoken [language]? 
@@
 A total of 5,281 unique workers completed our HITs.
-Among those, 3,890 provided valid responses to our survey questions, and we were able to geolocate 5,054.
+Among those, 3,890 provided responses to our survey questions, and we were able to geolocate 5,054.
 Figure \ref{map} plots the location of workers across 111 countries.
@@
 We drew our data from the different language versions of Wikipedia.
-We selected all of the  in terms of the number of available articles.
 We selected the 100 languages with the largest number of articles\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}}, and then selected an additional 19 languages low resource languages with $<$10,000 articles, giving a total of 119 languages (Table \ref{wikipedia-buckets}).
@@
 
-We checked Turkers who were working on this task by embedding pairs word which were either known to be synonyms (drawn from WordNet) or were known to be unrelated (randomly chosen from a corpus). 
+We checked Turkers who were working on this task by embedding pairs word which were either known to be synonyms (drawn from WordNet \cite{miller1995wordnet}) or were known to be unrelated (randomly chosen from a corpus).
 %We drew known synonyms from WordNet, and non-synonyms by pairing random words from a corpus of English (including them after they were determined to be unrelated according to WordNet).
@@
 \begin{itemize}
-\item How quickly is work completed in each language? 
-\item What is the quality of crowdsourced translations? 
-\item Do workers accurately represent their language abilities? 
+\item How quickly can we expect work to be completed in a particular language? 
+\item What is the quality of crowdsourced translations without quality control versus with it? 
+\item Do workers accurately represent their language abilities?  Should we constrain tasks by region? 
 \end{itemize}

### 2013-02-21 writeup/paper.tex
Additional questions that we could address

@@
 
+Other questions:
+\begin{itemize}
+\item Are Turkers cheating by using Google translate?  Is there a difference in their use of MT systems for Latin alphabet languages v. languages with scripts that are more difficult to type?
+\item Are there flaws in our gold standard translations?
+Are they too easy because they've already been indexed by Google?
+Are they too hard for some languages because they are obscure scientific terms?
+\item Can we select good gold standard translations for future studies?  Which translations are we confident in?
+\item How well do the Turker translations match external bilingual dictionaries?
+If we ranked Turkers by how well they performed on our controls, would those rankings stay stable if we ranked them based on their performance on external dictionaries?
+\item How well do Turkers agree with each other on non-control items?
+Should we run a synonym HIT on all of the non-identical translations?
+Would that help us understand which translations were good and which weren't?
+\end{itemize}
+
 %%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%

### 2013-02-22 code/compile_data_from_raw.py
updated code for extracting data and compiling qc scores

@@ -72,6 +72,8 @@ def assign_workers(path, langs, idlist=None):
         numlangmap, langmap = lang_map()
         data = {}
         for line in csv.DictReader(open(path)):
+		if line['mturk_status'] == 'Rejected':
+			continue
                 worker = line['worker_id']
                 assign = line['id']
 		if( (not(idlist==None)) and (assign not in idlist) ):
@@ -80,12 +82,14 @@ def assign_workers(path, langs, idlist=None):
 		data[assign]['worker'] = worker
 	return data
 		
-def assign_langs(path, langs, idlist=None):
+def assign_langs(path, langs, idlist=None, skip_rejected=False):
 	countrymap = country_map()
         codemap = code_map()
         numlangmap, langmap = lang_map()
         survey_data = {}
         for line in csv.DictReader(open(path)):
+		if skip_rejected and line['mturk_status'] == 'Rejected':
+			continue
                 worker = line['worker_id']
                 assign = line['id']
 		if( (not(idlist==None)) and (assign not in idlist) ):
@@ -113,11 +117,6 @@ def assign_langs(path, langs, idlist=None):
 		if('survey_is_native_foreign_speaker' in data): 
 			if(data['survey_is_native_foreign_speaker']=='yes'): 
 				survey_data[assign]['lang'] = numlangmap[langs[hit]] 
-
-		## ** assignments that don't trigger one of the above ifs end up as N/A in the final output. there are 1801 of these. ** #
-		## ** i checked a few, and they are mostly because the question 'is xx your native language' doesn't appear in the ** #
-		## ** data, not because they answer no to both questions. ** #
-
 		if(survey_data[assign]['lang'] == None):
 			survey_data[assign]['lang'] = 'N/A'
 		if('survey_years_speaking_english' in data): 

### 2013-02-22 code/qc.py

@@ -1,17 +1,13 @@
 import sys
 import csv
 import math
-import numpy
-import scipy
 import operator
 import itertools
-from scipy import stats
-from scipy.stats import norm
-import matplotlib.pyplot as plt
 
 RAW_DIR = '../data/dictionary-data-dump-2012-11-13_15:11/'
 OUTPUT_DIR = 'output'
 
+#map of assignment ID to turker ID
 def turker_map():
         tmap = dict()
         for line in open('%s/byassign.workerids.voc'%OUTPUT_DIR).readlines()[1:]:
@@ -19,9 +15,10 @@ def turker_map():
                 tmap[assign.strip()] = worker.strip()
         return tmap
 
+#map of assignment ID to quality score of that assignment, or N/A 
 def qual_map():
         qual_data = {}
-        for line in csv.DictReader(open('%s/byassign.voc.quality'%OUTPUT_DIR), delimiter='\t'):
+        for line in csv.DictReader(open('%s/byassign.voc.quality.related'%OUTPUT_DIR), delimiter='\t'):
                 assign = line['id']
                 qual = line['avg']
                 if(assign not in qual_data):
@@ -36,7 +33,7 @@ def word_map():
 	words = dict()
         for line in csv.DictReader(open('%s/dictionary'%RAW_DIR)):
 		wid = line['id']
-		word = line['translation']
+		word = line['translation'].strip().lower()
 		if wid not in words:
 			words[wid] = word
 	return words
@@ -46,8 +43,8 @@ def pair_map():
 	pairs = dict()
         for line in csv.DictReader(open('%s/syn_hits_data'%RAW_DIR)):
 		pid = line['id']
-		word = line['translation']
-		syn = line['synonym']
+		word = line['translation'].strip().lower()
+		syn = line['synonym'].strip().lower()
 		if pid not in pairs:
 			pairs[pid] = (word,syn)
 	return pairs
@@ -63,19 +60,24 @@ def get_syn_lists():
 	return (syns, nonsyns)
 
 #get a dictionary of word: list of acceptable synonyms. filter list of assignment ids used to restrict list of synonyms to come only from certain assignments
-def read_all_syns(filter_list=None):
+def read_all_syns(filter_list=None, use_related=False):
 	words = word_map()
 	pairs = pair_map()
 	syns = dict()
[…]

### 2013-02-28 writeup/paper.tex
updated code for extracting data and compiling qc scores
new figures and tables

@@
 \centering
-\includegraphics[height=\linewidth,angle=270]{figures/completiontime}
+%\includegraphics[height=\linewidth,angle=270]{figures/completiontime}
+\includegraphics[width=\linewidth]{figures/completiontime.pdf}
 \caption{Time (in days) to complete all HITs in each language. Red bars show time until first HIT was started,
@@
  blue bars show time until all HITs in each language were completed.}
-\label{completion-time}
+\label{completion-time-series}
 \end{figure}
@@
 \centering
-\includegraphics[width=6in]{figures/quality-hitlang-new}
-\caption{Translation quality of by source language}
+\includegraphics[width=6in]{figures/quality-hitlang-turkers}
+\caption{Average estimated translation quality of by source language.
+Quality is calculated as the average number of control words which were correct translations of the source word, where "correct" means that the provided translation was judged to be synonymous with the known translation by workers in a second-pass HIT.
+Error bars show 95\% confidence intervals of the mean quality score across all translators for the language.
+Quality estimates are only show for languages with at least 50 active turkers.
+}
 \label{hitlangqual-bar}
@@
 
-Measured in this way, the average quality score across all HITs was just under \textbf{XXXX}.
+Measured in this way, the average quality score across all HITs was just under 0.5.
 In general, countries which produced more translations did not produce lower quality translations, with India, Macedonia, and the US falling very close to average quality (figure \ref{quality-scatter}).
@@
 %%%%%%%%%%%%%%% NATIVE LANGUAGE QUALITY BAR %%%%%%%%%%%
-\begin{figure*}[h]
-\centering
-\includegraphics[width=6in]{figures/quality-natlang-sorted}
-\caption{Translation quality of native and non-native speakers}
-\label{natlangqual-bar}
-\end{figure*}
+%\begin{figure*}[h]
+%\centering
+%\includegraphics[width=6in]{figures/quality-natlang-sorted}
+%\caption{Translation quality of native and non-native speakers}
+%\label{natlangqual-bar}
+%\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\includegraphics[width=6in]{figures/quality-scatter-avgturkers-country-labeled-new}
-\caption{Quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country.}
+\includegraphics[width=6in]{figures/quality-scatter-avgturkers-country-labeled-turkers}
+\caption{Estimated quality of translations by country.
+Each circle is a country, sized proportional to the number of active Turkers from that country.
+Quality is calculated as the average number of control words which were correct translations of the source word, where "correct" means that the provided translation was judged to be synonymous with the known translation by workers in a second-pass HIT.
+Figure represents data from approx.
+281,000 assignments for which geolocation was known.}
 \label{quality-scatter}

### 2013-02-28 code/src/qc.py

@@ -88,6 +88,8 @@ def get_syns_quality_by_assign(path):
 		aid = line['assignment_id']
 		if line['is_control'] == '1':		
 			pair = line['pair_id']
+			#TODO
+			## FIX, EACH HAS 2 CONTROLS
 			if(line['are_synonyms'] == 'yes' and pair in syns):
 				quals.append(aid) 
 			elif(line['are_synonyms'] == 'no' and pair in nonsyns):

### 2013-02-28 writeup/paper.tex
Minor edits

--- 2013-02-21 writeup/paper.tex
@@
 Several researchers have investigated using MTurk to build parallel corpora for machine translation, a task which stands to benefit low cost, high volume  translation on demand \cite{Germann2001}.
-\newcite{ambati_act} conducted a pilot study by posting 25 sentences to MTurk for Spanish, Chinese Hindi, Telugu, Urdu, and Haitian Creole.
+\newcite{ambati_act} conducted a pilot study by posting 25 sentences to MTurk for Spanish, Chinese, Hindi, Telugu, Urdu, and Haitian Creole.
 In a study of 2000 Urdu sentences,
@@
 We drew our data from the different language versions of Wikipedia.
-We selected the 100 languages with the largest number of articles\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}}, and then selected an additional 19 languages low resource languages with $<$10,000 articles, giving a total of 119 languages (Table \ref{wikipedia-buckets}).
+We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} and then selected an additional 19 languages low resource languages with $<$10,000 articles, giving a total of 119 languages (Table \ref{wikipedia-buckets}).
 For each language, we chose the 1,000 most viewed articles,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and used these to extract the 10,000 most frequent words.
@@
 Misspellings like $<${\it lactation, lactiation} $>$ were judged to have same meaning, and were marked as misspelled.
-3 separate Turkers judged each pair, allowing majority votes in the cases of difficult cases.
+3 separate Turkers judged each pair, allowing majority votes for difficult cases.
 

### 2013-03-06 writeup/paper.tex
Minor edits

@@
 MTurk allows employers to provide micro-payments in return for workers completing micro-tasks.
-The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs).
+The basic units of work on MTurk are called `Human Intelligence Tasks' (HITs).
 MTurk was designed to accommodate tasks that are difficult for computers, but simple for people.
@@
 \section{Survey Design}
-The central task in this study was to study Mechanical Turk's bilingual population.
+The central task in this study was to investigate Mechanical Turk's bilingual population.
 We accomplished this through self-reported surveys combined with a HIT to translate individual words for over 100 languages.
@@
 We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} and then selected an additional 19 languages low resource languages with $<$10,000 articles, giving a total of 119 languages (Table \ref{wikipedia-buckets}).
-For each language, we chose the 1,000 most viewed articles,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and used these to extract the 10,000 most frequent words.
+For each language, we chose the 1,000 most viewed articles over a 1 year period,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and extracted the 10,000 most frequent words from them.
 The resulting vocabularies served as the input to our translation HIT.
 
+% Todo: sort by language code, rebalance the bottom set to have 19 languages in it.
 \begin{table}[h]
@@
 %Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.  
-For the translation task, we asked Turkers to translate individual words.
-We showed each word in the context of three sentences that were drawn from Wikipedia.
-Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems.
-%
+For the translation task, we asked Turkers to translate individual words.  We showed each word in the context of three sentences that were drawn from Wikipedia.  
 Turkers were allowed to mark that they were unable to translate a word.
 Each task contained 10 words, 8 of which were words with unknown translations, and the other two of which were quality control words with known translations.
+We gave special instruction for translating names of people and places, giving examples of how to handle `Barack Obama' and `Australia' using their interlanguage links.
+For languages with non-Latin alphabets, names were transliterated.
+
 %
@@
 We used Wikipedia's inter-language links to pair titles of English articles with their corresponding foreign articles title.
-To get a more translatable set of pairs, we excluded any pairs where: (1) the English word was not present in the WordNet ontology, (2) either article title was longer than a single word, (3) the English wikipedia page was a subcategory of person or place, or (4) the English and the foreign titles were identical or a substring of the other.
+To get a more translatable set of pairs, we excluded any pairs where: (1) the English word was not present in the WordNet ontology  \cite{miller1995wordnet}, (2) either article title was longer than a single word, (3) the English wikipedia page was a subcategory of person or place, or (4) the English and the foreign titles were identical or a substring of the other.
 
@@
 We counted all translations that exactly matched the gold standard translation as correct.  For non-exact matches we created a second-pass quality assurance HIT.  
-For the evaluation task, Turkers were shown a pair of English words, one which was a Turker's translation of the foreign word used for quality control, and the other was the gold-standard translation the foreign word.
+Turkers were shown a pair of English words, one of which was a Turker's translation of the foreign word used for quality control, and the other was the gold-standard translation the foreign word.
 Evaluators were asked whether the two words had the same meaning, and chose between three answers: `Yes', `No', or `Related but not synonymous.'  Examples of meaning equivalent pairs include: $<${\it petroglyphs, rock paintings}$>$, $<${\it demo, show}$>$ and  $<${\it loam, loam: soil rich in decaying matter}$>$.
@@
 
-We checked Turkers who were working on this task by embedding pairs word which were either known to be synonyms (drawn from WordNet \cite{miller1995wordnet}) or were known to be unrelated (randomly chosen from a corpus).
+We checked Turkers who were working on this task by embedding pairs word which were either known to be synonyms (drawn from WordNet) or  unrelated (randomly chosen from a corpus). 
 %We drew known synonyms from WordNet, and non-synonyms by pairing random words from a corpus of English (including them after they were determined to be unrelated according to WordNet).
-Automating the evaluation in this way allowed the whole pipeline to be run automatically.  Caching judgments meant that we ultimately needed only 
-20,955 synonym tasks to judge all of the submitted translations (a total of 55,880 unique word pairs).
+Automating approval/rejections for the second-pass evaluation allowed the whole pipeline to be run automatically.  Caching judgments meant that we ultimately needed only 
+20,955 synonym tasks to judge all of the submitted translations (a total of 55,880 unique non-matching word pairs).
 These were completed by an additional 1,006 workers.
@@
 \end{itemize}
+
+\paragraph{Use of machine translation}
+Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems.
+This strategy does not prevent workers from typing the words into a MT system, if they understand the language's script.
+%
 

### 2013-03-07 writeup/paper.tex
updated figure captions

--- 2013-02-28 writeup/paper.tex
@@
 %%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
-\begin{figure}[h]
+\begin{figure*}[h]
 \centering
-\includegraphics[height=\linewidth,angle=270]{figures/completiontime}
-\caption{Time (in days) to complete all HITs in each language. Red bars show time until first HIT was started,
+%\includegraphics[height=\linewidth,angle=270]{figures/completiontime-series}
+\includegraphics[width=6in]{figures/completiontime-series}
+\caption{Time (in days) to complete HITS in each language. Tick marks represent the completion of individual HITs. Elapsed time is relative to the first submitted HIT across all languages (Urdu). }
+%\caption{Time (in days) to complete all HITs in each language. Red bars show time until first HIT was started,
 % relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu). 
- blue bars show time until all HITs in each language were completed.}
+% blue bars show time until all HITs in each language were completed.}
 \label{completion-time}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\includegraphics[width=6in]{figures/assign-turk-scatter}
-\caption{Number of assignments and number of Turkers for each language. Each dot represents a language.}
+\includegraphics[width=6in]{figures/assign-turk-scatter-new}
+\caption{Number of assignments and number of Turkers for each language.
+Each dot represents a language.
+Figure includes only data from Turkers who reported only one native language consistantly across assignments, representing approx.
+3900 turkers across 139,000 assignments.}
 \label{ass-scatter}
@@
 \centering
-\includegraphics[width=6in]{figures/quality-hitlang-new}
-\caption{Translation quality of by source language}
+\includegraphics[width=6in]{figures/quality-hitlang-goog}
+\caption{Translation quality of by source language.
+Blue bars show quality estimates by language and green bars show proportion of translations which matched Google Translate.
+Total quality is calculated as the average number of control words which were correct translations of the source word, where ”correct” means that the provided translation was judged to be synonymous with the known translation by workers in a second-
+pass HIT.
+Dark blue bars indicate the proportion of translations which exactly matched known translations, and light blue indicate translations which were judged to be correct synonyms.
+Quality estimates are only show for languages with at least 50 active turkers.}
 \label{hitlangqual-bar}
@@
 \centering
-\includegraphics[width=6in]{figures/quality-scatter-avgturkers-country-labeled-new}
-\caption{Quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country.}
+\includegraphics[width=6in]{figures/quality-scatter}
+\caption{Estimated quality of translations by country.
+Each circle is a country, sized proportional to the number of active Turkers from that country.
+Quality is calculated as the average number of control words which were correct translations of the source word, where ”correct” means that the provided translation was judged to be synonymous with the known translation by workers in a second-pass HIT.
+Figure represents data from approx.
+281,000 assignments for which geolocation was known.}
 \label{quality-scatter}

### 2013-03-07 code/src/dictionaries/nonclpair/dictionary.cs
dictionaries for in and out of region assignments

@@ -1,0 +1,7175 @@
+přímou	direct,
+čáry	lines,
+užívané	of use,used,
+čapek	hats,
+středisko	center,
+nejlepších	best of,
+karlem	charles,
+odjel	he left,
+praze	prague,
+dobrého	good,
+průměrné	average,
+vojenské	military,
+lord	lord,
+mládí	youth,juvenile,
+průměrná	average,
+rychle	quickly,
+vojenská	military,vojenska,
+zákona	law,
+archeologické	archaeological,
+přešla	switched,
+bratislava	bratislava,
+bratislavy	bratislava,
+příliš	too,
+pouští	desert,
+stálé	permanent,
+řekou	river,
+něj	it,
+piva	beer,
+odpovídající	corresponding,
+materiálem	material,
+pivo	beer,
+polárních	polar,
+nulová	zero,
+pravé	right,
+nespokojenost	dissatisfaction,
+pravá	rights,
+nezávisle	independently,
+komunikaci	communication,
+životopis	biography,
+dobách	times,
+dialogy	dialogues,
+můžeme	we can,
+dlouhou	long,
+atomy	atoms,
+atomu	atom,
+podporou	support,alveolata,
+maďaři	hungarians,
+žádost	justice,request,
+činností	activities,
+zemích	countries,
+řešením	solution,
+postoj	stance,
+hrdinů	heroes,
+klasicismus	neoclassical eras,classicism,
+lidského	human,
+považováni	considered,
+unie	union,
+fašismus	fascism,
+nejen	not only,
+teroristické	terrorist,
+daní	taxes,
+zástupců	representatives,
+dané	given,
+víno	wine,
+vína	wine,
+dni	days,
+prvky	elements,
+neutrální	neutral,
+music	music,
+dns	dns,
+dny	days,
+havlík	havlik,
+bůh	god,
+stačí	just,
+zemi	country,
+schéma	scheme,
+pokrok	progress,
+očích	eyes,
+rozmach	boom,
+sňatku	marriage,
+nalezen	found,
+pobřeží	coast,
+poprava	execution,
+elektronických	electronic,
+skutečný	real,
+externí	external,
+popravy	execution,
+přijala	adopted,
+antické	antique,
+opravdu	really,
+pevnosti	strength,
+nálezy	findings,
+smtp	smtp,
+politika	policy,
+půl	half,
+maďarské	hungarian,
+starých	old,
+technicky	technical,technically,
+určitých	some,
[…]

### 2013-03-07 code/src/figures.py
comments in figures.py

@@ -15,8 +15,10 @@ from matplotlib import font_manager as fm
 
 QC = '' #'.related'
 OUTPUT_DIR = 'output'
-RAW_DIR = '../data/dictionary-data-dump-2012-11-13_15:11'
+RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11' 
 
+#filter data and return only entries which have the specified value in the specified column
+#e.g. only entries for which 'country' is 'IN'
 def select_by(data, col, value):
         dicts = dict()
         for d in data:
@@ -24,6 +26,8 @@ def select_by(data, col, value):
                         dicts[d] = data[d]
         return dicts
 
+#get a list of all possible values of the specified attribute 
+#e.g. if attr = 'country', get a list of all the values that appear in the column 'country'
 def all_keys(path, attr):
         ret = set()
         data = csv.DictReader(open(path),delimiter='\t')
@@ -35,7 +39,7 @@ def all_keys(path, attr):
                 ret.remove('')
         return list(ret)
 
-
+#read in tsv data file at path and return as dictionary of dictionaries, keyed by 'id'
 def read_data(path):
         ret = dict()
         data = csv.DictReader(open(path),delimiter='\t')
@@ -43,6 +47,9 @@ def read_data(path):
                 ret[d['id']] = d
         return ret
 
+#read in tsv data file at path and return as dictionary of dictionaries, keyed by 'id'
+#essentially the same as what is above, but slightly nicer format. mostly just here because
+#I was combining code from multiple files and didn't want to rework little details
 def read_table_file(path):
         ret = dict()
         data = csv.DictReader(open(path),delimiter='\t')
@@ -50,7 +57,9 @@ def read_table_file(path):
                 ret[d['id']] = {'lang':d['lang'],'country':d['country'], 'hitlang': d['hitlang'], 'survey':d['survey']}
         return ret
 
-def count_dicts(data, attr, mapname=False):
+#return a dictionary counting the number of occurances of each value of attr
+#e.g. if attr is 'country', a dictionary of {country : count}
+def count_dicts(data, attr):
         langs = dict()
[…]

### 2013-03-07 writeup/paper.tex
Minor mods to timeseries figure and captions

@@
 
-%
-%%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
-%\begin{figure}[h]
-%\centering
-%\includegraphics[width=\linewidth]{figures/natlang-pie}
-%\caption{Self-reported native language of 3,154 bilingual Turkers.
-Not shown are the languages of 243 Turkers who reported two native languages, 83 who reported $\geq$3 native languages, and 1.801 who failed to answer the language survey component of our translation HITs.}
-%\label{lang-pie}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
+%%%%%%%%%%%%%%% NAT LANG PIE TABLE %%%%%%%%%%%
+\begin{table}
+\footnotesize
+\begin{tabular}{lrlrlr}\hline\hline
+%Language&\# Turkers\\
+\hline
+English&591&	French&63&	Vietnamese&34\\
+Tamil&253&	Polish&61&	Macedonian&31\\
+Malayalam&219&	Urdu&56&	Cebuano&29\\
+Hindi&149&	Tagalog&54&	Swedish&26\\
+Spanish&131&	Marathi&48&	Bulgarian&25\\
+Telugu&87&	Russian&44&	Hungarian&23\\
+Chinese&86&	Italian&43&	Swahili&23\\
+Romanian&85&	Bengali&41&	Thai&22\\
+Portuguese&82&	Gujarati&39&	Catalan&22\\
+Arabic&74&	Hebrew&38&	Lithuanian&21\\
+Kannada&72&	Dutch&37&	Punjabi&21\\
+German&66&	Turkish&35&	Others &$\leq$20\\
+\hline\hline
+\end{tabular}
+\normalsize
+\caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 languages with $\leq$20 speakers . 
+%(for a total of 423 remaining speakers).  
+We omit 1,801 Turkers did not report their native language, 243 who reported 2 native languages, and 83 who reported $\geq$3 native languages.}\label{lang-pie}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Survey Design}
@@
 While most results presented are calculated across all Turkers, figures given for distributions across native languages are calculated only from Turkers who reported a single native language.\\
-
-%%%%%%%%%%%%%%% NAT LANG PIE TABLE %%%%%%%%%%%
-\begin{table}[h]
-\footnotesize
-\begin{tabular}{lrlrlr}\hline\hline
-%Language&\# Turkers\\
-\hline
-English&591&	French&63&	Vietnamese&34\\
-Tamil&253&	Polish&61&	Macedonian&31\\
-Malayalam&219&	Urdu&56&	Cebuano&29\\
-Hindi&149&	Tagalog&54&	Swedish&26\\
-Spanish&131&	Marathi&48&	Bulgarian&25\\
-Telugu&87&	Russian&44&	Hungarian&23\\
-Chinese&86&	Italian&43&	Swahili&23\\
-Romanian&85&	Bengali&41&	Thai&22\\
-Portuguese&82&	Gujarati&39&	Catalan&22\\
-Arabic&74&	Hebrew&38&	Lithuanian&21\\
-Kannada&72&	Dutch&37&	Punjabi&21\\
-German&66&	Turkish&35&	Others &$\leq$20\\
-\hline\hline
-\end{tabular}
-\normalsize
-\caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 languages with $\leq$20 speakers . 
-%(for a total of 423 remaining speakers).  
-We omit 1,801 Turkers did not report their native language, 243 who reported 2 native languages, and 83 who reported $\geq$3 native languages.}\label{lang-pie}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \includegraphics[width=6in]{figures/completiontime-series}
-\caption{Time (in days) to complete HITS in each language. Tick marks represent the completion of individual HITs. Elapsed time is relative to the first submitted HIT across all languages (Urdu). }
+\caption{Time (in days) to complete the translation HITs for 40 of the languages in our study.
+Tick marks represent the completion of individual assignments.
+Urdu and Russian were the first languages to be launched, followed by the others 2 days later.
+The languages which completed in the shortest amount of time were 4 Indian languages and Macedonian.}
 %\caption{Time (in days) to complete all HITs in each language. Red bars show time until first HIT was started,

### 2013-03-07 code/compile_data_from_raw.py
removing extra files

@@ -1,278 +1,0 @@
-import re
-import sys
-import csv
-import json
-import string
-import codecs
-
-RAW_DIR = '../data/dictionary-data-dump-2012-11-13_15:11/'
-OUTPUT_DIR = 'output'
-
-def hits_language():
-	hit_path = '%s/hits'%RAW_DIR
-	language_path = '%s/languages'%RAW_DIR
-        lang_data = {}
-        for line in csv.DictReader(open(language_path)):
-                lang = line['id']
-                if(lang not in lang_data):
-                        lang_data[lang] = lang
-        hit_data = {}
-        for line in csv.DictReader(open(hit_path)):
-                hit = line['id']
-                if(hit not in hit_data):
-                        l =  line['language_id']
-                        hit_data[hit] = lang_data[line['language_id']]
-        return hit_data
-
-def lang_map():
-        lang_data = {}
-        num_data = {}
-        for line in csv.DictReader(open('%s/languages'%RAW_DIR)):
-                lang = line['name'].lower()
-                id = line['id']
-                if(lang not in lang_data):
-                        lang_data[lang] = line['prefix']
-                if(id not in num_data):
-                        num_data[id] = line['prefix']
-        return num_data, lang_data
-
-def country_map():
-	ret = dict()
-	for l in open('data-files/countrymap').readlines():
-		ll = l.split('\t')
-		ret[ll[0]] = ll[1].strip()
-	return ret
-
-def code_map():
-	ret = dict()
-	for l in open('data-files/countrycodemap').readlines():
-		ll = l.split('\t')
-		ret[ll[0]] = ll[1].strip()
-	return ret
-
-def map_country(c, countrymap, codemap):
-	c = clean(c)
-	if c in countrymap:
-		c = countrymap[c]
-	if c in codemap:
-		return codemap[c]
-	return 'N/A'
-
-def list2str(lst):
-	s = ''
-	if len(lst) == 0:
-		s = 'N/A;'
-	for l in lst:
-		s+=l+';'
-	return s
-
-def assign_workers(path, langs, idlist=None):
-	countrymap = country_map()
-        codemap = code_map()
-        numlangmap, langmap = lang_map()
-        data = {}
[…]

### 2013-03-07 code/qc.py

@@ -1,178 +1,0 @@
-import sys
-import csv
-import math
-import operator
-import itertools
-
-RAW_DIR = '../data/dictionary-data-dump-2012-11-13_15:11/'
-OUTPUT_DIR = 'output'
-
-#map of assignment ID to turker ID
-def turker_map():
-        tmap = dict()
-        for line in open('%s/byassign.workerids.voc'%OUTPUT_DIR).readlines()[1:]:
-                assign, worker = line.split()
-                tmap[assign.strip()] = worker.strip()
-        return tmap
-
-#map of assignment ID to quality score of that assignment, or N/A 
-def qual_map():
-        qual_data = {}
-        for line in csv.DictReader(open('%s/byassign.voc.quality.related'%OUTPUT_DIR), delimiter='\t'):
-                assign = line['id']
-                qual = line['avg']
-                if(assign not in qual_data):
-                        if qual == 'N/A':
-                                qual_data[assign] = qual
-                        else:
-                                qual_data[assign] = float(qual)
-        return qual_data
-
-#map of word id to word
-def word_map():
-	words = dict()
-        for line in csv.DictReader(open('%s/dictionary'%RAW_DIR)):
-		wid = line['id']
-		word = line['translation'].strip().lower()
-		if wid not in words:
-			words[wid] = word
-	return words
-
-#map of pair id to word pair
-def pair_map():
-	pairs = dict()
-        for line in csv.DictReader(open('%s/syn_hits_data'%RAW_DIR)):
-		pid = line['id']
-		word = line['translation'].strip().lower()
-		syn = line['synonym'].strip().lower()
-		if pid not in pairs:
-			pairs[pid] = (word,syn)
-	return pairs
-
-#return (list of pair ids that are know synonyms, list of pair ids that are known nonsynonyms)
-def get_syn_lists():
-	syns = list()
-	nonsyns = list()
-        for line in csv.DictReader(open('%s/synonyms'%RAW_DIR)):
-		syns.append(line['id'])
-        for line in csv.DictReader(open('%s/non_synonyms'%RAW_DIR)):
-		nonsyns.append(line['id'])
-	return (syns, nonsyns)
-
[…]

### 2013-03-07 code/src/figures.py
save figs as pdf

@@ -1,4 +1,6 @@
 import re
+import os
+import os.path
 import csv
 import sys
 import math
@@ -12,6 +14,7 @@ from scipy import stats
 from scipy.stats import norm
 import matplotlib.pyplot as plt
 from matplotlib import font_manager as fm
+#plt.use('PDF')
 
 QC = '' #'.related'
 OUTPUT_DIR = 'output'
@@ -419,7 +422,7 @@ def exact_match_graphs(all_ci_dict, title='Graph', graph_avg=True, cutoff=3000):
         plt.ylabel('')
 	plt.ylim([0,max(yax)+.1])
 	plt.xlim([0,len(ci_dict)])
-        plt.show()
+	plt.savefig('figures/exact-match-bar.pdf')
 
 #stacked bar graph of proportion of exact matches and proportion of synonymn matches
 #side by side with proportion of google translate matches
@@ -456,7 +459,7 @@ def goog_graphs(all_ci_dict, title='Graph', graph_avg=True, cutoff=3000):
         plt.ylabel('')
 	plt.ylim([0,max(yax)+.1])
 	plt.xlim([0,len(ci_dict)])
-        plt.show()
+	plt.savefig('figures/google-match-bar.pdf')
 
 #bar graph with error bars
 def conf_int_graphs(all_ci_dict, title='Graph', graph_avg=True, cutoff=3000):	
@@ -473,7 +476,7 @@ def conf_int_graphs(all_ci_dict, title='Graph', graph_avg=True, cutoff=3000):
         plt.ylabel('')
 	plt.ylim([0,max(yax)+.1])
 	plt.xlim([0,len(ci_dict)])
-        plt.show()
+	plt.savefig('figures/hitlang-bar.pdf')
 
 #mapping of assign_id to hit_id
 def hit_map():
@@ -544,7 +547,7 @@ def compare_native_speakers_graph(ci_tups, title='Graph'):
 	plt.ylim([0,1])
 	plt.xlim([0,len(names)])
 	plt.legend(plots, ('native', 'non-native'))
-        plt.show()
+	plt.savefig('native-compare-bar.pdf')
 
 #side by side bar of native/non native speaker quality
 def native_compare():
@@ -625,7 +628,7 @@ def quality_scatter(title='Title'):
 	arrows = dict(arrowstyle = '->', connectionstyle = 'arc3,rad=0')
 	for label, x, y in zip(labels, labelx, labely):
[…]

### 2013-03-07 writeup/paper.tex
Analysis of performance within region v out of region

@@
 
-We performed an analysis of our data to address the following questions:
+We performed an analysis of our data to address the following questions, among others:
 \begin{itemize}
@@
 \end{itemize}
+
+%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
+\begin{figure}[h]
+\centering
+%\includegraphics[height=\linewidth,angle=270]{figures/completiontime-series}
+\includegraphics[height=\linewidth,angle=270]{figures/completiontime-series}
+\caption{Days to complete the translation HITs for 40 of the languages. Tick marks represent the completion of individual assignments. }
+\label{completion-time}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\paragraph{Speed of completion}
+
+Figure \ref{completion-time} gives the completion times for 40 languages.  
+Urdu and Russian were the first languages to be launched, followed by the others 2 days later.
+The 10 languages to finish in the shortest amount of time were: Tamil, Malayalam, Telugu, Hindi, Macedonian, Spanish, Serbian, Romanian, Gujarati, and Marathi.
+7 of the 10 fastest languages are from India, which is unsurprising given the geographic distribution of workers.
+Some languages follow the pattern of having a smattering of assignments completed early, with the rate picking up later.
+
+\paragraph{Agreement with controls}
+
+\paragraph{Use of machine translation}
+Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems.
+This strategy does not prevent workers from typing the words into a MT system, if they understand the language's script.
+%
+
+%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
+\include{summary}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\paragraph{Performance within region}
+
+We measured the average quality of workers who were in countries that plausibly speak a language, versus workers from countries that did not have large speaker populations of that language.
+We used the Ethnologue \cite{ethnologue} to compile the list of countries for each language.
+Table \ref{language-regions} reports the average translation quality of Turkers in countries with plausibly large speaker populations of each language, compared to the average quality of Turkers from outside the expected region for that language.
 
@@
 \end{itemize}
-
-\paragraph{Use of machine translation}
-Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems.
-This strategy does not prevent workers from typing the words into a MT system, if they understand the language's script.
-%
-
-%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
-\begin{figure*}[h]
-\centering
-%\includegraphics[height=\linewidth,angle=270]{figures/completiontime-series}
-\includegraphics[width=6in]{figures/completiontime-series}
-\caption{Time (in days) to complete the translation HITs for 40 of the languages in our study.
-Tick marks represent the completion of individual assignments.
-Urdu and Russian were the first languages to be launched, followed by the others 2 days later.
-The languages which completed in the shortest amount of time were 4 Indian languages and Macedonian.}
-%\caption{Time (in days) to complete all HITs in each language. Red bars show time until first HIT was started,
-% relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu). 
-% blue bars show time until all HITs in each language were completed.}
-\label{completion-time}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
-\include{summary}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-03-07 writeup/summary.tex
Analysis of performance within region v out of region

--- 2013-02-20 writeup/summary.tex
@@
-\begin{figure}[h]
-\footnotesize
-\begin{tabular}{lccl}
-\multicolumn{4}{c}{Number of turkers per language}\\
+\begin{table*}
+\scriptsize
+%\footnotesize
+\begin{center}
+\begin{tabular}{lllll}
 \hline\hline
-&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&Primary locations\\
-&In region&Out of region&of turkers in region\\
+&\multicolumn{2}{c}{Avg. quality (\# Turkers)}&Primary locations&Primary locations\\
+&In region&Outside&of Turkers in region&of Turkers out of region\\
 \hline\hline
-Hindi&\textbf{0.54} (299)&0.47 (63)&India (285) UAE (5) UK (5) \\
-Tamil&\textbf{0.55} (278)&0.54 (26)&India (271) US (3) Canada (2) \\
-Malayalam&0.48 (235) &\textbf{0.55} (49)&India (224) UAE (6) US (3) \\
-Spanish&\textbf{0.27} (205)&0.27 (39)&US (131) Mexico (18) Spain (14) \\
-French&0.29 (183) &\textbf{0.31} (34)&India (68) US (48) France (25) \\
-German&\textbf{0.35} (99)&0.31 (71)&Germany (51) US (29) Austria (9) \\
-Italian&\textbf{0.32} (98)&0.27 (68)&Italy (44) US (32) Romania (9) \\
-Chinese&\textbf{0.42} (123)&0.41 (28)&US (80) Singapore (15) China (14) \\
-Telugu&\textbf{0.48} (102)&0.41 (35)&India (98) US (3) UAE (1) \\
-Malay&\textbf{0.30} (15)&0.28 (116)&Malaysia (8) Singapore (4) US (2) \\
-Turkish&\textbf{0.30} (83)&0.27 (47)&Turkey (39) US (20) Macedonia (12) \\
-Kannada&0.64 (106) &\textbf{0.65} (21)&India (106) US (1) \\
-Portuguese&0.20 (107) &\textbf{0.24} (19)&Brazil (46) Portugal (32) US (15) \\
-Arabic&0.45 (62) &\textbf{0.45} (64)&Egypt (19) Jordan (17) Morocco (9) \\
-Romanian&0.29 (87) &\textbf{0.33} (37)&Romania (77) US (6) Moldova (3) \\
-Swedish&\textbf{0.30} (58)&0.29 (66)&US (28) Sweden (23) Finland (3) \\
-Czech&0.24 (52) &\textbf{0.25} (71)&US (19) Czechrepublic (15) Serbia (5) \\
-Irish&\textbf{0.32} (58)&0.26 (64)&US (41) Ireland (13) UK (4) \\
-Amharic&0.21 (17) &\textbf{0.42} (105)&US (14) Ethiopia (3) \\
-Russian&0.15 (72) &\textbf{0.16} (49)&US (38) Russia (8) Moldova (7) \\
+Hindi&\textbf{0.35} (299)&0.29 (7)&India (285) UAE (5) UK (5) &Saudi Arabia (2) Russia (1) Oman (1) \\
+Tamil&\textbf{0.39} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
+Malayalam&0.44 (235) &\textbf{0.56} (2)&India (224) UAE (6) US (3) &Saudi Arabia (1) Maldives (1) \\
+Spanish&\textbf{0.71} (205)&0.60 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) New Zealand (1) \\
+French&0.61 (183) &\textbf{0.80} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
+German&\textbf{0.80} (99)&0.56 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
+Italian&\textbf{0.79} (98)&0.67 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
+Chinese&\textbf{0.22} (121)&0.18 (19)&US (79) Singapore (15) China (14) &Hongkong (6) Australia (3) Germany (2) \\
+Malay&\textbf{0.76} (15)&0.72 (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
+Irish&0.61 (58) &\textbf{0.62} (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
+Czech&\textbf{0.70} (52)&0.62 (64)&US (19) Czech Republic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
+Turkish&\textbf{0.70} (83)&0.62 (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
+Amharic&\textbf{0.17} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
+Swedish&\textbf{0.64} (58)&0.57 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
+Portuguese&\textbf{0.75} (107)&0.62 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
+Arabic&0.21 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
+Kannada&\textbf{0.24} (106)&0.10 (1)&India (106) US (1) &France (1) Germany (1) \\
+Russian&\textbf{0.33} (72)&0.26 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
+Afrikaans&\textbf{0.73} (4)&0.64 (98)&South Africa (4) &India (93) Netherlands (2) UAE (1) \\
+Sindhi&\textbf{0.16} (93)&0.11 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
 \hline\hline
 \end{tabular}
-\end{figure}
+\end{center}
+\normalsize
+\caption{The average translation quality of Turkers within a countries with larger speaker populations of a language versus Turkers from countries without large speaker populations of that language.
+}\label{language-regions}
+\end{table*}

### 2013-03-13 writeup/summary.tex
control dictionaries

--- 2013-02-20 writeup/summary.tex
@@
 \footnotesize
-\begin{tabular}{lccl}
+\begin{tabular}{lllll}
 \multicolumn{4}{c}{Number of turkers per language}\\
 \hline\hline
-&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&Primary locations\\
-&In region&Out of region&of turkers in region\\
+&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&Primary locations&Primary locations\\
+&In region&Out of region&of turkers in region&of turkers out of region\\
 \hline\hline
-Hindi&\textbf{0.54} (299)&0.47 (63)&India (285) UAE (5) UK (5) \\
-Tamil&\textbf{0.55} (278)&0.54 (26)&India (271) US (3) Canada (2) \\
-Malayalam&0.48 (235) &\textbf{0.55} (49)&India (224) UAE (6) US (3) \\
-Spanish&\textbf{0.27} (205)&0.27 (39)&US (131) Mexico (18) Spain (14) \\
-French&0.29 (183) &\textbf{0.31} (34)&India (68) US (48) France (25) \\
-German&\textbf{0.35} (99)&0.31 (71)&Germany (51) US (29) Austria (9) \\
-Italian&\textbf{0.32} (98)&0.27 (68)&Italy (44) US (32) Romania (9) \\
-Chinese&\textbf{0.42} (123)&0.41 (28)&US (80) Singapore (15) China (14) \\
-Telugu&\textbf{0.48} (102)&0.41 (35)&India (98) US (3) UAE (1) \\
-Malay&\textbf{0.30} (15)&0.28 (116)&Malaysia (8) Singapore (4) US (2) \\
-Turkish&\textbf{0.30} (83)&0.27 (47)&Turkey (39) US (20) Macedonia (12) \\
-Kannada&0.64 (106) &\textbf{0.65} (21)&India (106) US (1) \\
-Portuguese&0.20 (107) &\textbf{0.24} (19)&Brazil (46) Portugal (32) US (15) \\
-Arabic&0.45 (62) &\textbf{0.45} (64)&Egypt (19) Jordan (17) Morocco (9) \\
-Romanian&0.29 (87) &\textbf{0.33} (37)&Romania (77) US (6) Moldova (3) \\
-Swedish&\textbf{0.30} (58)&0.29 (66)&US (28) Sweden (23) Finland (3) \\
-Czech&0.24 (52) &\textbf{0.25} (71)&US (19) Czechrepublic (15) Serbia (5) \\
-Irish&\textbf{0.32} (58)&0.26 (64)&US (41) Ireland (13) UK (4) \\
-Amharic&0.21 (17) &\textbf{0.42} (105)&US (14) Ethiopia (3) \\
-Russian&0.15 (72) &\textbf{0.16} (49)&US (38) Russia (8) Moldova (7) \\
+Hindi&\textbf{0.35} (299)&0.29 (7)&India (285) UAE (5) UK (5) &Saudiarabia (2) Russia (1) Oman (1) \\
+Tamil&\textbf{0.39} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
+Malayalam&0.44 (235) &\textbf{0.56} (2)&India (224) UAE (6) US (3) &Saudiarabia (1) Maldives (1) \\
+Spanish&\textbf{0.71} (205)&0.60 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) Newzealand (1) \\
+French&0.61 (183) &\textbf{0.80} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
+German&\textbf{0.80} (99)&0.56 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
+Italian&\textbf{0.79} (98)&0.67 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
+Chinese&\textbf{0.22} (121)&0.18 (19)&US (79) Singapore (15) China (14) &Hongkong (6) Australia (3) Germany (2) \\
+Malay&\textbf{0.76} (15)&0.72 (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
+Irish&0.61 (58) &\textbf{0.62} (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
+Czech&\textbf{0.70} (52)&0.62 (64)&US (19) Czechrepublic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
+Turkish&\textbf{0.70} (83)&0.62 (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
+Amharic&\textbf{0.17} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
+Swedish&\textbf{0.64} (58)&0.57 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
+Portuguese&\textbf{0.75} (107)&0.62 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
+Arabic&0.21 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
+Kannada&\textbf{0.24} (106)&0.10 (1)&India (106) US (1) &France (1) Germany (1) \\
+Russian&\textbf{0.33} (72)&0.26 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
+Afrikaans&\textbf{0.73} (4)&0.64 (98)&Southafrica (4) &India (93) Netherlands (2) UAE (1) \\
+Sindhi&\textbf{0.16} (93)&0.11 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
 \hline\hline

### 2013-03-13 code/src/compile_data_from_raw.py

@@ -5,7 +5,7 @@ import json
 import string
 import codecs
 
-RAW_DIR = '../data/dictionary-data-dump-2012-11-13_15:11/'
+RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11'
 OUTPUT_DIR = 'output'
 
 def hits_language():

### 2013-03-13 code/src/dictionaries.py

@@ -7,6 +7,7 @@ import codecs
 import os.path
 import operator
 import itertools
+from scipy import stats
 import compile_data_from_raw as dat
 
 RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11/'
@@ -171,7 +172,7 @@ def avg_score(assign_list, scores):
 
 def turker_qual_map():
         qual_data = {}
-        for line in open('%s/byturker.voc.quality'%OUTPUT_DIR).readlines():
+        for line in open('%s/byturker.voc.quality'%OUTPUT_DIR).readlines()[1:]:
                 assign, qual = line.split()
                 if(assign not in qual_data):
                         qual_data[assign] = float(qual)
@@ -361,25 +362,36 @@ def get_language_dicts_quals(path, qual_cutoff=None, strict=False, filter_list=N
 		all_dicts[alang]['denom'] += 1
 	return all_dicts
 
-def get_language_dicts(path, qual_cutoff=None, strict=False, filter_list=None):
+def get_language_dicts(path, qual_cutoff=None, strict=False, filter_list=None, match=True):
 	all_dicts = dict()
+	tmap = turker_map()
 	hitmap = hit_map()
 	langids, langcodes = dat.lang_map()
         hitlangs = dat.hits_language()
 	quals = qual_map()
-	for assign in open(path).readlines():
+	tquals = turker_qual_map()
+	filtered = 0
+	for cnt, assign in enumerate(open(path).readlines()):
 		comps = assign.strip().split('\t')
 		aid = comps[0]
-		if(aid == ''):
+		if cnt%1000 == 0:
+			print aid
+		if(aid == ''): # or aid not in tmap):
 			continue
-		if aid not in quals:
+		#if match, filter_list is list of assignments to include, otherwise, filter_list is list of assignments to skip
+		if(match):
+			list_pass = not(filter_list == None) and (aid not in filter_list)
+		else:
+			list_pass = not(filter_list == None) and (aid in filter_list)
+		if(list_pass):
+			filtered += 1
 			continue
-		if(not(filter_list == None) and (aid in filter_list)):
-			continue
[…]

### 2013-03-13 code/src/dictionaries/controls/dictionary.cs

@@ -1,0 +1,158 @@
+roura	pipe
+zisk	profit
+laktace	lactation
+zeměžluč	centaurium
+rdesno	polygonum
+inkubace	incubation
+vrchol	vertex
+ghůl	ghoul
+husy	anserinae
+polokeř	subshrub
+zub	tooth
+bakterie	bacteria
+nekov	nonmetal
+příslovce	adverb
+proxemika	proxemics
+trevír	trier
+medián	median
+monografie	monograph
+adjustace	adjustment
+kostra	skeleton
+rdestovité	potamogetonaceae
+fagocyt	phagocyte
+teodicea	theodicy
+biogeografie	biogeography
+účetnictví	accountancy
+provazovka	usnea
+mafie	mafia
+svinka	armadillidium
+koeficient	coefficient
+denudace	denudation
+geomorfologie	geomorphology
+kropenáč	swertia
+špirlicovité	sarraceniaceae
+bioetika	bioethics
+teratogen	teratology
+inženýr	engineer
+pavučinec	cortinarius
+makléř	broker
+efektivita	effectiveness
+šejdračka	zannichellia
+kapřivci	branchiura
+skaní	ply
+aspirace	aspiration
+afix	affix
+skript	script
+solitér	solitary
+kalorie	calorie
+outloňovití	lorisidae
+subjekt	subject
+taška	bag
+dělitelnost	divisor
+škvoři	earwig
+kambalovití	bothidae
+cyklus	cycle
+lubenice	citrullus
+mahónie	mahonia
+figura	figure
+chala	challah
+zirkon	zircon
+tlustonitník	pachysandra
+dálnice	autobahn
+epitaf	epitaph
+želvušky	tardigrade
+kvádr	cuboid
+sváření	welding
+anticyklóna	anticyclone
+hlíza	tuber
+ovsík	arrhenatherum
+prezident	president
+fúze	fusion
+emancipace	emancipation
+síťokřídlí	neuroptera
+diferenciál	differential
+likér	liqueur
+židelník	dirca
+účel	purpose
+hnízdo	nest
+fenol	phenol
+kalich	calyx
+kručinka	genista
+hrom	thunder
+surcot	surcoat
+producent	producer
+kalous	asio
+náklad	expense
+šachy	chess
+piškvorky	tic-tac-toe
+skandium	scandium
+starověk	antiquity
+ševčenko	shevchenko
+kra	iceberg
+břicho	abdomen
+zlatice	forsythia
[…]

### 2013-03-13 code/src/dictionaries/controls/dictionary.pl

@@ -1,0 +1,68 @@
+rajgras	arrhenatherum
+syrinks	syrinx
+elucja	elution
+wilgotnica	hygrocybe
+tłum	crowd
+możylinek	moehringia
+wiskozymetr	viscometer
+obuwie	footwear
+szczypiorek	chives
+pikornawirusy	picornavirus
+miopatie	myopathy
+cykl	cycle
+staurikozaur	staurikosaurus
+likier	liqueur
+przeplot	interlace
+satjagraha	satyagraha
+minuta	minute
+rdest	polygonum
+hipokaliemia	hypokalemia
+dziewczyna	girl
+kinetoskop	kinetoscope
+śródstopie	metatarsus
+wyspa	island
+baptyzm	baptist
+rubryk	rubric
+inżynier	engineer
+mizantropia	misanthropy
+statyw	tripod
+sternik	helmsman
+przywilej	privilege
+benzochinon	quinone
+gastrulacja	gastrulation
+anakonda	anaconda
+askokarp	ascocarp
+bobrkowate	menyanthaceae
+wypotnik	hydathode
+ślinotok	drooling
+strzykwy	holothuroidea
+bioetyka	bioethics
+reologia	rheology
+fagocyt	phagocyte
+cyprys	cupressus
+zasłonak	cortinarius
+sieciarki	neuroptera
+pokoślin	eriogonum
+azydek	azide
+lulek	hyoscyamus
+bufor	buffer
+laktacja	lactation
+wełniakowate	bombacaceae
+marzanka	asperula
+glosariusz	glossary
+petroglify	petroglyph
+krwiak	hematoma
+gęsi	anserinae
+redukcja	reduction
+tasznik	capsella
+barometr	barometer
+bakszysz	baksheesh
+zdradnicowate	elapidae
+faeton	phaeton
+wiciowce	flagellate
+karawanseraj	caravanserai
+częstotliwość	frequency
+żurawiowe	gruiformes
+molibden	molybdenum
+denudacja	denudation
+czartawa	circaea

### 2013-03-13 code/src/dictionaries/controls/dictionary.sh

@@ -1,0 +1,158 @@
+kompromis	compromise
+skakanje	jumping
+ubrzanje	acceleration
+ptica	bird
+euklid	euclid
+miraz	dowry
+mioza	miosis
+pentoda	pentode
+epidemija	epidemic
+гихт	gout
+metoda	method
+oblak	cloud
+dijamant	diamond
+kosmogonija	cosmogony
+geomorfologija	geomorphology
+vodik	hydrogen
+hortenzija	hydrangea
+lubanja	skull
+centrozom	centrosome
+makroekonomija	macroeconomics
+kadmijum	cadmium
+biofizika	biophysics
+hidroliza	hydrolysis
+slog	syllable
+iridijum	iridium
+predsjednik	president
+mač	sword
+fitoplankton	phytoplankton
+malarija	malaria
+ruka	hand
+fosil	fossil
+citozin	cytosine
+kralježnjaci	vertebrate
+elektronika	electronics
+teodiceja	theodicy
+molibden	molybdenum
+cvećarstvo	floriculture
+garnizon	garrison
+uranijum	uranium
+izmet	feces
+inkubacija	incubation
+nemetali	nonmetal
+filatelija	philately
+komplikacija	complication
+fanerozoik	phanerozoic
+žljebuša	rifling
+čekrk	pulley
+trokut	triangle
+radijan	radian
+raderfordijum	rutherfordium
+celuloza	cellulose
+žutica	jaundice
+alat	tool
+renijum	rhenium
+fagocitoza	phagocytosis
+kanalizacija	sewer
+aritmetika	arithmetic
+psilocibin	psilocybin
+tati	tats
+tlak	pressure
+hidrografija	hydrography
+peščar	sandstone
+šah	chess
+kontrola	control
+petroglif	petroglyph
+ditiramb	dithyramb
+talijum	thallium
+autizam	autism
+boja	color
+gladijator	gladiator
+cirkonijum	zirconium
+feminizam	feminism
+mrav	ant
+kalaj	tin
+skandij	scandium
+anamneza	anamnesis
+kirijum	curium
+mauzolej	mausoleum
+dovod	supply
+mokraćovod	ureter
+zrakoplovstvo	aviation
+pirit	pyrite
+parohija	parish
+interkalacija	intercalation
+titanij	titanium
+kocka	cube
+ostrvo	island
+tulijum	thulium
+sarkofag	sarcophagus
+sinteza	synthesis
+elektron	electron
+život	life
[…]

### 2013-03-13 code/src/figures.py

@@ -14,7 +14,6 @@ from scipy import stats
 from scipy.stats import norm
 import matplotlib.pyplot as plt
 from matplotlib import font_manager as fm
-#plt.use('PDF')
 
 QC = '' #'.related'
 OUTPUT_DIR = 'output'
@@ -107,13 +106,11 @@ def all_avg_scores(path, turkers=True):
 			try:
 				scores[l[0]] = float(l[1].strip())
 			except:
-				print line
 				continue
 		else:
 			try:
 				scores[l[0]] = float(l[3].strip())
 			except:
-				print line
 				continue
 	return scores
 
@@ -225,7 +222,6 @@ def hitlang_qual_turker(cut=50):
 		q = line['avg']
 		qual_by_assign[aid] = q
 	for l in assigns_by_lang.keys():
-		print l
 		qual = list()
 		for a in assigns_by_lang[l]:
 			if a not in qual_by_assign:
@@ -268,7 +264,6 @@ def exact_match_qual(cut=50):
 		q = line['avg']
 		match_by_assign[aid] = q
 	for l in assigns_by_lang.keys():
-		print l
 		qual = list()
 		match = list()
 		for a in assigns_by_lang[l]:
@@ -328,7 +323,6 @@ def goog_match_qual(cut=50):
 		q = line['avg']
 		goog_by_assign[aid] = q
 	for l in assigns_by_lang.keys():
-		print l,
 		qual = list()
 		match = list()
 		goog = list()
@@ -494,6 +488,8 @@ def hit_map():
 def two_way_quality(attr1, attr2):
 	breakdown = dict()
 	tw, scores = two_way_split(attr1, attr2)
+	print scores
+	return
 	for t in tw:
 		breakdown[t] = dict()
 		for tt in tw[t]:
@@ -517,11 +513,13 @@ def sort_data(data):
 def compare_native_speakers():
 	langs = all_keys('%s/byassign.voc.accepted'%OUTPUT_DIR, 'hitlang')
 	quals = two_way_quality('hitlang','lang')
+	return
 	graph_data = dict()	
 	graph_data_clean = dict()	
 	for l in langs:
 		graph_data[l] = clean_ints(quals[l])
 	for k in graph_data:
+		print k, graph_data[k]
 		new = dict()
 		for i in graph_data[k]:
 			if i[0] == k:
@@ -529,6 +527,7 @@ def compare_native_speakers():
 			elif i[0] == 'en':
 				new['no'] = i[1]
[…]

### 2013-03-13 code/src/qc.py

@@ -6,7 +6,7 @@ import itertools
 import dictionaries
 import compile_data_from_raw as dat
 
-RAW_DIR = '../data/dictionary-data-dump-2012-11-13_15:11/'
+RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11'
 OUTPUT_DIR = 'output'
 
 goog_langs = ['el', 'eo', 'zh', 'af', 'vi', 'is', 'it', 'kn', 'cs', 'cy', 'ar', 'eu', 'et', 'gl', 'id', 'es', 'ru', 'az', 'nl', 'pt', 'tr', 'lv', 'lt', 'th', 'gu', 'ro', 'ca', 'pl', 'ta', 'fr', 'bg', 'ms', 'hr', 'de', 'da', 'fa', 'fi', 'hy', 'hu', 'ja', 'he', 'te', 'sr', 'sq', 'ko', 'sv', 'ur', 'sk', 'uk', 'sl', 'sw']
@@ -35,13 +35,18 @@ def qual_map(path):
         return qual_data
 
 #map of word id to word
-def word_map():
+def word_map(lang=False):
 	words = dict()
         for line in csv.DictReader(open('%s/dictionary'%RAW_DIR)):
 		wid = line['id']
+		lang = line['language_id']
 		word = line['translation'].strip().lower()
 		if wid not in words:
-			words[wid] = word
+			if lang:
+				orig = line['word'].strip().lower()
+				words[wid] = (word, orig, lang)
+			else:
+				words[wid] = word
 	return words
 
 #map of pair id to word pair
@@ -93,6 +98,29 @@ def read_all_syns(filter_list=None, use_related=True, exact_match_only=False):
 			if(not(exact_match_only)):
 				syns[syn].add(pair[0].strip().lower())
 	return syns
+
+#get a dictionary of word: list of acceptable synonyms. filter list of assignment ids used to restrict list of synonyms to come only from certain assignments
+def write_all_syns():
+        words = word_map(lang=True)
+        data = {}
+	syns = dict()
+	numlangmap, langmap = dat.lang_map()
+        for word_id in words: 
+		word, orig, lang = words[word_id]
+		lang = numlangmap[lang]
+                if lang not in syns:
+			syns[lang] = list()
+		syns[lang].append((orig,word))
+	write_control_dicts(syns)
+
+def write_control_dicts(data, file_prefix='controls/dictionary'):
[…]

### 2013-03-13 code/src/summary.py

@@ -8,7 +8,7 @@ from matplotlib import font_manager as fm
 import string
 
 COUNTRIES = 'ref/countrycodemap'
-RAW_DIR = '../data/dictionary-data-dump-2012-11-13_15:11/'
+RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11'
 DICT_DIR = 'dictionaries'
 
 def reverse_lang_map(path):
@@ -94,8 +94,11 @@ def summary_table_condensed():
 		numout = int(d[1])
 		cstring = ''
 		nstring = ''
-		all_countries = [pp for pp in sorted(cbreakdown[lang], key=operator.itemgetter(1), reverse=True)] #if not (pp[0] == 'N/A')]
-		all_noncountries = [pp for pp in sorted(nbreakdown[lang], key=operator.itemgetter(1), reverse=True)] # if not (pp[0] == 'N/A')]
+		try:
+			all_countries = [pp for pp in sorted(cbreakdown[lang], key=operator.itemgetter(1), reverse=True)] #if not (pp[0] == 'N/A')]
+			all_noncountries = [pp for pp in sorted(nbreakdown[lang], key=operator.itemgetter(1), reverse=True)] # if not (pp[0] == 'N/A')]
+		except:
+			continue
 		for p in all_countries[:3]:
 			cstring += '%s (%d) '%(countries[p[0]],p[1],)
 		for p in all_noncountries[:3]:

### 2013-03-13 writeup/paper.tex
minor edit

@@
 \normalsize
-\caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 languages with $\leq$20 speakers . 
+\caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 languages with $\leq$20 speakers. 
 %(for a total of 423 remaining speakers).  
@@
 
-\paragraph{Performance within region}
+\paragraph{Language skills and location}
 
 We measured the average quality of workers who were in countries that plausibly speak a language, versus workers from countries that did not have large speaker populations of that language.
-We used the Ethnologue \cite{ethnologue} to compile the list of countries for each language.
-Table \ref{language-regions} reports the average translation quality of Turkers in countries with plausibly large speaker populations of each language, compared to the average quality of Turkers from outside the expected region for that language.
+We used the Ethnologue \cite{ethnologue} to compile the list of countries where each language is spoken.
+Table \ref{language-regions} compares the average translation quality of Turkers within the region of each language, and compares it to the quality of Turkers outside that region.
+
+Todo - overall, outliers, languages which are spoken everywhere. US workers get categorized into YY languages.
+
+\paragraph{Natives v. non-natives}
+Todo - analyze the translation quality of natives v.
+non-natives.
+Ideally we would plot average translation quality versus years speaking English.
+Two lines: one line for native speakers of the source language, one line for non-native speakers of the target language.
+We could average over all languages, and the points should show std-dev whiskers.
 

### 2013-03-15 writeup/paper.tex
completion time figure

@@
 Rather than posting a one-off survey, we posted paid tasks consisting of 1,000 assignments to translate a total of 10,000 words in each of 119 languages.
-Our study ran for weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilinguals workers would complete it.
+Our study ran for several weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilinguals workers would complete it.
 Our study was useful both to create bilingual dictionaries and to act as census of the bilingual speakers on MTurk.
@@
 This map was generated based on geolocating the IP address of  5,284 workers in our study.
-The size of the circles represents the number of worker from each country.
+The size of the circles represents the number of workers from each country.
 The two largest are India (2,022 workers) and the United States (904).
@@
 \newcite{irvine:10} had Turkers evaluate the accuracy of translations that had been automatically inducted from monolingual texts.
-They examined translations of 100 words in 42 low-resource languages, reported geolocated countries for their workers (India, the US, Romania, Pakistan, Macedonia, Latvia, Bangladesh and the Philippines).
+They examined translations of 100 words in 42 low-resource languages, and reported geolocated countries for their workers (India, the US, Romania, Pakistan, Macedonia, Latvia, Bangladesh and the Philippines).
 Irvine and Klementiev discussed the difficulty of quality control and assessing the plausibility of workers' language skills for rare languages, which we address in this paper.
@@
 %(for a total of 423 remaining speakers).  
-We omit 1,801 Turkers did not report their native language, 243 who reported 2 native languages, and 83 who reported $\geq$3 native languages.}\label{lang-pie}
+We omit 1,801 Turkers who did not report their native language, 243 who reported 2 native languages, and 83 who reported $\geq$3 native languages.}\label{lang-pie}
 \end{table}
@@
 We drew our data from the different language versions of Wikipedia.
-We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} and then selected an additional 19 languages low resource languages with $<$10,000 articles, giving a total of 119 languages (Table \ref{wikipedia-buckets}).
-For each language, we chose the 1,000 most viewed articles over a 1 year period,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and extracted the 10,000 most frequent words from them.
+We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} and then selected an additional 19 low resource languages with $<$10,000 articles, giving a total of 119 languages (Table \ref{wikipedia-buckets}).
+For each language, we chose the 1,000 most viewed articles over a 1 year period,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and extracted the 10,000 most frequent words from each.
 The resulting vocabularies served as the input to our translation HIT.
@@
 A set of gold standard translations were automatically harvested from Wikipedia  for every language to use as embedded controls.
-We used Wikipedia's inter-language links to pair titles of English articles with their corresponding foreign articles title.
+We used Wikipedia's inter-language links to pair titles of English articles with their corresponding foreign article's title.
 To get a more translatable set of pairs, we excluded any pairs where: (1) the English word was not present in the WordNet ontology  \cite{miller1995wordnet}, (2) either article title was longer than a single word, (3) the English wikipedia page was a subcategory of person or place, or (4) the English and the foreign titles were identical or a substring of the other.
@@
 We counted all translations that exactly matched the gold standard translation as correct.  For non-exact matches we created a second-pass quality assurance HIT.  
-Turkers were shown a pair of English words, one of which was a Turker's translation of the foreign word used for quality control, and the other was the gold-standard translation the foreign word.
+Turkers were shown a pair of English words, one of which was a Turker's translation of the foreign word used for quality control, and the other of which was the gold-standard translation of the foreign word.
 Evaluators were asked whether the two words had the same meaning, and chose between three answers: `Yes', `No', or `Related but not synonymous.'  Examples of meaning equivalent pairs include: $<${\it petroglyphs, rock paintings}$>$, $<${\it demo, show}$>$ and  $<${\it loam, loam: soil rich in decaying matter}$>$.
@@
 \centering
-%\includegraphics[height=\linewidth,angle=270]{figures/completiontime-series}
-\includegraphics[height=\linewidth,angle=270]{figures/completiontime-series}
+%\includegraphics[height=\linewidth,angle=270]{figures/completiontime}
+\includegraphics[height=\linewidth,angle=270]{figures/completiontime-new}
 \caption{Days to complete the translation HITs for 40 of the languages. Tick marks represent the completion of individual assignments. }
@@
 Hindi, Tamil, and Malayalam are especially well represented in terms of number of active translators, and Urdu, Telugu, and Macedonian are particularly productive in terms of number of assignments completed.
-As shown in figure \ref{langgeo-bar}, 11 of the top 25 languages, in terms of number of assignments submitted, were Indian languages, and the assignments for 15 of the top 25 were completed mostly or entirely by Turkers located in India.
+%As shown in figure \ref{langgeo-bar}, 11 of the top 25 languages, in terms of number of assignments submitted, were Indian languages, and the assignments for 15 of the top 25 were completed mostly or entirely by Turkers located in India.
 
@@
 In order to address the quality of the translations we received on the dictionary task, we constructed a pipeline in which the output of the translation HIT was reviewed by humans in a second evaluation HIT, described above.
-We quantified the quality of each translation assignment based on the output of the evaluation HIT.
-The quality of an assignment was scored as the fraction of known words which were acceptably translated: i.e, the supplied translation was judged to be synonymous with the gold standard translation.
+We quantified the quality of each translation assignment based on the output of the evaluation HIT as follows:
+\textit{In English, so people know what we did:}
+\begin{align}	
+	Quality = \frac{\# \text{translations in } Synonyms(\text{answer})}{\# \text{ controls}}
+\end{align}	
+where answer is the known translation and $Synonyms$(answer) is the set of words judged to be synonymous with the gold standard translation in the second pass HIT.
+\textit{Mathified, to give the impression of rigor and intellect:}
+\begin{align}	
+	Quality = \frac{1}{k}\sum\limits_{i=1}^k\mathbf{1}(t_i \in Synonyms(a_i))
+\end{align}	
+where $k$ is the number of controls in the assignment, $t_i$ is the Turker's provided translation of control word $i$, $a_i$ is the gold standard translation of the control word $i$, and $Synonyms(a_i)$ is the set of words judged to be synonymous with the $a_i$ in the second pass HIT and $\mathbf{1}(x)$ is 1 when $x$ is true.
+
 Since most assignments had two known words embedded, most assignments had scores of either 0, 0.5, or 1.
+Since by-assignment quality scores are noisy and sensitive to small numbers of highly active Turkers, we report quality scores reported the average per-turker quality in tables and figures, where a Turker's quality is just the average quality of all the assignments that the Turker completed.
 

### 2013-03-15 code/src/completetime.py

@@ -36,6 +36,7 @@ def get_language_dicts(path, filter_list=None):
 	return all_dicts
 
 def time_map():
+	print "Reading data"
 	tdict = dict()
 	for line in open('%s/byassign.times'%OUTPUT_DIR).readlines():
 		aid, start, end = line.split('\t')
@@ -58,14 +59,15 @@ def get_total_time(data):
 		print '%s\t%s'%(lang[0], str(lang[1][1] - lang[1][0]))
 
 def format_for_graph(data):
+	print "Formatting data"
 	ret = list()
 	mindate = None
-	for l in data: 
+	for l in data.keys(): 
 		lang = data[l]	
 		begin = lang[0]
 		if(mindate == None or begin < mindate):
 			mindate = begin
-	for l in data:
+	for l in data.keys():
 		lang = data[l]	
 		complete = lang[1] - lang[0]
 		start = lang[0] - mindate
@@ -87,6 +89,7 @@ def time_bar(data):
         plt.show()
 
 def format_for_time_series(data):
+	print "More formatting data"
 	hitmap = dictionaries.hit_map()
 	langids, langcodes = dat.lang_map()
         hitlangs = dat.hits_language()
@@ -96,7 +99,10 @@ def format_for_time_series(data):
 		if lang not in all_times:
 			all_times[lang] = list()
 		all_times[lang].append(total)
-	all_times.pop('en')
+	try:
+		all_times.pop('en')
+	except KeyError:
+		pass
 	return all_times
 
 def time_series(data, num=40):
@@ -119,6 +125,32 @@ def time_series(data, num=40):
         plt.xlabel('Time in days')
 	plt.show()
 
+def fancy_time_series(data, num=40):
+	SEC_PER_DAY = 86400
+	x = list()
+	y = list()
+	names = list()
+	sort_order = [t[0] for t in sorted(data.iteritems(), key=lambda t : max(t[1]))]
+	print sort_order
+	for i,lang in enumerate(sort_order[:num]):
+		names.append(lang)
+		x += [t.total_seconds() for t in data[lang]]
+		y += [5+(i*5)]*len(data[lang])
+	tot = len(y)
+	for i, (xx, yy) in enumerate(zip(x,y)):
+		if i % 1000 == 0: print (float(i)/tot) , xx, yy
+		plt.plot([xx, xx], [yy, yy+1], color = 'b')
+#	plt.scatter(x,y,marker='|')
[…]

### 2013-03-15 code/src/figures.py

@@ -56,7 +56,7 @@ def read_table_file(path):
         ret = dict()
         data = csv.DictReader(open(path),delimiter='\t')
         for d in data:
-                ret[d['id']] = {'lang':d['lang'],'country':d['country'], 'hitlang': d['hitlang'], 'survey':d['survey']}
+                ret[d['id']] = {'lang':d['lang'],'country':d['country'], 'hitlang': d['hitlang'], 'survey':d['survey'], 'yrseng':d['yrseng'], 'yrssrc':d['yrssrc']}
         return ret
 
 #return a dictionary counting the number of occurances of each value of attr
@@ -370,11 +370,11 @@ def goog_match_qual(cut=50):
 
 #returns a dict of {attr1: {attr2: list of assignments}}
 #e.g. if attr1 = 'country' and attr2 = 'language', returns a dict of scores keyed by assignment_id and a dictionary of form 
-#{IN : {hi: XX, ta:XX, en: XX, ...}, 'RU':{hi: XX, ta: XX, en: XX, ...}}
+#{IN : {hi: [{assign_id : {}], ta:X[], en: [], ...}, 'RU':{hi: [], ta: [], en: [], ...}}
 def two_way_split(attr1, attr2):
 	ret = dict()
 	data = read_table_file('%s/byassign.voc.accepted'%OUTPUT_DIR)
-	scores = all_avg_scores('%s/byassign.voc.quality%s'%(OUTPUT_DIR,QC,))
+	scores = all_avg_scores('%s/byassign.voc.quality%s'%(OUTPUT_DIR,QC,), turkers=False)
 	first = all_keys('%s/byassign.voc.accepted'%OUTPUT_DIR, attr1)
 	second = all_keys('%s/byassign.voc.accepted'%OUTPUT_DIR, attr2)
 	for k in first:
@@ -488,8 +488,6 @@ def hit_map():
 def two_way_quality(attr1, attr2):
 	breakdown = dict()
 	tw, scores = two_way_split(attr1, attr2)
-	print scores
-	return
 	for t in tw:
 		breakdown[t] = dict()
 		for tt in tw[t]:
@@ -510,10 +508,10 @@ def sort_data(data):
 	return [(t[1],t[2]) for t in sorted(tups, reverse=True)]
 
 #return dictionary of {language : {yes : quality estimate of native speakers, no : quality estimate of nonnative speakers}}
+#quality estimates by assignments
[…]

### 2013-03-15 writeup/paper.tex
equations

@@
 
-% Todo: sort by language code, rebalance the bottom set to have 19 languages in it.
 \begin{table}[h]
@@
 \hline
-{\sc 500k+ articles:}
-Dutch (nl), English (en), French (fr), German (de), Italian (it), Japanese (ja), Polish (pl), Portuguese (pt), Russian (ru), Spanish (es)\\
+{\sc 500k+ articles:} German (de), English (en), Spanish (es), French (fr), Italian (it), Japanese (ja), Dutch (nl), Polish (pl), Portuguese (pt), Russian (ru)\\
 \hline
-{\sc 100k-500k articles:} Arabic (ar), Basque (eu), Bulgarian (bg), Catalan (ca), Chinese (zh), Croatian (hr), Czech (cs), Danish (da), Esperanto (eo), Finnish (fi), Hebrew (he), Hindi (hi), Hungarian (hu), Indonesian (id), Kazakh (kk), Korean (ko), Lithuanian (lt), Malay (ms), Norwegian (Bokmal) (no), Persian (fa), Romanian (ro), Serbian (sr), Slovak (sk), Slovenian (sl), Swedish (sv), Turkish (tr), Ukrainian (uk), Vietnamese (vi), Waray-Waray (war)\\
+{\sc 100k-500k articles:} Arabic (ar), Bulgarian (bg), Catalan (ca), Czech (cs), Danish (da), Esperanto (eo), Basque (eu), Persian (fa), Finnish (fi), Hebrew (he), Hindi (hi), Croatian (hr), Hungarian (hu), Indonesian (id), Korean (ko), Lithuanian (lt), Malay (ms), Norwegian (Bokmal) (no), Romanian (ro), Slovak (sk), Slovenian (sl), Serbian (sr), Swedish (sv), Turkish (tr), Ukrainian (uk), Vietnamese (vi), Waray-Waray (war), Chinese (zh)\\
 \hline
-{\sc 10k-100k articles:}
-Azerbaijani (az), Afrikaans (af), Albanian (sq), Amharic (am), Aragonese (an), Armenian (hy), Asturian (ast), Belarusian (be), Bengali (bn), Bishnupriya Manipuri (bpy), Bosnian (bs), Breton (br), Cebuano (ceb), Galician (gl), Georgian (ka), Greek (el), Gujarati (gu), Haitian (ht), Icelandic (is), Ido (io), Irish (ga), Javanese (jv), Kannada (kn), Kurdish (ku), Latvian (lv), Low Saxon (nds), Luxembourgish (lb), Macedonian (mk), Malagasy (mg), Malayalam (ml), Marathi (mr), Neapolitan (nap), Nepali (ne), Newar / Nepal Bhasa (new), Norwegian (Nynorsk) (nn), Piedmontese (pms), Quechua (qu), Serbo-Croatian (sh), Sicilian (scn), Sundanese (su), Swahili (sw), Tagalog (tl), Tamil (ta), Tatar (tt), Telugu (te), Thai (th), Urdu (ur), Walloon (wa), Welsh (cy), West Frisian (fy), Yoruba (yo), Zazaki (diq)\\
+{\sc 17k-100k articles:}
+Afrikaans (af), Azerbaijani (az), Belarusian (be), Bengali (bn), Bishnupriya Manipuri (bpy), Breton (br), Bosnian (bs), Cebuano (ceb), Welsh (cy), Greek (el), West Frisian (fy), Galician (gl), Gujarati (gu), Haitian (ht), Icelandic (is), Javanese (jv), Georgian (ka), Kurdish (ku), Luxembourgish (lb), Latvian (lv), Malagasy (mg), Macedonian (mk), Malayalam (ml), Marathi (mr), Low Saxon (nds), Newar / Nepal Bhasa (new), Norwegian (Nynorsk) (nn), Piedmontese (pms), Sicilian (scn), Serbo-Croatian (sh), Albanian (sq), Swahili (sw), Tamil (ta), Telugu (te), Thai (th), Tagalog (tl), Urdu (ur), Yoruba (yo)\\
 \hline
-{\sc $<$10k articles:} Central Bicolano (bcl), Ilokano (ilo), Kapampangan (pam), Pashto (ps), Punjabi (pa), Sindhi (sd), Somali (so), Tibetan (bo), Uzbek (uz), Wolof (wo)\\
+{\sc $<$17k articles:} Amharic (am), Asturian (ast), Central Bicolano (bcl), Tibetan (bo), Zazaki (diq), Irish (ga), Armenian (hy), Ilokano (ilo), Kannada (kn), Neapolitan (nap), Nepali (ne), Punjabi (pa), Kapampangan (pam), Pashto (ps), Sindhi (sd), Somali (so), Sundanese (su), Uzbek (uz), Wolof (wo)\\
 \hline
@@
 In order to address the quality of the translations we received on the dictionary task, we constructed a pipeline in which the output of the translation HIT was reviewed by humans in a second evaluation HIT, described above.
-We quantified the quality of each translation assignment based on the output of the evaluation HIT as follows:
-\textit{In English, so people know what we did:}
+We quantified the quality of each translation assignment based on the output of the evaluation HIT as follows: \\
+\textbf{In English, so people know what we did:}
 \begin{align}	
-	Quality = \frac{\# \text{translations in } Synonyms(\text{answer})}{\# \text{ controls}}
+	Quality = \frac{\# \text{correct controls}}{\# \text{controls}}
 \end{align}	
-where answer is the known translation and $Synonyms$(answer) is the set of words judged to be synonymous with the gold standard translation in the second pass HIT.
-\textit{Mathified, to give the impression of rigor and intellect:}
+where a control is correct if it matches or is judged to be synonymous with the gold standard translation during the second pass HIT. \\
+\textbf{Mathified, to give the impression of rigor and intellect:}
 \begin{align}	
-	Quality = \frac{1}{k}\sum\limits_{i=1}^k\mathbf{1}(t_i \in Synonyms(a_i))
+	Quality(assign_i) = \frac{1}{k}\sum\limits_{j=1}^{k_i}\mathbf{1}(t_{ij} \in Syns(a_j))
 \end{align}	
-where $k$ is the number of controls in the assignment, $t_i$ is the Turker's provided translation of control word $i$, $a_i$ is the gold standard translation of the control word $i$, and $Synonyms(a_i)$ is the set of words judged to be synonymous with the $a_i$ in the second pass HIT and $\mathbf{1}(x)$ is 1 when $x$ is true.
+where $k_i$ is the number of controls in the assignment $i$, $t_j$ is the Turker's provided translation of control word $j$ in assignment $i$, $a_j$ is the gold standard translation of control word $j$, $Syns(a_j)$ is the set of words judged to be synonymous with $a_j$ during the second pass HIT, and $\mathbf{1}(x)$ is 1 when $x$ is true.
 
-Since most assignments had two known words embedded, most assignments had scores of either 0, 0.5, or 1.
-Since by-assignment quality scores are noisy and sensitive to small numbers of highly active Turkers, we report quality scores reported the average per-turker quality in tables and figures, where a Turker's quality is just the average quality of all the assignments that the Turker completed.
+Most assignments had two known words embedded, so most assignments had scores of either 0, 0.5, or 1.
+
+Since by-assignment quality scores are noisy and sensitive to small numbers of highly active Turkers, we report quality scores as the average per-turker quality, where a Turker's quality is just the average quality of all the assignments that the Turker completed.
+
+\textbf{Or in otherwords, because $\sum$ in latex is so lovely:}
+\begin{align}	
+	Quality(turker_i) = \frac{\sum_{a_j \in Assigns(i)}Quality(a_j)}{\mid Assigns(i) \mid}
+\end{align}	
+where $Assigns(i)$ is the assignments completed by turker $i$, and $Quality(a)$ is as above.
 

### 2013-03-15 code/src/wikilang/wikitables.py

@@ -1,29 +1,0 @@
-import re
-import csv
-import tex
-
-LANG_PATH = '../data/dictionary-data-dump-2012-11-13_15:11/languages'
-
-if __name__ == '__main__':
-	lmap = tex.reverse_lang_map(LANG_PATH)
-	all_classes = { '>500k':[], '100k-500k':[], '50k-100k':[], '10k-50k':[], '<10k':[]}
-	our_langs = set([l.strip() for l in open('alllangs').readlines()])
-	for line in csv.DictReader(open('wikicounts'), delimiter='\t'):
-		lang = line['Wiki']
-		num = int(re.sub(',','',line['Articles']))
-		if lang in our_langs:
-			if num > 500000:		
-				all_classes['>500k'].append(lang)
-			elif num > 100000:		
-				all_classes['100k-500k'].append(lang)
-			elif num > 50000:		
-				all_classes['50k-100k'].append(lang)
-			elif num > 10000:		
-				all_classes['10k-50k'].append(lang)
-			else:		
-				all_classes['<10k'].append(lang)
-	for c in all_classes:
-		print c
-		for l in all_classes[c]:
-			print '%s (%s)'%(lmap[l], l)
-		print

### 2013-03-15 writeup/paper.tex
equations

@@
 We quantified the quality of each translation assignment based on the output of the evaluation HIT as follows: \\
-\textbf{In English, so people know what we did:}
+\textbf{Version 1: In English, so people know what we did:}
 \begin{align}	
@@
 where a control is correct if it matches or is judged to be synonymous with the gold standard translation during the second pass HIT. \\
-\textbf{Mathified, to give the impression of rigor and intellect:}
+\textbf{Version 2 : Mathified, to give the impression of rigor and intellect:}
 \begin{align}	
@@
 where $Assigns(i)$ is the assignments completed by turker $i$, and $Quality(a)$ is as above.
+
+Quality for a language is then given by
+\begin{align}	
+	Quality(lang_i) = \frac{\sum_{t_j \in Turkers(i)}Quality(t_j)}{\mid Turkers(i) \mid}
+\end{align}	
+where $Turkers(i)$ is the set of turkers who completed assignments for language $i$, and $Quality(t)$ is as above.
 

### 2013-03-25 writeup/paper.tex
code for correlations

@@
 Rather than posting a one-off survey, we posted paid tasks consisting of 1,000 assignments to translate a total of 10,000 words in each of 119 languages.
-Our study ran for several weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilinguals workers would complete it.
+Our study ran for several weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilingual workers would complete it.
 Our study was useful both to create bilingual dictionaries and to act as census of the bilingual speakers on MTurk.
@@
 We quantified the quality of each translation assignment based on the output of the evaluation HIT as follows: \\
-\textbf{Version 1: In English, so people know what we did:}
-\begin{align}	
-	Quality = \frac{\# \text{correct controls}}{\# \text{controls}}
-\end{align}	
-where a control is correct if it matches or is judged to be synonymous with the gold standard translation during the second pass HIT. \\
-\textbf{Version 2 : Mathified, to give the impression of rigor and intellect:}
 \begin{align}	
@@
 
-Since by-assignment quality scores are noisy and sensitive to small numbers of highly active Turkers, we report quality scores as the average per-turker quality, where a Turker's quality is just the average quality of all the assignments that the Turker completed.
+Since by-assignment quality scores are noisy and sensitive to small numbers of highly active Turkers, we report quality scores as the average per-turker quality, where a Turker's quality is just the average quality of all the assignments that the Turker completed:
 
-\textbf{Or in otherwords, because $\sum$ in latex is so lovely:}
 \begin{align}	

### 2013-03-25 code/src/compile_data_from_raw.py

@@ -5,7 +5,7 @@ import json
 import string
 import codecs
 
-RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11'
+RAW_DIR = '../../'
 OUTPUT_DIR = 'output'
 
 def hits_language():

### 2013-03-25 code/src/completetime.py

@@ -14,7 +14,7 @@ import matplotlib.pyplot as plt
 import compile_data_from_raw as dat
 
 OUTPUT_DIR = 'output'
-RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11/'
+RAW_DIR = '../../'
 
 def get_language_dicts(path, filter_list=None):
 	all_dicts = dict()

### 2013-03-25 code/src/correlation.py

@@ -1,0 +1,39 @@
+#!/bin/python
+
+import sys
+import scipy.stats
+
+if len(sys.argv) < 3:
+	print 'USAGE ./correlation.py FILE1 FILE2'
+	exit(0)
+
+file1 = sys.argv[1]
+file2 = sys.argv[2]
+
+langs1 = [l.split('\t')[0] for l in open(file1).readlines()]
+langs2 = [l.split('\t')[0] for l in open(file2).readlines()]
+
+langs = list(set(langs1).intersection(set(langs2)))
+for l in langs: print '%s '%l,
+print
+
+scores1 = {l.split('\t')[0] : float(l.split('\t')[1]) for l in open(file1).readlines()}
+scores2 = {l.split('\t')[0] : float(l.split('\t')[1]) for l in open(file2).readlines()}
+
+s1 = list(); s2 = list()
+
+for l in langs:
+	s1.append(scores1[l])
+	s2.append(scores2[l])
+
+print 'Their average:', sum(s1)/len(s1)
+print 'Our average:', sum(s2)/len(s2)
+
+print 'Pearson:', scipy.stats.pearsonr(s1,s2)
+print 'Spearman:', scipy.stats.spearmanr(s1,s2)
+#print scipy.stats.stats.rankdata(s1)
+#print scipy.stats.stats.rankdata(s2)
+print 'Kendall Tau:', scipy.stats.kendalltau(scipy.stats.stats.rankdata(s1),scipy.stats.stats.rankdata(s2))
+
+print zip(langs,s1,s2)
+

### 2013-03-25 code/src/dictionaries.py

@@ -11,9 +11,9 @@ import itertools
 from scipy import stats
 import compile_data_from_raw as dat
 
-RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11/'
-DICT_PATH = '/home/steven/Documents/Ellie/Research/demographics/code.clean/translations.out'
-CLPAIRS = '/home/steven/Documents/Ellie/Research/demographics/data/cl-pairs.csv'
+RAW_DIR = '../..'
+DICT_PATH = './translations.out'
+CLPAIRS = './cl-pairs.csv'
 OUTPUT_DIR = 'output'
 DICT_DIR = 'dictionaries'
 
@@ -549,8 +549,6 @@ if __name__ == '__main__':
         parser.add_argument('--metastats', action='store_true', default=False, help='Overall in/out of region stats')
         
 	args = parser.parse_args()
-
-	print args
 
 	#check if raw translation files have alread been processed. if not, process them	
 	if not(os.path.exists(DICT_PATH)):

### 2013-03-25 code/src/external_compare.py

@@ -1,0 +1,53 @@
+#!/bin/python
+
+#format for external overlap file is
+#source_word target_word 1=control_word 1=target_word_known 1=observed_in_mturk_data 1=in_external_dictionary
+
+import re
+import os
+import sys
+
+EXTERN_OVERLAP = '../../dictionaries/anni/externalOverlap'
+
+def reg(s):
+	return s.strip().lower()
+
+if len(sys.argv) < 2:
+	print 'USAGE: ./external_compare.py DICTIONARY_ROOT'
+	print 'DICTIONARY_ROOT is directory containing dictionar.lang files to be validated'
+	exit(0)
+
+root_dir = sys.argv[1]
+
+pair_scores = dict()
+
+for dict_file in os.listdir(EXTERN_OVERLAP):
+	if not re.match('dict.(.*)',dict_file): continue
+	d, lang = dict_file.split('.')
+	if lang not in pair_scores: pair_scores[lang] = dict()
+	for line in open('%s/%s'%(EXTERN_OVERLAP,dict_file,)).readlines():
+		src, tran, is_control, known_correct, observed, is_match = line.strip().split('\t')
+		pair_scores[lang][(reg(src),reg(tran))] = int(is_match)
+
+lang_scores = dict()
+
+for dict_file in os.listdir(root_dir):
+	if not re.match('dictionary.(.*)',dict_file): continue
+	d, lang = dict_file.split('.')
+	if lang in pair_scores:
+		if lang not in lang_scores: lang_scores[lang] = [0.0,0.0,0.0]
+		for line in open('%s/%s'%(root_dir,dict_file,)).readlines():
+			try: src, trans = line.strip().split('\t')
+			except ValueError: continue
+			for tran in trans.split(','):
+				if not reg(tran) == '':
+					try:
+						lang_scores[lang][0] += pair_scores[lang][(reg(src), reg(tran))]
+						lang_scores[lang][1] += 1
+					except KeyError: lang_scores[lang][2] += 1
+
+for lang, (match, tot, skipped) in lang_scores.iteritems():
+	print '%s\t%.03f\t%d\t%d'%(lang, match/tot, tot, skipped)
+
+
+

### 2013-03-25 code/src/qc.py

@@ -329,6 +329,36 @@ def quality_by_turker(fname, path):
 		out.write('%s\t%.04f\n'%(t, all_turkers[t]['num']/all_turkers[t]['denom'],))
 	out.close()
 
+def turker_qual_map():
+        qual_data = {}
+        for line in open('%s/byturker.voc.quality.new'%OUTPUT_DIR).readlines()[1:]:
+                assign, qual = line.split()
+                if(assign not in qual_data):
+                        qual_data[assign] = float(qual)
+        return qual_data
+
+#get the average quality per turker and write to a file
+def quality_by_lang(fname, path):
+	out = open(fname, 'w')
+        all_langs= dict()
+        tmap = turker_map()
+        quals = turker_qual_map()
+	for nlang in ['nolang', 'onelang', 'multlang']:
+	        for turker in csv.DictReader('%s/byturker.voc.%s'%(OUTPUT_DIR,nlang,)):
+			worker = tmap[assign]
+                	q = quals[assign]
+  			if(assign == '' or assign not in tmap):
+                	        continue
+			if q == 'N/A':
+				continue
+			if not(worker in all_turkers):
+                	        all_turkers[worker] = {'num':0, 'denom':0}
+                	all_turkers[worker]['num'] += float(q)
+                	all_turkers[worker]['denom'] += 1
+	for t in all_turkers:
+		out.write('%s\t%.04f\n'%(t, all_turkers[t]['num']/all_turkers[t]['denom'],))
+	out.close()
+
 #get the average quality per turker and write to a file
 def googmatch_by_turker(fname, path):
 	out = open(fname, 'w')

### 2013-03-25 code/src/external_compare_assigns.py
more correlations

@@ -1,0 +1,63 @@
+#!/bin/python
+
+#format for external overlap file is
+#source_word target_word 1=control_word 1=target_word_known 1=observed_in_mturk_data 1=in_external_dictionary
+
+import re
+import os
+import sys
+import csv
+
+EXTERN_OVERLAP = '../../dictionaries/anni/externalOverlap'
+ASSIGNS = 'output/byassign.voc.accepted'
+
+def reg(s):
+	return s.strip().lower()
+
+if len(sys.argv) < 2:
+	print 'USAGE: ./external_compare.py TRANSLATIONS.OUT'
+	print 'TRANSLATIONS.OUT is file containing the word-to-word translations received from each assignment'
+	exit(0)
+
+tout = sys.argv[1]
+
+pair_scores = dict()
+
+for dict_file in os.listdir(EXTERN_OVERLAP):
+	if not re.match('dict.(.*)',dict_file): continue
+	d, lang = dict_file.split('.')
+	if lang not in pair_scores: pair_scores[lang] = dict()
+	for line in open('%s/%s'%(EXTERN_OVERLAP,dict_file,)).readlines():
+		src, tran, is_control, known_correct, observed, is_match = line.strip().split('\t')
+		pair_scores[lang][(reg(src),reg(tran))] = int(is_match)
+
+assign_pairs = dict()
+
+for line in open(tout).readlines():
+	t = line.strip().split('\t')
+	assign_pairs[t[0]] = t[1:]
+
+assign_scores = dict()
+
+for line in csv.DictReader(open(ASSIGNS), delimiter='\t'):
+	lang = line['hitlang']
+	aid = line['id']
+	if lang in pair_scores:
+		if aid not in assign_pairs:
+			print aid, 'skipped'
+			continue
+		if aid not in assign_scores: assign_scores[aid] = [0.0,0.0,0.0]
+		for pair in assign_pairs[aid]:
+			try : src, trans = pair.strip().split(':')
+			except ValueError: 
+				print pair, 'skipped'
+				continue
+			if not reg(tran) == '':
+				try:
+					assign_scores[aid][0] += pair_scores[lang][(reg(src), reg(tran))]
+					assign_scores[aid][1] += 1
+				except KeyError: assign_scores[aid][2] += 1 #word pair not in reference dictionaries
+
+for lang, (match, tot, skipped) in assign_scores.iteritems():
+	print '%s\t%.03f\t%d\t%d'%(lang, match/tot, tot, skipped)
+

### 2013-03-28 writeup/paper.tex
finalizing figures

@@
 \centering
-\includegraphics[width=\linewidth]{figures/turkermap-color-cropped}
+\includegraphics[width=\linewidth]{final-figures/turkermap}
 \caption{The number of workers per country.
@@
 The size of the circles represents the number of workers from each country.
-The two largest are India (2,022 workers) and the United States (904).
+The two largest are India (2,017 workers) and the United States (904).
 To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
@@
 \centering
-%\includegraphics[height=\linewidth,angle=270]{figures/completiontime}
-\includegraphics[height=\linewidth,angle=270]{figures/completiontime-new}
+%\includegraphics[height=\linewidth,angle=270]{figures/completetime}
+\includegraphics[height=\linewidth,angle=270]{final-figures/completetime}
 \caption{Days to complete the translation HITs for 40 of the languages. Tick marks represent the completion of individual assignments. }
@@
 \centering
-\includegraphics[width=6in]{figures/assign-turk-scatter-new}
+\includegraphics[width=6in]{final-figures/assign-turk-scatter}
 \caption{Number of assignments and number of Turkers for each language.
@@
 \centering
-\includegraphics[width=6in]{figures/quality-hitlang-goog}
+\includegraphics[width=6in]{final-figures/google-match-bar}
 \caption{Translation quality of by source language.
@@
 \centering
-\includegraphics[width=6in]{figures/quality-scatter}
+\includegraphics[width=6in]{final-figures/quality-scatter}
 \caption{Estimated quality of translations by country.
@@
 Figure represents data from approx.
-281,000 assignments for which geolocation was known.}
+295,000 assignments for which geolocation was known.}
 \label{quality-scatter}

### 2013-03-28 code/src/correlation_turkers.py

@@ -1,5 +1,6 @@
 #!/bin/python
 
+import csv
 import sys
 import scipy.stats
 
@@ -7,35 +8,108 @@ if len(sys.argv) < 3:
 	print 'USAGE ./correlation.py EXT_SCORES OUR_SCORES'
 	exit(0)
 
+cutoff = 100
+
+lfile1 = 'output/bylang.quality.external'
+lfile2 = 'dictionaries/all.turkerqual'
+
+langs1 = [l.split('\t')[0] for l in open(lfile1).readlines()]
+langs2 = [l.split('\t')[0] for l in open(lfile2).readlines()]
+
+extlangs = list(set(langs1).intersection(set(langs2)))
+for l in extlangs: print '%s '%l,
+print
+
 file1 = sys.argv[1]
 file2 = sys.argv[2]
 
 ids1 = [l.split('\t')[0] for l in open(file1).readlines()]
 ids2 = [l.split('\t')[0] for l in open(file2).readlines()]
 
-ids = list(set(ids1).intersection(set(ids2)))
-#for i in ids: print '%s '%i,
-#print
+all_ids = list(set(ids1).intersection(set(ids2)))
 
-print len(ids)
+turkers_by_lang = dict()
 
-scores1 = {l.split('\t')[0] : float(l.split('\t')[1]) for l in open(file1).readlines()}
-scores2 = {l.split('\t')[0] : float(l.split('\t')[1]) for l in open(file2).readlines()}
+#get mapping of lang: list of turkers
+for nl in ['onelang', 'nolang', 'multlang']:
+	for line in csv.DictReader(open('output/byturker.voc.%s'%nl), delimiter='\t'):
+		tid = line['id']; l = line['hitlang'];
+		for ll in l.strip().split(';'):
+			if not ll == '':
+				if ll not in turkers_by_lang: turkers_by_lang[ll] = set()
+				turkers_by_lang[ll].add(tid)
 
-s1 = list(); s2 = list()
+scores1 = dict()
+for l in open(file1).readlines():
+	ll = l.strip().split('\t')
+#	if len(ll) >= 2:
+#		if int(ll[2]) > cutoff:
+	scores1[ll[0]] = float(ll[1])
+#	else:
+#		print ll
 
-for i in ids:
-	s1.append(scores1[i])
-	s2.append(scores2[i])
+scores2 = dict()
+for l in open(file2).readlines():
[…]

### 2013-03-28 code/src/figures.py

@@ -725,7 +725,8 @@ def native_compare_line_graph(native, nonnative):
 
 #scatter plot of quality against # assignments, bubbles sized by # turkers
 def quality_scatter(title='Title'):
-	points_to_label = ['VN', 'RO', 'NG', 'AM', 'DZ','RU', 'UK', 'ET', 'PK', 'IN','US','MY','MK','ES', 'ID', '100 turkers']
+	#points_to_label = ['VN', 'RO', 'NG', 'AM', 'DZ','RU', 'UK', 'ET', 'PK', 'IN','US','MY','MK','ES', 'ID', '100 turkers']
+	points_to_label = ['RO', 'NG', 'AM', 'DZ','RU', 'UK', 'PK', 'IN','US','MY','MK','ES', 'ID', '100 turkers']
 	attr = 'country'
 	cmap = reverse_cntry_map('ref/countrynames')
 	cmap['100 turkers'] = '100 turkers'
@@ -759,13 +760,13 @@ def quality_scatter(title='Title'):
 	plt.xscale('log')
 	plt.xlim([.1,1000000])
 	plt.ylim([0,1])
-	plt.xlabel('Number of assignments', fontsize='16')
-	plt.ylabel('Average quality', fontsize='16')
+	plt.xlabel('Number of assignments', fontsize='14')
+	plt.ylabel('Average quality', fontsize='14')
 	plt.xticks(fontsize='16')
 	plt.yticks(fontsize='16')
 	arrows = dict(arrowstyle = '->', connectionstyle = 'arc3,rad=0')
 	for label, x, y in zip(labels, labelx, labely):
-        	plt.annotate(label,xy =(x,y),xytext=(20,-20),textcoords='offset points',ha ='left',va='bottom',arrowprops=arrows, fontsize=16)
+        	plt.annotate(label,xy =(x,y),xytext=(20,10),textcoords='offset points',ha ='left',va='bottom',arrowprops=arrows, fontsize=12)
 	plt.savefig('quality-scatter.pdf')
 
 #scatter plot of # assignments against # turkers

### 2013-03-28 code/src/qc.py

@@ -21,7 +21,7 @@ def turker_map(hittype='voc'):
         return tmap
 
 #map of assignment ID to quality score of that assignment, or N/A 
-def qual_map(path):
+def qual_map(path, totals=False):
         qual_data = {}
         #for line in csv.DictReader(open('%s/byassign.voc.quality.exactmatch'%OUTPUT_DIR), delimiter='\t'):
         #for line in csv.DictReader(open('%s/byassign.googmatch'%OUTPUT_DIR), delimiter='\t'):
@@ -32,7 +32,8 @@ def qual_map(path):
                         if qual == 'N/A':
                                 qual_data[assign] = qual
                         else:
-                                qual_data[assign] = float(qual)
+                        	if totals:  qual_data[assign] = (float(qual), line['tot'])
+                        	else:  qual_data[assign] = float(qual)
         return qual_data
 
 #map of word id to word
@@ -313,25 +314,30 @@ def quality_by_turker(fname, path):
 	out = open(fname, 'w')
         all_turkers = dict()
         tmap = turker_map()
-        quals = qual_map(path)
+        quals = qual_map(path) #, totals=True)
         for assign in tmap:
   		if(assign == '' or assign not in tmap or assign not in quals):
                         continue
 		worker = tmap[assign]
-                q = quals[assign]
+                qq = quals[assign]
+                #q = qq[0] #quals[assign][0]
+                q = qq
 		if q == 'N/A':
 			continue
 		if not(worker in all_turkers):
-                        all_turkers[worker] = {'num':0, 'denom':0}
+                        all_turkers[worker] = {'num':0, 'denom':0, 'atot':0}
                 all_turkers[worker]['num'] += float(q)
                 all_turkers[worker]['denom'] += 1
+                #all_turkers[worker]['atot'] += int(qq[1])
 	for t in all_turkers:
+		print t
 		out.write('%s\t%.04f\n'%(t, all_turkers[t]['num']/all_turkers[t]['denom'],))
+		#out.write('%s\t%.04f\t%d\n'%(t, all_turkers[t]['num']/all_turkers[t]['denom'],all_turkers[t]['atot'],))
 	out.close()
 
 def turker_qual_map():
[…]

### 2013-03-28 writeup/paper.tex

@@
 
-We checked Turkers who were working on this task by embedding pairs word which were either known to be synonyms (drawn from WordNet) or  unrelated (randomly chosen from a corpus). 
+We checked Turkers who were working on this task by embedding pairs of words which were either known to be synonyms (drawn from WordNet) or  unrelated (randomly chosen from a corpus). 
 %We drew known synonyms from WordNet, and non-synonyms by pairing random words from a corpus of English (including them after they were determined to be unrelated according to WordNet).
@@
 Figure \ref{ass-scatter} shows the volume of HITs completed and the number of workers participating for each language.
-While the bulk (22\%) of bilingual Turkers report English as their native language (see figure \ref{lang-pie}), Mechanical Turk's capacity to support the Indian languages is apparent.
-Hindi, Tamil, and Malayalam are especially well represented in terms of number of active translators, and Urdu, Telugu, and Macedonian are particularly productive in terms of number of assignments completed.
-%As shown in figure \ref{langgeo-bar}, 11 of the top 25 languages, in terms of number of assignments submitted, were Indian languages, and the assignments for 15 of the top 25 were completed mostly or entirely by Turkers located in India.
+\textbf{While the bulk (22\%) of bilingual Turkers report English as their native language (see figure \ref{lang-pie}), Mechanical Turk's capacity to support the Indian languages is apparent.
+Hindi, Tamil, and Malayalam are especially well represented in terms of number of active translators, and Urdu, Telugu, and Macedonian are particularly productive in terms of number of assignments completed.} %As shown in figure \ref{langgeo-bar}, 11 of the top 25 languages, in terms of number of assignments submitted, were Indian languages, and the assignments for 15 of the top 25 were completed mostly or entirely by Turkers located in India.
 
@@
 \section{Measuring Data Quality}
-The primary challenge of using crowdsourced language data is the widely variable quality of the collected annotations.
+%The primary challenge of using crowdsourced language data is the widely variable quality of the collected annotations.
 While it is possible to strengthen the signal by collecting redundant labels, this strategy becomes difficult in practice for more complex data annotation.
@@
 
+%In order to perform a rigorous study of translation quality, we quantify the translation quality of each Turker using our designed an internal method for quality control.
 In order to address the quality of the translations we received on the dictionary task, we constructed a pipeline in which the output of the translation HIT was reviewed by humans in a second evaluation HIT, described above.
 We quantified the quality of each translation assignment based on the output of the evaluation HIT as follows: \\
+
 \begin{align}	
-	Quality(assign_i) = \frac{1}{k}\sum\limits_{j=1}^{k_i}\mathbf{1}(t_{ij} \in Syns(a_j))
+	\text{Quality}(a_i) = \frac{1}{k}\sum\limits_{j=1}^{k_i}\mathbf{1}(tr_{ij} \in \texttt{syns[$g_j$]})
 \end{align}	
-where $k_i$ is the number of controls in the assignment $i$, $t_j$ is the Turker's provided translation of control word $j$ in assignment $i$, $a_j$ is the gold standard translation of control word $j$, $Syns(a_j)$ is the set of words judged to be synonymous with $a_j$ during the second pass HIT, and $\mathbf{1}(x)$ is 1 when $x$ is true.
+where $a_i$ is the $i^{th}$ assignment, $k_i$ is the number of controls in $a_i$, $tr_j$ is the Turker's provided translation of control word $j$ in assignment $i$, $g_j$ is the gold standard translation of control word $j$, \texttt{syns[$g_j$]} is the set of words judged to be synonymous with $g_j$ during the second pass HIT, and $\mathbf{1}(x)$ is 1 when $x$ is true.
 
@@
 \begin{align}	
-	Quality(turker_i) = \frac{\sum_{a_j \in Assigns(i)}Quality(a_j)}{\mid Assigns(i) \mid}
+	\text{Quality}(t_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}\text{Quality}(a_j)}}{\mid \texttt{assigns[$i$]} \mid}
 \end{align}	
-where $Assigns(i)$ is the assignments completed by turker $i$, and $Quality(a)$ is as above.
+where $t_i$ is the $i^{th}$ turker, \texttt{assigns[$i$]} is the assignments completed by turker $i$, and Quality($a$) is as above.
 
@@
 \begin{align}	
-	Quality(lang_i) = \frac{\sum_{t_j \in Turkers(i)}Quality(t_j)}{\mid Turkers(i) \mid}
+	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{turkers[$i$]}\text{Quality}(t_j)}}{\mid \texttt{turkers[$i$]} \mid}
 \end{align}	
-where $Turkers(i)$ is the set of turkers who completed assignments for language $i$, and $Quality(t)$ is as above.
+where $l_i$ is the ith language, \texttt{turkers[$i$]} is the set of turkers who completed assignments for language $i$, and Quality($t$) is as above.
 

### 2013-03-28 writeup/paper.tex

@@
 \centering
-\includegraphics[width=\linewidth]{final-figures/turkermap}
+\includegraphics[width=\linewidth]{figures/turkermap-color-cropped}
 \caption{The number of workers per country.
@@
 The size of the circles represents the number of workers from each country.
-The two largest are India (2,017 workers) and the United States (904).
+The two largest are India (2,022 workers) and the United States (904).
 To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
@@
 \centering
-%\includegraphics[height=\linewidth,angle=270]{figures/completetime}
-\includegraphics[height=\linewidth,angle=270]{final-figures/completetime}
+%\includegraphics[height=\linewidth,angle=270]{figures/completiontime}
+\includegraphics[height=\linewidth,angle=270]{figures/completiontime-new}
 \caption{Days to complete the translation HITs for 40 of the languages. Tick marks represent the completion of individual assignments. }
@@
 \centering
-\includegraphics[width=6in]{final-figures/assign-turk-scatter}
+\includegraphics[width=6in]{figures/assign-turk-scatter-new}
 \caption{Number of assignments and number of Turkers for each language.
@@
 \centering
-\includegraphics[width=6in]{final-figures/google-match-bar}
+\includegraphics[width=6in]{figures/quality-hitlang-goog}
 \caption{Translation quality of by source language.
@@
 \centering
-\includegraphics[width=6in]{final-figures/quality-scatter}
+\includegraphics[width=6in]{figures/quality-scatter}
 \caption{Estimated quality of translations by country.
@@
 Figure represents data from approx.
-295,000 assignments for which geolocation was known.}
+281,000 assignments for which geolocation was known.}
 \label{quality-scatter}

### 2013-03-28 writeup/paper.tex
sections 4 and 5

--- 2013-03-28 writeup/paper.tex
@@
 
-%Access to a fast, cheap, and flexible workforce has changed the way we collect data, and holds promise for enabling future language technologies.
-Crowdsourced work has proven effective for collecting massive amounts of simple data annotations, such as annotating data for face recognition software and labeling sentiment in twitter data.
-As the demands and expectations of automated systems progress, and the complexity of the data required for training increases, however, it becomes natural to ask about the strengths and limitations of the crowd as annotators for natural language data.
-%We evaluate the language skills of bilingual workers on Amazon's Mechanical Turk, and their ability to provide translated data for statistical machine translation.
-Collecting parallel translated texts has traditionally been assumed to require a higher level of expertise than what is available from non-professional crowd workers.
-However, with an increasing number of active crowd workers located outside of the United States, the potential to access fluent speakers of lower resource languages makes crowdsourcing an attractive resource for translation.
-
 There are several complicating factors when trying to take a census of workers on MTurk.
@@
 \caption{The number of workers per country.
-This map was generated based on geolocating the IP address of  5,284 workers in our study.
+This map was generated based on geolocating the IP address of  5,277 workers in our study.
 The size of the circles represents the number of workers from each country.
@@
 Turkers remain anonymous to Requesters, and all payment occurs through Amazon.
-Requesters are able to accept submitted work or reject work that they does not meet their standards.
+Requesters are able to accept submitted work or reject work that does not meet their standards.
 Turkers are only paid if a Requester accepts their work.
@@
 To contrast our research with previous work, the main contributions of this paper are: (1) a robust methodology for assessing the bilingual  skills of anonymous workers, (2) the largest-scale census to date of language skills of workers on MTurk, and (3) a detailed analysis of the data gathered in our study.
-%, including the quality of the translations and recommendations for  languages that are feasible for near-term creation of multi-lingual technologies.
-
-%%%%%%%%%%%%%%% HIT UIs %%%%%%%%%%%
-%\begin{figure}[h]
-%\centering
-%\includegraphics[width=3in]{figures/vocabulary_hit_mturk}
-%\caption{Translation HIT UI}
-%\label{tranhit}
-%\end{figure}
-%
-%\begin{figure}[h]
-%\centering
-%\includegraphics[width=3in]{figures/synonyms_hit_mturk}
-%\caption{Evaluation HIT UI}
-%\label{synhit}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
-%\begin{figure}[h]
-%\begin{tabular}{lc}\hline\hline\\
-%Is [HIT language/English]&\multirow{2}{*}{3,480}\\
-%your native language? &\\
-%How many years have you&\multirow{2}{*}{3,767}\\
-%spoken [HIT language]?&\\
-%How many years have you&\multirow{2}{*}{3,840}\\
-%spoken English?&\\
-%What country do you live in?&3,890\\
-%Geolocation (collected automatically)& 5,054\\
-%\hline\\
-%Total workers& 5,281\\
-%\hline\hline
-%\end{tabular}
-%\caption{Demographic survey questions and number of Turkers with valid responses for each}
-%\label{survey-tab}
-%\end{figure}
-
-%\begin{table*}[h]
-%\centering
-%\begin{tabular}{lc}\hline\hline\\
-%Is [HIT language/English] your native language? &3,480\\
-%How many years have you spoken [HIT language]?&3,767\\
-%How many years have you spoken English?&3,840\\
-%What country do you live in?&3,890\\
-%Current location (collected automatically)& 5,054\\
-%\hline\\
-%Total unique workers& 5,281\\
-%\hline\hline
-%\end{tabular}
-%\caption{Demographic survey questions and number of Turkers with valid responses for each}
-%\label{survey-tab}
-%\end{table*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \hline
-English&591&	French&63&	Vietnamese&34\\
+English&592&	French&63&	Vietnamese&34\\
 Tamil&253&	Polish&61&	Macedonian&31\\
@@
 \caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 languages with $\leq$20 speakers. 
-%(for a total of 423 remaining speakers).  
-We omit 1,801 Turkers who did not report their native language, 243 who reported 2 native languages, and 83 who reported $\geq$3 native languages.}\label{lang-pie}
+We omit 1,797 Turkers who did not report their native language, 243 who reported 2 native languages, and 83 who reported $\geq$3 native languages.}\label{lang-pie}
 \end{table}
@@
 We automatically collected each worker's current location by geolocating their IP address.
-A total of 5,281 unique workers completed our HITs.
-Among those, 3,890 provided responses to our survey questions, and we were able to geolocate 5,054.
+A total of 5,277 unique workers completed our HITs.
+Among those, 3,890 provided responses to our survey questions, and we were able to geolocate 5,114.
 Figure \ref{map} plots the location of workers across 111 countries.
 Table \ref{lang-pie} gives the most common self-reported native languages.
-
-% were not required in order to complete the HIT; survey questions and the number of valid responses received for each are listed in table \ref{survey-tab}.
-Although it was not required, Turkers who completed multiple HIT assignments could fill out the survey multiple times.
-This enabled some Turkers to report multiple native languages (see figure \ref{numlangs-tab}).
-While most results presented are calculated across all Turkers, figures given for distributions across native languages are calculated only from Turkers who reported a single native language.\\
 
@@
 We drew our data from the different language versions of Wikipedia.
-We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} and then selected an additional 19 low resource languages with $<$10,000 articles, giving a total of 119 languages (Table \ref{wikipedia-buckets}).
+We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} and then selected an additional 19 low resource languages, giving a total of 119 languages (Table \ref{wikipedia-buckets}).
 For each language, we chose the 1,000 most viewed articles over a 1 year period,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and extracted the 10,000 most frequent words from each.
@@
 \hline
-{\sc 17k-100k articles:}
-Afrikaans (af), Azerbaijani (az), Belarusian (be), Bengali (bn), Bishnupriya Manipuri (bpy), Breton (br), Bosnian (bs), Cebuano (ceb), Welsh (cy), Greek (el), West Frisian (fy), Galician (gl), Gujarati (gu), Haitian (ht), Icelandic (is), Javanese (jv), Georgian (ka), Kurdish (ku), Luxembourgish (lb), Latvian (lv), Malagasy (mg), Macedonian (mk), Malayalam (ml), Marathi (mr), Low Saxon (nds), Newar / Nepal Bhasa (new), Norwegian (Nynorsk) (nn), Piedmontese (pms), Sicilian (scn), Serbo-Croatian (sh), Albanian (sq), Swahili (sw), Tamil (ta), Telugu (te), Thai (th), Tagalog (tl), Urdu (ur), Yoruba (yo)\\
+{\sc 10k-100k articles:}
+Afrikaans (af) Amharic (am) Asturian (ast) Azerbaijani (az) Belarusian (be) Bengali (bn) Bishnupriya Manipuri (bpy) Breton (br) Bosnian (bs) Cebuano (ceb) Welsh (cy) Zazaki (diq) Greek (el) West Frisian (fy) Irish (ga) Galician (gl) Gujarati (gu) Haitian (ht) Armenian (hy) Icelandic (is) Javanese (jv) Georgian (ka) Kannada (kn) Kurdish (ku) Luxembourgish (lb) Latvian (lv) Malagasy (mg) Macedonian (mk) Malayalam (ml) Marathi (mr) Neapolitan (nap) Low Saxon (nds) Nepali (ne) Newar / Nepal Bhasa (new) Norwegian (Nynorsk) (nn) Piedmontese (pms) Sicilian (scn) Serbo-Croatian (sh) Albanian (sq) Sundanese (su) Swahili (sw) Tamil (ta) Telugu (te) Thai (th) Tagalog (tl) Urdu (ur) Yoruba (yo)\\
 \hline
-{\sc $<$17k articles:} Amharic (am), Asturian (ast), Central Bicolano (bcl), Tibetan (bo), Zazaki (diq), Irish (ga), Armenian (hy), Ilokano (ilo), Kannada (kn), Neapolitan (nap), Nepali (ne), Punjabi (pa), Kapampangan (pam), Pashto (ps), Sindhi (sd), Somali (so), Sundanese (su), Uzbek (uz), Wolof (wo)\\
+{\sc $<$10k articles:} Central Bicolano (bcl) Tibetan (bo) Ilokano (ilo) Punjabi (pa) Kapampangan (pam) Pashto (ps) Sindhi (sd) Somali (so) Uzbek (uz) Wolof (wo)\\
+
 \hline
@@
 
-%Our experiments consist of two task types: a translation HIT and an evaluation HIT. 
-%Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.  
 For the translation task, we asked Turkers to translate individual words.  We showed each word in the context of three sentences that were drawn from Wikipedia.  
@@
 
-%
 The task paid \$0.15 for the translation of 10 words.
-% 
-%Assignments which had less than XXX items translated was rejected, as were workers who failed the quality control measures more than XXX\% of the time.
+
 Each set of 10 words was independently translated by three separate workers.
-5,281 workers completed 308,079 translations assignments, totaling more than 3 million words, over a period of three and a half months.
+5,277 workers completed 308,079 translations assignments, totaling more than 3 million words, over a period of three and a half months.
 
@@
 We checked Turkers who were working on this task by embedding pairs of words which were either known to be synonyms (drawn from WordNet) or  unrelated (randomly chosen from a corpus). 
-%We drew known synonyms from WordNet, and non-synonyms by pairing random words from a corpus of English (including them after they were determined to be unrelated according to WordNet).
 Automating approval/rejections for the second-pass evaluation allowed the whole pipeline to be run automatically.  Caching judgments meant that we ultimately needed only 
@@
 Each of these assignments included 10 word pairs and paid \$0.10.
+
+\section{Measuring Data Quality}
+
+We quantified the quality of each translation assignment based on the output of the quality assurance HIT as follows:
+\begin{align}	
+	\text{Quality}(a_i) = \frac{1}{k}\sum\limits_{j=1}^{k_i}\mathbf{1}(tr_{ij} \in \texttt{syns[$g_j$]})
+\end{align}	
+where $a_i$ is the $i^{th}$ assignment, $k_i$ is the number of controls in $a_i$, $tr_j$ is the Turker's provided translation of control word $j$ in assignment $i$, $g_j$ is the gold standard translation of control word $j$, \texttt{syns[$g_j$]} is the set of words judged to be synonymous with $g_j$ during the second pass HIT, and $\mathbf{1}(x)$ is 1 when $x$ is true.
+
+Most assignments had two known words embedded, so most assignments had scores of either 0, 0.5, or 1.
+
+Since by-assignment quality scores are noisy and sensitive to small numbers of highly active Turkers, we report quality scores as the average per-turker quality, where a Turker's quality is just the average quality of all the assignments that the Turker completed:
+\begin{align}	
+	\text{Quality}(t_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}\text{Quality}(a_j)}}{\mid \texttt{assigns[$i$]} \mid}
+\end{align}	
+where $t_i$ is the $i^{th}$ turker, \texttt{assigns[$i$]} is the assignments completed by turker $i$, and Quality($a$) is as above.
+
+Quality for a language is then given by
+\begin{align}	
+	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{turkers[$i$]}\text{Quality}(t_j)}}{\mid \texttt{turkers[$i$]} \mid}
+\end{align}	
+where $l_i$ is the ith language, \texttt{turkers[$i$]} is the set of turkers who completed assignments for language $i$, and Quality($t$) is as above.
+
+Measured in this way, the average quality score across all HITs in all languages is just under 0.46. When restricted to languages with at least 50 Turkers, the average quality is 0.53.
+
+%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
+\begin{figure}[h]
+\centering
+\includegraphics[height=\linewidth,angle=270]{final-figures/google-match-bar}
+\caption{Translation quality of by source language.
+Blue bars show quality estimates by language and green bars show proportion of translations which matched Google Translate.
+Total quality is calculated as the average number of control words which were correct translations of the source word, where ”correct” means that the provided translation was judged to be synonymous with the known translation by workers in a second-
+pass HIT.
+Dark blue bars indicate the proportion of translations which exactly matched known translations, and light blue indicate translations which were judged to be correct synonyms.
+Quality estimates are only show for languages with at least 50 active turkers.
+Overall average quality was 0.46 (0.53 among languages with at least 50 Turkers).}
+\label{hitlangqual}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \centering
-%\includegraphics[height=\linewidth,angle=270]{figures/completetime}
 \includegraphics[height=\linewidth,angle=270]{final-figures/completetime}
@@
 
-\paragraph{Agreement with controls}
+\paragraph{Validation of controls} As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
+Turkers' performance on our control tasks is well correlated with this measure of quality.
+Results are show below in table \ref{corr-table}.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{lc}\hline\hline\\
+&$\rho$\\
+Language quality&0.58\\
+Turker quality (languages pooled)&0.37\\
+Avg. Turker quality (languages separate)&0.21\\
+\hline\hline
+\end{tabular}
+\caption{Pearson correlation of quality measured by accuracy on control translations vs.
+quality measured by overlap with external dictionaries.
+Language is the correlation of quality estimates for each language (across 27 languages), Turker quality is the correlation of quality estimates for each Turker (2,472 turkers).
+Avg.
+Turker quality is computed by taking the correlation of Turker quality estimates separately for each of the 27 languages, and then taking the average of the correlations.
+The figure reflects data from 27 languages for which we had available external dictionaries: az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, uz.}
+\label{corr-table}
+\end{table}
 
@@
 Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems.
-This strategy does not prevent workers from typing the words into a MT system, if they understand the language's script.
-%
+This strategy does not prevent workers from typing the words into an MT system, if they understand the language's script.
+We measured the percent of translations received that exactly matched the translation returned from google translate.
+Results are show in figure \ref{google-match-bar}.
+Assignments averaged around 43\% overlap with google translate.
+Higher overlap with google translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some of the control translations used may have been already indexed by Google.
+Languages with exotic scripts (such as Arabic (ar), Chinese (zh), and Telugu (te)) have especially low overlap with Google.
 
 %%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
-\include{summary}
+\begin{figure*}[h]
+\footnotesize
+\begin{tabular}{lllll}
+\hline\hline
+&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&Primary locations&Primary locations\\
+&In region&Out of region&of turkers in region&of turkers out of region\\
+\hline\hline
+Hindi&\textbf{0.35} (299)&0.29 (7)&India (285) UAE (5) UK (5) &Saudi Arabia (2) Russia (1) Oman (1) \\
+Tamil&\textbf{0.39} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
+Malayalam&0.44 (235) &\textbf{0.56} (2)&India (224) UAE (6) US (3) &Saudi Arabia (1) Maldives (1) \\
+Spanish&\textbf{0.71} (205)&0.60 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) New Zealand (1) \\
+French&0.61 (183) &\textbf{0.80} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
+German&\textbf{0.80} (99)&0.56 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
+Italian&\textbf{0.79} (98)&0.67 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
+Chinese&\textbf{0.22} (121)&0.18 (19)&US (79) Singapore (15) China (14) &HK (6) Australia (3) Germany (2) \\
+Malay&\textbf{0.76} (15)&0.72 (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
+Irish&0.61 (58) &\textbf{0.62} (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
+Czech&\textbf{0.70} (52)&0.62 (64)&US (19) Czech Republic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
+Turkish&\textbf{0.70} (83)&0.62 (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
+Amharic&\textbf{0.17} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
+Swedish&\textbf{0.64} (58)&0.57 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
+Portuguese&\textbf{0.75} (107)&0.62 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
+Arabic&0.21 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
+Kannada&\textbf{0.24} (106)&0.10 (1)&India (106) US (1) &France (1) Germany (1) \\
+Russian&\textbf{0.33} (72)&0.26 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
+Afrikaans&\textbf{0.73} (4)&0.64 (98)&South Africa (4) &India (93) Netherlands (2) UAE (1) \\
+Sindhi&\textbf{0.16} (93)&0.11 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
+\hline\hline
+\label{region-summary}
+\end{tabular}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We used the Ethnologue \cite{ethnologue} to compile the list of countries where each language is spoken.
-Table \ref{language-regions} compares the average translation quality of Turkers within the region of each language, and compares it to the quality of Turkers outside that region.
+Table \ref{region-summary} compares the average translation quality of Turkers within the region of each language, and compares it to the quality of Turkers outside that region.
 
-Todo - overall, outliers, languages which are spoken everywhere. US workers get categorized into YY languages.
+Our workers reported speaking 97 languages natively.
+US workers alone reported 59 native languages.
+Overall, 4,465 workers were located in a region likely to speak the language from which they were translating, and 3,170 workers were located in countries considered out of region (meaning almost half of our 5,277 Turkers completed HITs in multiple languages).
+Across all languages, there is no significant quality difference between turkers in region and out of region (0.504 and 0.496, respectively).
+However, within each language, the effect of location on quality varies greatly (table \ref{region-summary}).
 
-\paragraph{Natives v. non-natives}
-Todo - analyze the translation quality of natives v.
-non-natives.
-Ideally we would plot average translation quality versus years speaking English.
-Two lines: one line for native speakers of the source language, one line for non-native speakers of the target language.
-We could average over all languages, and the points should show std-dev whiskers.
-
-Other questions:
-\begin{itemize}
-\item Are Turkers cheating by using Google translate?  Is there a difference in their use of MT systems for Latin alphabet languages v. languages with scripts that are more difficult to type?
-\item Are there flaws in our gold standard translations?
-Are they too easy because they've already been indexed by Google?
-Are they too hard for some languages because they are obscure scientific terms?
-\item Can we select good gold standard translations for future studies?  Which translations are we confident in?
-\item How well do the Turker translations match external bilingual dictionaries?
-If we ranked Turkers by how well they performed on our controls, would those rankings stay stable if we ranked them based on their performance on external dictionaries?
-\item How well do Turkers agree with each other on non-control items?
-Should we run a synonym HIT on all of the non-identical translations?
-Would that help us understand which translations were good and which weren't?
-\end{itemize}
-
-%%%%%%%%%%%%%%% NUM LANGUAGES TABLE %%%%%%%%%%%
-%\begin{figure}[h]
-%\begin{tabular}{ccc}\hline\hline
-%&\# languages&\# Turkers\\ \hline
-%No languages&0&1801\\
-%One language&1&3154\\
-%Multiple languages&2&243	\\
-%&3&49\\
-%&4&12\\
-%&5&9\\
-%&6&5\\
-%&7&2\\
-%&8&1\\
-%&9&2\\
-%&10&2\\
-%&15&1\\
-%\hline\hline
-%\end{tabular}
-%\label{numlangs-tab}
-%\caption{Number of native languages reported during demographic survey.}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Among the languages with the largest number of Turkers total, most workers are in region (see table \ref{region-summary}).
+The majority of out-of-region Turkers were located in India; the languages with the most out of region Turkers are as follows (total number out of region and number located in India in parenthesis): Malay (110/106), Amharic (98/69), Afrikaans (98/93), Icelandic (90/83), and Breton (88/82).
 
@@
 Figure \ref{ass-scatter} shows the volume of HITs completed and the number of workers participating for each language.
-\textbf{While the bulk (22\%) of bilingual Turkers report English as their native language (see figure \ref{lang-pie}), Mechanical Turk's capacity to support the Indian languages is apparent.
-Hindi, Tamil, and Malayalam are especially well represented in terms of number of active translators, and Urdu, Telugu, and Macedonian are particularly productive in terms of number of assignments completed.} %As shown in figure \ref{langgeo-bar}, 11 of the top 25 languages, in terms of number of assignments submitted, were Indian languages, and the assignments for 15 of the top 25 were completed mostly or entirely by Turkers located in India.
-
-%%%%%%%%%%%%%%% LOCATION BAR %%%%%%%%%%%
-%\begin{figure*}[h]
-%\centering
-%\includegraphics[width=6in]{figures/assign-langgeo-sorted}
-%\caption{Geolocation of Turkers speaking 40 most represented languages, in terms of number of assignments submitted}
-%\label{langgeo-bar}
-%\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Measuring Data Quality}
-%The primary challenge of using crowdsourced language data is the widely variable quality of the collected annotations.
-While it is possible to strengthen the signal by collecting redundant labels, this strategy becomes difficult in practice for more complex data annotation.
-In the case of translation, low quality translations may have a high level of agreement (for example, when many workers use google translate) while high quality, even professional translations, can be expected to vary significantly.
-
-%In order to perform a rigorous study of translation quality, we quantify the translation quality of each Turker using our designed an internal method for quality control.
-In order to address the quality of the translations we received on the dictionary task, we constructed a pipeline in which the output of the translation HIT was reviewed by humans in a second evaluation HIT, described above.
-We quantified the quality of each translation assignment based on the output of the evaluation HIT as follows: \\
-
-\begin{align}	
-	\text{Quality}(a_i) = \frac{1}{k}\sum\limits_{j=1}^{k_i}\mathbf{1}(tr_{ij} \in \texttt{syns[$g_j$]})
-\end{align}	
-where $a_i$ is the $i^{th}$ assignment, $k_i$ is the number of controls in $a_i$, $tr_j$ is the Turker's provided translation of control word $j$ in assignment $i$, $g_j$ is the gold standard translation of control word $j$, \texttt{syns[$g_j$]} is the set of words judged to be synonymous with $g_j$ during the second pass HIT, and $\mathbf{1}(x)$ is 1 when $x$ is true.
-
-Most assignments had two known words embedded, so most assignments had scores of either 0, 0.5, or 1.
-
-Since by-assignment quality scores are noisy and sensitive to small numbers of highly active Turkers, we report quality scores as the average per-turker quality, where a Turker's quality is just the average quality of all the assignments that the Turker completed:
-
-\begin{align}	
-	\text{Quality}(t_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}\text{Quality}(a_j)}}{\mid \texttt{assigns[$i$]} \mid}
-\end{align}	
-where $t_i$ is the $i^{th}$ turker, \texttt{assigns[$i$]} is the assignments completed by turker $i$, and Quality($a$) is as above.
-
-Quality for a language is then given by
-\begin{align}	
-	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{turkers[$i$]}\text{Quality}(t_j)}}{\mid \texttt{turkers[$i$]} \mid}
-\end{align}	
-where $l_i$ is the ith language, \texttt{turkers[$i$]} is the set of turkers who completed assignments for language $i$, and Quality($t$) is as above.
-
-%%%%%%%%%%%%%%% MISREPORT TABLE %%%%%%%%%%%
-%\begin{figure}[h]
-%\centering
-%\begin{tabular}{cccc}\hline\hline\\
-%&Avg. & 99\%&\\
-%&Quality & Conf. Int.&n\\
-%Misreport&0.252&(0.244, 0.260)&10,479\\
-%Correct&0.282&(0.280, 0.283)&296,911\\
-%Overall&0.281&(0.279, 0.282)&307,390\\
-%\hline\hline
-%\end{tabular}
-%\label{mism-tab}
-%\caption{Quality of translations recieved from truthful versus misreporting Turkers.}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
-\begin{figure*}[h]
-\centering
-\includegraphics[width=6in]{final-figures/google-match-bar}
-\caption{Translation quality of by source language.
-Blue bars show quality estimates by language and green bars show proportion of translations which matched Google Translate.
-Total quality is calculated as the average number of control words which were correct translations of the source word, where ”correct” means that the provided translation was judged to be synonymous with the known translation by workers in a second-
-pass HIT.
-Dark blue bars indicate the proportion of translations which exactly matched known translations, and light blue indicate translations which were judged to be correct synonyms.
-Quality estimates are only show for languages with at least 50 active turkers.}
-\label{hitlangqual-bar}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Measured in this way, the average quality score across all HITs was just under 0.5.
-In general, countries which produced more translations did not produce lower quality translations, with India, Macedonia, and the US falling very close to average quality (figure \ref{quality-scatter}).
-In fact, likely as a result of the large number of India-based Turkers, most of the Indian languages fall above average quality, including Hindi, Telugu, Malayalam, Marathis, Tamil, Gujarati, Kannada, Bengali, and Punjabi, shown in figure \ref{hitlangqual-bar}.
-The notable exception is Urdu, which produced below average translations, likely due to the relatively low number of unique translators, making quality more susceptible to individual careless workers (see figure \ref{ass-scatter}).
-
-%%%%%%%%%%%%%%% NATIVE LANGUAGE QUALITY BAR %%%%%%%%%%%
-%\begin{figure*}[h]
-%\centering
-%\includegraphics[width=6in]{figures/quality-natlang-sorted}
-%\caption{Translation quality of native and non-native speakers}
-%\label{natlangqual-bar}
-%\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Interestingly, native speakers do not consistently outperform non-native speakers (see figure \ref{natlangqual-bar}).
-In certain unique cases, such as Vietnam, non-native speakers produce significantly better translations than native speakers, possibly due to a large population of fluent US-based workers (figure \ref{langgeo-bar}).
-In general, the quality difference between native and non-native speakers is not significant.
+While the bulk (19\%) of bilingual Turkers report English as their native language (see figure \ref{lang-pie}), Mechanical Turk's capacity to support the Indian languages is apparent.
+Hindi, Tamil, and Malayalam are especially well represented in terms of number of active translators.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Self-reported country information is typically reliable; about 96\% of self-reported locations agreed with automatically reported locations, 
-Three quarters of Turkers who reported their native language reported a single native language consistantly across all assignments (table \ref{numlangs-tab}), and of those reporting multiple native languages, the majority listed English in addition to the HIT's source language, meaning less than 5\% of Turkers gave unreasonable responses.
 

### 2013-03-28 writeup/summary.tex
sections 4 and 5

--- 2013-02-20 writeup/summary.tex
@@
 \footnotesize
-\begin{tabular}{llll}
+\begin{tabular}{lllll}
 \multicolumn{4}{c}{Number of turkers per language}\\
 \hline\hline
-&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&Primary locations\\
-&In region&Out of region&of turkers in region\\
+&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&Primary locations&Primary locations\\
+&In region&Out of region&of turkers in region&of turkers out of region\\
 \hline\hline
-Hindi&\textbf{0.410} (299)&0.406 (63)&India (285) UAE (5) UK (5) \\
-Tamil&0.339 (278) &\textbf{0.482} (26)&India (271) US (3) Canada (2) \\
-Malayalam&\textbf{0.534} (235)&0.505 (49)&India (224) UAE (6) US (3) \\
-Spanish&0.561 (205) &\textbf{0.682} (39)&US (131) Mexico (18) Spain (14) \\
-French&\textbf{0.636} (183)&0.541 (34)&India (68) US (48) France (25) \\
-German&\textbf{0.691} (99)&0.678 (71)&Germany (51) US (29) Austria (9) \\
-Italian&0.650 (98) &\textbf{0.716} (68)&Italy (44) US (32) Romania (9) \\
-Chinese&0.165 (123) &\textbf{0.207} (28)&US (80) Singapore (15) China (14) \\
-Telugu&\textbf{0.582} (102)&0.582 (35)&India (98) US (3) UAE (1) \\
-Malay&0.630 (15) &\textbf{0.649} (116)&Malaysia (8) Singapore (4) US (2) \\
-Turkish&0.593 (83) &\textbf{0.634} (47)&Turkey (39) US (20) Macedonia (12) \\
-Kannada&0.155 (106) &\textbf{0.284} (21)&India (106) US (1) \\
-Portuguese&0.599 (107) &\textbf{0.651} (19)&Brazil (46) Portugal (32) US (15) \\
-Arabic&\textbf{0.278} (62)&0.217 (64)&Egypt (19) Jordan (17) Morocco (9) \\
-Romanian&0.653 (87) &\textbf{0.668} (37)&Romania (77) US (6) Moldova (3) \\
-Swedish&0.497 (58) &\textbf{0.504} (66)&US (28) Sweden (23) Finland (3) \\
-Czech&0.536 (52) &\textbf{0.571} (71)&US (19) Czechrepublic (15) Serbia (5) \\
-Irish&\textbf{0.645} (58)&0.605 (64)&US (41) Ireland (13) UK (4) \\
-Amharic&0.080 (17) &\textbf{0.138} (105)&US (14) Ethiopia (3) \\
-Russian&0.202 (72) &\textbf{0.275} (49)&US (38) Russia (8) Moldova (7) \\
+Hindi&\textbf{0.35} (299)&0.29 (7)&India (285) UAE (5) UK (5) &Saudi Arabia (2) Russia (1) Oman (1) \\
+Tamil&\textbf{0.39} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
+Malayalam&0.44 (235) &\textbf{0.56} (2)&India (224) UAE (6) US (3) &Saudi Arabia (1) Maldives (1) \\
+Spanish&\textbf{0.71} (205)&0.60 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) New Zealand (1) \\
+French&0.61 (183) &\textbf{0.80} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
+German&\textbf{0.80} (99)&0.56 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
+Italian&\textbf{0.79} (98)&0.67 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
+Chinese&\textbf{0.22} (121)&0.18 (19)&US (79) Singapore (15) China (14) &HK (6) Australia (3) Germany (2) \\
+Malay&\textbf{0.76} (15)&0.72 (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
+Irish&0.61 (58) &\textbf{0.62} (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
+Czech&\textbf{0.70} (52)&0.62 (64)&US (19) Czech Republic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
+Turkish&\textbf{0.70} (83)&0.62 (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
+Amharic&\textbf{0.17} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
+Swedish&\textbf{0.64} (58)&0.57 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
+Portuguese&\textbf{0.75} (107)&0.62 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
+Arabic&0.21 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
+Kannada&\textbf{0.24} (106)&0.10 (1)&India (106) US (1) &France (1) Germany (1) \\
+Russian&\textbf{0.33} (72)&0.26 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
+Afrikaans&\textbf{0.73} (4)&0.64 (98)&South Africa (4) &India (93) Netherlands (2) UAE (1) \\
+Sindhi&\textbf{0.16} (93)&0.11 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
 \hline\hline

### 2013-03-28 code/src/compile_data_from_raw.py

@@ -5,7 +5,7 @@ import json
 import string
 import codecs
 
-RAW_DIR = '../../'
+RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11'
 OUTPUT_DIR = 'output'
 
 def hits_language():

### 2013-03-28 code/src/completetime.py

@@ -14,7 +14,7 @@ import matplotlib.pyplot as plt
 import compile_data_from_raw as dat
 
 OUTPUT_DIR = 'output'
-RAW_DIR = '../../'
+RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11'
 
 def get_language_dicts(path, filter_list=None):
 	all_dicts = dict()
@@ -115,7 +115,7 @@ def time_series(data, num=40):
 		names.append(lang)
 		x += [t.total_seconds() for t in data[lang]]
 		y += [5+(i*5)]*len(data[lang])
-	plt.scatter(x,y,marker='|')
+	plt.scatter(x,y,marker='|', alpha=0.1)
 	plt.xlim([0,max(x)+5])
 	plt.ylim([0,max(y)+5])
         plt.yticks(sorted(list(set(y))), tuple(names))
@@ -165,7 +165,7 @@ if __name__ == '__main__':
         if(do == 'bar'):
 		time_bar(format_for_graph(get_language_dicts('%s/byassign.voc.accepted'%OUTPUT_DIR)))
         if(do == 'series'):
-		#time_series(format_for_time_series(format_for_graph(time_map())))
-		fancy_time_series(format_for_time_series(format_for_graph(time_map())), num=40)
+		time_series(format_for_time_series(format_for_graph(time_map())))
+		#fancy_time_series(format_for_time_series(format_for_graph(time_map())), num=40)
 
 

### 2013-03-28 code/src/correlation.py

@@ -7,6 +7,9 @@ if len(sys.argv) < 3:
 	print 'USAGE ./correlation.py FILE1 FILE2'
 	exit(0)
 
+extlangs = ['az','bg','bn','bs','cy','es','fa','hi','id','lv','ms','ne','pl','ro','ru','sk','so','sq','sr','ta','tr','uk','ur','uz']
+
+
 file1 = sys.argv[1]
 file2 = sys.argv[2]
 
@@ -22,7 +25,7 @@ scores2 = {l.split('\t')[0] : float(l.split('\t')[1]) for l in open(file2).readl
 
 s1 = list(); s2 = list()
 
-for l in langs:
+for l in extlangs:
 	s1.append(scores1[l])
 	s2.append(scores2[l])
 

### 2013-03-28 code/src/correlation_turkers.py

@@ -16,9 +16,11 @@ lfile2 = 'dictionaries/all.turkerqual'
 langs1 = [l.split('\t')[0] for l in open(lfile1).readlines()]
 langs2 = [l.split('\t')[0] for l in open(lfile2).readlines()]
 
-extlangs = list(set(langs1).intersection(set(langs2)))
-for l in extlangs: print '%s '%l,
-print
+extlangs = ['az','bg','bn','bs','cy','es','fa','hi','id','lv','ms','ne','pl','ro','ru','sk','so','sq','sr','ta','tr','uk','ur','uz']
+
+#extlangs = list(set(langs1).intersection(set(langs2)))
+#for l in extlangs: print '%s '%l,
+#print
 
 file1 = sys.argv[1]
 file2 = sys.argv[2]
@@ -88,8 +90,6 @@ for lang in turkers_by_lang:
 #	print 'Total Turkers: %d'%len(s1)
 
 	if len(s1) > 0 and len(s2) > 0:
-		
-		all1 += s1; all2 += s2;
 
 #		print '\tTheir average:', sum(s1)/len(s1)
 #		print '\tOur average:', sum(s2)/len(s2)
@@ -98,11 +98,14 @@ for lang in turkers_by_lang:
 #		print '\tSpearman:', scipy.stats.spearmanr(s1,s2)
 #		print '\tKendall Tau:', scipy.stats.kendalltau(scipy.stats.stats.rankdata(s1),scipy.stats.stats.rankdata(s2))
 		if lang in extlangs: 
+			all1 += s1; all2 += s2;
+
 			pavged.append(scipy.stats.pearsonr(s1,s2))
 			savged.append(scipy.stats.spearmanr(s1,s2))
 			kavged.append(scipy.stats.kendalltau(scipy.stats.stats.rankdata(s1),scipy.stats.stats.rankdata(s2)))
 #	print
 	#print zip(ids,s1,s2)
+print len(all1), len(all2)
 print 'Their average:', sum(all1)/len(all1)
 print 'Our average:', sum(all2)/len(all2)
 

### 2013-03-28 code/src/dictionaries.py

@@ -11,7 +11,7 @@ import itertools
 from scipy import stats
 import compile_data_from_raw as dat
 
-RAW_DIR = '../..'
+RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11'
 DICT_PATH = './translations.out'
 CLPAIRS = './cl-pairs.csv'
 OUTPUT_DIR = 'output'

### 2013-03-28 code/src/figures.py

@@ -357,15 +357,18 @@ def goog_match_qual(cut=50):
 	        	n, (smin, smax), sm, sv, ss, sk = stats.describe(goog)
         		moe = math.sqrt(sv)/math.sqrt(n) * 2.576
 			goog_by_lang[l] = (sm, (sm - moe, sm + moe), n, moe)
-        n, (smin, smax), sm, sv, ss, sk = stats.describe(avg_qual)
-        moe = math.sqrt(sv)/math.sqrt(n) * 2.576
-	qual_by_lang['avg'] = (sm, (sm - moe, sm + moe), n, moe)
-        n, (smin, smax), sm, sv, ss, sk = stats.describe(avg_match)
-        moe = math.sqrt(sv)/math.sqrt(n) * 2.576
-	match_by_lang['avg'] = (sm, (sm - moe, sm + moe), n, moe)
-        n, (smin, smax), sm, sv, ss, sk = stats.describe(avg_goog)
-        moe = math.sqrt(sv)/math.sqrt(n) * 2.576
-	goog_by_lang['avg'] = (sm, (sm - moe, sm + moe), n, moe)
+        #n, (smin, smax), sm, sv, ss, sk = stats.describe(avg_qual)
+        #moe = math.sqrt(sv)/math.sqrt(n) * 2.576
+	#qual_by_lang['avg'] = (sm, (sm - moe, sm + moe), n, moe)
+        #n, (smin, smax), sm, sv, ss, sk = stats.describe(avg_match)
+        #moe = math.sqrt(sv)/math.sqrt(n) * 2.576
+	#match_by_lang['avg'] = (sm, (sm - moe, sm + moe), n, moe)
+        #n, (smin, smax), sm, sv, ss, sk = stats.describe(avg_goog)
+        #moe = math.sqrt(sv)/math.sqrt(n) * 2.576
+	#goog_by_lang['avg'] = (sm, (sm - moe, sm + moe), n, moe)
+	#print 'qual', qual_by_lang['avg'] 
+	#print 'match', match_by_lang['avg'] 
+	#print 'goog', goog_by_lang['avg'] 
 	goog_graphs(sorted([(k,qual_by_lang[k],match_by_lang[k], goog_by_lang[k]) for k in qual_by_lang], key=operator.itemgetter(1), reverse=True), cutoff=cut)
 
 #returns a dict of {attr1: {attr2: list of assignments}}
[…]

### 2013-03-28 code/src/wikitables.py

@@ -6,7 +6,8 @@ LANG_PATH = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-
 
 if __name__ == '__main__':
 	lmap = figures.reverse_lang_map(LANG_PATH)
-	all_classes = { '>500k':[], '100k-500k':[], '50k-100k':[], '20k-50k':[], '<20k':[]}
+#	all_classes = { '>500k':[], '100k-500k':[], '50k-100k':[], '10k-50k':[], '<10k':[]}
+	all_classes = { '>500k':[], '100k-500k':[], '10k-100k':[], '<10k':[]}
 	our_langs = set([l.strip() for l in open('alllangs').readlines()])
 	for line in csv.DictReader(open('wikicounts'), delimiter='\t'):
 		lang = line['Wiki']
@@ -16,13 +17,13 @@ if __name__ == '__main__':
 				all_classes['>500k'].append(lang)
 			elif num > 100000:		
 				all_classes['100k-500k'].append(lang)
-			elif num > 50000:		
-				all_classes['50k-100k'].append(lang)
-			elif num > 17050:		
+#			elif num > 50000:		
+#				all_classes['50k-100k'].append(lang)
+			elif num > 10000:		
 				print '%s_%d'%(lang,num)
-				all_classes['20k-50k'].append(lang)
+				all_classes['10k-100k'].append(lang)
 			else:		
-				all_classes['<20k'].append(lang)
+				all_classes['<10k'].append(lang)
 	for c in all_classes:
 		print c
 		for l in sorted(all_classes[c]):

### 2013-03-29 writeup/paper.tex
code changes for correlations, figures, etc

@@
 
-We quantified the quality of each translation assignment based on the output of the quality assurance HIT as follows:
+We quantified the quality of each translation assignment based on the output of the quality assurance HIT by taking proportion of correct controls.
+A control was considered correct if it exactly matched the gold standard translation, or if it was judged to be synonymous with the correct translation.
+I.e.:
 \begin{align}	
-	\text{Quality}(a_i) = \frac{1}{k}\sum\limits_{j=1}^{k_i}\mathbf{1}(tr_{ij} \in \texttt{syns[$g_j$]})
+	\text{Quality}(a_i) = \frac{1}{k_i}\sum\limits_{j=1}^{k_i}\mathbf{1}(tr_{ij} \in \texttt{syns[$g_j$]})
 \end{align}	
@@
 Figure \ref{completion-time} gives the completion times for 40 languages.  
-Urdu and Russian were the first languages to be launched, followed by the others 2 days later.
+Workers for Urdu and Russian HITs responded almost immediately; workers in the other languages began slightly later.
 The 10 languages to finish in the shortest amount of time were: Tamil, Malayalam, Telugu, Hindi, Macedonian, Spanish, Serbian, Romanian, Gujarati, and Marathi.
@@
 Results are show below in table \ref{corr-table}.
+We were able to validate the dictionaries we received from MTurk in the 27 languages for which we had external dictionaries: az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, uz.
+Across all 27 languages, 23\% of the source words from the Mechanical Turk dictionaries appeared in the external dictionaries, and could be validated.
+This was an average of 22\% per language.
 
@@
 &$\rho$\\
-Language quality&0.58\\
-Turker quality (languages pooled)&0.37\\
-Avg. Turker quality (languages separate)&0.21\\
+Language quality&0.41\\
+Turker quality (languages pooled)&0.43\\
+Avg. Turker quality (languages separate)&0.26\\
 \hline\hline

### 2013-03-29 code/src/anova_for_matlab.py

@@ -1,0 +1,107 @@
+import re
+import os
+import os.path
+import csv
+import sys
+import math
+import numpy
+import scipy
+import string
+import operator
+import itertools
+import dictionaries
+from scipy import stats
+from scipy.stats import norm
+import matplotlib.pyplot as plt
+from matplotlib import font_manager as fm
+
+DATA_DIR = 'output'
+tmap = dictionaries.turker_map()
+
+def scores():
+        scores = dict()
+        for line in open('%s/byturker.voc.quality.new'%DATA_DIR).readlines():
+                l = line.split('\t')
+		try:
+	                scores[l[0]] = float(l[1].strip())
+		except ValueError:
+			print 'Error', l
+			continue
+        return scores
+
+def cl_list():
+	s = scores()
+	assigns = [l.strip() for l in open('%s/byassign.voc.validclpair'%DATA_DIR).readlines()]
+	score_dist = list()
+	for a in assigns:
+		t = tmap[a]
+		if t in s:
+			score_dist.append(s[t])
+	return score_dist
+
+def noncl_list():
+	s = scores()
+	assigns = [l.strip() for l in open('%s/byassign.voc.invalidclpair'%DATA_DIR).readlines()]
+	score_dist = list()
+	for a in assigns:
+		t = tmap[a]
+		if t in s:
+			score_dist.append(s[t])
+	return score_dist
+
+def natlang_list(match=True):
+	s = scores()
+	score_dist = list()
+        for line in csv.DictReader(open('%s/byassign.voc.accepted'%DATA_DIR), delimiter='\t'):
+		a = line['id']
+		if match:
+			use = line['lang'] == line['hitlang']
+		else:
+			use = not(line['lang'] == line['hitlang'])
+		if use:
+			t = tmap[a]
+			if t in s:
+				score_dist.append(s[t])
+	return score_dist
+
+def yrseng_list(cutoff = 10):
+	s = scores()
+	score_dist = list()
+        for line in csv.DictReader(open('%s/byassign.voc.accepted'%DATA_DIR), delimiter='\t'):
+		a = line['id']
+		if line['yrseng'] >= cutoff:
+			t = tmap[a]
+			if t in s:
+				score_dist.append(s[t])
+	return score_dist
+
+def full_list():
+	s = scores()
+	score_dist = [s[t] for t in s]
+	return score_dist
+
+def anova(lists):
[…]

### 2013-03-29 code/src/correlation_google.py

@@ -1,0 +1,30 @@
+#!/bin/python
+
+import sys
+import scipy.stats
+
+if len(sys.argv) < 3:
+	print 'USAGE ./correlation.py FILE1 FILE2'
+	exit(0)
+
+
+file1 = sys.argv[1]
+file2 = sys.argv[2]
+
+scores1 = list(); scores2 = list()
+
+for s1, s2 in zip(open(file1).readlines(), open(file2).readlines()):
+	s1 = s1.strip(); s2 = s2.strip();
+	if s1 == 'N/A' or s2 == 'N/A':
+		continue
+	scores1.append(float(s1))
+	scores2.append(float(s2))
+
+
+print 'Their average:', sum(scores1)/len(scores1)
+print 'Our average:', sum(scores2)/len(scores2)
+
+print 'Pearson:', scipy.stats.pearsonr(scores1,scores2)
+print 'Spearman:', scipy.stats.spearmanr(scores1,scores2)
+print 'Kendall Tau:', scipy.stats.kendalltau(scipy.stats.stats.rankdata(scores1),scipy.stats.stats.rankdata(scores2))
+

### 2013-03-29 code/src/external_compare.py

@@ -26,8 +26,8 @@ for dict_file in os.listdir(EXTERN_OVERLAP):
 	d, lang = dict_file.split('.')
 	if lang not in pair_scores: pair_scores[lang] = dict()
 	for line in open('%s/%s'%(EXTERN_OVERLAP,dict_file,)).readlines():
-		src, tran, is_control, known_correct, observed, is_match = line.strip().split('\t')
-		pair_scores[lang][(reg(src),reg(tran))] = int(is_match)
+		src, tran, is_control, known_correct, observed, is_match, in_ext = line.strip().split('\t')
+		if int(in_ext) == 1: pair_scores[lang][(reg(src),reg(tran))] = int(is_match)
 
 lang_scores = dict()
 
@@ -47,7 +47,8 @@ for dict_file in os.listdir(root_dir):
 					except KeyError: lang_scores[lang][2] += 1
 
 for lang, (match, tot, skipped) in lang_scores.iteritems():
-	print '%s\t%.03f\t%d\t%d'%(lang, match/tot, tot, skipped)
+	if tot == 0 : print '%s\t%.03f\t%d\t%d'%(lang, 0, tot, skipped)
+	else: print '%s\t%.03f\t%d\t%d'%(lang, match/tot, tot, skipped)
 
 
 

### 2013-03-29 code/src/external_compare_assigns.py

@@ -28,8 +28,8 @@ for dict_file in os.listdir(EXTERN_OVERLAP):
 	d, lang = dict_file.split('.')
 	if lang not in pair_scores: pair_scores[lang] = dict()
 	for line in open('%s/%s'%(EXTERN_OVERLAP,dict_file,)).readlines():
-		src, tran, is_control, known_correct, observed, is_match = line.strip().split('\t')
-		pair_scores[lang][(reg(src),reg(tran))] = int(is_match)
+		src, tran, is_control, known_correct, observed, is_match, in_ext = line.strip().split('\t')
+		if int(in_ext) == 1:pair_scores[lang][(reg(src),reg(tran))] = int(is_match)
 
 assign_pairs = dict()
 

### 2013-03-29 code/src/figures.py

@@ -170,6 +170,32 @@ def conf_int_by_attr_turker(attr):
 	print "n/a", ret['N/A'][2]
 	return ret
 
+#return a dict of {attr: quality estimate}
+#e.g. if attr is 'country', returns something like {IN: quality estimate of IN, RU: quality estimate of RU...}
+#quality estimates are average qualities over turkers 
+def conf_int_by_attr_region(attr, filterlist=[]):
+        tmap = dictionaries.turker_map()
+        ret = dict()
+        data = read_table_file('%s/byassign.voc.accepted'%OUTPUT_DIR)
+        scores = all_avg_scores('%s/byturker.voc.quality%s'%(OUTPUT_DIR,QC,))
+        langs = all_keys('%s/byassign.voc.accepted'%OUTPUT_DIR, attr)
+        tot = 0
+        avg = list()
+        for l in langs:
+                alist = select_by(data, attr, l).keys()
+		alist = list(set(alist).intersection(set(filterlist)))
+                num_assign = len(alist)
+                tot += num_assign
+                tlist = list(set([tmap[a] for a in alist]))
+		num_turker = len(tlist)
+                avg += tlist
+                ci = avg_score(tlist, scores)
+		if ci is not None: ret[l] = (ci[0], ci[1], num_assign, num_turker, ci[3])
+        ci = avg_score(avg, scores)
+        ret['avg'] = ci
+        print "tot", tot
+        return ret
+
 #compile quality estimates by hit language, and graph the results
 #quality estimates are averages over assignments, cut is minimum number of assignments needed for a hitlang
 #to be included in the graph
@@ -729,6 +755,159 @@ def native_compare_line_graph(native, nonnative):
 	plt.title('Number of native vs. nonnative turkers by # of years speaking English')
 	plt.show()
 
+def dictionary_stats_turker():
+#tr      NL:3    GR:1    CA:1    TR:39   MK:12   GE:1    AU:1    US:20   RO:5    BA:1
+	DICT_DIR = 'dictionaries'
+        dict_files=['%s/nonclpair.turkerlist'%DICT_DIR, '%s/clpair.turkerlist'%DICT_DIR]
+        data = dict()
[…]

### 2013-03-29 code/src/predict_turker_qual.py

@@ -1,0 +1,180 @@
+import os
+import re
+import csv
+import sys
+import string
+import random
+import os.path
+import argparse
+import operator
+
+import pickle
+import dictionaries
+
+import math
+import numpy
+import scipy
+from scipy import stats
+from scipy.stats import norm
+
+from sklearn.cross_validation import KFold
+from sklearn.grid_search import GridSearchCV
+from sklearn.cross_validation import cross_val_score
+from sklearn.linear_model import LogisticRegression
+
+DATA_DIR = 'output'
+tmap = dictionaries.turker_map()
+
+def pr(clf, X, Y):
+        """Print precision, recall, and accuracie for error detection classifier"""
+        tp = 0.0
+        fp = 0.0
+        tn = 0.0
+        fn = 0.0
+        total = 0.0
+        for x,y in zip(X,Y):
+                total += 1
+                yhat = clf.predict(x)
+                if y == 0:
+                        if yhat == 0: tn += 1
+                        elif yhat == 1: fp += 1
+                elif y == 1:
+                        if yhat == 0: fn += 1
+                        elif yhat == 1: tp += 1
+        a =  (tp + tn) / total
+	if (tp + fp) == 0: p = 0
+	else: p = tp / (tp + fp)
+        if (tp + fn) == 0: r = 0
+        else: r = tp / (tp + fn)
+        print 'Guessed Positive: %.03f\tGuessed Negative: %.03f'%(tp+fp,tn+fn)
+        print 'Total Positive: %.03f\tTotal Negative: %.03f'%(tp+fn,tn+fp)
+        print 'Precision: %.03f\tRecall: %.03f\tAccuracy: %.03f'%(p,r,a,)
+
+
+
+def cv_clf(X, Y):
+        """Prints 3fold cross validation accuracie of SVM on labels Y and features X"""
+        res = cross_val_score(LogisticRegression(), X, Y)
+	return res
+
+def train_clf(X, Y):
+        """Trains SVM on features X and labels Y"""
+        #params = [{'C':[.01, .1, 1, 10, 100], 'kernel':['linear', 'poly', 'rbf']}]
+        #clf = GridSearchCV(SVC(), params, refit=True)
[…]

### 2013-03-29 code/src/qc.py

@@ -390,8 +390,8 @@ if __name__ == '__main__':
 	if sys.argv[1] == 'assignments': 
 		write_avg_quals(get_quality_by_assign('%s/voc_hits_results'%RAW_DIR), '%s/byassign.voc.quality'%OUTPUT_DIR)
 	if sys.argv[1] == 'turker':
-#		quality_by_turker('%s/byturker.voc.quality.external'%OUTPUT_DIR, '%s/byassign.voc.quality.external'%OUTPUT_DIR)
-		quality_by_turker('%s/byturker.voc.quality'%OUTPUT_DIR, '%s/byassign.voc.quality'%OUTPUT_DIR)
+		quality_by_turker('%s/byturker.voc.quality.external.ext'%OUTPUT_DIR, '%s/byassign.voc.quality.external.ext'%OUTPUT_DIR)
+#		quality_by_turker('%s/byturker.voc.quality'%OUTPUT_DIR, '%s/byassign.voc.quality'%OUTPUT_DIR)
 	if sys.argv[1] == 'goog':
 		write_avg_quals(get_goog_match_by_assign('%s/voc_hits_results'%RAW_DIR), '%s/byassign.googmatch'%OUTPUT_DIR)
 		googmatch_by_turker('%s/byturker.googmatch'%OUTPUT_DIR,'%s/byassign.googmatch'%OUTPUT_DIR)

### 2013-03-29 code/src/region_scatter.py

@@ -1,0 +1,112 @@
+import re
+import csv
+import itertools
+import operator
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import font_manager as fm
+import string
+
+COUNTRIES = 'ref/countrycodemap'
+RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11'
+DICT_DIR = 'dictionaries'
+
+def reverse_lang_map(path):
+        lang_data = {}
+        for line in csv.DictReader(open(path)):
+                lang = line['name']
+                prefix = line['prefix']
+                if(prefix not in lang_data):
+                        lang_data[prefix] = re.sub('_',' ',lang)
+        return lang_data
+	
+def country_breakdown():
+        dict_file='%s/clpair.turkerlist'%DICT_DIR
+        nondict_file='%s/nonclpair.turkerlist'%DICT_DIR
+	data = dict()
+	for line in open(dict_file).readlines():
+		comps = line.split()
+		lang = comps[0]
+		breakdown = [(c.split(':')[0], int(c.split(':')[1])) for c in comps[1:]]
+		data[lang] = breakdown
+	nondata = dict()
+	for line in open(nondict_file).readlines():
+		comps = line.split()
+		lang = comps[0]
+		breakdown = [(c.split(':')[0], int(c.split(':')[1])) for c in comps[1:]]
+		nondata[lang] = breakdown
+	return ({k: data[k] for k in data if not k == 'total'},{k: nondata[k] for k in nondata if not k == 'total'})
+
+def dictionary_stats_turker():
+        dict_files=['%s/nonclpair.numturkers'%DICT_DIR, '%s/clpair.numturkers'%DICT_DIR]
+        data = dict()
+        for line in open(dict_files[0]).readlines():
+                lang, count = line.split()
+                data[lang] = (float(count), 0)
+        for line in open(dict_files[1]).readlines():
+                lang, count = line.split()
+		if lang in data:
+                	data[lang] = (data[lang][0], float(count))
+	ret = list()
+	for d in data:
+		ret.append((d, data[d][0], data[d][1], data[d][0] + data[d][1]))
+        return ret 
+
+def dictionary_stats_turkerqual():
+        dict_files=['%s/nonclpair.turkerqual'%DICT_DIR, '%s/clpair.turkerqual'%DICT_DIR]
[…]

### 2013-03-30 writeup/paper.tex
Made some changes to the description of translation quality
We'll change these again, since we're going to move towards assignment
quality instead of averaging over Turker quality.

--- 2013-03-28 writeup/paper.tex
@@
 
+%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
+\begin{figure*}[h]
+\includegraphics[width=\linewidth]{final-figures/google-match-bar}
+\caption{Translation quality for languages with at least 50 active turkers.
+The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms.
+Overall average quality was 0.46 (0.53 among languages with at least 50 Turkers).}
+\label{hitlangqual}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \paragraph{Translation HIT}
@@
 
-We quantified the quality of each translation assignment based on the output of the quality assurance HIT as follows:
+We calculate the quality of translations on the level of individual assignments, individual workers, and languages.
+We define an assignment's quality as the proportion of controls that are correct in a given assignment, where correct means exactly correct or judged to be synonymous.
 \begin{align}	
-	\text{Quality}(a_i) = \frac{1}{k}\sum\limits_{j=1}^{k_i}\mathbf{1}(tr_{ij} \in \texttt{syns[$g_j$]})
+	\text{Quality}(a_i) = \frac{1}{k}\sum\limits_{j=1}^{k_i}\mathbf{\delta}(tr_{ij} \in \texttt{syns[$g_j$]})
 \end{align}	
-where $a_i$ is the $i^{th}$ assignment, $k_i$ is the number of controls in $a_i$, $tr_j$ is the Turker's provided translation of control word $j$ in assignment $i$, $g_j$ is the gold standard translation of control word $j$, \texttt{syns[$g_j$]} is the set of words judged to be synonymous with $g_j$ during the second pass HIT, and $\mathbf{1}(x)$ is 1 when $x$ is true.
-
+where $a_i$ is the $i^{th}$ assignment, $k_i$ is the number of controls in $a_i$, $tr_j$ is the Turker's provided translation of control word $j$ in assignment $i$, $g_j$ is the gold standard translation of control word $j$, \texttt{syns[$g_j$]} is the set of words judged to be synonymous with $g_j$ and includes $g_j$, and $\mathbf{\delta}(x)$ is Kronecker's delta and takes value 1 when $x$ is true.
 Most assignments had two known words embedded, so most assignments had scores of either 0, 0.5, or 1.
 
-Since by-assignment quality scores are noisy and sensitive to small numbers of highly active Turkers, we report quality scores as the average per-turker quality, where a Turker's quality is just the average quality of all the assignments that the Turker completed:
+Since judging overall quality for a language with assignment quality scores is biased towards to small numbers of highly active Turkers, we instead report language quality scores as the average per-turker quality, where a Turker's quality is  the average quality of all the assignments that she completed:
 \begin{align}	
@@
 where $t_i$ is the $i^{th}$ turker, \texttt{assigns[$i$]} is the assignments completed by turker $i$, and Quality($a$) is as above.
-
+%
 Quality for a language is then given by
@@
 
-Measured in this way, the average quality score across all HITs in all languages is just under 0.46. When restricted to languages with at least 50 Turkers, the average quality is 0.53.
-
-%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
-\begin{figure}[h]
-\centering
-\includegraphics[height=\linewidth,angle=270]{final-figures/google-match-bar}
-\caption{Translation quality of by source language.
-Blue bars show quality estimates by language and green bars show proportion of translations which matched Google Translate.
-Total quality is calculated as the average number of control words which were correct translations of the source word, where ”correct” means that the provided translation was judged to be synonymous with the known translation by workers in a second-
-pass HIT.
-Dark blue bars indicate the proportion of translations which exactly matched known translations, and light blue indicate translations which were judged to be correct synonyms.
-Quality estimates are only show for languages with at least 50 active turkers.
-Overall average quality was 0.46 (0.53 among languages with at least 50 Turkers).}
-\label{hitlangqual}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Figure \ref{hitlangqual} shows the translation quality for for languages with contributions from at least 50 workers. The 
+%Measured in this way, the average quality score across all HITs in all languages is just under 0.46. When restricted to languages with at least 50 Turkers, the average quality is 0.53.
 

### 2013-03-30 code/src/figures.py
qualities by assignments

@@ -125,26 +125,44 @@ def avg_score(assign_list, scores):
 		return None
 	n, (smin, smax), sm, sv, ss, sk = stats.describe(dist)
 	moe = math.sqrt(sv)/math.sqrt(n) * 2.576
-	return (sm, (sm - moe, sm + moe), n, moe)
+	return (sm, (sm - moe, sm + moe), n, moe, sv)
 
 #return a dict of {attr: quality estimate}
 #e.g. if attr is 'country', returns something like {IN: quality estimate of IN, RU: quality estimate of RU...}
 #quality estimates are average qualities over assignments
 def conf_int_by_attr(attr):
-	ret = dict()
-	data = read_table_file('%s/byassign.voc.accepted'%OUTPUT_DIR)
-	scores = all_avg_scores('%s/byassign.voc.quality%s'%(OUTPUT_DIR,QC,))
-	langs = all_keys('%s/byassign.voc.accepted'%OUTPUT_DIR, attr)
-	avg = list()
-	for l in langs:
-		alist = select_by(data, attr, l).keys()
-		avg += alist
-		ci = avg_score(alist, scores)
-		ret[l] = ci
-	ci = avg_score(avg, scores)
-	ret['avg'] = ci
+#	ret = dict()
+#	data = read_table_file('%s/byassign.voc.accepted'%OUTPUT_DIR)
+#	scores = all_avg_scores('%s/byassign.voc.quality%s'%(OUTPUT_DIR,QC,))
+#	langs = all_keys('%s/byassign.voc.accepted'%OUTPUT_DIR, attr)
+#	avg = list()
+#	for l in langs:
+#		alist = select_by(data, attr, l).keys()
+#		avg += alist
+#		ci = avg_score(alist, scores)
+#		ret[l] = ci
+#	ci = avg_score(avg, scores)
+#	ret['avg'] = ci
+#	return ret
+        ret = dict()
+        data = read_table_file('%s/byassign.voc.accepted'%OUTPUT_DIR)
+        scores = all_avg_scores('%s/byassign.voc.quality%s'%(OUTPUT_DIR,QC,), turkers=False)
+        langs = all_keys('%s/byassign.voc.accepted'%OUTPUT_DIR, attr)
+        tot = 0
+        avg = list()
+        for l in langs:
+                alist = select_by(data, attr, l).keys()
+                num_assign = len(alist)
+                tot += num_assign
+                avg += alist
[…]

### 2013-03-30 writeup/paper.tex
Moved and cropped some figures
Further reorganizing

--- 2013-03-30 writeup/paper.tex
@@
 \caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 languages with $\leq$20 speakers. 
-We omit 1,797 Turkers who did not report their native language, 243 who reported 2 native languages, and 83 who reported $\geq$3 native languages.}\label{lang-pie}
+We omit 1,797 Turkers who did not report their native language, 243 who reported 2 native languages, and 83 with $\geq$3 native languages.}\label{lang-pie}
 \end{table}
@@
 \begin{figure*}[h]
-\includegraphics[width=\linewidth]{final-figures/google-match-bar}
+\includegraphics[width=\linewidth]{final-figures/Google-match-bar}
 \caption{Translation quality for languages with at least 50 active turkers.
@@
 
-\section{Measuring Data Quality}
+\section{Measuring Translation Quality}
 
@@
 
-Figure \ref{hitlangqual} shows the translation quality for for languages with contributions from at least 50 workers. The 
-%Measured in this way, the average quality score across all HITs in all languages is just under 0.46. When restricted to languages with at least 50 Turkers, the average quality is 0.53.
+Figure \ref{hitlangqual} shows the translation quality for for languages with contributions from at least 50 workers.
 
-\section{Data Analysis}
+\section{Additional Data Analysis}
 
@@
 \item How quickly can we expect work to be completed in a particular language? 
+\item Do workers accurately represent their language abilities?  Should we constrain tasks by region? 
 \item What is the quality of crowdsourced translations without quality control versus with it?
-\item Do workers accurately represent their language abilities?  Should we constrain tasks by region? 
+
 \end{itemize}
+
+\paragraph{Speed of completion}
 
@@
 \begin{figure}[h]
-\centering
 \includegraphics[height=\linewidth,angle=270]{final-figures/completetime}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph{Speed of completion}
 
@@
 
-\paragraph{Validation of controls} As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
-Turkers' performance on our control tasks is well correlated with this measure of quality.
-Results are show below in table \ref{corr-table}.
-
-\begin{table}[h]
-\centering
-\begin{tabular}{lc}\hline\hline\\
-&$\rho$\\
-Language quality&0.58\\
-Turker quality (languages pooled)&0.37\\
-Avg. Turker quality (languages separate)&0.21\\
-\hline\hline
-\end{tabular}
-\caption{Pearson correlation of quality measured by accuracy on control translations vs.
-quality measured by overlap with external dictionaries.
-Language is the correlation of quality estimates for each language (across 27 languages), Turker quality is the correlation of quality estimates for each Turker (2,472 turkers).
-Avg.
-Turker quality is computed by taking the correlation of Turker quality estimates separately for each of the 27 languages, and then taking the average of the correlations.
-The figure reflects data from 27 languages for which we had available external dictionaries: az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, uz.}
-\label{corr-table}
-\end{table}
-
-\paragraph{Use of machine translation}
-Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems.
-This strategy does not prevent workers from typing the words into an MT system, if they understand the language's script.
-We measured the percent of translations received that exactly matched the translation returned from google translate.
-Results are show in figure \ref{google-match-bar}.
-Assignments averaged around 43\% overlap with google translate.
-Higher overlap with google translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some of the control translations used may have been already indexed by Google.
-Languages with exotic scripts (such as Arabic (ar), Chinese (zh), and Telugu (te)) have especially low overlap with Google.
-
 %%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
-\begin{figure*}[h]
+\begin{table*}[h]
 \footnotesize
@@
 \hline\hline
-\label{region-summary}
 \end{tabular}
-\end{figure*}
+\caption{Translation quality when partitioning the translations into two groups, one contains translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other contains translations from Turkers outside those regions.
+}\label{region-summary}
+\end{table*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\paragraph{Use of machine translation}
+Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems.
+This strategy does not prevent workers from typing the words into an MT system, if they understand the language's script.
+We measured the percent of translations received that exactly matched the translation returned from Google translate.
+Results are show in figure \ref{Google-match-bar}.
+Assignments averaged around 43\% overlap with Google translate.
+Higher overlap with Google translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some of the control translations used may have been already indexed by Google.
+Languages with exotic scripts (such as Arabic (ar), Chinese (zh), and Telugu (te)) have especially low overlap with Google.
+
+\paragraph{Validation of controls} As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
+Turkers' performance on our control tasks is well correlated with this measure of quality.
+Results are show below in Table \ref{corr-table}.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{lc}
+&$\rho$\\
+\hline\hline
+Language quality&0.58\\
+Turker quality (languages pooled)&0.37\\
+Avg. Turker quality (languages separate)&0.21\\
+\hline\hline
+\end{tabular}
+\caption{Pearson correlation of quality measured by accuracy on control translations vs.
+quality measured by overlap with external dictionaries.
+Language is the correlation of quality estimates for each language (across 27 languages), Turker quality is the correlation of quality estimates for each Turker (2,472 turkers).
+Avg.
+Turker quality is computed by taking the correlation of Turker quality estimates separately for each of the 27 languages, and then taking the average of the correlations.
+The figure reflects data from 27 languages for which we had available external dictionaries: az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, uz.}
+\label{corr-table}
+\end{table}
+
 \section{Discussion}

### 2013-03-30 writeup/paper.tex
Cropped image.
Tweaking the validation of controls subsection

@@
 \centering
-\includegraphics[width=\linewidth]{final-figures/turkermap}
+\includegraphics[width=\linewidth]{final-figures/Turkermap}
 \caption{The number of workers per country.
@@
 \begin{figure*}[h]
-\includegraphics[width=\linewidth]{final-figures/Google-match-bar}
-\caption{Translation quality for languages with at least 50 active turkers.
+\begin{center}
+\includegraphics[width=0.8\linewidth]{final-figures/Google-match-bar}
+\caption{Translation quality for languages with at least 50 active Turkers.
 The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms.
@@
 \label{hitlangqual} 
+\end{center}
 \end{figure*}
@@
 
-Since judging overall quality for a language with assignment quality scores is biased towards to small numbers of highly active Turkers, we instead report language quality scores as the average per-turker quality, where a Turker's quality is  the average quality of all the assignments that she completed:
+Since judging overall quality for a language with assignment quality scores is biased towards to small numbers of highly active Turkers, we instead report language quality scores as the average per-Turker quality, where a Turker's quality is  the average quality of all the assignments that she completed:
 \begin{align}	
@@
 \end{align}	
-where $t_i$ is the $i^{th}$ turker, \texttt{assigns[$i$]} is the assignments completed by turker $i$, and Quality($a$) is as above.
+where $t_i$ is the $i^{th}$ Turker, \texttt{assigns[$i$]} is the assignments completed by Turker $i$, and Quality($a$) is as above.
 %
@@
 \begin{align}	
-	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{turkers[$i$]}\text{Quality}(t_j)}}{\mid \texttt{turkers[$i$]} \mid}
+	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{Turkers[$i$]}\text{Quality}(t_j)}}{\mid \texttt{Turkers[$i$]} \mid}
 \end{align}	
-where $l_i$ is the ith language, \texttt{turkers[$i$]} is the set of turkers who completed assignments for language $i$, and Quality($t$) is as above.
+where $l_i$ is the ith language, \texttt{Turkers[$i$]} is the set of Turkers who completed assignments for language $i$, and Quality($t$) is as above.
 
@@
 
-\section{Additional Data Analysis}
+\section{Further Data Analysis}
 
@@
 \item Do workers accurately represent their language abilities?  Should we constrain tasks by region? 
-\item What is the quality of crowdsourced translations without quality control versus with it?
-
+\item How prevalent is the use of machine translation? 
+%\item What is the quality of crowdsourced translations without quality control versus with it? 
 \end{itemize}
@@
 
-%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
+%%%%%%%%%%%%%%% Turker QUAL SUMMARY TABLE %%%%%%%%%%%
 \begin{table*}[h]
@@
 \hline\hline
-&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&Primary locations&Primary locations\\
-&In region&Out of region&of turkers in region&of turkers out of region\\
+&\multicolumn{2}{c}{Avg. Turker quality (\# Ts)}&Primary locations&Primary locations\\
+&In region&Out of region&of Turkers in region&of Turkers out of region\\
 \hline\hline
@@
 \end{tabular}
+\normalsize
 \caption{Translation quality when partitioning the translations into two groups, one contains translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other contains translations from Turkers outside those regions.
@@
 Overall, 4,465 workers were located in a region likely to speak the language from which they were translating, and 3,170 workers were located in countries considered out of region (meaning almost half of our 5,277 Turkers completed HITs in multiple languages).
-Across all languages, there is no significant quality difference between turkers in region and out of region (0.504 and 0.496, respectively).
-However, within each language, the effect of location on quality varies greatly (table \ref{region-summary}).
 
-Among the languages with the largest number of Turkers total, most workers are in region (see table \ref{region-summary}).
-The majority of out-of-region Turkers were located in India; the languages with the most out of region Turkers are as follows (total number out of region and number located in India in parenthesis): Malay (110/106), Amharic (98/69), Afrikaans (98/93), Icelandic (90/83), and Breton (88/82).
+Table \ref{region-summary} shows the differences in translation quality when computed using in-region versus out-of-region Turkers, for the languages with the greatest number of workers.
+Within region workers typically produced higher quality translations.
+Given the number of Indian workers on Mechanical Turk, it is unsurprising that they represent majority of out-of-region workers.
+For the languages that had more than 80 out of region workers (Malay, Amharic, Afrikaans, Icelandic, and Breton), Indian workers represented 90\% of the out of region workers for all of them aside from Amharic.
 
-%%%%%%%%%%%%%%% ASSIGNMENT SCATTER %%%%%%%%%%%
-\begin{figure*}[h]
-\centering
-\includegraphics[width=6in]{final-figures/assign-turk-scatter}
-\caption{Number of assignments and number of Turkers for each language.
+%When averaged across all languages, there is no significant quality difference between Turkers in region and out of region (0.504 and 0.496, respectively).
+However, within each language, the effect of location on quality varies greatly (Table \ref{region-summary}).
+
+% CCB - commented out this figure and paragraph.  I'm not sure that this figure adds any new information
+%
+%%%%%%%%%%%%%%%% ASSIGNMENT SCATTER %%%%%%%%%%%
+%\begin{figure*}[h]
+%\centering
+%\includegraphics[width=6in]{final-figures/assign-turk-scatter}
+%\caption{Number of assignments and number of Turkers for each language.
 Each dot represents a language.
 Figure includes only data from Turkers who reported only one native language consistantly across assignments, representing approx.
-3900 turkers across 139,000 assignments.}
-\label{ass-scatter}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Figure \ref{ass-scatter} shows the volume of HITs completed and the number of workers participating for each language.
-While the bulk (19\%) of bilingual Turkers report English as their native language (see figure \ref{lang-pie}), Mechanical Turk's capacity to support the Indian languages is apparent.
+3900 Turkers across 139,000 assignments.}
+%\label{ass-scatter}
+%\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%Figure \ref{ass-scatter} shows the volume of HITs completed and the number of workers participating for each language.
+While the bulk (19\%) of bilingual Turkers report English as their native language (see Figure \ref{lang-pie}), Mechanical Turk's capacity to support the Indian languages is apparent.
 Hindi, Tamil, and Malayalam are especially well represented in terms of number of active translators.
@@
 \paragraph{Use of machine translation}
+
 Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems.
@@
 We measured the percent of translations received that exactly matched the translation returned from Google translate.
-Results are show in figure \ref{Google-match-bar}.
+Results are show in Figure \ref{Google-match-bar}.
 Assignments averaged around 43\% overlap with Google translate.
@@
 
-\paragraph{Validation of controls} As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
+\paragraph{Validation of controls} 
+We investigated the validity of our use of Wikipedia inter-language links as gold standard translations, since they may have been included Google Translate.
+%
+As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
 Turkers' performance on our control tasks is well correlated with this measure of quality.
-Results are show below in Table \ref{corr-table}.
+We had external bilingual dictionaries for 27 of the 119 languages examined in this study.\footnote{The bilingual dictionaries were between en and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz.
+}  We used each of these bilingual dictionaries to computer language-level quality scores, using the dictionary's translation as a gold standard translation for any of the 10,000 foreign words in our study.
+In some cases, the overlap of words was low, since dictionaries list root forms of words and we translated inflected forms.
 
-\begin{table}[h]
-\centering
-\begin{tabular}{lc}
-&$\rho$\\
-\hline\hline
-Language quality&0.58\\
-Turker quality (languages pooled)&0.37\\
-Avg. Turker quality (languages separate)&0.21\\
-\hline\hline
-\end{tabular}
-\caption{Pearson correlation of quality measured by accuracy on control translations vs.
-quality measured by overlap with external dictionaries.
-Language is the correlation of quality estimates for each language (across 27 languages), Turker quality is the correlation of quality estimates for each Turker (2,472 turkers).
-Avg.
-Turker quality is computed by taking the correlation of Turker quality estimates separately for each of the 27 languages, and then taking the average of the correlations.
-The figure reflects data from 27 languages for which we had available external dictionaries: az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, uz.}
-\label{corr-table}
-\end{table}
+We ranked the 27 languages based on their translation quality scores according to the external dictionaries, and its calculated correlation when compared to the ranking produced by our gold standard control.
+The Pearson correlation was $\rho=0.58$.
+We computed a correlation coefficient of $\rho=0.37$ for ranking of the translation quality of individual Turkers using the two sources of reference translations.
+
+Given the strong positive correlation, we are satisfied that the trends reported in this paper hold when using either our gold standard translations or external bilingual dictionaries.
 

### 2013-03-30 writeup/paper.tex
Updated the Use of Machine Translation subsection

@@
 The task paid \$0.15 for the translation of 10 words.  
-
 Each set of 10 words was independently translated by three separate workers.
@@
 
-Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems.
-This strategy does not prevent workers from typing the words into an MT system, if they understand the language's script.
+Given then prevalence of out of region workers, we investigated what proportion of the translations submitted by workers were simply replicating translations from a machine translation system.
+Although we followed best practices to deter copying-and-pasting into online MT systems  by  rendering words and sentences as images \cite{zaidan-callisonburch:2011:ACL-HLT2011a}, this strategy does not prevent workers from typing the words into an MT system, if they are able to type in the language's script.
+
+We used Google Translate to translate all 10,000 words for each of the XXX foreign language that Google Translate covers.
 We measured the percent of translations received that exactly matched the translation returned from Google translate.
@@
 Assignments averaged around 43\% overlap with Google translate.
-Higher overlap with Google translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some of the control translations used may have been already indexed by Google.
-Languages with exotic scripts (such as Arabic (ar), Chinese (zh), and Telugu (te)) have especially low overlap with Google.
+Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphaabet) have lower overlap with Google, suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.
 
 \paragraph{Validation of controls} 
-We investigated the validity of our use of Wikipedia inter-language links as gold standard translations, since they may have been included Google Translate.
-%
+Higher overlap with Google translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some of the control translations used may have been already indexed by Google.
+We therefore investigated the validity of our use of Wikipedia inter-language links as gold standard translations.
+
 As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.

### 2013-03-30 writeup/paper.tex
Modified the discussion section

@@
 \begin{figure*}[h]
-\centering
-\includegraphics[width=6in]{final-figures/quality-scatter}
+\begin{center}
+\includegraphics[width=.8\linewidth]{final-figures/quality-scatter}
+\end{center}
+
 \caption{Estimated quality of translations by country.
@@
 \section{Discussion}
-MTurk has a strong and diverse presence of bilingual workers, making it a promising resource for researchers and developers of multilingual systems.
-Although unfiltered data can contain large amounts of noise, crowdsourced pipelines, which contain human oversight as a means of evaluation, offer a feasible way of ensuring high quality data, even on tasks which require more complex labels.
-While MTurk does offer the ability to restrict workers based on country, embedded per-task controls which are checked either automatically when possible, or manually in a second-pass HIT, are likely to provide higher quality data than naive demographic filters.
+The Mechanical Turk gives research access to a diverse set of bilingual workers, making it a promising resource for researchers and developers of multilingual systems. 
+Although unfiltered data can contain large amounts of noise, 
+a variety of techniques can be incorporated into crowdsourcing pipelines to ensure high quality data.
+Based on our study, we suggest restricting workers to countries that plausibly speak the foreign language of interest, and embedding gold standard controls where possible, rather than relying solely on self-reported language skills.
 
-Although our research targeted bilingual workers on Mechanical Turk, and neglected monolingual workers, we believe our results reliably represent the current speaker populations, since the vast majority of the work available on the crowdsourced platform is currently English-only.
+Although our study targeted bilingual workers on Mechanical Turk, and neglected monolingual workers, we believe our results reliably represent the current speaker populations, since the vast majority of the work available on the crowdsourced platform is currently English-only.
 We therefore assume the number of non-English speakers is small.
@@
 
+\section{Data release}
+
+We plan to release all data used in this study upon publication of this paper.  Our data release will include the raw data, along with bilingual dictionaries that are filtered to be high quality.
+
 \bibliographystyle{acl2012}

### 2013-03-30 writeup/paper.tex
quality by assign

--- 2013-03-30 writeup/paper.tex
@@
 \centering
-\includegraphics[width=\linewidth]{final-figures/Turkermap}
+\includegraphics[width=\linewidth]{final-figures/turkermap}
 \caption{The number of workers per country.
@@
 \caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 languages with $\leq$20 speakers. 
-We omit 1,797 Turkers who did not report their native language, 243 who reported 2 native languages, and 83 with $\geq$3 native languages.}\label{lang-pie}
+We omit 1,797 Turkers who did not report their native language, 243 who reported 2 native languages, and 83 who reported $\geq$3 native languages.}\label{lang-pie}
 \end{table}
@@
 \begin{figure*}[h]
-\begin{center}
-\includegraphics[width=0.8\linewidth]{final-figures/Google-match-bar}
-\caption{Translation quality for languages with at least 50 active Turkers.
+\includegraphics[width=\linewidth]{final-figures/google-match-bar}
+\caption{Translation quality for languages with at least 50 active turkers.
 The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms.
-Overall average quality was 0.46 (0.53 among languages with at least 50 Turkers).}
+Overall average quality was 0.55.}
 \label{hitlangqual}
-\end{center}
 \end{figure*}
@@
 
-\section{Measuring Translation Quality}
+\section{Measuring Data Quality}
 
@@
 
-Since judging overall quality for a language with assignment quality scores is biased towards to small numbers of highly active Turkers, we instead report language quality scores as the average per-Turker quality, where a Turker's quality is  the average quality of all the assignments that she completed:
+Since judging overall quality for a language with assignment quality scores is biased towards to small numbers of highly active Turkers, we instead report language quality scores as the average per-turker quality, where a Turker's quality is  the average quality of all the assignments that she completed:
 \begin{align}	
@@
 \end{align}	
-where $t_i$ is the $i^{th}$ Turker, \texttt{assigns[$i$]} is the assignments completed by Turker $i$, and Quality($a$) is as above.
+where $t_i$ is the $i^{th}$ turker, \texttt{assigns[$i$]} is the assignments completed by turker $i$, and Quality($a$) is as above.
 %
@@
 \begin{align}	
-	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{Turkers[$i$]}\text{Quality}(t_j)}}{\mid \texttt{Turkers[$i$]} \mid}
+	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{turkers[$i$]}\text{Quality}(t_j)}}{\mid \texttt{turkers[$i$]} \mid}
 \end{align}	
-where $l_i$ is the ith language, \texttt{Turkers[$i$]} is the set of Turkers who completed assignments for language $i$, and Quality($t$) is as above.
+where $l_i$ is the ith language, \texttt{turkers[$i$]} is the set of turkers who completed assignments for language $i$, and Quality($t$) is as above.
 
-Figure \ref{hitlangqual} shows the translation quality for for languages with contributions from at least 50 workers.
+Figure \ref{hitlangqual} shows the translation quality for for languages with contributions from at least 50 workers. The 
+%Measured in this way, the average quality score across all HITs in all languages is just under 0.46. When restricted to languages with at least 50 Turkers, the average quality is 0.53.
 
-\section{Further Data Analysis}
+\section{Data Analysis}
 
@@
 \item How quickly can we expect work to be completed in a particular language? 
+\item What is the quality of crowdsourced translations without quality control versus with it? 
 \item Do workers accurately represent their language abilities?  Should we constrain tasks by region? 
-\item How prevalent is the use of machine translation? 
-%\item What is the quality of crowdsourced translations without quality control versus with it? 
 \end{itemize}
-
-\paragraph{Speed of completion}
 
@@
 \begin{figure}[h]
+\centering
 \includegraphics[height=\linewidth,angle=270]{final-figures/completetime}
@@
 
+\paragraph{Speed of completion}
+
 Figure \ref{completion-time} gives the completion times for 40 languages.  
-Urdu and Russian were the first languages to be launched, followed by the others 2 days later.
+Workers for Urdu and Russian HITs responded almost immediately; workers in the other languages began slightly later.
 The 10 languages to finish in the shortest amount of time were: Tamil, Malayalam, Telugu, Hindi, Macedonian, Spanish, Serbian, Romanian, Gujarati, and Marathi.
@@
 
-%%%%%%%%%%%%%%% Turker QUAL SUMMARY TABLE %%%%%%%%%%%
-\begin{table*}[h]
+\paragraph{Validation of controls} As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
+Turkers' performance on our control tasks is well correlated with this measure of quality.
+Results are show below in table \ref{corr-table}.
+We were able to validate the dictionaries we received from MTurk in the 27 languages for which we had external dictionaries: az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, uz.
+Across all 27 languages, 23\% of the source words from the Mechanical Turk dictionaries appeared in the external dictionaries, and could be validated.
+This was an average of 22\% per language.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{lc}\hline\hline\\
+&$\rho$\\
+Language quality&0.41\\
+Turker quality (languages pooled)&0.43\\
+Avg. Turker quality (languages separate)&0.26\\
+\hline\hline
+\end{tabular}
+\caption{Pearson correlation of quality measured by accuracy on control translations vs.
+quality measured by overlap with external dictionaries.
+Language is the correlation of quality estimates for each language (across 27 languages), Turker quality is the correlation of quality estimates for each Turker (2,472 turkers).
+Avg.
+Turker quality is computed by taking the correlation of Turker quality estimates separately for each of the 27 languages, and then taking the average of the correlations.
+The figure reflects data from 27 languages for which we had available external dictionaries: az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, uz.}
+\label{corr-table}
+\end{table}
+
+\paragraph{Use of machine translation}
+Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems.
+This strategy does not prevent workers from typing the words into an MT system, if they understand the language's script.
+We measured the percent of translations received that exactly matched the translation returned from google translate.
+Results are show in figure \ref{google-match-bar}.
+Assignments averaged around 43\% overlap with google translate.
+Higher overlap with google translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some of the control translations used may have been already indexed by Google.
+Languages with exotic scripts (such as Arabic (ar), Chinese (zh), and Telugu (te)) have especially low overlap with Google.
+
+%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
+\begin{figure*}[h]
 \footnotesize
 \begin{tabular}{lllll}
+\multicolumn{4}{c}{Number of turkers per language}\\
 \hline\hline
-&\multicolumn{2}{c}{Avg. Turker quality (\# Ts)}&Primary locations&Primary locations\\
-&In region&Out of region&of Turkers in region&of Turkers out of region\\
+&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&Primary locations&Primary locations\\
+&In region&Out of region&of turkers in region&of turkers out of region\\
 \hline\hline
-Hindi&\textbf{0.35} (299)&0.29 (7)&India (285) UAE (5) UK (5) &Saudi Arabia (2) Russia (1) Oman (1) \\
-Tamil&\textbf{0.39} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
-Malayalam&0.44 (235) &\textbf{0.56} (2)&India (224) UAE (6) US (3) &Saudi Arabia (1) Maldives (1) \\
-Spanish&\textbf{0.71} (205)&0.60 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) New Zealand (1) \\
-French&0.61 (183) &\textbf{0.80} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
-German&\textbf{0.80} (99)&0.56 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
-Italian&\textbf{0.79} (98)&0.67 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
-Chinese&\textbf{0.22} (121)&0.18 (19)&US (79) Singapore (15) China (14) &HK (6) Australia (3) Germany (2) \\
-Malay&\textbf{0.76} (15)&0.72 (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
-Irish&0.61 (58) &\textbf{0.62} (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
-Czech&\textbf{0.70} (52)&0.62 (64)&US (19) Czech Republic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
-Turkish&\textbf{0.70} (83)&0.62 (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
-Amharic&\textbf{0.17} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
-Swedish&\textbf{0.64} (58)&0.57 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
-Portuguese&\textbf{0.75} (107)&0.62 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
-Arabic&0.21 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
-Kannada&\textbf{0.24} (106)&0.10 (1)&India (106) US (1) &France (1) Germany (1) \\
-Russian&\textbf{0.33} (72)&0.26 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
-Afrikaans&\textbf{0.73} (4)&0.64 (98)&South Africa (4) &India (93) Netherlands (2) UAE (1) \\
-Sindhi&\textbf{0.16} (93)&0.11 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
+Hindi&\textbf{0.35} (299)&0.34 (7)&India (285) UAE (5) UK (5) &Saudiarabia (2) Russia (1) Oman (1) \\
+Tamil&\textbf{0.37} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
+Malayalam&0.48 (235) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudiarabia (1) Maldives (1) \\
+Spanish&\textbf{0.72} (205)&0.61 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) Newzealand (1) \\
+French&0.65 (183) &\textbf{0.86} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
+German&\textbf{0.83} (99)&0.65 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
+Italian&\textbf{0.78} (98)&0.71 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
+Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hongkong (6) Australia (3) Germany (2) \\
+Malay&0.76 (15) &\textbf{0.83} (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
+Irish&\textbf{0.68} (58)&0.64 (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
+Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czechrepublic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
+Turkish&0.72 (83) &\textbf{0.73} (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
+Amharic&\textbf{0.18} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
+Swedish&\textbf{0.66} (58)&0.61 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
+Portuguese&\textbf{0.77} (107)&0.74 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
+Arabic&0.22 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
+Kannada&\textbf{0.24} (106)&0.00 (1)&India (106) US (1) &France (1) Germany (1) \\
+Russian&\textbf{0.09} (72)&0.06 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
+Afrikaans&\textbf{0.74} (4)&0.73 (98)&Southafrica (4) &India (93) Netherlands (2) UAE (1) \\
+Sindhi&\textbf{0.15} (93)&0.02 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
 \hline\hline
 \end{tabular}
-\normalsize
-\caption{Translation quality when partitioning the translations into two groups, one contains translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other contains translations from Turkers outside those regions.
-}\label{region-summary}
-\end{table*}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Overall, 4,465 workers were located in a region likely to speak the language from which they were translating, and 3,170 workers were located in countries considered out of region (meaning almost half of our 5,277 Turkers completed HITs in multiple languages).
+Across all languages, there is no significant quality difference between turkers in region and out of region (0.504 and 0.496, respectively).
+However, within each language, the effect of location on quality varies greatly (table \ref{region-summary}).
 
-Table \ref{region-summary} shows the differences in translation quality when computed using in-region versus out-of-region Turkers, for the languages with the greatest number of workers.
-Within region workers typically produced higher quality translations.
-Given the number of Indian workers on Mechanical Turk, it is unsurprising that they represent majority of out-of-region workers.
-For the languages that had more than 80 out of region workers (Malay, Amharic, Afrikaans, Icelandic, and Breton), Indian workers represented 90\% of the out of region workers for all of them aside from Amharic.
+Among the languages with the largest number of Turkers total, most workers are in region (see table \ref{region-summary}).
+The majority of out-of-region Turkers were located in India; the languages with the most out of region Turkers are as follows (total number out of region and number located in India in parenthesis): Malay (110/106), Amharic (98/69), Afrikaans (98/93), Icelandic (90/83), and Breton (88/82).
 
-%When averaged across all languages, there is no significant quality difference between Turkers in region and out of region (0.504 and 0.496, respectively).
-However, within each language, the effect of location on quality varies greatly (Table \ref{region-summary}).
-
-% CCB - commented out this figure and paragraph.  I'm not sure that this figure adds any new information
-%
-%%%%%%%%%%%%%%%% ASSIGNMENT SCATTER %%%%%%%%%%%
-%\begin{figure*}[h]
-%\centering
-%\includegraphics[width=6in]{final-figures/assign-turk-scatter}
-%\caption{Number of assignments and number of Turkers for each language.
+%%%%%%%%%%%%%%% ASSIGNMENT SCATTER %%%%%%%%%%%
+\begin{figure*}[h]
+\centering
+\includegraphics[width=6in]{final-figures/assign-turk-scatter}
+\caption{Number of assignments and number of Turkers for each language.
 Each dot represents a language.
 Figure includes only data from Turkers who reported only one native language consistantly across assignments, representing approx.
-3900 Turkers across 139,000 assignments.}
-%\label{ass-scatter}
-%\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%Figure \ref{ass-scatter} shows the volume of HITs completed and the number of workers participating for each language.
-While the bulk (19\%) of bilingual Turkers report English as their native language (see Figure \ref{lang-pie}), Mechanical Turk's capacity to support the Indian languages is apparent.
+3900 turkers across 139,000 assignments.}
+\label{ass-scatter}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Figure \ref{ass-scatter} shows the volume of HITs completed and the number of workers participating for each language.
+While the bulk (19\%) of bilingual Turkers report English as their native language (see figure \ref{lang-pie}), Mechanical Turk's capacity to support the Indian languages is apparent.
 Hindi, Tamil, and Malayalam are especially well represented in terms of number of active translators.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\paragraph{Use of machine translation}
-
-Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems.
-This strategy does not prevent workers from typing the words into an MT system, if they understand the language's script.
-We measured the percent of translations received that exactly matched the translation returned from Google translate.
-Results are show in Figure \ref{Google-match-bar}.
-Assignments averaged around 43\% overlap with Google translate.
-Higher overlap with Google translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some of the control translations used may have been already indexed by Google.
-Languages with exotic scripts (such as Arabic (ar), Chinese (zh), and Telugu (te)) have especially low overlap with Google.
-
-\paragraph{Validation of controls} 
-We investigated the validity of our use of Wikipedia inter-language links as gold standard translations, since they may have been included Google Translate.
-%
-As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
-Turkers' performance on our control tasks is well correlated with this measure of quality.
-We had external bilingual dictionaries for 27 of the 119 languages examined in this study.\footnote{The bilingual dictionaries were between en and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz.
-}  We used each of these bilingual dictionaries to computer language-level quality scores, using the dictionary's translation as a gold standard translation for any of the 10,000 foreign words in our study.
-In some cases, the overlap of words was low, since dictionaries list root forms of words and we translated inflected forms.
-
-We ranked the 27 languages based on their translation quality scores according to the external dictionaries, and its calculated correlation when compared to the ranking produced by our gold standard control.
-The Pearson correlation was $\rho=0.58$.
-We computed a correlation coefficient of $\rho=0.37$ for ranking of the translation quality of individual Turkers using the two sources of reference translations.
-
-Given the strong positive correlation, we are satisfied that the trends reported in this paper hold when using either our gold standard translations or external bilingual dictionaries.
 

### 2013-03-30 writeup/summary.tex
quality by assign

@@
 \hline\hline
-Hindi&\textbf{0.35} (299)&0.29 (7)&India (285) UAE (5) UK (5) &Saudi Arabia (2) Russia (1) Oman (1) \\
-Tamil&\textbf{0.39} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
-Malayalam&0.44 (235) &\textbf{0.56} (2)&India (224) UAE (6) US (3) &Saudi Arabia (1) Maldives (1) \\
-Spanish&\textbf{0.71} (205)&0.60 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) New Zealand (1) \\
-French&0.61 (183) &\textbf{0.80} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
-German&\textbf{0.80} (99)&0.56 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
-Italian&\textbf{0.79} (98)&0.67 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
-Chinese&\textbf{0.22} (121)&0.18 (19)&US (79) Singapore (15) China (14) &HK (6) Australia (3) Germany (2) \\
-Malay&\textbf{0.76} (15)&0.72 (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
-Irish&0.61 (58) &\textbf{0.62} (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
-Czech&\textbf{0.70} (52)&0.62 (64)&US (19) Czech Republic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
-Turkish&\textbf{0.70} (83)&0.62 (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
-Amharic&\textbf{0.17} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
-Swedish&\textbf{0.64} (58)&0.57 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
-Portuguese&\textbf{0.75} (107)&0.62 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
-Arabic&0.21 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
-Kannada&\textbf{0.24} (106)&0.10 (1)&India (106) US (1) &France (1) Germany (1) \\
-Russian&\textbf{0.33} (72)&0.26 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
-Afrikaans&\textbf{0.73} (4)&0.64 (98)&South Africa (4) &India (93) Netherlands (2) UAE (1) \\
-Sindhi&\textbf{0.16} (93)&0.11 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
+Hindi&\textbf{0.35} (299)&0.34 (7)&India (285) UAE (5) UK (5) &Saudiarabia (2) Russia (1) Oman (1) \\
+Tamil&\textbf{0.37} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
+Malayalam&0.48 (235) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudiarabia (1) Maldives (1) \\
+Spanish&\textbf{0.72} (205)&0.61 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) Newzealand (1) \\
+French&0.65 (183) &\textbf{0.86} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
+German&\textbf{0.83} (99)&0.65 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
+Italian&\textbf{0.78} (98)&0.71 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
+Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hongkong (6) Australia (3) Germany (2) \\
+Malay&0.76 (15) &\textbf{0.83} (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
+Irish&\textbf{0.68} (58)&0.64 (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
+Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czechrepublic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
+Turkish&0.72 (83) &\textbf{0.73} (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
+Amharic&\textbf{0.18} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
+Swedish&\textbf{0.66} (58)&0.61 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
+Portuguese&\textbf{0.77} (107)&0.74 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
+Arabic&0.22 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
+Kannada&\textbf{0.24} (106)&0.00 (1)&India (106) US (1) &France (1) Germany (1) \\
+Russian&\textbf{0.09} (72)&0.06 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
+Afrikaans&\textbf{0.74} (4)&0.73 (98)&Southafrica (4) &India (93) Netherlands (2) UAE (1) \\
+Sindhi&\textbf{0.15} (93)&0.02 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
 \hline\hline

### 2013-03-30 code/src/completetime.py

@@ -71,6 +71,8 @@ def format_for_graph(data):
 		lang = data[l]	
 		complete = lang[1] - lang[0]
 		start = lang[0] - mindate
+#		if lang == 'ru' or lang == 'ur': ret.append((l,complete, start+(86400*2), start+complete))
+#		else: ret.append((l,complete, start, start+complete))
 		ret.append((l,complete, start, start+complete))
 	return sorted(ret, key=operator.itemgetter(3)) 
 
@@ -98,7 +100,10 @@ def format_for_time_series(data):
 		lang = langids[hitlangs[hitmap[aid]]]
 		if lang not in all_times:
 			all_times[lang] = list()
-		all_times[lang].append(total)
+		if lang == 'ru' or lang == 'ur': 
+			all_times[lang].append(total+datetime.timedelta(days=2))
+		else:
+			all_times[lang].append(total)
 	try:
 		all_times.pop('en')
 	except KeyError:
@@ -116,12 +121,13 @@ def time_series(data, num=40):
 		x += [t.total_seconds() for t in data[lang]]
 		y += [5+(i*5)]*len(data[lang])
 	plt.scatter(x,y,marker='|', alpha=0.1)
-	plt.xlim([0,max(x)+5])
+	plt.xlim([min(x),max(x)+5])
 	plt.ylim([0,max(y)+5])
         plt.yticks(sorted(list(set(y))), tuple(names))
 	xmax = int(math.ceil(max(x)))
+	xmin = int(math.ceil(min(x)))
 	max_days = int(math.ceil(max(x)/SEC_PER_DAY))
-        plt.xticks(range(0,xmax,5*SEC_PER_DAY), range(0,max_days,5))
+        plt.xticks(range(xmin,xmax,5*SEC_PER_DAY), range(0,max_days,5))
         plt.xlabel('Time in days')
 	plt.show()
 

### 2013-03-30 code/src/dictionaries.py

@@ -15,7 +15,7 @@ RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-da
 DICT_PATH = './translations.out'
 CLPAIRS = './cl-pairs.csv'
 OUTPUT_DIR = 'output'
-DICT_DIR = 'dictionaries'
+DICT_DIR = '../../dictionaries/ellie/clpair' #'dictionaries'
 
 def read_valid_clpairs():
 	codes, words = dat.lang_map()
@@ -302,6 +302,41 @@ def count_turkers(path, qual_cutoff=None, strict=False, filter_list=None, match=
 	return {l: list(set(all_dicts[l])) for l in all_dicts}
 
 #get estimated turker quality by language, returns dictionary of {language : {'num': # of correct QC words, 'denom': # of QC words} }
+def get_language_dicts_quals_assigns(path, qual_cutoff=None, strict=False, filter_list=None, match=True):
+        all_dicts = dict()
+        hitmap = hit_map()
+        langids, langcodes = dat.lang_map()
+        hitlangs = dat.hits_language()
+        quals = qual_map()
+        for assign in open(path).readlines():
+                comps = assign.strip().split('\t')
+                aid = comps[0]
+                if(aid == '' or aid not in quals):
+                        continue
+                #if match, filter_list is list of assignments to include, otherwise, filter_list is list of assignments to skip
+                if(match):
+                        list_pass = not(filter_list == None) and (aid not in filter_list)
+                else:
+                        list_pass = not(filter_list == None) and (aid in filter_list)
+                if(list_pass):
+                        continue
+                #if strict, assignments must be greater than qual_cutoff to pass, otherwise, assignments can be greater or equal to qual_cutoff
+                if(strict):
+                        qual_pass = not(qual_cutoff == None) and (quals[aid] == 'N/A' or quals[aid] <= qual_cutoff)
+                else:
+                        qual_pass = not(qual_cutoff == None) and (quals[aid] == 'N/A' or quals[aid] < qual_cutoff)
+                if(qual_pass):
+                        print 'below cutoff', aid, quals[aid]
+                        continue
+                alang =  langids[hitlangs[hitmap[aid]]]
+                if not(alang in all_dicts):
+                        all_dicts[alang] = {'num':0, 'denom':0}
+                all_dicts[alang]['num'] += quals[aid]
+                all_dicts[alang]['denom'] += 1
+        return all_dicts
+
+
[…]

### 2013-03-30 code/src/figures.py

@@ -560,7 +560,7 @@ def goog_graphs(all_ci_dict, title='Graph', graph_avg=False, cutoff=3000, sort=N
 	        names = [c for c in sort]
         plt.bar(xax, yax, width/2, ecolor='black',color='#60AFFE')
         plt.bar(xax, yax2, width/2, ecolor='black',color='b')
-        plt.bar([x+width/2 for x in xax], yax3, width/2, ecolor='black',color='g')
+    #    plt.bar([x+width/2 for x in xax], yax3, width/2, ecolor='black',color='g')
 	if(graph_avg):
 		bidx = names.index('avg')
 		plt.bar(xax[bidx], yax[bidx], width/2, color='r') 
@@ -1016,7 +1016,7 @@ def quality_scatter(title='Title'):
 	cmap['100 turkers'] = '100 turkers'
 	cia = conf_int_by_attr(attr)
 	ci = conf_int_by_attr_turker(attr)
-	print_table(ci, cia)
+	#print_table(ci, cia)
 	turker_counts = count_turkers(attr)
 	names = list()
 	x = list()
@@ -1026,13 +1026,13 @@ def quality_scatter(title='Title'):
 	for c in ci:
 		if(c in turker_counts and not(ci[c] == None) and not(cia[c] == None) and (len(ci[c]) > 3)):
 			names.append(c)
-			y.append(ci[c][0])
-			ya.append(cia[c][0])
+			#y.append(ci[c][0])
+			y.append(cia[c][0])
 			e.append(ci[c][3])
 			x.append(ci[c][2])
-			xa.append(ci[c][2])
 	names.append('100 turkers')
 	y.append(0.9)
+	ya.append(0.9)
 	x.append(50000)
 	turker_counts['100 turkers'] = 100
         labels = list()
@@ -1045,8 +1045,8 @@ def quality_scatter(title='Title'):
                 labely.append(y[idx])
 	area = [turker_counts[n] for i,n in enumerate(names)]
 	print len(x), len(y), len(ya)
+#	plt.scatter(x, y, s=area)
 	plt.scatter(x, y, s=area)
-	plt.scatter(xa, ya, s=area, color='r')
 	plt.xscale('log')
 	plt.xlim([.1,1000000])
 	plt.ylim([0,1])
@@ -1295,8 +1295,8 @@ if __name__ == '__main__':
 	if(plot == 'exact_match'):
 		exact_match_qual()
 	if(plot == 'goog'):
[…]

### 2013-03-30 code/src/summary.py

@@ -53,7 +53,8 @@ def dictionary_stats_turker():
         return ret 
 
 def dictionary_stats_turkerqual():
-        dict_files=['%s/nonclpair.turkerqual'%DICT_DIR, '%s/clpair.turkerqual'%DICT_DIR]
+#        dict_files=['%s/nonclpair.turkerqual'%DICT_DIR, '%s/clpair.turkerqual'%DICT_DIR]
+        dict_files=['%s/nonclpair.assignqual'%DICT_DIR, '%s/clpair.assignqual'%DICT_DIR]
         data = dict()
         for line in open(dict_files[0]).readlines():
                 lang, count = line.split()

### 2013-03-30 writeup/paper.tex
Added question

--- 2013-03-30 writeup/paper.tex
@@
 
-We performed an analysis of our data to address the following questions, among others:
+We performed an analysis of our data to address the following questions:
 \begin{itemize}
@@
 \item Do workers accurately represent their language abilities?  Should we constrain tasks by region? 
-\item How prevalent is the use of machine translation? 
+\item Is the use of machine translation prevalent?  
+\item Are our gold standard translations valid? 
 %\item What is the quality of crowdsourced translations without quality control versus with it? 

### 2013-03-30 writeup/paper.tex
ellie messed up the tex

@@
 \centering
-\includegraphics[width=\linewidth]{final-figures/Turkermap}
+%\includegraphics[width=\linewidth]{final-figures/Turkermap}
 \caption{The number of workers per country.
@@
 \begin{center}
-\includegraphics[width=0.8\linewidth]{final-figures/Google-match-bar}
+%\includegraphics[width=0.8\linewidth]{final-figures/Google-match-bar}
 \caption{Translation quality for languages with at least 50 active Turkers.
@@
 \end{center}
+>>>>>>> 81a8da54c546f6a3c6f965f1934e41d70ed91b62
 \end{figure*}
@@
 
-%%%%%%%%%%%%%%% Turker QUAL SUMMARY TABLE %%%%%%%%%%%
-\begin{table*}[h]
+\paragraph{Validation of controls} As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
+Turkers' performance on our control tasks is well correlated with this measure of quality.
+Results are show below in table \ref{corr-table}.
+We were able to validate the dictionaries we received from MTurk in the 27 languages for which we had external dictionaries: az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, uz.
+Across all 27 languages, 23\% of the source words from the Mechanical Turk dictionaries appeared in the external dictionaries, and could be validated.
+This was an average of 22\% per language.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{lc}\hline\hline\\
+&$\rho$\\
+Language quality&0.41\\
+Turker quality (languages pooled)&0.43\\
+Avg. Turker quality (languages separate)&0.26\\
+\hline\hline
+\end{tabular}
+\caption{Pearson correlation of quality measured by accuracy on control translations vs.
+quality measured by overlap with external dictionaries.
+Language is the correlation of quality estimates for each language (across 27 languages), Turker quality is the correlation of quality estimates for each Turker (2,472 turkers).
+Avg.
+Turker quality is computed by taking the correlation of Turker quality estimates separately for each of the 27 languages, and then taking the average of the correlations.
+The figure reflects data from 27 languages for which we had available external dictionaries: az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, uz.}
+\label{corr-table}
+\end{table}
+
+\paragraph{Use of machine translation}
+Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems.
+This strategy does not prevent workers from typing the words into an MT system, if they understand the language's script.
+We measured the percent of translations received that exactly matched the translation returned from google translate.
+Results are show in figure \ref{google-match-bar}.
+Assignments averaged around 43\% overlap with google translate.
+Higher overlap with google translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some of the control translations used may have been already indexed by Google.
+Languages with exotic scripts (such as Arabic (ar), Chinese (zh), and Telugu (te)) have especially low overlap with Google.
+
+%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
 \footnotesize
+\begin{figure*}
 \begin{tabular}{lllll}
+\multicolumn{4}{c}{Number of turkers per language}\\
 \hline\hline
@@
 \normalsize
-\caption{Translation quality when partitioning the translations into two groups, one contains translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other contains translations from Turkers outside those regions.
-}\label{region-summary}
-\end{table*}
+\caption{Translation quality when partitioning the translations into two groups, one contains translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other contains translations from Turkers outside those regions.} \label{region-summary}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-03-30 writeup/paper.tex
more tex problems
Added Anni to the author list.

@@
 
-\author{Ellie Pavlick\affliationPenn \ \ \ \ \ \ \ \ \ \ Dmitry Kachaev\affliationJHU \ \ \ \ \ \ \ \ \ \  Chris Callison-Burch\affliationPenn$^{,}$\affliationJHU \\
+\author{Ellie Pavlick\affliationPenn \ \ \ \ \ Ann Irvine\affliationJHU  \ \ \ \ \ Dmitry Kachaev\affliationJHU  \ \ \ \ \  Chris Callison-Burch\affliationPenn$^{,}$\affliationJHU \\
 \affliationPenn Computer and Information Science Department, University of Pennsylvania \\
@@
 \centering
-%\includegraphics[width=\linewidth]{final-figures/Turkermap}
+\includegraphics[width=\linewidth]{final-figures/turkermap}
 \caption{The number of workers per country.
@@
 \begin{center}
-%\includegraphics[width=0.8\linewidth]{final-figures/Google-match-bar}
+\includegraphics[width=0.8\linewidth]{final-figures/google-match-bar}
 \caption{Translation quality for languages with at least 50 active Turkers.
@@
 \end{center}
->>>>>>> 81a8da54c546f6a3c6f965f1934e41d70ed91b62
 \end{figure*}

### 2013-03-30 writeup/paper.tex
Removed old paragraphs

@@
 
-\paragraph{Validation of controls} As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
-Turkers' performance on our control tasks is well correlated with this measure of quality.
-Results are show below in table \ref{corr-table}.
-We were able to validate the dictionaries we received from MTurk in the 27 languages for which we had external dictionaries: az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, uz.
-Across all 27 languages, 23\% of the source words from the Mechanical Turk dictionaries appeared in the external dictionaries, and could be validated.
-This was an average of 22\% per language.
-
-\begin{table}[h]
-\centering
-\begin{tabular}{lc}\hline\hline\\
-&$\rho$\\
-Language quality&0.41\\
-Turker quality (languages pooled)&0.43\\
-Avg. Turker quality (languages separate)&0.26\\
-\hline\hline
-\end{tabular}
-\caption{Pearson correlation of quality measured by accuracy on control translations vs.
-quality measured by overlap with external dictionaries.
-Language is the correlation of quality estimates for each language (across 27 languages), Turker quality is the correlation of quality estimates for each Turker (2,472 turkers).
-Avg.
-Turker quality is computed by taking the correlation of Turker quality estimates separately for each of the 27 languages, and then taking the average of the correlations.
-The figure reflects data from 27 languages for which we had available external dictionaries: az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, uz.}
-\label{corr-table}
-\end{table}
-
-\paragraph{Use of machine translation}
-Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems.
-This strategy does not prevent workers from typing the words into an MT system, if they understand the language's script.
-We measured the percent of translations received that exactly matched the translation returned from google translate.
-Results are show in figure \ref{google-match-bar}.
-Assignments averaged around 43\% overlap with google translate.
-Higher overlap with google translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some of the control translations used may have been already indexed by Google.
-Languages with exotic scripts (such as Arabic (ar), Chinese (zh), and Telugu (te)) have especially low overlap with Google.
-
 %%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
-\footnotesize
 \begin{figure*}

### 2013-03-30 writeup/paper.tex
Tweaks to layout
Minor tweaks

@@
 \caption{Translation quality for languages with at least 50 active Turkers.
-The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms.
-Overall average quality was 0.46 (0.53 among languages with at least 50 Turkers).}
+The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms.}
 \label{hitlangqual} 
@@
 \begin{figure*}
+\footnotesize
 \begin{tabular}{lllll}
-\multicolumn{4}{c}{Number of turkers per language}\\
 \hline\hline
@@
 
-We used Google Translate to translate all 10,000 words for each of the XXX foreign language that Google Translate covers.
+We used Google Translate to translate all 10,000 words for each of the 64 foreign language that Google Translate covers.
 We measured the percent of translations received that exactly matched the translation returned from Google translate.
@@
 Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphaabet) have lower overlap with Google, suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.
+
+% Google supports:
+%Afrikaans
+%Albanian
+%Arabic
+%Belarusian
+%Bulgarian
+%Catalan
+%Chinese
+%Chinese
+%Croatian
+%Czech
+%Danish
+%Dutch
+%English
+%Estonian
+%Esperanto
+%Filipino
+%Finnish
+%French
+%Galician
+%German
+%Greek
+%Hebrew
+%Hindi
+%Hungarian
+%Icelandic
+%Indonesian
+%Irish
+%Italian
+%Japanese
+%Korean
+%Latvian
+%Lithuanian
+%Macedonian
+%Malay
+%Maltese
+%Norwegian
+%Persian
+%Polish
+%Portuguese
+%Romanian
+%Russian
+%Serbian
+%Slovak
+%Slovenian
+%Spanish
+%Swahili
+%Swedish
+%Thai
+%Turkish
+%Ukrainian
+%Vietnamese
+%Welsh
+%Yiddish
+%Armenian
+%Azerbaijani
+%Basque
+%Georgian
+%Gujarati
+%Haitian Creole
+%Kannada
+%Latin
+%Lao
+%Tamil
+%Telugu
+%Urdu
 

### 2013-03-30 writeup/paper.tex
Fixed country names

@@
 \includegraphics[width=0.8\linewidth]{final-figures/google-match-bar}
-\caption{Translation quality for languages with at least 50 active Turkers.
+\caption{Translation quality for languages with at least 50 Turkers.
 The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms.}
@@
 \hline\hline
-Hindi&\textbf{0.35} (299)&0.34 (7)&India (285) UAE (5) UK (5) &Saudiarabia (2) Russia (1) Oman (1) \\
+Hindi&\textbf{0.35} (299)&0.34 (7)&India (285) UAE (5) UK (5) &Saudi Arabia (2) Russia (1) Oman (1) \\
 Tamil&\textbf{0.37} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
-Malayalam&0.48 (235) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudiarabia (1) Maldives (1) \\
-Spanish&\textbf{0.72} (205)&0.61 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) Newzealand (1) \\
+Malayalam&0.48 (235) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudi Arabia (1) Maldives (1) \\
+Spanish&\textbf{0.72} (205)&0.61 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) New Zealand (1) \\
 French&0.65 (183) &\textbf{0.86} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
@@
 Irish&\textbf{0.68} (58)&0.64 (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
-Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czechrepublic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
+Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czechr Rpublic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
 Turkish&0.72 (83) &\textbf{0.73} (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\

### 2013-03-30 code/src/figures.py
google translate

@@ -334,7 +334,7 @@ def exact_match_qual(cut=50):
 	match_by_lang['avg'] = (sm, (sm - moe, sm + moe), n, moe)
 	exact_match_graphs(sorted([(k,qual_by_lang[k],match_by_lang[k]) for k in qual_by_lang], key=operator.itemgetter(1), reverse=True), cutoff=cut)
 
-def goog_match_qual_assign(cut=50, sort=None):
+def goog_match_qual_assign(cut=0, sort=None):
 	assigns_by_lang = dict()
 	qual_by_assign = dict()
 	match_by_assign = dict()
@@ -362,7 +362,7 @@ def goog_match_qual_assign(cut=50, sort=None):
 		aid = line['id']
 		q = line['avg']
 		goog_by_assign[aid] = q
-	for l in assigns_by_lang.keys():
+	for l in ['el', 'eo', 'zh', 'af', 'vi', 'is', 'it', 'kn', 'cs', 'cy', 'ar', 'eu', 'gl', 'id', 'es', 'ru', 'az', 'nl', 'pt', 'tr', 'lv', 'lt', 'th', 'gu', 'ro', 'ca', 'pl', 'ta', 'fr', 'bg', 'ms', 'hr', 'de', 'da', 'fa', 'fi', 'hy', 'hu', 'ja', 'he', 'te', 'sr', 'sq', 'ko', 'sv', 'ur', 'sk', 'uk', 'sl', 'sw']: #assigns_by_lang.keys():
 		qual = list()
 		match = list()
 		goog = list()
@@ -398,13 +398,15 @@ def goog_match_qual_assign(cut=50, sort=None):
 	        		n, (smin, smax), sm, sv, ss, sk = stats.describe(goog)
         			moe = math.sqrt(sv)/math.sqrt(n) * 2.576
 				goog_by_lang[l] = (sm, (sm - moe, sm + moe), n, moe)
-	goog_graphs(sorted([(k,qual_by_lang[k],match_by_lang[k], goog_by_lang[k]) for k in qual_by_lang], key=operator.itemgetter(1), reverse=True), cutoff=cut, sort=sort)
+	print goog_by_lang
+	print len(goog_by_lang)
+	goog_graphs(sorted([(k,qual_by_lang[k],match_by_lang[k], goog_by_lang[k]) for k in qual_by_lang], key=operator.itemgetter(3), reverse=True), cutoff=cut, sort=sort)
 
 
 #compile exact match ratios, google translate ratios,  and quality estimates by hit language, and graph the results
[…]

### 2013-03-30 writeup/paper.tex
google translate
google and correlations

@@
 \begin{center}
-\includegraphics[width=0.8\linewidth]{final-figures/google-match-bar}
+\includegraphics[width=0.8\linewidth]{final-figures/quality-bar}
 \caption{Translation quality for languages with at least 50 Turkers.
@@
 \label{hitlangqual} 
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
+\begin{figure*}[h]
+\begin{center}
+\includegraphics[width=0.8\linewidth]{final-figures/google-match}
+\caption{Average proportion of Turker translations matching GoogleTranslate, per assignment. Overall average overlap was 0.42}
+\label{googlematch} 
 \end{center}
@@
 
-We used Google Translate to translate all 10,000 words for each of the 64 foreign language that Google Translate covers.
+We used Google Translate to translate all 10,000 words for each of the 50 foreign language that Google Translate covers.
 We measured the percent of translations received that exactly matched the translation returned from Google translate.
-Results are show in Figure \ref{Google-match-bar}.
-Assignments averaged around 43\% overlap with Google translate.
+Results are show in Figure \ref{googlematch}.
+Assignments averaged around 42\% overlap with Google translate.
 Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphaabet) have lower overlap with Google, suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.
@@
 We ranked the 27 languages based on their translation quality scores according to the external dictionaries, and its calculated correlation when compared to the ranking produced by our gold standard control.
-The Pearson correlation was $\rho=0.58$.
+The Pearson correlation was $\rho=0.53$.
 We computed a correlation coefficient of $\rho=0.37$ for ranking of the translation quality of individual Turkers using the two sources of reference translations.

### 2013-03-31 writeup/paper.tex
small changes

@@
 
-Since judging overall quality for a language with assignment quality scores is biased towards to small numbers of highly active Turkers, we instead report language quality scores as the average per-Turker quality, where a Turker's quality is  the average quality of all the assignments that she completed:
-\begin{align}	
-	\text{Quality}(t_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}\text{Quality}(a_j)}}{\mid \texttt{assigns[$i$]} \mid}
-\end{align}	
-where $t_i$ is the $i^{th}$ Turker, \texttt{assigns[$i$]} is the assignments completed by Turker $i$, and Quality($a$) is as above.
+%Since judging overall quality for a language with assignment quality scores is biased towards to small numbers of highly active Turkers, we instead report language quality scores as the average per-Turker quality, where a Turker's quality is  the average quality of all the assignments that she completed:
+%\begin{align}	
+%	\text{Quality}(t_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}\text{Quality}(a_j)}}{\mid \texttt{assigns[$i$]} \mid}
+%\end{align}	
+%where $t_i$ is the $i^{th}$ Turker, \texttt{assigns[$i$]} is the assignments completed by Turker $i$, and Quality($a$) is as above.
 %
+
 Quality for a language is then given by
 \begin{align}	
-	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{Turkers[$i$]}\text{Quality}(t_j)}}{\mid \texttt{Turkers[$i$]} \mid}
+	\text{Quality}(l_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}\text{Quality}(a_j)}}{\mid \texttt{assigns[$i$]} \mid}
 \end{align}	
-where $l_i$ is the ith language, \texttt{Turkers[$i$]} is the set of Turkers who completed assignments for language $i$, and Quality($t$) is as above.
+where $l_i$ is the ith language, \texttt{assigns[$i$]} is the set of completed assignments for language $i$, and Quality($a$) is as above.
+
+%Quality for a language is then given by
+%\begin{align}	
+%	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{Turkers[$i$]}\text{Quality}(t_j)}}{\mid \texttt{Turkers[$i$]} \mid}
+%\end{align}	
+%where $l_i$ is the ith language, \texttt{Turkers[$i$]} is the set of Turkers who completed assignments for language $i$, and Quality($t$) is as above.
 
@@
 
-We used Google Translate to translate all 10,000 words for each of the 50 foreign language that Google Translate covers.
+We used Google Translate to translate all 10,000 words for 50 foreign languages that Google Translate covers.
 We measured the percent of translations received that exactly matched the translation returned from Google translate.
@@
 Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphaabet) have lower overlap with Google, suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.
+
+%We translated: af ar az bg ca cs cy da de el eo es eu fa fi fr gl gu he hr hu hy id is it ja kn ko lt lv ms nl pl pt ro ru sk sl sq sr sv sw ta te th tr uk ur vi zh
 

### 2013-03-31 code/src/figures.py

@@ -362,12 +362,14 @@ def goog_match_qual_assign(cut=0, sort=None):
 		aid = line['id']
 		q = line['avg']
 		goog_by_assign[aid] = q
-	for l in ['el', 'eo', 'zh', 'af', 'vi', 'is', 'it', 'kn', 'cs', 'cy', 'ar', 'eu', 'gl', 'id', 'es', 'ru', 'az', 'nl', 'pt', 'tr', 'lv', 'lt', 'th', 'gu', 'ro', 'ca', 'pl', 'ta', 'fr', 'bg', 'ms', 'hr', 'de', 'da', 'fa', 'fi', 'hy', 'hu', 'ja', 'he', 'te', 'sr', 'sq', 'ko', 'sv', 'ur', 'sk', 'uk', 'sl', 'sw']: #assigns_by_lang.keys():
+
+	for l in ['af', 'sq', 'ar', 'be', 'bg', 'ca', 'zh', 'zh', 'hr', 'cs', 'da', 'nl', 'eo', 'fi', 'fr', 'gl', 'de', 'el', 'he', 'hi', 'hu', 'is', 'id', 'ga', 'it', 'ja', 'ko', 'lv', 'lt', 'mk', 'ms', 'fa', 'pl', 'pt', 'ro', 'ru', 'sr', 'sk', 'sl', 'es', 'sw', 'sv', 'th', 'tr', 'uk', 'vi', 'cy', 'hy', 'az', 'eu', 'ka', 'gu', 'kn', 'ta', 'te', 'ur']: #assigns_by_lang.keys():
 		qual = list()
 		match = list()
 		goog = list()
 		for a in assigns_by_lang[l]:
 			if a not in qual_by_assign or a not in match_by_assign:
+				print l
 				continue
 			q = qual_by_assign[a]
 			m = match_by_assign[a]
@@ -385,6 +387,7 @@ def goog_match_qual_assign(cut=0, sort=None):
 					avg_goog.append(float(g))
 				else:
 					goog.append(None)
+			else: print 'N/As %s'%l
 		if len(qual) > 0 and len(match) > 0:
 	        	n, (smin, smax), sm, sv, ss, sk = stats.describe(qual)
         		moe = math.sqrt(sv)/math.sqrt(n) * 2.576
@@ -398,7 +401,8 @@ def goog_match_qual_assign(cut=0, sort=None):
[…]

### 2013-03-31 writeup/paper.tex
small changes

@@
 The workers' identities are anonymized, and Amazon provides no information about their countries of origin or their language abilities.
-Posting a simple survey to have workers self-report this information may be inadequate, since (a) many worker may never see the survey, (b) many opt not to do one-off surveys since potential payment is low, and (c) validating the answers of respondents is not straightforward.
+Posting a simple survey to have workers self-report this information may be inadequate, since (a) many workers may never see the survey, (b) many opt not to do one-off surveys since potential payment is low, and (c) validating the answers of respondents is not straightforward.
 
 Our study establishes a methodology for determining the language demographics of anonymous crowd workers that is more robust than simple surveying.
-We ask workers what languages they speak and what country they live in, and validate their claims by measuring their ability to correctly translate words and by geolocating them.
+We ask workers what languages they speak and what country they live in, and validate their claims by measuring their ability to correctly translate words and by recording their geolocation.
 To increase the visibility and the desirability of our tasks, we post 1,000 assignments in each of 119 languages.
 These tasks each consist of translating 10 foreign words into English.
-Two of the 10 words have known translations, allowing us to validate the the workers' translations are accurate.
+Two of the 10 words have known translations, allowing us to validate that the workers' translations are accurate.
 We construct bilingual dictionaries with up to 10,000 entries, with the majority of entries being new.
@@
 
-We calculate the quality of translations on the level of individual assignments, individual workers, and languages.
+We calculate the quality of translations on the level of individual assignments and aggregated over languages and countries.
 We define an assignment's quality as the proportion of controls that are correct in a given assignment, where correct means exactly correct or judged to be synonymous.
@@
 \end{align}	
-where $l_i$ is the ith language, \texttt{assigns[$i$]} is the set of completed assignments for language $i$, and Quality($a$) is as above.
+where $l_i$ is the ith language, \texttt{assigns[$i$]} is the set of completed assignments for language $i$, and Quality($a$) is as above. Quality for a country is computed the same way.
 
@@
 Italian&\textbf{0.78} (98)&0.71 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
-Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hongkong (6) Australia (3) Germany (2) \\
+Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hong Kong (6) Australia (3) Germany (2) \\
 Malay&0.76 (15) &\textbf{0.83} (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
 Irish&\textbf{0.68} (58)&0.64 (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
-Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czechr Rpublic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
+Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czech Republic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
 Turkish&0.72 (83) &\textbf{0.73} (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
@@
 Russian&\textbf{0.09} (72)&0.06 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
-Afrikaans&\textbf{0.74} (4)&0.73 (98)&Southafrica (4) &India (93) Netherlands (2) UAE (1) \\
+Afrikaans&\textbf{0.74} (4)&0.73 (98)&South Africa (4) &India (93) Netherlands (2) UAE (1) \\
 Sindhi&\textbf{0.15} (93)&0.02 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
@@
 We used the Ethnologue \cite{ethnologue} to compile the list of countries where each language is spoken.
-Table \ref{region-summary} compares the average translation quality of Turkers within the region of each language, and compares it to the quality of Turkers outside that region.
+Table \ref{region-summary} compares the average translation quality of assignments completed within the region of each language, and compares it to the quality of assignments completed outside that region.
 

### 2013-03-31 code/src/correlation_google.py

@@ -13,12 +13,12 @@ file2 = sys.argv[2]
 
 scores1 = list(); scores2 = list()
 
-for s1, s2 in zip(open(file1).readlines(), open(file2).readlines()):
-	s1 = s1.strip(); s2 = s2.strip();
-	if s1 == 'N/A' or s2 == 'N/A':
+for s1, s2 in zip(open(file1).readlines()[1:], open(file2).readlines()[1:]):
+	s1 = s1.strip().split(); s2 = s2.strip().split();
+	if s1[3] == 'N/A' or s2[3] == 'N/A':
 		continue
-	scores1.append(float(s1))
-	scores2.append(float(s2))
+	scores1.append(float(s1[3]))
+	scores2.append(float(s2[3]))
 
 
 print 'Their average:', sum(scores1)/len(scores1)

### 2013-03-31 writeup/paper.tex
Cropped and moved the Google match figure.
Fixed typos

@@
 \DeclareMathOperator*{\argmax}{arg\,max}
-\setlength\titlebox{5.2cm}    % Expanding the titlebox
+\setlength\titlebox{5cm}    % Expanding the titlebox
 
@@
 The workers' identities are anonymized, and Amazon provides no information about their countries of origin or their language abilities.
-Posting a simple survey to have workers self-report this information may be inadequate, since (a) many workers may never see the survey, (b) many opt not to do one-off surveys since potential payment is low, and (c) validating the answers of respondents is not straightforward.
+Posting a simple survey to have workers report this information may be inadequate, since (a) many workers may never see the survey, (b) many opt not to do one-off surveys since potential payment is low, and (c) validating the answers of respondents is not straightforward.
 
@@
 
-Several researchers have investigated using MTurk to build parallel corpora for machine translation, a task which stands to benefit low cost, high volume  translation on demand \cite{Germann2001}.
+Several researchers have investigated using MTurk to build bilingual parallel corpora for machine translation, a task which stands to benefit low cost, high volume  translation on demand \cite{Germann2001}.
 \newcite{ambati_act} conducted a pilot study by posting 25 sentences to MTurk for Spanish, Chinese, Hindi, Telugu, Urdu, and Haitian Creole.
@@
 We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} and then selected an additional 19 low resource languages, giving a total of 119 languages (Table \ref{wikipedia-buckets}).
-For each language, we chose the 1,000 most viewed articles over a 1 year period,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and extracted the 10,000 most frequent words from each.
+For each language, we chose the 1,000 most viewed articles over a 1 year period,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and extracted the 10,000 most frequent words from them.
 The resulting vocabularies served as the input to our translation HIT.
@@
 
-%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
-\begin{figure*}[h]
-\begin{center}
-\includegraphics[width=0.8\linewidth]{final-figures/google-match}
-\caption{Average proportion of Turker translations matching GoogleTranslate, per assignment. Overall average overlap was 0.42}
-\label{googlematch} 
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \paragraph{Translation HIT}
@@
 Turkers were allowed to mark that they were unable to translate a word.
-Each task contained 10 words, 8 of which were words with unknown translations, and the other two of which were quality control words with known translations.
+Each task contained 10 words, 8 of which were words with unknown translations, and 2 of which were quality control words with known translations.
 We gave special instruction for translating names of people and places, giving examples of how to handle `Barack Obama' and `Australia' using their interlanguage links.
@@
 We calculate the quality of translations on the level of individual assignments and aggregated over languages and countries.
-We define an assignment's quality as the proportion of controls that are correct in a given assignment, where correct means exactly correct or judged to be synonymous.
+We define an assignment's quality as the proportion of controls that are correct in a given assignment, where correct means exactly correct or judged to be synonymous or related.
 \begin{align}	
@@
 
+Figure \ref{completion-time} gives the completion times for 40 languages.  
+The 10 languages to finish in the shortest amount of time were: Tamil, Malayalam, Telugu, Hindi, Macedonian, Spanish, Serbian, Romanian, Gujarati, and Marathi.
+7 of the 10 fastest languages are from India, which is unsurprising given the geographic distribution of workers.
+Some languages follow the pattern of having a smattering of assignments completed early, with the rate picking up later.
+
 %%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
@@
 
-Figure \ref{completion-time} gives the completion times for 40 languages.  
-Workers for Urdu and Russian HITs responded almost immediately; workers in the other languages began slightly later.
-The 10 languages to finish in the shortest amount of time were: Tamil, Malayalam, Telugu, Hindi, Macedonian, Spanish, Serbian, Romanian, Gujarati, and Marathi.
-7 of the 10 fastest languages are from India, which is unsurprising given the geographic distribution of workers.
-Some languages follow the pattern of having a smattering of assignments completed early, with the rate picking up later.
-
 %%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
-\begin{figure*}
+\begin{table*}
 \footnotesize
@@
 \caption{Translation quality when partitioning the translations into two groups, one contains translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other contains translations from Turkers outside those regions.} \label{region-summary}
-\end{figure*}
+\end{table*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=1\linewidth]{final-figures/google-match}
+\caption{Average proportion of Turker translations matching GoogleTranslate, per assignment. Overall average overlap was 0.42}
+\label{googlematch} 
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
@@
 Assignments averaged around 42\% overlap with Google translate.
-Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphaabet) have lower overlap with Google, suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.
+Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphabet) have lower overlap with Google, suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.
 
@@
 \paragraph{Validation of controls} 
-Higher overlap with Google translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some of the control translations used may have been already indexed by Google.
+Higher overlap with Google translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some control translations have already been indexed by Google.
 We therefore investigated the validity of our use of Wikipedia inter-language links as gold standard translations.
@@
 Turkers' performance on our control tasks is well correlated with this measure of quality.
-We had external bilingual dictionaries for 27 of the 119 languages examined in this study.\footnote{The bilingual dictionaries were between en and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz.
+We had external bilingual dictionaries for 27 of the 119 languages examined in this study.\footnote{The bilingual dictionaries were between English and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz.
 }  We used each of these bilingual dictionaries to computer language-level quality scores, using the dictionary's translation as a gold standard translation for any of the 10,000 foreign words in our study.
@@
 
-We ranked the 27 languages based on their translation quality scores according to the external dictionaries, and its calculated correlation when compared to the ranking produced by our gold standard control.
+We ranked the 27 languages based on their translation quality scores according to the external dictionaries, and calculated correlation when compared to the ranking produced by our gold standard control.
 The Pearson correlation was $\rho=0.53$.

### 2013-03-31 writeup/paper.tex
Added an additional nocite reference
minor changes

--- 2013-03-31 writeup/paper.tex
@@
 \hline\hline
-Hindi&\textbf{0.35} (299)&0.34 (7)&India (285) UAE (5) UK (5) &Saudi Arabia (2) Russia (1) Oman (1) \\
-Tamil&\textbf{0.37} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
-Malayalam&0.48 (235) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudi Arabia (1) Maldives (1) \\
-Spanish&\textbf{0.72} (205)&0.61 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) New Zealand (1) \\
-French&0.65 (183) &\textbf{0.86} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
-German&\textbf{0.83} (99)&0.65 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
-Italian&\textbf{0.78} (98)&0.71 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
-Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hong Kong (6) Australia (3) Germany (2) \\
-Malay&0.76 (15) &\textbf{0.83} (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
-Irish&\textbf{0.68} (58)&0.64 (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
-Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czech Republic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
-Turkish&0.72 (83) &\textbf{0.73} (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
-Amharic&\textbf{0.18} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
-Swedish&\textbf{0.66} (58)&0.61 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
-Portuguese&\textbf{0.77} (107)&0.74 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
-Arabic&0.22 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
-Kannada&\textbf{0.24} (106)&0.00 (1)&India (106) US (1) &France (1) Germany (1) \\
-Russian&\textbf{0.09} (72)&0.06 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
-Afrikaans&\textbf{0.74} (4)&0.73 (98)&South Africa (4) &India (93) Netherlands (2) UAE (1) \\
-Sindhi&\textbf{0.15} (93)&0.02 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
+Hindi&\textbf{0.35} (295)&0.34 (4)&India (285) UAE (5) UK (5) &Saudiarabia (2) Russia (1) Oman (1) \\
+Tamil&\textbf{0.37} (276)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
+Malayalam&0.48 (233) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudiarabia (1) Maldives (1) \\
+Spanish&\textbf{0.72} (163)&0.61 (22)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) Newzealand (1) \\
+French&0.65 (141) &\textbf{0.86} (6)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
+German&\textbf{0.83} (89)&0.65 (51)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
+Italian&\textbf{0.78} (85)&0.71 (42)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
+Chinese&\textbf{0.24} (108)&0.16 (11)&US (79) Singapore (15) China (14) &Hongkong (6) Australia (3) Germany (2) \\
+Malay&0.76 (14) &\textbf{0.83} (109)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
+Irish&\textbf{0.68} (58)&0.64 (55)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
+Czech&\textbf{0.71} (39)&0.63 (50)&US (19) Czechrepublic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
+Turkish&0.72 (71) &\textbf{0.73} (29)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
+Amharic&\textbf{0.18} (17)&0.02 (83)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
+Swedish&\textbf{0.66} (54)&0.61 (39)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
+Portuguese&\textbf{0.77} (93)&0.74 (3)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
+Arabic&0.22 (45) &\textbf{0.26} (35)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
+Kannada&\textbf{0.24} (107)&0.00 (2)&India (106) US (1) &France (1) Germany (1) \\
+Russian&\textbf{0.09} (53)&0.06 (25)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
+Afrikaans&\textbf{0.74} (4)&0.73 (96)&Southafrica (4) &India (93) Netherlands (2) UAE (1) \\
+Sindhi&\textbf{0.15} (93)&0.02 (7)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
 \hline\hline

### 2013-03-31 code/src/correlation_google.py

@@ -13,12 +13,14 @@ file2 = sys.argv[2]
 
 scores1 = list(); scores2 = list()
 
+num = 1
+
 for s1, s2 in zip(open(file1).readlines()[1:], open(file2).readlines()[1:]):
-	s1 = s1.strip().split(); s2 = s2.strip().split();
-	if s1[3] == 'N/A' or s2[3] == 'N/A':
+	s1 = s1.strip().split()[num]; s2 = s2.strip().split()[num];
+	if s1 == 'N/A' or s2 == 'N/A':
 		continue
-	scores1.append(float(s1[3]))
-	scores2.append(float(s2[3]))
+	scores1.append(float(s1))
+	scores2.append(float(s2))
 
 
 print 'Their average:', sum(scores1)/len(scores1)

### 2013-03-31 code/src/figures.py

@@ -1034,7 +1034,7 @@ def quality_scatter(title='Title'):
 	for c in ci:
 		if(c in turker_counts and not(ci[c] == None) and not(cia[c] == None) and (len(ci[c]) > 3)):
 			names.append(c)
-			#y.append(ci[c][0])
+			ya.append(ci[c][0])
 			y.append(cia[c][0])
 			e.append(ci[c][3])
 			x.append(ci[c][2])
@@ -1056,7 +1056,7 @@ def quality_scatter(title='Title'):
 #	plt.scatter(x, y, s=area)
 	plt.scatter(x, y, s=area)
 	plt.xscale('log')
-	plt.xlim([.1,1000000])
+	plt.xlim([1,1000000])
 	plt.ylim([0,1])
 	plt.xlabel('Number of assignments', fontsize='14')
 	plt.ylabel('Average quality', fontsize='14')

### 2013-03-31 code/src/summary.py

@@ -91,8 +91,10 @@ def summary_table_condensed():
 		lang = d[0]
                 nomatch, match= tquals[lang]
 		total = int(d[3])
-		numin = int(d[2])
-		numout = int(d[1])
+		xnumin = int(d[2])
+		xnumout = int(d[1])
+		numin = 0
+		numout = 0
 		cstring = ''
 		nstring = ''
 		try:
@@ -102,8 +104,12 @@ def summary_table_condensed():
 			continue
 		for p in all_countries[:3]:
 			cstring += '%s (%d) '%(countries[p[0]],p[1],)
+			numin += p[1]
 		for p in all_noncountries[:3]:
 			nstring += '%s (%d) '%(countries[p[0]],p[1],)
+			numout += p[1]
+		if (xnumin < numin) or (xnumout < numout):
+			print countries[p[0]], xnumin, numin, xnumout, numout
 		if(match < nomatch):
 			print '%s&%.02f (%d) &\\textbf{%.02f} (%d)&%s&%s\\\\'%(langmap[lang],match,numin,nomatch,numout,cstring,nstring,)
 		elif(nomatch < match):

### 2013-03-31 writeup/paper.tex

@@
 MTurk is a true market, meaning that Turkers are free to choose to complete the HITs which interest them, and Requesters can price their tasks competitively to try to attract workers and have their tasks done quickly \cite{faridani-et-al:2011,singer-mittal:2011}.
-Turkers remain anonymous to Requesters, and all payment occurs through Amazon.
-Requesters are able to accept submitted work or reject work that does not meet their standards.
-Turkers are only paid if a Requester accepts their work.
+Turkers remain anonymous to Requesters, \nocite{Lease2013}
+and all payment occurs through Amazon. Requesters are able to accept submitted work or reject work that does not meet their standards.  Turkers are only paid if a Requester accepts their work.
 

### 2013-03-31 writeup/paper.tex
Minor edits

--- 2013-03-31 writeup/paper.tex
@@
 
-\section{Further Data Analysis}
+\section{Data Analysis}
 
@@
 
+Figure \ref{quality-scatter} shows the number of assignments competed per country and per-country quality estimates.
+
 \paragraph{Use of machine translation}
@@
 Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphabet) have lower overlap with Google,  suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.
+% suggesting that it is easier for Turkers to use MT for Latin alphabet languages.
 
@@
 As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
-Turkers' performance on our control tasks is well correlated with this measure of quality.
 We had external bilingual dictionaries for 27 of the 119 languages examined in this study.\footnote{The bilingual dictionaries were between English and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz.

### 2013-03-31 writeup/paper.tex
quality figures

--- 2013-03-31 writeup/paper.tex
@@
 \hline\hline
-Hindi&\textbf{0.35} (295)&0.34 (4)&India (285) UAE (5) UK (5) &Saudiarabia (2) Russia (1) Oman (1) \\
-Tamil&\textbf{0.37} (276)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
-Malayalam&0.48 (233) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudiarabia (1) Maldives (1) \\
-Spanish&\textbf{0.72} (163)&0.61 (22)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) Newzealand (1) \\
-French&0.65 (141) &\textbf{0.86} (6)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
-German&\textbf{0.83} (89)&0.65 (51)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
-Italian&\textbf{0.78} (85)&0.71 (42)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
-Chinese&\textbf{0.24} (108)&0.16 (11)&US (79) Singapore (15) China (14) &Hongkong (6) Australia (3) Germany (2) \\
-Malay&0.76 (14) &\textbf{0.83} (109)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
-Irish&\textbf{0.68} (58)&0.64 (55)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
-Czech&\textbf{0.71} (39)&0.63 (50)&US (19) Czechrepublic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
-Turkish&0.72 (71) &\textbf{0.73} (29)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
-Amharic&\textbf{0.18} (17)&0.02 (83)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
-Swedish&\textbf{0.66} (54)&0.61 (39)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
-Portuguese&\textbf{0.77} (93)&0.74 (3)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
-Arabic&0.22 (45) &\textbf{0.26} (35)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
-Kannada&\textbf{0.24} (107)&0.00 (2)&India (106) US (1) &France (1) Germany (1) \\
-Russian&\textbf{0.09} (53)&0.06 (25)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
-Afrikaans&\textbf{0.74} (4)&0.73 (96)&Southafrica (4) &India (93) Netherlands (2) UAE (1) \\
-Sindhi&\textbf{0.15} (93)&0.02 (7)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
+Hindi&\textbf{0.35} (299)&0.34 (7)&India (285) UAE (5) UK (5) &Saudiarabia (2) Russia (1) Oman (1) \\
+Tamil&\textbf{0.37} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
+Malayalam&0.48 (235) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudiarabia (1) Maldives (1) \\
+Spanish&\textbf{0.72} (205)&0.61 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) Newzealand (1) \\
+French&0.65 (183) &\textbf{0.86} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
+German&\textbf{0.83} (99)&0.65 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
+Italian&\textbf{0.78} (98)&0.71 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
+Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hongkong (6) Australia (3) Germany (2) \\
+Malay&0.76 (15) &\textbf{0.83} (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
+Irish&\textbf{0.68} (58)&0.64 (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
+Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czechrepublic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
+Turkish&0.72 (83) &\textbf{0.73} (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
+Amharic&\textbf{0.18} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
+Swedish&\textbf{0.66} (58)&0.61 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
+Portuguese&\textbf{0.77} (107)&0.74 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
+Arabic&0.22 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
+Kannada&\textbf{0.24} (106)&0.00 (1)&India (106) US (1) &France (1) Germany (1) \\
+Russian&\textbf{0.09} (72)&0.06 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
+Afrikaans&\textbf{0.74} (4)&0.73 (98)&Southafrica (4) &India (93) Netherlands (2) UAE (1) \\
+Sindhi&\textbf{0.15} (93)&0.02 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
 \hline\hline

### 2013-03-31 code/src/figures.py

@@ -939,7 +939,7 @@ def region_scatter(title='Title'):
 	plt.scatter(xboth, yboth, s=areaboth)
 	plt.scatter([50000], [0.9], s=[100], color='k')
 	plt.xscale('log')
-	plt.xlim([0,1000000])
+	plt.xlim([1,1000000])
 	plt.ylim([0,1])
 	plt.xlabel('Number of assignments', fontsize='14')
 	plt.ylabel('Average quality', fontsize='14')
@@ -951,13 +951,12 @@ def region_scatter(title='Title'):
         plt.annotate('100 turkers',xy =(50000,0.9),xytext=(20,10),textcoords='offset points',ha ='left',va='bottom',arrowprops=arrows, fontsize=14)
 	plt.show()
         plt.clf()
-	return
 	#just in region
 	plt.scatter(xin, yin, s=areain)
-	plt.scatter([50000], [0.9], s=[100], color='k')
+#	plt.scatter([50000], [0.9], s=[100], color='k')
 	print zip(namesin, xin, yin)
 	plt.xscale('log')
-	plt.xlim([0,100000])
+	plt.xlim([0,1000000])
 	plt.ylim([0,1])
 	plt.xlabel('Number of assignments', fontsize='14')
 	plt.ylabel('Average quality', fontsize='14')
@@ -966,15 +965,15 @@ def region_scatter(title='Title'):
 	arrows = dict(arrowstyle = '->', connectionstyle = 'arc3,rad=0')
 	for label, x, y in zip(labelsin, labelxin, labelyin):
         	plt.annotate(label,xy =(x,y),xytext=(20,10),textcoords='offset points',ha ='left',va='bottom',arrowprops=arrows, fontsize=14)
-        plt.annotate('100 turkers',xy =(50000,0.9),xytext=(20,10),textcoords='offset points',ha ='left',va='bottom',arrowprops=arrows, fontsize=14)
+    #    plt.annotate('100 turkers',xy =(50000,0.9),xytext=(20,10),textcoords='offset points',ha ='left',va='bottom',arrowprops=arrows, fontsize=14)
 	plt.show()
         plt.clf()
 	#just out of region
 	plt.scatter(xout, yout, s=areaout)
-	plt.scatter([50000], [0.9], s=[100], color='k')
+#	plt.scatter([50000], [0.9], s=[100], color='k')
 	print zip(namesout, xout, yout)
 	plt.xscale('log')
-	plt.xlim([0,100000])
[…]

### 2013-03-31 code/src/summary.py

@@ -111,9 +111,9 @@ def summary_table_condensed():
 		if (xnumin < numin) or (xnumout < numout):
 			print countries[p[0]], xnumin, numin, xnumout, numout
 		if(match < nomatch):
-			print '%s&%.02f (%d) &\\textbf{%.02f} (%d)&%s&%s\\\\'%(langmap[lang],match,numin,nomatch,numout,cstring,nstring,)
+			print '%s&%.02f (%d) &\\textbf{%.02f} (%d)&%s&%s\\\\'%(langmap[lang],match,xnumin,nomatch,xnumout,cstring,nstring,)
 		elif(nomatch < match):
-			print '%s&\\textbf{%.02f} (%d)&%.02f (%d)&%s&%s\\\\'%(langmap[lang],match,numin,nomatch,numout,cstring,nstring,)
+			print '%s&\\textbf{%.02f} (%d)&%.02f (%d)&%s&%s\\\\'%(langmap[lang],match,xnumin,nomatch,xnumout,cstring,nstring,)
 	
 	print '\\hline\\hline'
 	print '\\end{tabular}'

### 2013-03-31 writeup/paper.tex
data release

@@
 
-We plan to release all data used in this study upon publication of this paper.  Our data release will include the raw data, along with bilingual dictionaries that are filtered to be high quality.
+We plan to release all data and code used in this study upon publication of this paper.
+Our data release will include the raw data, along with bilingual dictionaries that are filtered to be high quality.
+It will include 308,079 translation assignments from 5,277 Turkers and 20,955 synonym assignments from 1,006 Turkers, along with meta information like geolocation and time submitted, plus external dictionaries used for validation.
+The dictionaries will contain 850,907 total translated words in 101 languages, along with code to filter the dictionaries based on different criteria.
 

### 2013-03-31 code/src/figures.py
google filter quality scatter

@@ -852,7 +852,6 @@ def native_compare_line_graph(native, nonnative):
 	plt.show()
 
 def dictionary_stats_turker():
-#tr      NL:3    GR:1    CA:1    TR:39   MK:12   GE:1    AU:1    US:20   RO:5    BA:1
 	DICT_DIR = 'dictionaries'
         dict_files=['%s/nonclpair.turkerlist'%DICT_DIR, '%s/clpair.turkerlist'%DICT_DIR]
         data = dict()
@@ -872,6 +871,60 @@ def dictionary_stats_turker():
         for d in data:
                 ret[d] = (data[d][0], data[d][1])
         return ret
+
+def get_goog_filter(c=1.0):
+	assigns = list()
+	for line in csv.DictReader(open('%s/byassign.googmatch'%OUTPUT_DIR), delimiter='\t'):
+		aid = line['id']
+		q = line['avg']
+		if not q == 'N/A':
+			if float(q) < c:
+				assigns.append(aid)	
+	print assigns
+	return assigns
+
+
+def region_scatter_googfilter(title='Title'):
+	points_to_label = ['RO','RU','PK','IN','US','MY','MK','ES','DE','FR','CA','100 turkers']
+	cmap = reverse_cntry_map('ref/countrynames')
+	cmap['100 turkers'] = '100 turkers'
+	attr= 'country'
+	infilter = [l.strip() for l in open('output/byassign.voc.validclpair').readlines()]
+	outfilter = [l.strip() for l in open('output/byassign.voc.invalidclpair').readlines()]
+	googfilter = get_goog_filter(c=0.5)
+	ciout = conf_int_by_attr_region(attr, filterlist=list(set(outfilter).intersection(set(googfilter))))
+	turker_counts = dictionary_stats_turker()
+	namesout = list(); xout = list(); yout = list();areaout=list();
+	for c in ciout:
+		if(c in turker_counts and not(ciout[c] == None) and (len(ciout[c]) > 3)):
+			namesout.append(c)
+			yout.append(ciout[c][0])
+			xout.append(ciout[c][2])
+			areaout.append(ciout[c][3])
+        labelsout = list(); labelxout = list(); labelyout = list();
+	for nm in points_to_label:
+		try:
+			idx = namesout.index(nm)
+        	        labelsout.append(cmap[nm])
+                	labelxout.append(xout[idx])
[…]

### 2013-03-31 writeup/paper.tex
google filter quality scatter
Added joined figure with first 3
Added new joined scatters
Pushed paper with 1column scatter join

@@
 A total of 5,277 unique workers completed our HITs.
-Among those, 3,890 provided responses to our survey questions, and we were able to geolocate 5,114.
+Among those, 3,890 provided responses to our survey questions, and we were able to geolocate 5,050.
 Figure \ref{map} plots the location of workers across 111 countries.
@@
 \begin{table*}
-\footnotesize
+\scriptsize
+\begin{center}
 \begin{tabular}{lllll}
@@
 \normalsize
+\end{center}
 \caption{Translation quality when partitioning the translations into two groups, one contains translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other contains translations from Turkers outside those regions.} \label{region-summary}
@@
 %%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
-\begin{figure*}[h]
+\begin{figure}
 \begin{center}
-\includegraphics[width=.8\linewidth]{final-figures/quality-scatter}
+\includegraphics[width=0.78\linewidth]{final-figures/quality-scatter_joined-1column}
 \end{center}
 
-\caption{Estimated quality of translations by country.
-Each circle is a country, sized proportional to the number of active Turkers from that country.
-Quality is calculated as the average number of control words which were correct translations of the source word, where ”correct” means that the provided translation was judged to be synonymous with the known translation by workers in a second-pass HIT.
-Figure represents data from approx.
-295,000 assignments for which geolocation was known.}
+\caption{Estimated quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country. }
 \label{quality-scatter}
-\end{figure*}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-03-31 writeup/paper.tex
final commit

--- 2013-03-31 writeup/paper.tex
@@
 Misspellings like $<${\it lactation, lactiation} $>$ were judged to have same meaning, and were marked as misspelled.
-3 separate Turkers judged each pair, allowing majority votes for difficult cases.
+Three separate Turkers judged each pair, allowing majority votes for difficult cases.
 
@@
 \begin{align}	
-	\text{Quality}(a_i) = \frac{1}{k}\sum\limits_{j=1}^{k_i}\mathbf{\delta}(tr_{ij} \in \texttt{syns[$g_j$]})
+	\text{Quality}(a_i) = \frac{1}{k_i}\sum\limits_{j=1}^{k_i}\mathbf{\delta}(tr_{ij} \in \texttt{syns[$g_j$]})
 \end{align}	
-where $a_i$ is the $i^{th}$ assignment, $k_i$ is the number of controls in $a_i$, $tr_j$ is the Turker's provided translation of control word $j$ in assignment $i$, $g_j$ is the gold standard translation of control word $j$, \texttt{syns[$g_j$]} is the set of words judged to be synonymous with $g_j$ and includes $g_j$, and $\mathbf{\delta}(x)$ is Kronecker's delta and takes value 1 when $x$ is true.
+where $a_i$ is the $i^{th}$ assignment, $k_i$ is the number of controls in $a_i$, $tr_{ij}$ is the Turker's provided translation of control word $j$ in assignment $i$, $g_j$ is the gold standard translation of control word $j$, \texttt{syns[$g_j$]} is the set of words judged to be synonymous with $g_j$ and includes $g_j$, and $\mathbf{\delta}(x)$ is Kronecker's delta and takes value 1 when $x$ is true.
 Most assignments had two known words embedded, so most assignments had scores of either 0, 0.5, or 1.
@@
 The 10 languages to finish in the shortest amount of time were: Tamil, Malayalam, Telugu, Hindi, Macedonian, Spanish, Serbian, Romanian, Gujarati, and Marathi.
-7 of the 10 fastest languages are from India, which is unsurprising given the geographic distribution of workers.
+Seven of the ten fastest languages are from India, which is unsurprising given the geographic distribution of workers.
 Some languages follow the pattern of having a smattering of assignments completed early, with the rate picking up later.
@@
 Italian&\textbf{0.78} (98)&0.71 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
-Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hongkong (6) Australia (3) Germany (2) \\
+Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hong Kong (6) Australia (3) Germany (2) \\
 Malay&0.76 (15) &\textbf{0.83} (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
 Irish&\textbf{0.68} (58)&0.64 (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
-Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czechrepublic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
+Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czech Republic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
 Turkish&0.72 (83) &\textbf{0.73} (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
@@
 \begin{center}
-\includegraphics[width=.8\linewidth]{final-figures/quality-scatter}
+\includegraphics[width=0.8\linewidth]{final-figures/quality-scatter_joined}
 \end{center}
@@
 
-Figure \ref{quality-scatter} shows the number of assignments competed per country and per-country quality estimates.
+Figure \ref{quality-scatter} shows the number of assignments completed per country and per-country quality estimates for 4 scenerios: (a) overall, (b) for assignments completed in region, (c) for assignments completed out of region, and (d) for out of region assignments which contained low overlap with GoogleTranslate.
 
@@
 
-We used Google Translate to translate all 10,000 words for 50 foreign languages that Google Translate covers.
-We measured the percent of translations received that exactly matched the translation returned from Google translate.
+We used GoogleTranslate to translate all 10,000 words for 50 foreign languages that GoogleTranslate covers.
+We measured the percent of translations received that exactly matched the translation returned from GoogleTranslate.
 Results are show in Figure \ref{googlematch}.
-Assignments averaged around 42\% overlap with Google translate.
+Assignments averaged around 42\% overlap with GoogleTranslate.
 Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphabet) have lower overlap with Google,  suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.
@@
 \paragraph{Validation of controls} 
-Higher overlap with Google translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some control translations have already been indexed by Google.
+Higher overlap with GoogleTranslate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some control translations have already been indexed by Google.
 We therefore investigated the validity of our use of Wikipedia inter-language links as gold standard translations.
@@
 As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
-We had external bilingual dictionaries for 27 of the 119 languages examined in this study.\footnote{The bilingual dictionaries were between English and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz.
-}  We used each of these bilingual dictionaries to computer language-level quality scores, using the dictionary's translation as a gold standard translation for any of the 10,000 foreign words in our study.
+We had external bilingual dictionaries for 24 of the 119 languages examined in this study.\footnote{The bilingual dictionaries were between English and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz.
+}  We used each of these bilingual dictionaries to compute language-level quality scores, using the dictionary's translation as a gold standard translation for any of the 10,000 foreign words in our study.
 In some cases, the overlap of words was low, since dictionaries list root forms of words and we translated inflected forms.
 
-We ranked the 27 languages based on their translation quality scores according to the external dictionaries, and calculated correlation when compared to the ranking produced by our gold standard control.
+We ranked the 24 languages based on their translation quality scores according to the external dictionaries, and calculated correlation when compared to the ranking produced by our gold standard control.
 The Pearson correlation was $\rho=0.53$.

### 2013-11-05 writeup/reviewer-response/paper.tex
response to reviewers

\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage[fit]{truncate}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{multirow}
\usepackage{dblfloatfix}
\usepackage{float}
\usepackage{subfloat}
\usepackage{subcaption}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{5cm}    % Expanding the titlebox

\newcommand{\affliationPenn}{\ensuremath{{}^\text{1}}}
\newcommand{\affliationJHU}{\ensuremath{{}^\text{2}}}

\title{The Language Demographics of  Amazon Mechanical Turk : Response  to Reviewers}

\author{Ellie Pavlick\affliationPenn \ \ \ \ \ Ann Irvine\affliationJHU  \ \ \ \ \ Dmitry Kachaev\affliationJHU  \ \ \ \ \  Chris Callison-Burch\affliationPenn$^{,}$\affliationJHU \\
\affliationPenn Computer and Information Science Department, University of Pennsylvania \\
\affliationJHU Human Language Technology Center of Excellence, Johns Hopkins University \\
  }

% Anonymized for submission
\author{}

\date{}

\begin{document}
\maketitle

\begin{figure}
\centering
\begin{subfigure}[b]{1\linewidth}
\includegraphics[width=\textwidth]{figures/turker-googmatch-distribution.png}
\caption{Individual turker overlap with google translate. We believe the inflection point at ~60\% overlap with Google suggests a reasonable cutoff by which to filter workers. Workers with \textgreater 60\% overlap can be reasonably considered to be cheating and can be removed.}                
\label{dist}
\end{subfigure}
\begin{subfigure}[b]{1\linewidth}
\includegraphics[width=\textwidth]{figures/google-cdf-googlangs.png}
\caption{Cumulative distribution of overlap with Google translate for workers and translations. We see that eliminating all workers with \textgreater 60\% overlap with google translate still preserves \textgreater 80\% of workers and \textgreater 70\% of translations.}
\label{cdf}
\end{subfigure}
\caption{}\label{cheaters}
\end{figure}

\section{Use of Google Translate}

The primary concern across reviewers was the high amount of overlap between workers' translations and translations available through online resources, i.e. Google Translate. The editor summarized : 
\begin{quote}
All reviewers had issues with the amount of cheating taking place among Turkers. It would be useful to quantify/detect this and remove such participants from your results.
\end{quote}

We took at closer look at the amount of overlap with Google translate in our collected translations in order to address this issue. We found that while overall overlap is high, it is not consistantly high across all turkers. Figure \ref{dist} shows that while a small number of turkers have a very high amount of overlap with Google (near 80\%) the majority overlap less than half of the time.

As Reviewer E noted :

\begin{quote}
..it is quite possible that a fluent speaker of a language provides the same translation as Google Translate for a given word.  In other words, the performance results are inconclusive.
\end{quote}

We see a clear inflection near the 60\% overlap point, suggesting that this cutoff may work well to eliminate turkers who are likely using Google Translate to cheat without punishing those who are producing honest translations that happen to overlap with Googe Translate.

Figure \ref{cdf} shows that removing workers with suspiciously high overlap with Google retains the majority of workers and translations, and will not greatly decrease the size of the study.

We have rerun the quality analysis in the paper, omitting workers with \textgreater 60\% overlap with Google Translate. The quality scores and rankings do not change substantially. For reference, figure 2 from the paper is reproduced in figure \ref{qual}, both with and without the high-overlap Turkers included.

\begin{figure}
\centering
\begin{subfigure}[b]{1\linewidth}
\includegraphics[width=\textwidth]{figures/fig2with.png}
\caption{All turkers.}                
\label{dist}
\end{subfigure}
\begin{subfigure}[b]{1\linewidth}
\includegraphics[width=\textwidth]{figures/fig2without.png}
\caption{Turkers with \textless 60\% overlap with Google Translate.}
\label{cdf}
\end{subfigure}
\caption{Qualities for languages with \textgreater 50 turkers. Dark blue shows quality measured by perfect match on the control translation. Light blue indicates quality measured by included synonymous translations.}\label{qual}
\end{figure}

\section{Robustness of results to removing few big players}

The editor and reviewer G highlighted the possibility that the quality results are due to a few large players, and may not be robust if the experiment were rerun with a different group of workers : 
\begin{quote}
It is possible that a small number of workers could have driven response accuracies for some languages. The authors could have accounted for this in a straightforward way by regressing out the contributions of individual workers, e.g. by using random effects models.
\end{quote}
We ran a random effects model and found blah blah blah blah blah blah blah.

\section{Extrinsic evalutation of mturk data for SMT}

All the reviewers expressed desire for further evidence of the usefulness of the Turker-provided translations for statistical machine translation, and the possibility of extending the demonstrated methods to multiple word translations. The editor requests :

\begin{quote}
It would be interesting to show that the proposed approach brings an advantage over current SMT technology, i.e., improves lexical translations for an existing SMT system....It would also be interesting to assess whether your results carry over to multiple words and/or sentences. 
\end{quote}

Previous work by Matt Post in the 2010 WMT has demonstrated not only that turkers are able to provide high quality translations of complete sentences, but also that these translations, when added into an SMT pipeline, measurably improve translation quality. \textbf{MORE HERE.}

\section{Affect of time of day when HIT was posted}

Reviewer F raised an interesting question about the affect of time of day on Turker activity :

\begin{quote}
Did the authors take into account time of day, when the HIT was posted etc. to get a sense of whether one time of day is more optimal than others for each language? Does it matter at all?
\end{quote}
Figure \ref{time} shows the activity over a 24 hour day for 23 languages with greater than 100 turkers each. The plot shows that activity does vary across time zones, and suggests that choosing the release time intelligently based on the HIT language is likely to affect how quickly it is completed.
\begin{figure*}
\includegraphics[width=1\linewidth]{figures/times.png}
\caption{Number of HITs completed during each hour of the day for languages with \textgreater 100 turkers.}
\label{time}
\end{figure*}

\section{Changes in results if study continued over time}

Reviewer B asked : 
\begin{quote}
The authors ran an experiment over 3.5 months, but I wonder how the demographics change over time. Are there seasonal effects in the workforce? Has it changed over the past year? And more importantly, will it change substantially in the future? I'm somewhat skeptical that these demographics will remain constant, especially as Amazon rolls out changes to the service.
\end{quote}

While we agree that the questions posed are very interesting, we feel that answering these questions is the subject of another study. Our study is aimed at capturing the current demographics of Mechanical Turk, and proposing a way to empiracally validate self-reported demographic information about language skills. It is true that the current demongraphic makeup of MTurk workers is likely to shift, but the time and expense of tracking these changes over time puts the reviewer's questions outside the scope of this project.

\section{Accuracy of Geolocation}

We understand that geolocation is not perfect, which is why we propose the use of location data as just one of several criteria by which to identify likely qualified translators. The trends that we observe in our analysis, where we show that turkers geolocated within a region likely to speak the source language being translated tend to perform better on our controls, coincide with what we would expect to see if geolcation were accurate. This seems to support the assumption that, on average, the geolocation is performing sufficiently well.

\section{Novelty}

Its novel. Trust us.

\end{document}

### 2013-11-05 code/src/anova.py

@@ -20,7 +20,7 @@ tmap = dictionaries.turker_map()
 
 def scores():
         scores = dict()
-        for line in open('%s/byturker.voc.quality.new'%DATA_DIR).readlines():
+        for line in open('%s/byturker.voc.quality'%DATA_DIR).readlines():
                 l = line.split('\t')
 		try:
 	                scores[l[0]] = float(l[1].strip())

### 2013-11-05 code/src/compile_data_from_raw.py

@@ -6,9 +6,10 @@ import string
 import codecs
 
 RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11'
-OUTPUT_DIR = 'output'
+OUTPUT_DIR = 'new-output'
 
 def hits_language():
+	nm, lm = lang_map()
 	hit_path = '%s/hits'%RAW_DIR
 	language_path = '%s/languages'%RAW_DIR
         lang_data = {}
@@ -29,11 +30,11 @@ def lang_map():
         num_data = {}
         for line in csv.DictReader(open('%s/languages'%RAW_DIR)):
                 lang = line['name'].lower()
-                id = line['id']
+                lid = line['id']
                 if(lang not in lang_data):
                         lang_data[lang] = line['prefix']
-                if(id not in num_data):
-                        num_data[id] = line['prefix']
+                if(lid not in num_data):
+                        num_data[lid] = line['prefix']
         return num_data, lang_data
 
 def country_map():
@@ -72,8 +73,8 @@ def assign_workers(path, langs, idlist=None):
         numlangmap, langmap = lang_map()
         data = {}
         for line in csv.DictReader(open(path)):
-		if line['mturk_status'] == 'Rejected':
-			continue
+#		if line['mturk_status'] == 'Rejected':
+#			continue
                 worker = line['worker_id']
                 assign = line['id']
 		if( (not(idlist==None)) and (assign not in idlist) ):
@@ -88,12 +89,12 @@ def assign_langs(path, langs, idlist=None, skip_rejected=False):
         numlangmap, langmap = lang_map()
         survey_data = {}
         for line in csv.DictReader(open(path)):
-		if skip_rejected and line['mturk_status'] == 'Rejected':
-			continue
+#		if skip_rejected and line['mturk_status'] == 'Rejected':
+#			continue
                 worker = line['worker_id']
                 assign = line['id']
-		if( (not(idlist==None)) and (assign not in idlist) ):
-			continue
+#		if( (not(idlist==None)) and (assign not in idlist) ):
+#			continue
[…]

### 2013-11-05 code/src/dictionaries.py

@@ -12,7 +12,7 @@ from scipy import stats
 import compile_data_from_raw as dat
 
 RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11'
-DICT_PATH = './translations.out'
+DICT_PATH = './translations.all.control.tagged.out'
 CLPAIRS = './cl-pairs.csv'
 OUTPUT_DIR = 'output'
 DICT_DIR = '../../dictionaries/ellie/clpair' #'dictionaries'
@@ -75,10 +75,8 @@ def yrs_list(cutoff):
 
 def word_map(path):
 	words = dict()
-	print 'reading vocab'
         for i,line in enumerate(codecs.open(path, encoding='utf-8').readlines()[1:]):
-		if(i % 10000 == 0):
-			print i
+	#	if(i % 10000 == 0): print i
 		comps = line.split(',')
 		if(len(comps) > 1):
 			wid = comps[0]
@@ -121,10 +119,10 @@ def resolve_word_ids(data):
 		retdict[a] = list()
 		for wid,trans in data[a]:
 			just_wid, iscontrol = justid(wid)	
-			if iscontrol == '0':
-				if just_wid in words:
-					word = words[just_wid]
-					retdict[a].append((word,trans))
+#			if iscontrol == '0':
+			if just_wid in words:
+				word = words[just_wid]
+				retdict[a].append((just_wid,word,trans,iscontrol))
 	return retdict
 			
 
@@ -204,12 +202,15 @@ def write_translations(data, fname):
 	print 'writing dict file'
 	outfile = codecs.open(fname, encoding='utf-8', mode='w', errors='ignore')
 	for i,aid in enumerate(data):
-		if(i%100 == 0):
+		if(i%1000 == 0):
 			print i
 		outfile.write('%s\t'%aid)
-		for word,tran in data[aid]:
+		for wid,word,tran,cntrl in data[aid]:
 			try:
-				outfile.write('%s:%s\t'%(word,re.sub('\n',' ',tran)))
+				tran = tran.replace('\n',' ')
+				tran = tran.replace(':','-')
+				tran = tran.replace('\t',' ')
+				outfile.write('%s:%s:%s:%s\t'%(wid,word,tran,cntrl))
 			except UnicodeDecodeError:
 				print 'unicode error, ignoring'
 				outfile.write('<decode-err>\t')
@@ -589,7 +590,7 @@ if __name__ == '__main__':
[…]

### 2013-11-05 code/src/figures.py

@@ -536,7 +536,7 @@ def exact_match_graphs(all_ci_dict, title='Graph', graph_avg=True, cutoff=3000):
         plt.ylabel('')
 	plt.ylim([0,max(yax)+.1])
 	plt.xlim([0,len(ci_dict)])
-	plt.savefig('figures/exact-match-bar.pdf')
+	plt.show() #savefig('figures/exact-match-bar.pdf')
 
 #stacked bar graph of proportion of exact matches and proportion of synonymn matches
 #side by side with proportion of google translate matches
@@ -598,7 +598,7 @@ def conf_int_graphs(all_ci_dict, title='Graph', graph_avg=True, cutoff=3000):
         plt.ylabel('')
 	plt.ylim([0,max(yax)+.1])
 	plt.xlim([0,len(ci_dict)])
-	plt.savefig('figures/hitlang-bar.pdf')
+	plt.show() #savefig('figures/hitlang-bar.pdf')
 
 #mapping of assign_id to hit_id
 def hit_map():
@@ -1229,7 +1229,7 @@ def natlang_pie(tuples):
         proptease.set_size('medium')
         plt.setp(autotexts, fontproperties=proptease)
         plt.setp(texts, fontproperties=proptease)
-	plt.savefig('figures/natlang-pie.pdf')
+	plt.show() #savefig('figures/natlang-pie.pdf')
 
 #return statistics on turkers' native languages as a list of (language, count) tuples
 def natlang_table():

### 2013-11-05 code/src/qc.py

@@ -8,7 +8,9 @@ import dictionaries
 import compile_data_from_raw as dat
 
 RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11'
-OUTPUT_DIR = 'output'
+OUTPUT_DIR = 'new-output'
+
+import pickle
 
 goog_langs = ['el', 'eo', 'zh', 'af', 'vi', 'is', 'it', 'kn', 'cs', 'cy', 'ar', 'eu', 'et', 'gl', 'id', 'es', 'ru', 'az', 'nl', 'pt', 'tr', 'lv', 'lt', 'th', 'gu', 'ro', 'ca', 'pl', 'ta', 'fr', 'bg', 'ms', 'hr', 'de', 'da', 'fa', 'fi', 'hy', 'hu', 'ja', 'he', 'te', 'sr', 'sq', 'ko', 'sv', 'ur', 'sk', 'uk', 'sl', 'sw']
 
@@ -74,7 +76,7 @@ def get_syn_lists():
 
 def get_goog_translations():
 	trans = dict()
-	for line in open('goog_trans').readlines():
+	for line in open('output/goog_trans').readlines():
 		wid, word, tran, lang = line.strip().split('\t')
 		trans[wid.strip()] = tran.strip()		
 	return trans
@@ -257,12 +259,14 @@ def get_good_and_bad_translations(path):
 	for lang in controls:
 		pos[lang]=[(orig,string.join(controls[lang][orig]['pos'],',')) for orig in controls[lang] if len(controls[lang][orig]['pos'])>0]
 		neg[lang]=[(orig,string.join(controls[lang][orig]['neg'],',')) for orig in controls[lang] if len(controls[lang][orig]['neg'])>0]
-	write_control_dicts(pos, file_prefix='poscontrols/dictionary')
-	write_control_dicts(neg, file_prefix='negcontrols/dictionary')
+	write_control_dicts(pos, file_prefix='new-output/poscontrols/dictionary')
+	write_control_dicts(neg, file_prefix='new-output/negcontrols/dictionary')
 
 #returns a dictionary of {assignment : # of controls attempted, # of controls correct, average performance on controls}
 def get_goog_match_by_assign(path):
         matches = get_goog_translations()
[…]

### 2013-11-15 code/src/20130905/paper-rewrite/figures/code/goog-cheaters.py
new code for rewrite

@@ -1,0 +1,69 @@
+#!/bin/python
+# -*- coding: utf-8 -*- 
+
+import csv
+import sys
+import operator
+import numpy as np
+import scipy.stats
+import operator
+import matplotlib.pyplot as plt
+import sys; sys.path.append('/home/steven/Documents/Ellie/Research/demographics/repo/code/src/20130905')
+#from settings import settings
+
+goog_langs = ['el', 'eo', 'zh', 'af', 'vi', 'is', 'it', 'kn', 'cs', 'cy', 'ar', 'eu', 'et', 'gl', 'id', 'es', 'ru', 'az', 'nl', 'pt', 'tr', 'lv', 'lt', 'th', 'gu', 'ro', 'ca', 'pl', 'ta', 'fr', 'bg', 'ms', 'hr', 'de', 'da', 'fa', 'fi', 'hy', 'hu', 'ja', 'he', 'te', 'sr', 'sq', 'ko', 'sv', 'ur', 'sk', 'uk', 'sl', 'sw']
+
+workers = {}
+trans = {}
+turkers = {row['worker'] : row for row in csv.DictReader(open('results/data/googmatch.turkers.txt'), delimiter='\t')}
+
+def use(worker, threshold) : return (float(turkers[worker]['match']) <= threshold)
+
+for cutoff in [0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0]:
+
+	for line in open('data/pass-1').readlines():
+		hitid, lang, word, control, goog, responses = line.split('\t', 5)
+			
+		if lang not in goog_langs : continue
+
+		word = word.lower()
+
+		for response in responses.split('\t'):
+
+			t = response.strip().split(':')
+
+			if len(t) > 1 : 
+
+				worker = t[0]
+				translation = t[1].lower()
+
+				if(use(worker, cutoff)):
+					if cutoff not in workers: workers[cutoff] = set(); trans[cutoff] = [];
+					workers[cutoff].add(worker)
+					trans[cutoff].append(translation)
+
+#data = [(0,2305), (0.1,2475), (0.2,2758), (0.3,3198), (0.4,3690), (0.5,4312), (0.6,4836), (0.7,5129), (0.8,5266), (0.9,5280), (1.0,5281)]
+	
+data = sorted([(w,len(workers[w])) for w in workers], key=operator.itemgetter(0))
[…]

### 2013-11-15 code/src/20130905/paper-rewrite/figures/code/google_bar.py

@@ -1,0 +1,61 @@
+#!/bin/python
+import csv
+import math
+import operator
+import numpy as np
+import sys
+sys.path.append('scripts')
+from settings import settings
+from scipy import stats
+from scipy.stats import ttest_1samp
+import matplotlib.pyplot as plt
+
+data = {}
+all_data = []
+
+goog_langs = ['el', 'eo', 'zh', 'af', 'vi', 'is', 'it', 'kn', 'cs', 'cy', 'ar', 'eu', 'et', 'gl', 'id', 'es', 'ru', 'az', 'nl', 'pt', 'tr', 'lv', 'lt', 'th', 'gu', 'ro', 'ca', 'pl', 'ta', 'fr', 'bg', 'ms', 'hr', 'de', 'da', 'fa', 'fi', 'hy', 'hu', 'ja', 'he', 'te', 'sr', 'sq', 'ko', 'sv', 'ur', 'sk', 'uk', 'sl', 'sw']
+
+n=0.0;d=0.0;
+
+gmatch = csv.DictReader(open('results/data/googmatch.turkers.txt'), delimiter='\t')
+#worker_gmatch = {line['worker']: float(line['match']) for line in gmatch}
+worker_gmatch = {}
+for line in gmatch : 
+	w = line['worker']; l = line['lang']; m = float(line['match'])
+	if w not in worker_gmatch : worker_gmatch[w] = {}
+	worker_gmatch[w][l] = m
+
+for row in csv.DictReader(open('results/data/googmatch.assigns.txt'), delimiter = '\t'):
+	lang = row['lang']
+	if lang not in goog_langs : continue
+	if worker_gmatch[row['worker']][lang] >= settings['google_overlap_cutoff'] : continue
+	if lang not in data : data[lang] = []
+	data[lang].append(float(row['match-overall']))
+	n += float(row['match-overall']);d+=1
+	#if lang == 'cy' : print row['worker'],  worker_gmatch[row['worker']] 
+	#data[lang].append(float(row['match']))
+	
+print n / d
+
+graph_data = [] 
+t = 0 
+for lang in sorted(data.keys()) : 
+	if lang not in goog_langs : continue
+	x1 = data[lang]
+	n1, (smin1, smax1), m1, v1, ss1, sk1 = stats.describe(x1)
+	t += n1
+	#if n1 < 50 : continue
+	graph_data.append((lang,m1)) 
+
+print "total turkers,", t
+
[…]

### 2013-11-15 code/src/20130905/paper-rewrite/figures/code/language_table.py

@@ -1,0 +1,60 @@
+#\begin{tabular}{lrlrlr}\hline\hline
+#%Language&\# Turkers\\
+#\hline
+#English&592&	French&63&	Vietnamese&34\\
+#Tamil&253&	Polish&61&	Macedonian&31\\
+#Malayalam&219&	Urdu&56&	Cebuano&29\\
+#Hindi&149&	Tagalog&54&	Swedish&26\\
+#Spanish&131&	Marathi&48&	Bulgarian&25\\
+#Telugu&87&	Russian&44&	Hungarian&23\\
+#Chinese&86&	Italian&43&	Swahili&23\\
+#Romanian&85&	Bengali&41&	Thai&22\\
+#Portuguese&82&	Gujarati&39&	Catalan&22\\
+#Arabic&74&	Hebrew&38&	Lithuanian&21\\
+#Kannada&72&	Dutch&37&	Punjabi&21\\
+#German&66&	Turkish&35&	Others &$\leq$20\\
+#\hline\hline
+#\end{tabular}
+
+import csv
+import operator
+import itertools
+
+def batch(iterable, n = 3):
+   l = len(iterable)
+   for ndx in range(0, l, n):
+       yield iterable[ndx:min(ndx+n, l)]
+
+def capitalize(s) : return s.capitalize()
+
+def print_table(lang_counts) : 
+	for l1,l2,l3 in batch(sorted(lang_counts.iteritems(), key=operator.itemgetter(1), reverse=True),n=3) :
+		print '%s & %d & %s & %d & %s & %d \\\\'%(capitalize(l1[0]),l1[1],capitalize(l2[0]),l2[1],capitalize(l3[0]),l3[1])
+	
+		
+pass1_turkers = set()
+
+for line in open('data/pass-1').readlines() :
+	_, _, _, _, _, workers = line.strip().split('\t',5)
+	for wt in workers.split('\t'):
+		w,t = wt.split(':',1)
+		pass1_turkers.add(w)
+
+lmap = {l.strip().split()[1] : l.strip().split()[0] for l in open('ref/lang2name.txt').readlines()}
+
+lang_counts = {}
+tot = 0
+
+for line in csv.DictReader(open('data/turkers.tsv'), delimiter='\t') :
+	langs = [c for c in line['langs'].split(':') if not c.strip() == '']
+	if len(langs) > 1 : print langs; continue;
+	for lang in langs : 
+		try : lang = lmap[lang]
+		except : continue
[…]

### 2013-11-15 code/src/20130905/paper-rewrite/figures/code/map.py

@@ -1,0 +1,32 @@
+#99682	pam	arung	nose	NA	3275:Nose
+#1788	hi:en:	IN:	IN:	new:hi:	15:	5:23:
+#['Italy',78],
+
+import csv
+
+pass1_turkers = set()
+
+for line in open('data/pass-1').readlines() :
+	_, _, _, _, _, workers = line.strip().split('\t',5)
+	for wt in workers.split('\t'):
+		w,t = wt.split(':',1)
+		pass1_turkers.add(w)
+
+cmap = {l.strip().split()[1] : l.strip().split()[0] for l in open('../ref/countrynames').readlines()}
+
+country_counts = {}
+tot = 0
+
+for line in csv.DictReader(open('data/turkers.tsv'), delimiter='\t') :
+	countries = [c for c in line['country'].split(':') if not c.strip() == '']
+	if len(countries) > 1 : print countries; continue;
+	for country in countries : 
+		try : country = cmap[country]
+		except : continue
+		if country not in country_counts : country_counts[country] = 0
+		if line['id'] in pass1_turkers : country_counts[country] += 1; tot += 1;
+
+print tot
+
+for l in sorted(country_counts.keys()) : 
+	print "['%s',%d],"%(l,country_counts[l])

### 2013-11-15 code/src/20130905/paper-rewrite/figures/code/quality_bar.py

@@ -1,0 +1,46 @@
+#!/bin/python
+import csv
+import math
+import operator
+import numpy as np
+from scipy import stats
+from scipy.stats import ttest_1samp
+import matplotlib.pyplot as plt
+
+data = {}
+all_data = []
+
+goog_langs = ['el', 'eo', 'zh', 'af', 'vi', 'is', 'it', 'kn', 'cs', 'cy', 'ar', 'eu', 'et', 'gl', 'id', 'es', 'ru', 'az', 'nl', 'pt', 'tr', 'lv', 'lt', 'th', 'gu', 'ro', 'ca', 'pl', 'ta', 'fr', 'bg', 'ms', 'hr', 'de', 'da', 'fa', 'fi', 'hy', 'hu', 'ja', 'he', 'te', 'sr', 'sq', 'ko', 'sv', 'ur', 'sk', 'uk', 'sl', 'sw']
+
+for row in csv.DictReader(open('results/data/quality.turkers.txt'), delimiter = '\t'):
+	lang = row['lang']
+	if lang not in data : data[lang] = []
+	data[lang].append((float(row['quality']), float(row['quality_syn'])))
+	
+graph_data = [] 
+t = 0 
+for lang in sorted(data.keys()) : 
+	#if lang not in goog_langs : continue
+	x1 = [d[0] for d in data[lang]]
+	x2 = [d[1] for d in data[lang]]
+	n1, (smin1, smax1), m1, v1, ss1, sk1 = stats.describe(x1)
+	n2, (smin2, smax2), m2, v2, ss2, sk2 = stats.describe(x2)
+	t += n1
+	if n1 < 50 : continue
+	graph_data.append((m1,m2,1.96*(math.sqrt(v2) / math.sqrt(n2)),lang))
+#	tstat, pval = stats.ttest_1samp(x, am)
+#	print '%s\t%.02f\t%.02f\t%.02f\t'%(lang, m, v, pval)
+
+print "total turkers,", t
+
+graph_data = sorted(graph_data, key=operator.itemgetter(1), reverse=True) 
+
+w = .5
+p1 = plt.bar(np.arange(len(graph_data)), [d[1] for d in graph_data], width=w, color='#6699FF', yerr=[d[2] for d in graph_data], ecolor='black')
+p1 = plt.bar(np.arange(len(graph_data)), [d[0] for d in graph_data], width=w, color='#0000FF')
+#plt.ylabel('% accuracy against controls')
+plt.ylim(0,1)
[…]

### 2013-11-15 code/src/20130905/paper-rewrite/figures/code/region_table.py

@@ -1,0 +1,104 @@
+#Hindi&\textbf{0.35} (299)&0.34 (7)&India (285) UAE (5) UK (5) &Saudi Arabia (2) Russia (1) Oman (1) \\
+#Tamil&\textbf{0.37} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
+#Malayalam&0.48 (235) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudi Arabia (1) Maldives (1) \\
+#Spanish&\textbf{0.72} (205)&0.61 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) New Zealand (1) \\
+
+import csv
+import operator
+import itertools
+import sys
+sys.path.append('scripts')
+from settings import settings
+from scipy import stats
+from scipy.stats import ttest_ind
+
+def print_table(lang_counts) : 
+	for l, inavg, incnt, outavg, outcnt, locs, tot, sig  in lang_counts[:20]: 
+		topin = sorted(locs['in'].iteritems(), key=operator.itemgetter(1), reverse=True)[:3]
+		topinstr = ''
+		for c,n in topin : 
+			try : topinstr += '%s (%d) '%(cmap[c].capitalize(),n)
+			except : topinstr += '%s (%d) '%(c,n)
+		topout = sorted(locs['out'].iteritems(), key=operator.itemgetter(1), reverse=True)[:3]
+		topoutstr = ''
+		for c,n in topout : 
+			try : topoutstr += '%s (%d) '%(cmap[c].capitalize(),n)
+			except : topoutstr += '%s (%d) '%(c,n)
+		params = (lmap[l].capitalize(),inavg,incnt,outavg,outcnt,topinstr,topoutstr)
+		try : 
+			if inavg > outavg : 
+				if sig : print '%s & \\textbf{%.03f} (%d) * & %.03f (%d) & %s & %s \\\\'%params
+				else : print '%s & \\textbf{%.03f} (%d) & %.03f (%d) & %s & %s \\\\'%params
+			else: 
+				if sig : print '%s & %.03f (%d) & \\textbf{%.03f} (%d) * & %s & %s\\\\'%params
+				else : print '%s & %.03f (%d) & \\textbf{%.03f} (%d) & %s & %s\\\\'%params
+		except : 
[…]

### 2013-11-15 code/src/20130905/paper-rewrite/figures/code/time_of_day.py

@@ -1,0 +1,78 @@
+#!/bin/python
+
+import csv
+import datetime
+import operator
+import numpy as np
+import matplotlib.pyplot as plt
+
+OUTPUT_DIR = 'results/data'
+RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11'
+
+def turker_counts():
+	counts = {}
+	for line in csv.DictReader(open('results/data/quality.langs.txt'), delimiter='\t'):
+		counts[line['lang']] = int(line['num_turkers'])
+	return counts
+
+def time_map():
+	print "Reading data"
+	tdict = dict()
+	for line in open('%s/byassign.times'%OUTPUT_DIR).readlines():
+		aid, start, end = line.split('\t')
+		start_t = datetime.datetime.strptime(start.strip(), "%Y-%m-%d %H:%M:%S")
+		end_t = datetime.datetime.strptime(end.strip(), "%Y-%m-%d %H:%M:%S")
+		tdict[aid] = (start_t, end_t)
+	return tdict
+
+def write_all_times():
+        out = open('%s/byassign.times'%OUTPUT_DIR, 'w')
+        for line in csv.DictReader(open('%s/assignments'%RAW_DIR)):
+                aid = line['id']
+                start = line['accept_time']
+                end = line['submit_time']
+                out.write('%s\t%s\t%s\n'%(aid,start,end,))
+        out.close()
+
+def graph(langtimes):
+	langnum = 0
+	y = []
+	x = []
+	size = []
+	yax = []
+	langcounts = []
+	tcounts = turker_counts()
+	for lang in tcounts :
+		langcounts.append((lang,sum([langtimes[lang][h] for h in langtimes[lang]])))
+	langs = [t[0] for t in sorted(langcounts, key=operator.itemgetter(1), reverse=True) if tcounts[t[0]] >= 100]
+	print [t for t in sorted(langcounts, key=operator.itemgetter(1), reverse=True) if tcounts[t[0]] >= 100]
+	for lang in langs: 
+		langnum += 1
+		yax.append(lang)
+		for h in langtimes[lang] : 
+			y.append(langnum)
+			x.append(h)
+			size.append(langtimes[lang][h])
+	plt.scatter(x,y, s=size)
+	plt.yticks(range(1,langnum+1,1),tuple(yax),rotation=90)
[…]

### 2013-11-15 code/src/20130905/paper-rewrite/figures/code/turker_numhit_dist.py

@@ -1,0 +1,57 @@
+#!/bin/python
+
+import csv
+import operator
+import numpy as np
+import matplotlib.pyplot as plt
+
+data = []
+
+for line in csv.DictReader(open('results/data/quality.turkers.txt'), delimiter='\t') : 
+	if line['approved'] == 'True': data.append((line['lang'], line['worker'], int(line['num_hits'])))
+
+
+langs = [d[0] for d in sorted(data, key = operator.itemgetter(2), reverse=True)]
+data = [d[2] for d in sorted(data, key = operator.itemgetter(2), reverse=True)]
+lang_counts = {} 
+
+bins=5
+all_data = []
+
+for lang in set(langs) :
+	ldata = [d for d,l in zip(data, langs) if (l == lang)]
+	if len(ldata) < 50 : continue
+	lang_counts[lang] = len(ldata)
+	#count, edges = np.histogram(ldata, bins)
+	count = []
+	for i in range(bins-1) : count.append(sum(ldata[10*i:10*(i+1)]))
+	count.append(sum(ldata[40:]))
+	tot = sum(count)
+	pcnthits = [float(c) / tot for c in count]
+	all_data.append(tuple([lang]+pcnthits))
+
+all_data = sorted(all_data, key=operator.itemgetter(1))
+
+last = [] 
+
+key = []
+
+#colors = ['w','#E8E8F5', '#CECFF6', '#BBBDF9', '#A4A7FA', '#8A8DFA', '#7176FA', '#5157FA', '#343BFB', '#1A22FA']
+colors = ['#E8E8F5', '#BBBDF9', '#8A8DFA', '#5157FA', '#1A22FA']
+w = 0.8
+for i in range(bins) : 
+	pcnt = [e[i+1] for e in all_data]
+	if i == 0 : 
+		key.append(plt.bar(np.arange(len(all_data)), pcnt, color=colors[len(colors)-(i+1)], width=w))
+		last = pcnt
+	else : 
+		key.append(plt.bar(np.arange(len(all_data)), pcnt, bottom=last, color=colors[len(colors)-(i+1)], width=w))
+		last = [last[i] + p for i,p in enumerate(pcnt)]
+
+plt.ylim(0,1)
+plt.ylabel('Proportion of HITs contributed', rotation=90)
+plt.yticks(rotation=90)
[…]

### 2013-11-15 code/src/20130905/paper-rewrite/regenerate.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+#cat data/pass-1 | python scripts/googtrans-over-assigns.py > results/data/googmatch.assigns.txt
+#python scripts/googtrans-over-turkers.py > results/data/googmatch.turkers.txt
+#python scripts/googtrans-over-langs.py > results/data/googmatch.langs.txt
+
+#python scripts/quality-over-assigns-syns.py > results/data/quality.assigns.txt 
+python scripts/quality-over-turkers-syns.py > results/data/quality.turkers.txt 
+python scripts/quality-over-langs-syns.py > results/data/quality.langs.txt 
+

### 2013-11-15 code/src/20130905/paper-rewrite/scripts/get_region_data.py

@@ -1,0 +1,56 @@
+#!/bin/python
+
+import csv
+
+RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11'
+CLPAIRS = 'ref/cl-pairs.csv'
+
+def lang_map():
+        lang_data = {}
+        num_data = {}
+        for line in csv.DictReader(open('%s/languages'%RAW_DIR)):
+                lang = line['name'].lower()
+                lid = line['id']
+                if(lang not in lang_data):
+                        lang_data[lang] = line['prefix']
+                if(lid not in num_data):
+                        num_data[lid] = line['prefix']
+        return num_data, lang_data
+
+def code_map():
+	ret = dict()
+	for l in open('ref/countrycodemap').readlines():
+		ll = l.split('\t')
+		ret[ll[0]] = ll[1].strip()
+	return ret
+
+def get_valid_pairs():
+        codes, words = lang_map()
+        cmap = code_map()
+        valid_pairs = dict()
+        for line in csv.DictReader(open(CLPAIRS)):
+                lang = words[line['Input.language'].lower()]
+                if not lang in valid_pairs:
+                        valid_pairs[lang] = dict()
+                main = cmap[line['Answer.primary_country'].lower()]
+                if not main in valid_pairs[lang]:
+                        valid_pairs[lang][main] = 0
+                valid_pairs[lang][main] += 1
+                for ctry in [cmap[c.lower()] for c in line['Answer.countries'].split('|') if not c=='']:
+                        if not ctry in valid_pairs[lang]:
+                                valid_pairs[lang][ctry] = 0
+                        valid_pairs[lang][ctry] += 1
+        ret = dict()
+        for p in valid_pairs:
+                ret[p] = list()
+                for pp in valid_pairs[p]:
+                        if valid_pairs[p][pp] >= 2:
+                                ret[p].append(pp)
+        return ret
+
+pairs = get_valid_pairs() 
+
+for lang in pairs: 
+	
+	print lang+'\t'+','.join(pairs[lang])	
+

### 2013-11-15 code/src/20130905/paper-rewrite/scripts/googtrans-over-assigns.py

@@ -1,0 +1,63 @@
+#!/bin/python
+# -*- coding: utf-8 -*- 
+
+# hit-id | lang | word | control_translation | google_transalation | worker_1_id | worker_1_response | worker_2_id | worker_2_response | ...
+
+import sys
+import operator
+
+byassign = {}
+
+idmap = {line.strip().split()[1] : line.strip().split()[0] for line in open('ref/approved-ids').readlines() + open('ref/rejected-ids').readlines()}
+
+approved = set([idmap[line.strip().split()[1]] for line in open('ref/approved-ids').readlines()])
+rejected = set([idmap[line.strip().split()[1]] for line in open('ref/rejected-ids').readlines()])
+
+worker_map = {}
+
+for line in sys.stdin:
+	hitid, lang, word, control, goog, responses = line.split('\t', 5)
+	for response in responses.split('\t'):
+		
+		t = response.strip().split(':')
+		if len(t) > 1 : 
+			worker = t[0]
+			translation = t[1]
+		else:
+			worker = t[0]
+			translation = ''
+		
+		taid = '%s-%s'%(hitid, worker)
+		aid = idmap[taid]
+
+		worker_map[aid] = worker
+
+		if lang not in byassign: byassign[lang] = {}
+
+		if aid not in byassign[lang] : byassign[lang][aid] = {'overlap_c' : 0, 'overlap_nc' : 0, 'total_c' : 0, 'total_nc' : 0}
+		
+		if goog.lower() == translation.lower() : 
+			if control == 'NA' : byassign[lang][aid]['overlap_nc'] += 1	
+			else : byassign[lang][aid]['overlap_c'] += 1	
+		if control == 'NA' : byassign[lang][aid]['total_nc'] += 1	
+		else : byassign[lang][aid]['total_c'] += 1	
+		
+
+print 'lang\tassign\tworker\tmatch-overall\tmatch-c\tmatch-nc\tnum-match-overall\tnum-match-c\tnum-match-nc\ttotal\tstatus'
+for lang in byassign:
+	for aid in byassign[lang]:
+		if aid in approved : status = 'approved'
+		elif aid in rejected : status = 'rejected'
+		num_c = float(byassign[lang][aid]['overlap_c'])
+		num_nc = float(byassign[lang][aid]['overlap_nc'])
+		total_c = float(byassign[lang][aid]['total_c'])
[…]

### 2013-11-15 code/src/20130905/paper-rewrite/scripts/googtrans-over-langs.py

@@ -1,0 +1,29 @@
+#!/bin/python
+
+#lang	assign	worker	match-overall	match-c	match-nc	num-match-overall	num-match-c	num-match-nc	total	status
+#gu	267659	1416	0.400	0.000	0.500	4.000	0.000	4.000	10.000	approved
+import sys
+import csv
+
+bylang = {}
+
+lang_counts = {'1' : [l.strip() for l in open('ref/single-lang').readlines()],
+	'0' : [l.strip() for l in open('ref/no-lang').readlines()],
+	'many' : [l.strip() for l in open('ref/mult-lang').readlines()]}
+
+for line in csv.DictReader(open('results/data/googmatch.assigns.txt'), delimiter='\t'):
+	lang = line['lang']; worker = line['worker'];
+	match_overall = line['match-overall']; match_c = line['match-c']; match_nc = line['match-nc']
+	if lang not in bylang: bylang[lang] = {'match' : 0, 'match-c' : 0 , 'match-nc' : 0, 'total' : 0}
+	bylang[lang]['match'] += float(match_overall)
+	bylang[lang]['match-c'] += float(match_c)
+	bylang[lang]['match-nc'] += float(match_nc)
+	bylang[lang]['total'] += 1
+
+print 'lang\tnum_hits\tmatch\tmatch-c\tmatch-nc'
+for lang in bylang:
+	quality = float(bylang[lang]['match'])/bylang[lang]['total']
+	quality_c = float(bylang[lang]['match-c'])/bylang[lang]['total']
+	quality_nc = float(bylang[lang]['match-nc'])/bylang[lang]['total']
+	print '%s\t%d\t%.03f\t%.03f\t%.03f'%(lang,bylang[lang]['total'],quality,quality_c,quality_nc)
+	

### 2013-11-15 code/src/20130905/paper-rewrite/scripts/googtrans-over-turkers.py

@@ -1,0 +1,33 @@
+#!/bin/python
+
+#lang	assign	worker	match-overall	match-c	match-nc	num-match-overall	num-match-c	num-match-nc	total	status
+#gu	267659	1416	0.400	0.000	0.500	4.000	0.000	4.000	10.000	approved
+import sys
+import csv
+
+byworker = {}
+lang_counts = {'1' : [l.strip() for l in open('ref/single-lang').readlines()],
+	'0' : [l.strip() for l in open('ref/no-lang').readlines()],
+	'many' : [l.strip() for l in open('ref/mult-lang').readlines()]}
+
+for line in csv.DictReader(open('results/data/googmatch.assigns.txt'), delimiter='\t'):
+	lang = line['lang']; worker = line['worker'];
+	match_overall = line['match-overall']; match_c = line['match-c']; match_nc = line['match-nc']
+	if lang not in byworker: byworker[lang] = {}
+	if worker not in byworker[lang] : byworker[lang][worker] = {'match' : 0, 'match-c' : 0 , 'match-nc' : 0, 'total' : 0}
+	byworker[lang][worker]['match'] += float(match_overall)
+	byworker[lang][worker]['match-c'] += float(match_c)
+	byworker[lang][worker]['match-nc'] += float(match_nc)
+	byworker[lang][worker]['total'] += 1
+
+print 'lang\tworker\tnum_hits\tmatch\tmatch-c\tmatch-nc\tnum_langs'
+for lang in byworker:
+	for worker in byworker[lang]:
+		quality = float(byworker[lang][worker]['match'])/byworker[lang][worker]['total']
+		quality_c = float(byworker[lang][worker]['match-c'])/byworker[lang][worker]['total']
+		quality_nc = float(byworker[lang][worker]['match-nc'])/byworker[lang][worker]['total']
+		if worker in lang_counts['0'] :  num_langs = '0'
+		elif worker in lang_counts['1'] :  num_langs = '1'
+		elif worker in lang_counts['many'] :  num_langs = 'many'
+		print '%s\t%s\t%d\t%.03f\t%.03f\t%.03f\t%s'%(lang,worker,byworker[lang][worker]['total'],quality,quality_c,quality_nc,num_langs)
+	

### 2013-11-15 code/src/20130905/paper-rewrite/scripts/quality-over-assigns-syns.py

@@ -1,0 +1,102 @@
+#!/bin/python
+# -*- coding: utf-8 -*- 
+
+# hit-id | lang | word | control_translation | google_transalation | worker_1_id | worker_1_response | worker_2_id | worker_2_response | ...
+# hit-id | word | synonym | control_judgement | worker_1_id | worker_1_judgement | ...
+
+import sys
+import csv
+import operator
+from settings import settings
+
+byassign = {}
+
+ids = open('ref/approved-ids').readlines()+open('ref/rejected-ids').readlines()
+
+idmap = {line.strip().split()[1]: line.strip().split()[0] for line in ids}
+approved = set([idmap[line.strip().split()[1]] for line in open('ref/approved-ids').readlines()])
+rejected = set([idmap[line.strip().split()[1]] for line in open('ref/rejected-ids').readlines()])
+
+gmatch = csv.DictReader(open('results/data/googmatch.turkers.txt'), delimiter='\t')
+worker_gmatch = {line['worker']: float(line['match']) for line in gmatch}
+
+worker_map = {}
+synonyms = {}
+
+CUTOFF = settings['synonym_control_cutoff']
+
+#first pass to determine which synonym graders to trust
+worker_scores = {}
+for line in open('data/pass-2').readlines():
+	hitid, word, synonym, control_judgement, judgements = line.strip().split('\t',4)
+	if control_judgement == 'NA' : continue
+	for j in judgements.split('\t'):
+		worker, judgement = j.split(':')
+		if worker not in worker_scores: worker_scores[worker] = {'correct' : 0.0, 'total' : 0.0}
+		if judgement == control_judgement : worker_scores[worker]['correct'] += 1	
+		worker_scores[worker]['total'] += 1	
+
+approved_workers = [worker for worker in worker_scores if (worker_scores[worker]['correct']/worker_scores[worker]['total']) > CUTOFF]
+
+for line in open('data/pass-2').readlines():
+	hitid, word, synonym, control_judgement, judgements = line.strip().split('\t',4)
+	if word.lower() not in synonyms : synonyms[word.lower()] = set()
+	for j in judgements.split('\t'):
+		worker, judgement = j.split(':')
+		if worker in approved_workers:
+			if judgement == 'yes' : synonyms[word.lower()].add(synonym.lower())
+
+for line in open('data/pass-1').readlines():
[…]

### 2013-11-15 code/src/20130905/paper-rewrite/scripts/quality-over-langs-syns.py

@@ -1,0 +1,61 @@
+#!/bin/python
+
+#lang	assign	worker	overall	overall-ng	num-correct	num-total	num-correct-ng	num-total-ng	status
+#gu	267659	1416	0.500	0.500	1.000	2.000	1.000	2.000	approved
+
+#lang	worker	num_hits	quality	quality_ng	quality_syn	quality_syn_ng	num_langs	goog	approved
+
+import sys
+import csv
+from settings import settings
+
+bylang = {}
+
+lang_counts = {
+	'1' : [l.strip() for l in open('ref/single-lang').readlines()],
+	'0' : [l.strip() for l in open('ref/no-lang').readlines()],
+	'many' : [l.strip() for l in open('ref/mult-lang').readlines()]
+}
+
+turkers = {row['worker'] : row for row in csv.DictReader(open('results/data/googmatch.turkers.txt'), delimiter='\t')}
+
+allow = []	
+for lang_count in settings['use_workers_with_langcounts'] : 
+	allow += lang_counts[lang_count]
+
+if settings['avg_lang_over'] == 'assigns' : 
+	data_file = 'results/data/quality.assigns.txt'
+	label_overall = 'overall'
+	label_overall_syn = 'overall-syn'
+	
+elif settings['avg_lang_over'] == 'turkers' : 
+	data_file = 'results/data/quality.turkers.txt'
+	label_overall = 'quality'
+	label_overall_syn = 'quality_syn'
+
+for line in csv.DictReader(open(data_file), delimiter='\t'):
+
+	lang = line['lang']; worker = line['worker']
+	
+	if worker not in allow : continue
+	
+	overall = line[label_overall]
+	overall_syn = line[label_overall_syn]
+
+	if lang not in bylang: bylang[lang] = {'correct' : 0, 'correct-syn' : 0, 'total' : 0, 'turkers' : set() }
+
+	bylang[lang]['correct'] += float(overall)
+	bylang[lang]['correct-syn'] += float(overall_syn)
+
+	bylang[lang]['total'] += 1
+	bylang[lang]['turkers'].add(worker)
+
+print 'lang\tnum_hits\tnum_turkers\tquality\tquality_syn'
+for lang in bylang:
+	quality = float(bylang[lang]['correct'])/bylang[lang]['total']
+	quality_syn = float(bylang[lang]['correct-syn'])/bylang[lang]['total']
[…]

### 2013-11-15 code/src/20130905/paper-rewrite/scripts/quality-over-turkers-syns.py

@@ -1,0 +1,45 @@
+#!/bin/python
+
+#lang	assign	worker	overall	overall-ng	num-correct	num-total	num-correct-ng	num-total-ng	status
+#gu	267659	1416	0.500	0.500	1.000	2.000	1.000	2.000	approved
+
+import sys
+import csv
+from settings import settings
+
+byworker = {}
+lang_counts = {'1' : [l.strip() for l in open('ref/single-lang').readlines()],
+	'0' : [l.strip() for l in open('ref/no-lang').readlines()],
+	'many' : [l.strip() for l in open('ref/mult-lang').readlines()]}
+
+turkers = {row['worker'] : row for row in csv.DictReader(open('results/data/googmatch.turkers.txt'), delimiter='\t')}
+
+for line in csv.DictReader(open('results/data/quality.assigns.txt'), delimiter='\t'):
+	lang = line['lang']
+	worker = line['worker'];
+	overall = line['overall']
+	overall_syn = line['overall-syn']
+
+	if lang not in byworker: byworker[lang] = {}
+	if worker not in byworker[lang] : byworker[lang][worker] = {'correct' : 0 , 'correct-syn' : 0, 'total' : 0, }
+
+	byworker[lang][worker]['correct'] += float(overall)
+	byworker[lang][worker]['correct-syn'] += float(overall_syn)
+	byworker[lang][worker]['total'] += 1
+
+print 'lang\tworker\tnum_hits\tquality\tquality_syn\tnum_langs\tgoog'
+for lang in byworker:
+	for worker in byworker[lang]:
+		quality = float(byworker[lang][worker]['correct'])/byworker[lang][worker]['total']
+		quality_syn = float(byworker[lang][worker]['correct-syn'])/byworker[lang][worker]['total']
+
+		if worker in lang_counts['0'] :  num_langs = '0'
+		elif worker in lang_counts['1'] :  num_langs = '1'
+		elif worker in lang_counts['many'] :  num_langs = 'many'
+
+		num_hits = byworker[lang][worker]['total']
+		goog = float(turkers[worker]['match'])
+
+		params = (lang,worker,num_hits,quality,quality_syn,num_langs,goog)
+
+		print '%s\t%s\t%d\t%.03f\t%.03f\t%s\t%s'%params

### 2013-11-15 code/src/20130905/paper-rewrite/scripts/settings.py

@@ -1,0 +1,16 @@
+
+settings = {
+
+	'google_overlap_cutoff' : 0.60,
+	'synonym_control_cutoff' : 0.70,
+	'use_workers_with_langcounts' : ['0', '1', 'many'],
+	'avg_lang_over' : 'turkers', 
+
+	'figures' : {
+	
+		'apply_google_filter' : False,
+		'exclude_google_from_quality' : False
+	
+	}
+	
+}

### 2013-11-15 writeup/reviewer-response/paper.tex
rewrite

@@
 \usepackage{subcaption}
-\DeclareMathOperator*{\argmax}{arg\,max}
+
 \setlength\titlebox{5cm}    % Expanding the titlebox
@@
 \begin{subfigure}[b]{1\linewidth}
-\includegraphics[width=\textwidth]{figures/fig2with.png}
+\includegraphics[width=\textwidth]{figures/fig2all_errorbars.png}
 \caption{All turkers.}                
@@
 \begin{subfigure}[b]{1\linewidth}
-\includegraphics[width=\textwidth]{figures/fig2without.png}
+\includegraphics[width=\textwidth]{figures/fig2filter_errorbars.png}
 \caption{Turkers with \textless 60\% overlap with Google Translate.}
@@
 
+\begin{figure}
+\includegraphics[width=1\linewidth]{figures/turker_hit_contributions.png}
+\caption{Contributions of individual turkers to the overall number of HITs in each language.
+The dark blue bar represents the proportion of total HITs which were completed by the 10 highest-contributing turkers.
+The next darkest bar represents the next 10 highest-contributing turkers, and likewise for the thrid and forth darkest.
+The final bar represents the remaining turkers which were not one of the top 40 contributors.}
+\label{numhits}
+\end{figure}
+
 \section{Extrinsic evalutation of mturk data for SMT}
@@
 Previous work by Matt Post in the 2010 WMT has demonstrated not only that turkers are able to provide high quality translations of complete sentences, but also that these translations, when added into an SMT pipeline, measurably improve translation quality.
-\textbf{MORE HERE.}
+
+\begin{table}[t]
+\centering
+\begin{tabular}{l|rr}
+  language  & SAMT &  Google \\
+  \hline\hline
+  Bengali    & 13.53  &  20.01 \\
+  Hindi      & 17.29  & 25.21 \\  
+  Malayalam    & 14.28  & - \\      
+  Tamil      &  9.85  &  13.51 \\  
+  Telugu     & 12.61  & 16.03  \\  
+  Urdu        & 20.99  & 23.09 \\   
+\end{tabular}
+\caption{BLEU scores translating into English (four references).  BLEU
+scores are the mean of three MERT runs.}
+\label{table:bleu}
+\end{table}
+
+\begin{figure*}[t]
+  \centering
+  \includegraphics[width=\textwidth]{figures/tamil.png}
+  \begin{tabular}{l}
+    \hline
+    In March 15,2007 Wiki got a place in Oxford English dictionary. \\
+    On March 15, 2007 wiki was included in the Oxford English
+    dictionary. (5) \\
+    ON MARCH 15, 2007, WIKI FOUND A PLACE IN THE OXFORD ENGLISH
+    DICTIONARY \\
+    March 15, 2007 oxford english index of wiki's place. \\ \\
+
+  \end{tabular}
+  \caption{An example of the variance in translation quality for the
+    human translations of a Tamil sentence; the formatting of the
+    translations has been preserved exactly.  The parenthesized number
+    indicates the number of votes received in the voting task
+    (\S\ref{section:votes}).}
+  \label{figure:variance}
+\end{figure*}
 
@@
 
-\section{Novelty}
-
-Its novel. Trust us.
-
 \end{document}

### 2013-11-15 writeup/version1/paper.tex
rewrite

--- 2013-03-31 writeup/paper.tex
@@
 \usepackage{float}
-\usepackage{subfigure}
+\usepackage{subfloat}
+\usepackage{subcaption}
+
 \DeclareMathOperator*{\argmax}{arg\,max}
@@
 \centering
-\includegraphics[width=\linewidth]{final-figures/turkermap}
+\includegraphics[width=\linewidth]{../version1-figures/map.png}
 \caption{The number of workers per country.
@@
 \hline
-English&592&	French&63&	Vietnamese&34\\
-Tamil&253&	Polish&61&	Macedonian&31\\
-Malayalam&219&	Urdu&56&	Cebuano&29\\
-Hindi&149&	Tagalog&54&	Swedish&26\\
-Spanish&131&	Marathi&48&	Bulgarian&25\\
-Telugu&87&	Russian&44&	Hungarian&23\\
-Chinese&86&	Italian&43&	Swahili&23\\
-Romanian&85&	Bengali&41&	Thai&22\\
-Portuguese&82&	Gujarati&39&	Catalan&22\\
-Arabic&74&	Hebrew&38&	Lithuanian&21\\
-Kannada&72&	Dutch&37&	Punjabi&21\\
-German&66&	Turkish&35&	Others &$\leq$20\\
+English & 689 & Tamil & 253 & Malayalam & 219 \\
+Hindi & 149 & Spanish & 131 & Telugu & 87 \\
+Chinese & 86 & Romanian & 85 & Portuguese & 82 \\
+Arabic & 74 & Kannada & 72 & German & 66 \\
+French & 63 & Polish & 61 & Urdu & 56 \\
+Tagalog & 54 & Marathi & 48 & Russian & 44 \\
+Italian & 43 & Bengali & 41 & Gujarati & 39 \\
+Hebrew & 38 & Dutch & 37 & Turkish & 35 \\
+Vietnamese & 34 & Macedonian & 31 & Cebuano & 29 \\
+Swedish & 26 & Bulgarian & 25 & Swahili & 23 \\
+Hungarian & 23 & Catalan & 22 & Thai & 22 \\
+Lithuanian & 21 & Punjabi & 21 & Others & $\leq$ 20 \\
 \hline\hline
@@
 \begin{center}
-\includegraphics[width=0.8\linewidth]{final-figures/quality-bar}
+\includegraphics[width=\linewidth]{../version1-figures/quality_bar.png}
 \caption{Translation quality for languages with at least 50 Turkers.
@@
 \begin{figure}[h]
-\includegraphics[height=\linewidth,angle=270]{final-figures/completetime}
+\includegraphics[height=\linewidth,angle=270]{../final-figures/completetime}
 \caption{Days to complete the translation HITs for 40 of the languages. Tick marks represent the completion of individual assignments. }
@@
 \hline\hline
-Hindi&\textbf{0.35} (299)&0.34 (7)&India (285) UAE (5) UK (5) &Saudi Arabia (2) Russia (1) Oman (1) \\
-Tamil&\textbf{0.37} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
-Malayalam&0.48 (235) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudi Arabia (1) Maldives (1) \\
-Spanish&\textbf{0.72} (205)&0.61 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) New Zealand (1) \\
-French&0.65 (183) &\textbf{0.86} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
-German&\textbf{0.83} (99)&0.65 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
-Italian&\textbf{0.78} (98)&0.71 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
-Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hong Kong (6) Australia (3) Germany (2) \\
-Malay&0.76 (15) &\textbf{0.83} (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
-Irish&\textbf{0.68} (58)&0.64 (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
-Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czech Republic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
-Turkish&0.72 (83) &\textbf{0.73} (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
-Amharic&\textbf{0.18} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
-Swedish&\textbf{0.66} (58)&0.61 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
-Portuguese&\textbf{0.77} (107)&0.74 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
-Arabic&0.22 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
-Kannada&\textbf{0.24} (106)&0.00 (1)&India (106) US (1) &France (1) Germany (1) \\
-Russian&\textbf{0.09} (72)&0.06 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
-Afrikaans&\textbf{0.74} (4)&0.73 (98)&South Africa (4) &India (93) Netherlands (2) UAE (1) \\
-Sindhi&\textbf{0.15} (93)&0.02 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
+Hindi & 0.636 (291) & \textbf{0.715} (6) & India (279) Uae (5) Uk (3)  & Russia (1) Oman (1) Denmark (1) \\
+Tamil & \textbf{0.652} (267) * & 0.250 (2) & India (260) Unitedstates (3) Canada (2)  & Tunisia (1) Egypt (1)  \\
+Malayalam & 0.763 (233) & \textbf{0.827} (2) & India (222) Uae (6) Unitedstates (3)  & Saudiarabia (1) Maldives (1) \\
+Spanish & \textbf{0.794} (152) & 0.788 (12) & Unitedstates (98) Mexico (16) Spain (12)  & India (10) Newzealand (1) Macedonia (1)  \\
+French & 0.744 (146) & \textbf{0.816} (11) & India (50) Unitedstates (37) France (22)  & Greece (2) Netherlands (1) Japan (1) \\
+Chinese & \textbf{0.597} (115) & 0.597 (19) & Unitedstates (74) Singapore (13) China (9)  & Hongkong (6) Australia (3) Germany (2)  \\
+German & \textbf{0.818} (81) & 0.769 (37) & Germany (45) Unitedstates (22) Austria (6)  & India (31) Netherlands (1) Greece (1)  \\
+Amharic & \textbf{0.136} (16) * & 0.009 (99) & Unitedstates (14) Ethiopia (2)  & India (70) Georgia (9) Macedonia (5)  \\
+Kannada & 0.704 (105) & NA (0) & India (105)  & \\
+Sindhi & \textbf{0.190} (96) & 0.062 (9) & India (58) Pakistan (37) Unitedstates (1)  & Macedonia (4) Georgia (2) Indonesia (2)  \\
+Italian & \textbf{0.857} (72) & 0.775 (32) & Italy (37) Unitedstates (19) Romania (6)  & India (25) Ireland (2) Spain (2)  \\
+Arabic & \textbf{0.732} (58) * & 0.607 (44) & Egypt (19) Jordan (16) Morocco (8)  & Unitedstates (19) India (11) Canada (3)  \\
+Telugu & \textbf{0.796} (100) & 0.500 (1) & India (96) Unitedstates (3) Uae (1)  & Saudiarabia (1)  \\
+Turkish & 0.749 (69) & \textbf{0.779} (23) & Turkey (37) Unitedstates (16) Macedonia (5)  & India (16) Pakistan (4) Tunisia (1) \\
+Breton & 0.167 (3) & \textbf{0.178} (89) & Unitedstates (3)  & India (83) Macedonia (2) China (1) \\
+Russian & \textbf{0.148} (64) & 0.120 (24) & Unitedstates (33) Moldova (7) Russia (6)  & India (12) Macedonia (4) Uk (3)  \\
+Pashto & \textbf{0.495} (20) * & 0.051 (68) & Pakistan (20)  & India (59) Georgia (2) Macedonia (2)  \\
+Irish & \textbf{0.740} (51) & 0.717 (36) & Unitedstates (36) Ireland (13) Uk (2)  & India (28) Romania (3) Pakistan (2)  \\
+Tagalog & \textbf{0.849} (76) & 0.825 (9) & Philippines (60) Unitedstates (14) Canada (1)  & Taiwan (2) India (2) Bangladesh (1)  \\
+Marathi & 0.654 (82) & \textbf{0.833} (3) & India (80) Mauritius (1) Unitedstates (1)  & Uae (1) Oman (1) Ukraine (1) \\
+
 \hline\hline
@@
 \begin{center}
-\includegraphics[width=1\linewidth]{final-figures/google-match}
-\caption{Average proportion of Turker translations matching GoogleTranslate, per assignment. Overall average overlap was 0.42}
+\includegraphics[width=1\linewidth]{../version1-figures/google_bar.png}
+\caption{Average proportion of Turker translations matching GoogleTranslate, per assignment. Overall average overlap was 0.37.}
 \label{googlematch} 
@@
 %%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
-\begin{figure*}[h]
-\begin{center}
-\includegraphics[width=0.8\linewidth]{final-figures/quality-scatter_joined}
-\end{center}
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=0.78\linewidth]{../final-figures/quality-scatter_joined-1column}
+%\end{center}
 
-\caption{Estimated quality of translations by country.
-Each circle is a country, sized proportional to the number of active Turkers from that country.
-Quality is calculated as the average number of control words which were correct translations of the source word, where ”correct” means that the provided translation was judged to be synonymous with the known translation by workers in a second-pass HIT.
-Figure represents data from approx.
-295,000 assignments for which geolocation was known.}
-\label{quality-scatter}
-\end{figure*}
+%\caption{Estimated quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country. }
+%\label{quality-scatter}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Figure \ref{quality-scatter} shows the number of assignments completed per country and per-country quality estimates for 4 scenerios: (a) overall, (b) for assignments completed in region, (c) for assignments completed out of region, and (d) for out of region assignments which contained low overlap with GoogleTranslate.
+%Figure \ref{quality-scatter} shows the number of assignments completed per country and per-country quality estimates for 4 scenerios: (a) overall, (b) for assignments completed in region, (c) for assignments completed out of region, and (d) for out of region assignments which contained low overlap with GoogleTranslate.
 
 \paragraph{Use of machine translation}
+
+\begin{figure}
+\centering
+\begin{subfigure}[b]{1\linewidth}
+\includegraphics[width=\textwidth]{../version1-figures/turker-googmatch-distribution.png}
+\caption{Individual turker overlap with google translate.
+We believe the inflection point at ~60\% overlap with Google suggests a reasonable cutoff by which to filter workers.
+Workers with \textgreater 60\% overlap can be reasonably considered to be cheating and can be removed.}
+\label{dist}
+\end{subfigure}
+\begin{subfigure}[b]{1\linewidth}
+\includegraphics[width=\textwidth]{../version1-figures/google-cdf-googlangs.png}
+\caption{Cumulative distribution of overlap with Google translate for workers and translations.
+We see that eliminating all workers with \textgreater 60\% overlap with google translate still preserves \textgreater 80\% of workers and \textgreater 70\% of translations.}
+\label{cdf}
+\end{subfigure}
+\caption{}\label{cheaters}
+\end{figure}
 
@@
 Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphabet) have lower overlap with Google,  suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.
-% suggesting that it is easier for Turkers to use MT for Latin alphabet languages.
-
-%We translated: af ar az bg ca cs cy da de el eo es eu fa fi fr gl gu he hr hu hy id is it ja kn ko lt lv ms nl pl pt ro ru sk sl sq sr sv sw ta te th tr uk ur vi zh
-
-% Google supports:
-%Afrikaans
-%Albanian
-%Arabic
-%Belarusian
-%Bulgarian
-%Catalan
-%Chinese
-%Chinese
-%Croatian
-%Czech
-%Danish
-%Dutch
-%English
-%Estonian
-%Esperanto
-%Filipino
-%Finnish
-%French
-%Galician
-%German
-%Greek
-%Hebrew
-%Hindi
-%Hungarian
-%Icelandic
-%Indonesian
-%Irish
-%Italian
-%Japanese
-%Korean
-%Latvian
-%Lithuanian
-%Macedonian
-%Malay
-%Maltese
-%Norwegian
-%Persian
-%Polish
-%Portuguese
-%Romanian
-%Russian
-%Serbian
-%Slovak
-%Slovenian
-%Spanish
-%Swahili
-%Swedish
-%Thai
-%Turkish
-%Ukrainian
-%Vietnamese
-%Welsh
-%Yiddish
-%Armenian
-%Azerbaijani
-%Basque
-%Georgian
-%Gujarati
-%Haitian Creole
-%Kannada
-%Latin
-%Lao
-%Tamil
-%Telugu
-%Urdu
 
@@
 Given the strong positive correlation, we are satisfied that the trends reported in this paper hold when using either our gold standard translations or external bilingual dictionaries.
+
+\section{Application to SMT}
+With the dictionaries in hand, we moved on to translate the entire
+Wikipedia documents.  Each human intelligence task (HIT) posted on
+MTurk contained ten sequential source-language sentences from a
+document, and asked the worker to enter a free-form translation for
+each.  We collected four translations from different translators for
+each source sentence.  To discourage cheating through
+cutting-and-pasting into automatic translation systems, sentences were
+presented as images.  Workers were paid \$0.70 per HIT.  We then
+manually determined whether to accept or reject a worker's HITs based
+on a review of each worker's submissions, which included a comparison
+of the translations to a monotonic gloss (produced with the
+dictionary), the percentage of empty translations, the amount of time
+the worker took to complete the HIT, geographic
+location (self-reported and geolocated by way of the worker's
+IP address), and by comparing different translations of the same
+source segments against one another.
+
+We obtained translations of the
+source-language documents in a relatively short amount of time. Malayalam provided the highest throughput,
+generating half a million words in just under a week.  For comparison,
+the Europarl corpus \cite{koehn2005europarl} has about 50 million
+words of English for each of the Spanish and French parallel corpora.
+
+The tradeoff for low-cost translations is increased variance in
+translation quality when compared to the more consistently-good
+professional translations.  Figure~\ref{figure:variance} contains some
+hand-picked examples of the sorts of translations we obtained.  Later,
+in the Experiments section (\S\ref{section:experiments}), we will
+investigate the effects this variance in translation quality has on
+the quality of the models that can be constructed.  For now, the
+variance motivated the collection of an additional dataset, described
+in the next section.
+
+A prevailing issue with translations collected on MTurk is the
+prevalence of low-quality translations.  Quality suffers for a variety
+of reasons: Turkers lack formal training, often translate into a
+nonnative tongue, may give insufficient attention to the task, and
+likely desire to maximize their throughput (and thus their wage).
+Unlike \newcite{zaidan2011crowdsourcing}, who embed controls
+containing source language sentences with known professional
+translations, we had no professionally translated data.  Therefore, we
+could not measure the BLEU score of the Turkers.
+
+Motivated by desire to have some measure of the relative quality and variance of the translations,
+we designed another task in which we presented an independent set of Turkers with an original
+sentence and its four translations, and asked them to vote on which was best.\footnote{We did not
+  collect votes for Malayalam.}  Five independent workers voted on the translations of each source
+sentence.  Tallying the resulting votes, we found that roughly 65\% of the sentences had five votes
+cast on just one or two of the translations, and about 95\% of the sentences had all the votes cast
+on one, two, or three sentences.  This suggests both (1) that there was a difference in the quality
+of the translations, and (2) the voters were able to discern these differences, and took their task
+seriously enough to report them.
+
+\begin{table}[t]
+\centering
+\begin{tabular}{l|rr}
+  language  & SAMT &  Google \\
+  \hline\hline
+  Bengali    & 13.53  &  20.01 \\
+  Hindi      & 17.29  & 25.21 \\  
+  Malayalam    & 14.28  & - \\      
+  Tamil      &  9.85  &  13.51 \\  
+  Telugu     & 12.61  & 16.03  \\  
+  Urdu        & 20.99  & 23.09 \\   
+\end{tabular}
+\caption{BLEU scores translating into English (four references).  BLEU
+scores are the mean of three MERT runs.}
+\label{table:bleu}
+\end{table}
+
+\begin{figure*}[t]
+  \centering
+  \includegraphics[width=\textwidth]{../version1-figures/tamil.png}
+  \begin{tabular}{l}
+    \hline
+    In March 15,2007 Wiki got a place in Oxford English dictionary. \\
+    On March 15, 2007 wiki was included in the Oxford English
+    dictionary. (5) \\
+    ON MARCH 15, 2007, WIKI FOUND A PLACE IN THE OXFORD ENGLISH
+    DICTIONARY \\
+    March 15, 2007 oxford english index of wiki's place. \\ \\
+
+  \end{tabular}
+  \caption{An example of the variance in translation quality for the
+    human translations of a Tamil sentence; the formatting of the
+    translations has been preserved exactly.  The parenthesized number
+    indicates the number of votes received in the voting task
+    (\S\ref{section:votes}).}
+  \label{figure:variance}
+\end{figure*}
 

### 2013-11-18 writeup/reviewer-response/paper.tex
reviewer response and version 1 updates

--- 2013-11-05 writeup/reviewer-response/paper.tex
@@
 \usepackage{graphicx}
-\usepackage{caption}
+%\usepackage{caption}
+\usepackage[font=small]{caption}
 \usepackage{multirow}
@@
 \usepackage{subcaption}
-\DeclareMathOperator*{\argmax}{arg\,max}
+
 \setlength\titlebox{5cm}    % Expanding the titlebox
+\setlength{\abovecaptionskip}{1pt plus 1pt minus 1pt} % Chosen fairly arbitrarily
+\setlength{\belowcaptionskip}{1pt plus 1pt minus 1pt} % Chosen fairly arbitrarily
 
@@
 
-\begin{figure}
-\centering
-\begin{subfigure}[b]{1\linewidth}
-\includegraphics[width=\textwidth]{figures/turker-googmatch-distribution.png}
-\caption{Individual turker overlap with google translate.
-We believe the inflection point at ~60\% overlap with Google suggests a reasonable cutoff by which to filter workers.
-Workers with \textgreater 60\% overlap can be reasonably considered to be cheating and can be removed.}
-\label{dist}
-\end{subfigure}
-\begin{subfigure}[b]{1\linewidth}
-\includegraphics[width=\textwidth]{figures/google-cdf-googlangs.png}
-\caption{Cumulative distribution of overlap with Google translate for workers and translations.
-We see that eliminating all workers with \textgreater 60\% overlap with google translate still preserves \textgreater 80\% of workers and \textgreater 70\% of translations.}
-\label{cdf}
-\end{subfigure}
-\caption{}\label{cheaters}
-\end{figure}
+%\begin{figure}
+%\centering
+%\begin{subfigure}[b]{1\linewidth}
+%\includegraphics[width=\textwidth]{figures/turker-googmatch-distribution.png}
+%\caption{Individual turker overlap with Google Translate.
+We remove the 500 workers with the highest overlap (shaded region on the left) from our analysis, as it is reasonable to assume these workers are cheating by submitting translations from Google.
+We believe the workers with no overlap (shaded region on the right) are also likely to be cheating, e.g.
+by submitting random text, and we target these workers through our embedded quality controls.}
+%\label{dist}
+%\end{subfigure}
+%\begin{subfigure}[b]{1\linewidth}
+%\includegraphics[width=\textwidth]{figures/google-cdf-googlangs.png}
+%\caption{Cumulative distribution of overlap with Google translate for workers and translations.
+We see that eliminating all workers with \textgreater 70\% overlap with google translate still preserves 90\% of translations and \textgreater 90\% of workers.}
+%\label{cdf}
+%\end{subfigure}
+%\caption{}\label{cheaters}
+%\end{figure}
 
@@
 
+\begin{figure}[ht]
+\includegraphics[width=\linewidth]{figures/turker-googmatch-distribution.png}
+\caption{Individual turker overlap with Google Translate.
+We remove the 500 workers with the highest overlap (shaded region on left) from our analysis.
+Workers with no overlap (on right) are also likely to be cheating, e.g.
+by submitting random text.
+We target these workers through our embedded controls.}
+\label{dist}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=\linewidth]{figures/google-cdf-googlangs.png}
+\caption{Cumulative distribution of overlap with Google translate for workers and translations.
+Eliminating all workers with \textgreater 70\% overlap with google translate still preserves 90\% of translations and \textgreater 90\% of workers.}
+\label{cdf}
+\end{figure}
+
 We took at closer look at the amount of overlap with Google translate in our collected translations in order to address this issue.
@@
 
-As Reviewer E noted :
+%As Reviewer E noted :
 
-\begin{quote}
-..it is quite possible that a fluent speaker of a language provides the same translation as Google Translate for a given word.  In other words, the performance results are inconclusive.
-\end{quote}
+%\begin{quote}
+%..it is quite possible that a fluent speaker of a language provides the same translation as Google Translate for a given word.  In other words, the performance results are inconclusive.
+%\end{quote}
 
-We see a clear inflection near the 60\% overlap point, suggesting that this cutoff may work well to eliminate turkers who are likely using Google Translate to cheat without punishing those who are producing honest translations that happen to overlap with Googe Translate.
+It seems likely that those with very high overlap are cheating, but it is also reasonable to assume that honest turkers will overlap with Google with some regularity.
+We therefore divide the workers into three groups : those with very high overlap with Google (likely cheating by using Google to translate words), those with reasonable overlap, and those with no overlap (likely cheating by other means, e.g.
+submitting random text).
+Our controls are designed to identify workers that fall into the third group (those who are spamming or providing useless translations), but they will not effectively flag workers who are cheating with Google Translate.
 
-Figure \ref{cdf} shows that removing workers with suspiciously high overlap with Google retains the majority of workers and translations, and will not greatly decrease the size of the study.
-
-We have rerun the quality analysis in the paper, omitting workers with \textgreater 60\% overlap with Google Translate.
-The quality scores and rankings do not change substantially.
-For reference, figure 2 from the paper is reproduced in figure \ref{qual}, both with and without the high-overlap Turkers included.
+We chose to remove the 500 turkers with the highest overlap with Google.
+This equates to removing all workers with greater than 70\% overlap.
+Figure \ref{cdf} shows that removing workers at or above the 70\% threshold retains 90\% of the collected translations and over 90\% of the workers.
 
@@
 \begin{subfigure}[b]{1\linewidth}
-\includegraphics[width=\textwidth]{figures/fig2with.png}
+\includegraphics[width=\textwidth]{figures/quality-all.png}
 \caption{All turkers.}                
-\label{dist}
+\label{quality-all}
 \end{subfigure}
 \begin{subfigure}[b]{1\linewidth}
-\includegraphics[width=\textwidth]{figures/fig2without.png}
-\caption{Turkers with \textless 60\% overlap with Google Translate.}
-\label{cdf}
+\includegraphics[width=\textwidth]{figures/quality-filtered.png}
+\caption{Turkers with \textless 70\% overlap with Google Translate.}
+\label{quality-filtered}
 \end{subfigure}
@@
 
+We have rerun the quality analysis in the paper, omitting workers with \textgreater 70\% overlap with Google Translate.
+The quality scores and rankings do not change substantially.
+For reference, figure \ref{qual} shows the quality scores for languages when computed over all Turkers as in the original draft of the paper (figure \ref{quality-all}) and computed over only Turkers with less than 70\% overlap with Google (figure \ref{quality-filtered}).
+In our new draft of the paper, we have omitted Tukers with more than 70\% overlap from all of our quality computations.
+
+%\begin{figure}
+%\includegraphics[width=\linewidth]{figures/quality-all.png}
+%\caption{All turkers.}                
+%\label{quality-all}
+%\end{figure}
+%\begin{figure}
+%\includegraphics[width=\linewidth]{figures/quality-filtered.png}
+%\caption{Turkers with \textless 70\% overlap with Google Translate.}
+%\label{quality-filtered}
+%\caption{Qualities for languages with \textgreater 50 turkers.
+Dark blue shows quality measured by perfect match on the control translation.
+Light blue indicates quality measured by included synonymous translations.}\label{qual}
+%\end{figure}
+
 \section{Robustness of results to removing few big players}
@@
 \begin{quote}
-It is possible that a small number of workers could have driven response accuracies for some languages.
-The authors could have accounted for this in a straightforward way by regressing out the contributions of individual workers, e.g.
-by using random effects models.
+Provide additional analysis showing that translation accuracy is not due to a few individuals who happened to do most of your tasks.
 \end{quote}
-We ran a random effects model and found blah blah blah blah blah blah blah.
+
+We agree that this is a valid concern since many languages followed the pattern of having a small number of very active Turkers complete the majority of assignments.
+We account of this by reporting qualities of each language as an average over Turker qualities, rather than over assignment qualities.
+By this method, each Turker contributes equally to the language's average quality, regardless of the number of HITs that that Turker submitted.
+Section 4 of the paper has been updated to reflect this change.
+Figure \ref{qual_dots} shows the quality scores for languages computed over assignments and over Turkers, and the change in each when the 10 most active Turkers in each language are removed.
+We can see that the per-Turker quality measure is robust to the exclusion of these highly-contributing Turkers.
+
+For completeness, we have also updated our reported quality scores in the paper to include confidence intervals and p-values, where appropriate.
+We hope this helps to reduce concern about the robustness of these measures.
+
+%\begin{figure}
+%\includegraphics[height=1\linewidth, angle=270]{figures/turker-hit-contributions.png}
+%\caption{Contributions of individual turkers to the overall number of HITs in each language.
+The dark blue bar represents the proportion of total HITs which were completed by the 10 highest-contributing turkers.
+The next darkest bar represents the next 10 highest-contributing turkers, and likewise for the thrid and forth darkest.
+The final bar represents the remaining turkers which were not one of the top 40 contributors.}
+%\label{num./hits}
+%\end{figure}
+
+\begin{figure}
+\includegraphics[height=1\linewidth, angle=270]{figures/quality_compare.png}
+\caption{Quality scores of languages computed as averages over assignments (red) and over turkers (blue).
+Light blue and light red dots reflect the quality scores that result when the 10 turkers with who contributed the highest number of HITs are removed.
+We see that while the quality calculated over assignments responds noticeably to the exclusion of these highly active turkers, the quality calculated over turkers is quite robust to the change.}
+\label{qual_dots}
+\end{figure}
 
@@
 
-Previous work by Matt Post in the 2010 WMT has demonstrated not only that turkers are able to provide high quality translations of complete sentences, but also that these translations, when added into an SMT pipeline, measurably improve translation quality.
-\textbf{MORE HERE.}
+To address these concerns, we incorporate previous work from a workshop publication from our colleague.
+The workshop publication will be cited appropriately in the final version of the paper, but we omit the citation now so as not to de-anonymize the submission.
+
+In this work, we collect full-sentence translations for six Indian languages which are well-represented on MTurk but for which there are currently no professionally-translated corpora available.
+We use the collected sentences to train and evaluate an SMT system, and show that the systems achieve decent performance.
+Furthermore, we add the collected single-word dictionaries to the training of these systems, and show that this produces measurable improvement in performance.
+Table \ref{dictionary_bleu} highlights these results.
+Please see sections 3 and 5 for a complete discussion of the data and experiments.
+
+\begin{table}[t]
+\centering
+\begin{tabular}{l|ccc}
+  language  & sentences &  dictionaries & Google \\
+  \hline\hline
+  Bengali    &  12.03 & 17.29 & 20.01 \\
+  Hindi      & 16.19 & 18.10 & 25.21\\  
+  Malayalam    &  6.65 & 9.72 & - \\      
+  Tamil      & 8.08 & 9.66 & 13.51\\  
+  Telugu     & 11.94 & 13.70 & 16.03\\  
+  Urdu        & 19.22 & 21.98 & 23.09\\   
+\end{tabular}
+\caption{BLEU scores for translating into English using full sentence translations alone, and with the addition of single-word dictionaries.
+Scores are calculated using four reference translations and represent the mean of three MERT runs.}
+\label{dictionary_bleu}
+\end{table}
 
@@
 The plot shows that activity does vary across time zones, and suggests that choosing the release time intelligently based on the HIT language is likely to affect how quickly it is completed.
-\begin{figure*}
-\includegraphics[width=1\linewidth]{figures/times.png}
+We include this analysis here for the interest of the reviewer.
+We do not include it in the paper, however, as we do not feel it meaningfully changes the analysis presented there.
+
+\begin{figure}
+\centering
+\includegraphics[height=.8\linewidth, angle=270]{figures/times.png}
 \caption{Number of HITs completed during each hour of the day for languages with \textgreater 100 turkers.}
 \label{time}
-\end{figure*}
+\end{figure}
 
@@
 The trends that we observe in our analysis, where we show that turkers geolocated within a region likely to speak the source language being translated tend to perform better on our controls, coincide with what we would expect to see if geolcation were accurate.
-This seems to support the assumption that, on average, the geolocation is performing sufficiently well.
-
-\section{Novelty}
-
-Its novel. Trust us.
+Additionally, of the turkers who responded to our survey questions, 95\% of their self-reported locations agreed with our geolocations.
+These facts reassure us that, on average, the geolocation is performing sufficiently well.
 

### 2013-11-18 writeup/version1/paper.tex
reviewer response and version 1 updates

--- 2013-03-31 writeup/paper.tex
@@
 We validate workers' self-reported language skill claims by measuring their ability to correctly translate words, and by geolocating workers to see if they reside in countries where the languages are likely to be spoken.
-Rather than posting a one-off survey, we posted paid tasks consisting of 1,000 assignments to translate a total of 10,000 words in each of 119 languages.
+Rather than posting a one-off survey, we posted paid tasks consisting of 1,000 assignments to translate a total of 10,000 words in each of 100 languages.
 Our study ran for several weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilingual workers would complete it.
@@
 We ask workers what languages they speak and what country they live in, and validate their claims by measuring their ability to correctly translate words and by recording their geolocation.
-To increase the visibility and the desirability of our tasks, we post 1,000 assignments in each of 119 languages.
+To increase the visibility and the desirability of our tasks, we post 1,000 assignments in each of 100 languages.
 These tasks each consist of translating 10 foreign words into English.
@@
 
-Surveying thousands of workers allows us to analyze current speaker populations for more than 100 languages.  The data also allows us to answer questions like: 
+Surveying thousands of workers allows us to analyze current speaker populations for 100 languages.  The data also allows us to answer questions like: 
 How quickly is work completed in a given language? 
@@
 \centering
-\includegraphics[width=\linewidth]{final-figures/turkermap}
+\includegraphics[width=\linewidth]{../version1-figures/map.png}
 \caption{The number of workers per country.
-This map was generated based on geolocating the IP address of  5,277 workers in our study.
+This map was generated based on geolocating the IP address of  4,983 workers in our study.
+Omitted are 60 workers who were located in more than one country during the study, and 238 workers who could not be geolocated.
 The size of the circles represents the number of workers from each country.
-The two largest are India (2,017 workers) and the United States (904).
-To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
+The two largest are India (1,998 workers) and the United States (866).
+To calibrate the sizes: the Philippines has 142 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
 \label{map}
@@
 \newcite{Zbib-etal:2012:NAACL} used crowdsourcing to construct a 1.5 million word parallel corpus of dialect Arabic and English, training a statistical machine translation system that produced higher quality translations of dialect Arabic than a system a trained on 100 times more Modern Standard Arabic-English parallel data.
+\textbf{??
 \newcite{post-callisonburch-osborne:2012:WMT} used MTurk to build parallel corpora between English and six Indian languages, ranging from .5M to 1.5M words, and use them to demonstrate the efficacy of syntactic machine translation on verb-final languages.
+??}
 Several researchers have examined cost optimization using active learning techniques to select the most useful sentences or fragments to translate \cite{ambati_naacl,bloodgood-callisonburch:2010:ACL,AmbatiThesis}.
@@
 \normalsize
-\caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 languages with $\leq$20 speakers. 
-We omit 1,797 Turkers who did not report their native language, 243 who reported 2 native languages, and 83 with $\geq$3 native languages.}\label{lang-pie}
+\caption{Self-reported native language of 3,216 bilingual Turkers. Not shown are 49 languages with $\leq$20 speakers. 
+We omit 1,801 Turkers who did not report their native language, 243 who reported 2 native languages, and 83 with $\geq$3 native languages.}\label{lang-pie}
 \end{table}
@@
 
-\section{Survey Design}
+\section{Experimental Design}
 The central task in this study was to investigate Mechanical Turk's bilingual population.
-We accomplished this through self-reported surveys combined with a HIT to translate individual words for over 100 languages.
+We accomplished this through self-reported surveys combined with a HIT to translate individual words for 100 languages.
 We evaluate the accuracy of the workers' translations against known translations.
@@
 We automatically collected each worker's current location by geolocating their IP address.
-A total of 5,277 unique workers completed our HITs.
-Among those, 3,890 provided responses to our survey questions, and we were able to geolocate 5,050.
-Figure \ref{map} plots the location of workers across 111 countries.
+A total of 5,281 unique workers completed our HITs.
+Of these, 3,625 provided answers to our survey questions, and we were able to geolocate 5,043.
+Figure \ref{map} plots the location of workers across 106 countries.
 Table \ref{lang-pie} gives the most common self-reported native languages.
@@
 We drew our data from the different language versions of Wikipedia.
-We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} and then selected an additional 19 low resource languages, giving a total of 119 languages (Table \ref{wikipedia-buckets}).
+We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} (Table \ref{wikipedia-buckets}).
 For each language, we chose the 1,000 most viewed articles over a 1 year period,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and extracted the 10,000 most frequent words from them.
@@
 
-%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
-\begin{figure*}[h]
-\begin{center}
-\includegraphics[width=0.8\linewidth]{final-figures/quality-bar}
-\caption{Translation quality for languages with at least 50 Turkers.
-The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms.}
-\label{hitlangqual} 
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \paragraph{Translation HIT}
@@
 Each set of 10 words was independently translated by three separate workers.
-5,277 workers completed 308,079 translations assignments, totaling more than 3 million words, over a period of three and a half months.
+5,281 workers completed 256,604 translations assignments, totaling more than 3 million words, over a period of three and a half months.
 
@@
 Automating approval/rejections for the second-pass evaluation allowed the whole pipeline to be run automatically.  Caching judgments meant that we ultimately needed only 
-20,955 synonym tasks to judge all of the submitted translations (a total of 55,880 unique non-matching word pairs).
-These were completed by an additional 1,006 workers.
+20,952 synonym tasks to judge all of the submitted translations (a total of  74,572 non-matching word pairs).
+These were completed by an additional 1,005 workers.
 Each of these assignments included 10 word pairs and paid \$0.10.
+
+\begin{figure*}[t]
+  \centering
+  \includegraphics[width=\textwidth]{../version1-figures/tamil.png}
+  \begin{tabular}{l}
+    \hline
+    In March 15,2007 Wiki got a place in Oxford English dictionary. \\
+    On March 15, 2007 wiki was included in the Oxford English
+    dictionary. \\
+    ON MARCH 15, 2007, WIKI FOUND A PLACE IN THE OXFORD ENGLISH
+    DICTIONARY \\
+    March 15, 2007 oxford english index of wiki's place. \\ \\
+
+  \end{tabular}
+  \caption{An example of the variance in translation quality for the
+    human translations of a Tamil sentence; the formatting of the
+    translations has been preserved exactly.}
+  \label{figure:variance}
+\end{figure*}
+
+\paragraph{Full sentence translations}
+In addition to the bilingual dictionaries, we are interested in Turkers' ability to translate complete sentences.
+Because the Indian subcontinent is so well represented among our workers, we chose six Indian languages for which to gather translations of full sentences.
+We selected Bengali, Malyalam, Hindi, Tamil, Telugu, and Urdu as good candidates for our study : these languages have large native speaker populations and are well represented on Wikipedia but they are currently not covered by any professionally translated corpora.
+
+Each of the sentence translation HITs contained ten sequential sentences from a source-language Wikipedia article and asked the worker to enter a free-form translation for each.
+We collected four translations from different translators for each source sentence.
+Workers were paid \$0.70 per HIT.
+
+Since there is no gold-standard data available for our chosen languages, and it could not be mined in a straight-forward way as in the single word case, we were unable to embed controls into our HITs.
+We instead accepted or rejected translations based on a review of each worker's submissions, which included a comparison of the translations to a monotonic gloss (produced with a dictionary), and metadata such as the amount of time the worker took to complete the HIT and their geographic location.
+
+Figure~\ref{figure:variance} contains some hand-picked examples of the sorts of translations we obtained.
+While the lack of a gold-standard data set prevented us from evaluating the collected translations in terms of BLEU scores, as in \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we evaluate the quality of the data by using it to train an SMT system.
+We present results in section \ref{sec:data-analysis}.
 
@@
 
-We calculate the quality of translations on the level of individual assignments and aggregated over languages and countries.
-We define an assignment's quality as the proportion of controls that are correct in a given assignment, where correct means exactly correct or judged to be synonymous or related.
+We calculate the quality of translations on the level of individual assignments and aggregated over workers and languages.
+We define an assignment's quality as the proportion of controls that are correct in a given assignment, where correct means exactly correct or judged to be synonymous.
 \begin{align}	
@@
 
-%Since judging overall quality for a language with assignment quality scores is biased towards to small numbers of highly active Turkers, we instead report language quality scores as the average per-Turker quality, where a Turker's quality is  the average quality of all the assignments that she completed:
-%\begin{align}	
-%	\text{Quality}(t_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}\text{Quality}(a_j)}}{\mid \texttt{assigns[$i$]} \mid}
-%\end{align}	
-%where $t_i$ is the $i^{th}$ Turker, \texttt{assigns[$i$]} is the assignments completed by Turker $i$, and Quality($a$) is as above.
-%
+Since computing overall quality for a language as the average assignment quality score is biased towards a small number of highly active Turkers, we instead report language quality scores as the average per-Turker quality, where a Turker's quality is  the average quality of all the assignments that she completed:
+\begin{align}	
+	\text{Quality}(t_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}\text{Quality}(a_j)}}{\mid \texttt{assigns[$i$]} \mid}
+\end{align}	
+where \texttt{assigns[$i$]} is the assignments completed by Turker $i$, and Quality($a$) is as above.
 
@@
 \begin{align}	
-	\text{Quality}(l_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}\text{Quality}(a_j)}}{\mid \texttt{assigns[$i$]} \mid}
+	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{turkers[$i$]}\text{Quality}(t_j)}}{\mid \texttt{turkers[$i$]} \mid}
 \end{align}	
-where $l_i$ is the ith language, \texttt{assigns[$i$]} is the set of completed assignments for language $i$, and Quality($a$) is as above. Quality for a country is computed the same way.
+When a turker completed assignments in more than one language, their quality was computed separately for each language.
 
-%Quality for a language is then given by
-%\begin{align}	
-%	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{Turkers[$i$]}\text{Quality}(t_j)}}{\mid \texttt{Turkers[$i$]} \mid}
-%\end{align}	
-%where $l_i$ is the ith language, \texttt{Turkers[$i$]} is the set of Turkers who completed assignments for language $i$, and Quality($t$) is as above.
+Figure \ref{hitlangqual} shows the translation quality for languages with contributions from at least 50 workers.
 
-Figure \ref{hitlangqual} shows the translation quality for for languages with contributions from at least 50 workers.
+%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
+\begin{figure*}[h]
+\begin{center}
+\includegraphics[width=\linewidth]{../version1-figures/quality_bar.png}
+\caption{Translation quality for languages with at least 50 Turkers.
+The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms.
+Error bars show the 95\% confidence intervals for each language.}
+\label{hitlangqual} 
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Data Analysis}
+\begin{figure}
+\centering
+\begin{subfigure}[b]{\linewidth}
+%\includegraphics[width=\textwidth]{../version1-figures/turker-googmatch-distribution.png}
+\includegraphics[width=\linewidth]{../version1-figures/turker-googmatch-distribution.png}
+\caption{Individual turker overlap with Google Translate.
+We remove the 500 workers with the highest overlap (shaded region on the left) from our analysis, as it is reasonable to assume these workers are cheating by submitting translations from Google.
+We believe the workers with no overlap (shaded region on the right) are also likely to be cheating, e.g.
+by submitting random text, and we target these workers through our embedded quality controls.}
+\label{dist}
+\end{subfigure}
+\begin{subfigure}[b]{\linewidth}
+%\includegraphics[width=\textwidth]{../version1-figures/google-cdf-googlangs.png}
+\includegraphics[width=\linewidth]{../version1-figures/google-cdf-googlangs.png}
+\caption{Cumulative distribution of overlap with Google translate for workers and translations.
+We see that eliminating all workers with \textgreater 70\% overlap with google translate still preserves 90\% of translations and \textgreater 90\% of workers.}
+\label{cdf}
+\end{subfigure}
+\caption{}\label{cheaters}
+\end{figure}
+
+\paragraph{Use of machine translation}
+
+One obvious way for dishonest workers to shortcut is to use available online translation tools.
+Although we followed best practices to deter copying-and-pasting into online MT systems  by  rendering words and sentences as images \cite{zaidan-callisonburch:2011:ACL-HLT2011a}, this strategy does not prevent workers from typing the words into an MT system if they are able to type in the language's script.
+
+We quantified each turker's overlap with the Google translations so that we could identify and remove workers that appeared to be misusing Google Translate.
+We used Google to translate all 10,000 words for the 51 foreign languages that Google Translate covered at the time of the study.
+We measured the percent of workers' translations that exactly matched the translation returned from Google.
+
+%Results are show in Figure \ref{googlematch}.
+Assignments averaged around 42\% overlap with GoogleTranslate.
+Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphabet) have lower overlap with Google,  suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.
+
+%%%%%%%%%%%%%%% GOOGLE OVERLAP BAR %%%%%%%%%%%
+%\begin{figure}[h]
+%\begin{center}
+%\includegraphics[width=1\linewidth]{../version1-figures/google_bar.png}
+%\caption{Average proportion of Turker translations matching GoogleTranslate, per assignment. Overall average overlap was 0.37.}
+%\label{googlematch} 
+%\end{center}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We found that while overall overlap is high (the average turker's overlap was 41\%), it is not consistently high across all turkers.
+Figure \ref{dist} shows that while a small number of turkers have a very high amount of overlap with Google (near 80\%) the majority overlap less than half of the time.
+It seems likely that those with very high overlap are cheating, but it is also reasonable to assume that honest turkers will overlap with Google with some regularity.
+We therefore divide the workers into three groups : those with very high overlap with Google (likely cheating by using Google to translate words), those with reasonable overlap, and those with no overlap (likely cheating by other means, e.g.
+submitting random text).
+
+Our controls are designed to identify workers that fall into the third group (those who are spamming or providing useless translations), but they will not effectively flag workers who are cheating with Google Translate.
+We therefore remove the 500 turkers with the highest overlap with Google.
+This equates to removing all workers with greater than 70\% overlap.
+Figure \ref{cdf} shows that removing workers at or above the 70\% threshold retains 90\% of the collected translations and over 90\% of the workers.
+
+Quality scores reported throughout the paper reflect only translations from turkers whose overlap with Google falls below this 70\% threshold.
+
+\section{Data Analysis} \label{sec:data-analysis}
 
@@
 \item Do workers accurately represent their language abilities?  Should we constrain tasks by region? 
-\item Is the use of machine translation prevalent?  
 \item Are our gold standard translations valid? 
-%\item What is the quality of crowdsourced translations without quality control versus with it? 
+\item Can Turkers' translations be used to train an MT system? 
 \end{itemize}
@@
 %%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
-\begin{figure}[h]
-\includegraphics[height=\linewidth,angle=270]{final-figures/completetime}
+\begin{figure*}[h]
+%\includegraphics[height=\linewidth,angle=270]{../final-figures/completetime}
+\includegraphics[width=\linewidth]{../final-figures/completetime}
 \caption{Days to complete the translation HITs for 40 of the languages. Tick marks represent the completion of individual assignments. }
 \label{completion-time}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \hline\hline
-Hindi&\textbf{0.35} (299)&0.34 (7)&India (285) UAE (5) UK (5) &Saudi Arabia (2) Russia (1) Oman (1) \\
-Tamil&\textbf{0.37} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
-Malayalam&0.48 (235) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudi Arabia (1) Maldives (1) \\
-Spanish&\textbf{0.72} (205)&0.61 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) New Zealand (1) \\
-French&0.65 (183) &\textbf{0.86} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
-German&\textbf{0.83} (99)&0.65 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
-Italian&\textbf{0.78} (98)&0.71 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
-Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hong Kong (6) Australia (3) Germany (2) \\
-Malay&0.76 (15) &\textbf{0.83} (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
-Irish&\textbf{0.68} (58)&0.64 (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
-Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czech Republic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
-Turkish&0.72 (83) &\textbf{0.73} (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
-Amharic&\textbf{0.18} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
-Swedish&\textbf{0.66} (58)&0.61 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
-Portuguese&\textbf{0.77} (107)&0.74 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
-Arabic&0.22 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
-Kannada&\textbf{0.24} (106)&0.00 (1)&India (106) US (1) &France (1) Germany (1) \\
-Russian&\textbf{0.09} (72)&0.06 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
-Afrikaans&\textbf{0.74} (4)&0.73 (98)&South Africa (4) &India (93) Netherlands (2) UAE (1) \\
-Sindhi&\textbf{0.15} (93)&0.02 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
+Hindi & 0.635 (296) & \textbf{0.695} (7) & India (284) Uae (5) Uk (3)  & Saudiarabia (2) Russia (1) Oman (1) \\
+Tamil & \textbf{0.653} (273) * & 0.250 (2) & India (266) Unitedstates (3) Canada (2)  & Tunisia (1) Egypt (1)  \\
+Malayalam & 0.764 (234) & \textbf{0.827} (2) & India (223) Uae (6) Unitedstates (3)  & Saudiarabia (1) Maldives (1) \\
+Spanish & 0.814 (191) & \textbf{0.837} (18) & Unitedstates (122) Mexico (16) Spain (14)  & India (15) Newzealand (1) Brazil (1) \\
+French & 0.750 (170) & \textbf{0.816} (11) & India (62) Unitedstates (45) France (23)  & Greece (2) Netherlands (1) Japan (1) \\
+Chinese & \textbf{0.601} (116) & 0.552 (21) & Unitedstates (75) Singapore (13) China (9)  & Hongkong (6) Australia (3) Germany (2)  \\
+German & \textbf{0.825} (91) & 0.768 (41) & Germany (48) Unitedstates (25) Austria (7)  & India (34) Netherlands (1) Greece (1)  \\
+Italian & \textbf{0.863} (90) & 0.796 (42) & Italy (42) Unitedstates (29) Romania (7)  & India (33) Ireland (2) Spain (2)  \\
+Amharic & \textbf{0.136} (16) * & 0.009 (99) & Unitedstates (14) Ethiopia (2)  & India (70) Georgia (9) Macedonia (5)  \\
+Kannada & 0.704 (105) & NA (0) & India (105)  & \\
+Arabic & \textbf{0.741} (60) * & 0.604 (45) & Egypt (19) Jordan (16) Morocco (9)  & Unitedstates (19) India (11) Canada (3)  \\
+Sindhi & \textbf{0.190} (96) & 0.062 (9) & India (58) Pakistan (37) Unitedstates (1)  & Macedonia (4) Georgia (2) Indonesia (2)  \\
+Portuguese & 0.869 (101) & \textbf{0.963} (3) & Brazil (44) Portugal (31) Unitedstates (15)  & Romania (1) Japan (1) Israel (1) \\
+Turkish & 0.759 (76) & \textbf{0.804} (27) & Turkey (38) Unitedstates (18) Macedonia (8)  & India (19) Pakistan (4) Taiwan (1) \\
+Telugu & \textbf{0.799} (102) & 0.500 (1) & India (98) Unitedstates (3) Uae (1)  & Saudiarabia (1)  \\
+Irish & \textbf{0.742} (54) & 0.709 (47) & Unitedstates (39) Ireland (13) Uk (2)  & India (36) Romania (5) Macedonia (2)  \\
+Swedish & \textbf{0.734} (54) & 0.711 (45) & Unitedstates (25) Sweden (22) Finland (3)  & India (23) Macedonia (6) Croatia (2)  \\
+Czech & \textbf{0.706} (45) & 0.612 (50) & Unitedstates (17) Czechrepublic (14) Serbia (5)  & Macedonia (22) India (10) Uk (5)  \\
+Russian & \textbf{0.146} (67) & 0.119 (27) & Unitedstates (36) Moldova (7) Russia (6)  & India (14) Macedonia (4) Uk (3)  \\
+Breton & 0.167 (3) & \textbf{0.178} (89) & Unitedstates (3)  & India (83) Macedonia (2) China (1) \\
+
 \hline\hline
@@
 \end{center}
-\caption{Translation quality when partitioning the translations into two groups, one contains translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other contains translations from Turkers outside those regions.} \label{region-summary}
+\caption{Translation quality when partitioning the translations into two groups, one containing translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other containing translations from Turkers outside those regions.
+In general, in-region Turkers provide higher quality translations.
+(*) indicates differences significant at p=0.05.} \label{region-summary}
 \end{table*}
@@
 
-Our workers reported speaking 97 languages natively.
-US workers alone reported 59 native languages.
-Overall, 4,465 workers were located in a region likely to speak the language from which they were translating, and 3,170 workers were located in countries considered out of region (meaning almost half of our 5,277 Turkers completed HITs in multiple languages).
+Our workers reported speaking 95 languages natively.
+US workers alone reported 61 native languages.
+Overall, XXXX workers were located in a region likely to speak the language from which they were translating, and XXXX workers were located in countries considered out of region (meaning almost half of our 5,281 Turkers completed HITs in multiple languages).
 
@@
 Given the number of Indian workers on Mechanical Turk, it is unsurprising that they represent majority of out-of-region workers.
-For the languages that had more than 80 out of region workers (Malay, Amharic, Afrikaans, Icelandic, and Breton), Indian workers represented 90\% of the out of region workers for all of them aside from Amharic.
+\textbf{For the languages that had more than 80 out of region workers (Malay, Amharic, Afrikaans, Icelandic, and Breton), Indian workers represented 90\% of the out of region workers for all of them aside from Amharic}.
 
@@
 
-%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=1\linewidth]{final-figures/google-match}
-\caption{Average proportion of Turker translations matching GoogleTranslate, per assignment. Overall average overlap was 0.42}
-\label{googlematch} 
-\end{center}
-\end{figure}
+%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=0.78\linewidth]{../final-figures/quality-scatter_joined-1column}
+%\end{center}
+
+%\caption{Estimated quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country. }
+%\label{quality-scatter}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
-\begin{figure*}[h]
-\begin{center}
-\includegraphics[width=0.8\linewidth]{final-figures/quality-scatter_joined}
-\end{center}
-
-\caption{Estimated quality of translations by country.
-Each circle is a country, sized proportional to the number of active Turkers from that country.
-Quality is calculated as the average number of control words which were correct translations of the source word, where ”correct” means that the provided translation was judged to be synonymous with the known translation by workers in a second-pass HIT.
-Figure represents data from approx.
-295,000 assignments for which geolocation was known.}
-\label{quality-scatter}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Figure \ref{quality-scatter} shows the number of assignments completed per country and per-country quality estimates for 4 scenerios: (a) overall, (b) for assignments completed in region, (c) for assignments completed out of region, and (d) for out of region assignments which contained low overlap with GoogleTranslate.
-
-\paragraph{Use of machine translation}
-
-Given then prevalence of out of region workers, we investigated what proportion of the translations submitted by workers were simply replicating translations from a machine translation system.
-Although we followed best practices to deter copying-and-pasting into online MT systems  by  rendering words and sentences as images \cite{zaidan-callisonburch:2011:ACL-HLT2011a}, this strategy does not prevent workers from typing the words into an MT system, if they are able to type in the language's script.
-
-We used GoogleTranslate to translate all 10,000 words for 50 foreign languages that GoogleTranslate covers.
-We measured the percent of translations received that exactly matched the translation returned from GoogleTranslate.
-Results are show in Figure \ref{googlematch}.
-Assignments averaged around 42\% overlap with GoogleTranslate.
-Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphabet) have lower overlap with Google,  suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.
-% suggesting that it is easier for Turkers to use MT for Latin alphabet languages.
-
-%We translated: af ar az bg ca cs cy da de el eo es eu fa fi fr gl gu he hr hu hy id is it ja kn ko lt lv ms nl pl pt ro ru sk sl sq sr sv sw ta te th tr uk ur vi zh
-
-% Google supports:
-%Afrikaans
-%Albanian
-%Arabic
-%Belarusian
-%Bulgarian
-%Catalan
-%Chinese
-%Chinese
-%Croatian
-%Czech
-%Danish
-%Dutch
-%English
-%Estonian
-%Esperanto
-%Filipino
-%Finnish
-%French
-%Galician
-%German
-%Greek
-%Hebrew
-%Hindi
-%Hungarian
-%Icelandic
-%Indonesian
-%Irish
-%Italian
-%Japanese
-%Korean
-%Latvian
-%Lithuanian
-%Macedonian
-%Malay
-%Maltese
-%Norwegian
-%Persian
-%Polish
-%Portuguese
-%Romanian
-%Russian
-%Serbian
-%Slovak
-%Slovenian
-%Spanish
-%Swahili
-%Swedish
-%Thai
-%Turkish
-%Ukrainian
-%Vietnamese
-%Welsh
-%Yiddish
-%Armenian
-%Azerbaijani
-%Basque
-%Georgian
-%Gujarati
-%Haitian Creole
-%Kannada
-%Latin
-%Lao
-%Tamil
-%Telugu
-%Urdu
-
+%Figure \ref{quality-scatter} shows the number of assignments completed per country and per-country quality estimates for 4 scenerios: (a) overall, (b) for assignments completed in region, (c) for assignments completed out of region, and (d) for out of region assignments which contained low overlap with GoogleTranslate.
 \paragraph{Validation of controls} 
-Higher overlap with GoogleTranslate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some control translations have already been indexed by Google.
+Higher overlap with Google Translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.XXX), suggesting that some control translations have already been indexed by Google.
 We therefore investigated the validity of our use of Wikipedia inter-language links as gold standard translations.
@@
 As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
-We had external bilingual dictionaries for 24 of the 119 languages examined in this study.\footnote{The bilingual dictionaries were between English and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz.
+We had external bilingual dictionaries for 24 of the 100 languages examined in this study.\footnote{The bilingual dictionaries were between English and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz.
 }  We used each of these bilingual dictionaries to compute language-level quality scores, using the dictionary's translation as a gold standard translation for any of the 10,000 foreign words in our study.
@@
 
+\paragraph{Quality improvements for SMT systems}
+Using the full sentence translations we gathered for the six Indian languages, we were able to train a statistical machine translation system.
+Table \ref{table:data-size} gives the size of the data set for each of these languages.
+Table \ref{dictionary_bleu} shows that the sentences alone produce decent translation performance, with BLEU scores as high as 19.22 for Urdu.
+We also see that adding the single-word dictionaries to the training set produces consistent performance gains, ranging from 1 to 5 BLEU points.
+Unfortunately, we do not have professionally translated data against which to compare the resulting performances.
+We do, however, report the BLEU scores achieved by Google Translate, where available.
+Given that the sizes of the data sets used to train Google's system are likely much greater than ours, we find these results encouraging as an indication of the potential of Turkers to provide high quality translations.
+
+\begin{table}[t]
+  \centering
+  \small
+  \begin{tabular}{l|rr}
+    language & full sentences & dictionaries \\
+    \hline\hline
+    Bengali & 732k (22k)  & 22k \\
+    Hindi   & 1,488k (40k) & 22k \\
+    Malayalam & 863k (32k) & 23k \\
+    Tamil & 916k (38k) & 25k \\
+    Telugu & 1,097k (46k) & 21k \\
+    Urdu & 1,356k (35k) & 20k \\
+  \end{tabular}
+  \caption{Size of data set (number of words) collected for each language. For full sentences, number of parallel sentences is shown in parentheses.}
+  \label{table:data-size}
+\end{table}
+
+\begin{table}[t]
+\centering
+\begin{tabular}{l|ccc}
+  language  & sentences &  dictionaries & Google \\
+  \hline\hline
+  Bengali    &  12.03 & 17.29 & 20.01 \\
+  Hindi      & 16.19 & 18.10 & 25.21\\  
+  Malayalam    &  6.65 & 9.72 & - \\      
+  Tamil      & 8.08 & 9.66 & 13.51\\  
+  Telugu     & 11.94 & 13.70 & 16.03\\  
+  Urdu        & 19.22 & 21.98 & 23.09\\   
+\end{tabular}
+\caption{BLEU scores for translating into English using full sentence translations alone, and with the addition of single-word dictionaries.
+Scores are calculated using four reference translations and represent the mean of three MERT runs.}
+\label{dictionary_bleu}
+\end{table}
+
+%\begin{table}[t]
+%\centering
+%\begin{tabular}{l|rr}
+ % language  & SAMT &  Google \\
+  %\hline\hline
+ % Bengali    & 13.53  &  20.01 \\
+ % Hindi      & 17.29  & 25.21 \\  
+ % Malayalam    & 14.28  & - \\      
+ % Tamil      &  9.85  &  13.51 \\  
+ % Telugu     & 12.61  & 16.03  \\  
+ % Urdu        & 20.99  & 23.09 \\   
+%\end{tabular}
+%\caption{BLEU scores translating into English (four references).  BLEU scores are the mean of three MERT runs.}
+%\label{table:bleu}
+%\end{table}
+
 \section{Discussion}
-The Mechanical Turk gives research access to a diverse set of bilingual workers, making it a promising resource for researchers and developers of multilingual systems. 
+Mechanical Turk gives researchers access to a diverse set of bilingual workers, making it a promising resource for researchers and developers of multilingual systems. 
 Although unfiltered data can contain large amounts of noise, 
@@
 Our data release will include the raw data, along with bilingual dictionaries that are filtered to be high quality.
-It will include 308,079 translation assignments from 5,277 Turkers and 20,955 synonym assignments from 1,006 Turkers, along with meta information like geolocation and time submitted, plus external dictionaries used for validation.
-The dictionaries will contain 850,907 total translated words in 101 languages, along with code to filter the dictionaries based on different criteria.
+It will include 256,604 translation assignments from 5,281 Turkers and 20,952 synonym assignments from 1,005 Turkers, along with meta information like geolocation and time submitted, plus external dictionaries used for validation.
+The dictionaries will contain 1.5M total translated words in 100 languages, along with code to filter the dictionaries based on different criteria.
 

### 2013-11-18 code/src/20130905/paper-rewrite/figures/code/language_table.py

@@ -44,17 +44,25 @@ lmap = {l.strip().split()[1] : l.strip().split()[0] for l in open('ref/lang2name
 
 lang_counts = {}
 tot = 0
+no = 0
+two = 0
+mult = 0
 
 for line in csv.DictReader(open('data/turkers.tsv'), delimiter='\t') :
 	langs = [c for c in line['langs'].split(':') if not c.strip() == '']
-	if len(langs) > 1 : print langs; continue;
+	if len(langs) == 2 : print langs; two+=1; continue;
+	if len(langs) > 2 : print langs; mult+=1; continue;
+	if len(langs) == 0 : print langs; no+=1; continue;
 	for lang in langs : 
 		try : lang = lmap[lang]
-		except : continue
+		except : print lang; continue
 		if lang not in lang_counts : lang_counts[lang] = 0
 		if line['id'] in pass1_turkers : lang_counts[lang] += 1; tot += 1;
 
-#print tot
+print 'Total', tot, tot - (mult+no+two)
+print 'No lang', no
+print 'two lang', two
+print 'mult lang', mult
 #for l in sorted(lang_counts.keys()) : 
 #	print "%s,%d"%(l,lang_counts[l])
 print_table(lang_counts)

### 2013-11-18 code/src/20130905/paper-rewrite/figures/code/map.py

@@ -12,21 +12,28 @@ for line in open('data/pass-1').readlines() :
 		w,t = wt.split(':',1)
 		pass1_turkers.add(w)
 
-cmap = {l.strip().split()[1] : l.strip().split()[0] for l in open('../ref/countrynames').readlines()}
+cmap = {l.strip().split()[1] : l.strip().split()[0] for l in open('ref/countrynames').readlines()}
 
 country_counts = {}
 tot = 0
+no = 0
+mult = 0
+used = set()
 
-for line in csv.DictReader(open('data/turkers.tsv'), delimiter='\t') :
-	countries = [c for c in line['country'].split(':') if not c.strip() == '']
-	if len(countries) > 1 : print countries; continue;
-	for country in countries : 
-		try : country = cmap[country]
-		except : continue
-		if country not in country_counts : country_counts[country] = 0
-		if line['id'] in pass1_turkers : country_counts[country] += 1; tot += 1;
+for line in csv.DictReader(open('data/pass1_turkers.tsv'), delimiter='\t') : 
+	if line['id'] not in used :
+		used.add(line['id'])
+		countries = [c for c in line['survey'].split(':') if not c.strip() == '']
+		if len(countries) > 1 : print countries; mult += 1; continue;
+		if len(countries) == 0 : print countries; no += 1; continue;
+		for country in countries : 
+			try : country = cmap[country]
+			except : print country; no+= 1; continue
+			if country not in country_counts : country_counts[country] = 0
+		#if line['id'] in pass1_turkers : country_counts[country] += 1; tot += 1;
+			country_counts[country] += 1; tot += 1;
 
-print tot
+print tot, no, mult, (tot+no+mult)
 
-for l in sorted(country_counts.keys()) : 
-	print "['%s',%d],"%(l,country_counts[l])
+#for l in sorted(country_counts.keys()) : 
+#	print "['%s',%d],"%(l,country_counts[l])

### 2013-11-18 code/src/20130905/paper-rewrite/figures/code/quality_bar.py

@@ -20,7 +20,7 @@ for row in csv.DictReader(open('results/data/quality.turkers.txt'), delimiter = 
 graph_data = [] 
 t = 0 
 for lang in sorted(data.keys()) : 
-	#if lang not in goog_langs : continue
+	if lang not in goog_langs : continue
 	x1 = [d[0] for d in data[lang]]
 	x2 = [d[1] for d in data[lang]]
 	n1, (smin1, smax1), m1, v1, ss1, sk1 = stats.describe(x1)

### 2013-11-18 code/src/20130905/paper-rewrite/figures/code/turker_numhit_dist.py

@@ -8,7 +8,8 @@ import matplotlib.pyplot as plt
 data = []
 
 for line in csv.DictReader(open('results/data/quality.turkers.txt'), delimiter='\t') : 
-	if line['approved'] == 'True': data.append((line['lang'], line['worker'], int(line['num_hits'])))
+#	if line['status'] == 'True': data.append((line['lang'], line['worker'], int(line['num_hits'])))
+	data.append((line['lang'], line['worker'], int(line['num_hits'])))
 
 
 langs = [d[0] for d in sorted(data, key = operator.itemgetter(2), reverse=True)]
@@ -49,9 +50,11 @@ for i in range(bins) :
 		last = [last[i] + p for i,p in enumerate(pcnt)]
 
 plt.ylim(0,1)
+plt.xlim(0,len(all_data))
 plt.ylabel('Proportion of HITs contributed', rotation=90)
 plt.yticks(rotation=90)
 plt.xticks(np.arange(len(all_data))+w/2., ['%s %d'%(e[0],lang_counts[e[0]]) for e in all_data], rotation=90, size='small') 
+print [e[0] for e in sorted([(e[0],lang_counts[e[0]]) for e in all_data], key=operator.itemgetter(1),reverse=True)]
 #plt.legend(tuple(key), ('10 turkers with the most HITs', 'Next 10 turkers', 'Next 10 turkers', 'Next 10 turkers', 'Remaining turkers'), loc='lower right')
 plt.show()
 

### 2013-11-18 code/src/20130905/paper-rewrite/regenerate.sh

@@ -4,7 +4,7 @@
 #python scripts/googtrans-over-turkers.py > results/data/googmatch.turkers.txt
 #python scripts/googtrans-over-langs.py > results/data/googmatch.langs.txt
 
-#python scripts/quality-over-assigns-syns.py > results/data/quality.assigns.txt 
+python scripts/quality-over-assigns-syns.py > results/data/quality.assigns.txt 
 python scripts/quality-over-turkers-syns.py > results/data/quality.turkers.txt 
 python scripts/quality-over-langs-syns.py > results/data/quality.langs.txt 
 

### 2013-11-18 code/src/20130905/paper-rewrite/scripts/settings.py

@@ -1,7 +1,7 @@
 
 settings = {
 
-	'google_overlap_cutoff' : 0.60,
+	'google_overlap_cutoff' : 0.70,
 	'synonym_control_cutoff' : 0.70,
 	'use_workers_with_langcounts' : ['0', '1', 'many'],
 	'avg_lang_over' : 'turkers', 

### 2013-11-25 writeup/reviewer-response/reviewer-response.tex
updates to reviewer response

\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage[fit]{truncate}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
%\usepackage{caption}
\usepackage[font=small]{caption}
\usepackage{multirow}
\usepackage{dblfloatfix}
\usepackage{float}
\usepackage{subfloat}
\usepackage{subcaption}

\setlength\titlebox{5cm}    % Expanding the titlebox
\setlength{\abovecaptionskip}{1pt plus 1pt minus 1pt} % Chosen fairly arbitrarily
\setlength{\belowcaptionskip}{1pt plus 1pt minus 1pt} % Chosen fairly arbitrarily

\newcommand{\affliationPenn}{\ensuremath{{}^\text{1}}}
\newcommand{\affliationJHU}{\ensuremath{{}^\text{2}}}

\title{The Language Demographics of  Amazon Mechanical Turk : Response  to Reviewers}

\author{Ellie Pavlick\affliationPenn \ \ \ \ \ Ann Irvine\affliationJHU  \ \ \ \ \ Dmitry Kachaev\affliationJHU  \ \ \ \ \  Chris Callison-Burch\affliationPenn$^{,}$\affliationJHU \\
\affliationPenn Computer and Information Science Department, University of Pennsylvania \\
\affliationJHU Human Language Technology Center of Excellence, Johns Hopkins University \\
  }

% Anonymized for submission
\author{}

\date{}

\begin{document}
\maketitle

%\begin{figure}
%\centering
%\begin{subfigure}[b]{1\linewidth}
%\includegraphics[width=\textwidth]{figures/turker-googmatch-distribution.png}
%\caption{Individual turker overlap with Google Translate. We remove the 500 workers with the highest overlap (shaded region on the left) from our analysis, as it is reasonable to assume these workers are cheating by submitting translations from Google. We believe the workers with no overlap (shaded region on the right) are also likely to be cheating, e.g. by submitting random text, and we target these workers through our embedded quality controls.}                
%\label{dist}
%\end{subfigure}
%\begin{subfigure}[b]{1\linewidth}
%\includegraphics[width=\textwidth]{figures/google-cdf-googlangs.png}
%\caption{Cumulative distribution of overlap with Google translate for workers and translations. We see that eliminating all workers with \textgreater 70\% overlap with google translate still preserves 90\% of translations and \textgreater 90\% of workers.}
%\label{cdf}
%\end{subfigure}
%\caption{}\label{cheaters}
%\end{figure}

\section{Use of Google Translate : Editor and all reviewers}

The primary concern across reviewers was the high amount of overlap between workers' translations and translations available through online resources, i.e. Google Translate. The editor summarized : 
\begin{quote}
All reviewers had issues with the amount of cheating taking place among Turkers. It would be useful to quantify/detect this and remove such participants from your results.
\end{quote}

\begin{figure}[ht]
\includegraphics[width=\linewidth]{figures/turker-googmatch-distribution.png}
\caption{Individual turker overlap with Google Translate. We remove the 500 workers with the highest overlap (shaded region on left) from our analysis. Workers with no overlap (on right) are also likely to be cheating, e.g. by submitting random text. We target these workers through our embedded controls.}                
\label{dist}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{figures/google-cdf-googlangs.png}
\caption{Cumulative distribution of overlap with Google translate for workers and translations. Eliminating all workers with \textgreater 70\% overlap with google translate still preserves 90\% of translations and \textgreater 90\% of workers.}
\label{cdf}
\end{figure}

We took at closer look at the amount of overlap with Google translate in our collected translations in order to address this issue. We found that while overall overlap is high, it is not consistantly high across all turkers. Figure \ref{dist} shows that while a small number of turkers have a very high amount of overlap with Google (near 80\%) the majority overlap less than half of the time.

%As Reviewer E noted :

%\begin{quote}
%..it is quite possible that a fluent speaker of a language provides the same translation as Google Translate for a given word.  In other words, the performance results are inconclusive.
%\end{quote}

It seems likely that those with very high overlap are cheating, but it is also reasonable to assume that honest turkers will overlap with Google with some regularity. We therefore divide the workers into three groups : those with very high overlap with Google (likely cheating by using Google to translate words), those with reasonable overlap, and those with no overlap (likely cheating by other means, e.g. submitting random text). Our controls are designed to identify workers that fall into the third group (those who are spamming or providing useless translations), but they will not effectively flag workers who are cheating with Google Translate.

We chose to remove the 500 turkers with the highest overlap with Google. This equates to removing all workers with greater than 70\% overlap. Figure \ref{cdf} shows that removing workers at or above the 70\% threshold retains 90\% of the collected translations and over 90\% of the workers.

\begin{figure}
\centering
\begin{subfigure}[b]{1\linewidth}
\includegraphics[width=\textwidth]{figures/quality-all.png}
\caption{All turkers.}                
\label{quality-all}
\end{subfigure}
\begin{subfigure}[b]{1\linewidth}
\includegraphics[width=\textwidth]{figures/quality-filtered.png}
\caption{Turkers with \textless 70\% overlap with Google Translate.}
\label{quality-filtered}
\end{subfigure}
\caption{Qualities for languages with \textgreater 50 turkers. Dark blue shows quality measured by perfect match on the control translation. Light blue indicates quality measured by included synonymous translations.}\label{qual}
\end{figure}

We have rerun the quality analysis in the paper, omitting workers with \textgreater 70\% overlap with Google Translate. The quality scores and rankings do not change substantially. For reference, figure \ref{qual} shows the quality scores for languages when computed over all Turkers as in the original draft of the paper (figure \ref{quality-all}) and computed over only Turkers with less than 70\% overlap with Google (figure \ref{quality-filtered}). In our new draft of the paper, we have omitted Tukers with more than 70\% overlap from all of our quality computations.

%\begin{figure}
%\includegraphics[width=\linewidth]{figures/quality-all.png}
%\caption{All turkers.}                
%\label{quality-all}
%\end{figure}
%\begin{figure}
%\includegraphics[width=\linewidth]{figures/quality-filtered.png}
%\caption{Turkers with \textless 70\% overlap with Google Translate.}
%\label{quality-filtered}
%\caption{Qualities for languages with \textgreater 50 turkers. Dark blue shows quality measured by perfect match on the control translation. Light blue indicates quality measured by included synonymous translations.}\label{qual}
%\end{figure}

\section{Robustness of results to removing few big players: Editor and all reviewers}

The editor and reviewer G highlighted the possibility that the quality results are due to a few large players, and may not be robust if the experiment were rerun with a different group of workers : 
\begin{quote}
Provide additional analysis showing that translation accuracy is not due to a few individuals who happened to do most of your tasks.
\end{quote}

We agree that this is a valid concern since many languages followed the pattern of having a small number of very active Turkers complete the majority of assignments. We account of this by reporting qualities of each language as an average over Turker qualities, rather than over assignment qualities. By this method, each Turker contributes equally to the language's average quality, regardless of the number of HITs that that Turker submitted. Section 4 of the paper has been updated to reflect this change. Figure \ref{qual_dots} shows the quality scores for languages computed over assignments and over Turkers, and the change in each when the 10 most active Turkers in each language are removed. We can see that the per-Turker quality measure is robust to the exclusion of these highly-contributing Turkers.

For completeness, we have also updated our reported quality scores in the paper to include confidence intervals and p-values, where appropriate. We hope this helps to reduce concern about the robustness of these measures.

%\begin{figure}
%\includegraphics[height=1\linewidth, angle=270]{figures/turker-hit-contributions.png}
%\caption{Contributions of individual turkers to the overall number of HITs in each language. The dark blue bar represents the proportion of total HITs which were completed by the 10 highest-contributing turkers. The next darkest bar represents the next 10 highest-contributing turkers, and likewise for the thrid and forth darkest. The final bar represents the remaining turkers which were not one of the top 40 contributors.}
%\label{num./hits}
%\end{figure}

\begin{figure}
\includegraphics[height=1\linewidth, angle=270]{figures/quality_compare.png}
\caption{Quality scores of languages computed as averages over assignments (red) and over turkers (blue). Light blue and light red dots reflect the quality scores that result when the 10 turkers with who contributed the highest number of HITs are removed. We see that while the quality calculated over assignments responds noticeably to the exclusion of these highly active turkers, the quality calculated over turkers is quite robust to the change.}
\label{qual_dots}
\end{figure}

\section{Extrinsic evalutation of mturk data for SMT: Editor and all reviewers}

All the reviewers expressed desire for further evidence of the usefulness of the Turker-provided translations for statistical machine translation, and the possibility of extending the demonstrated methods to multiple word translations. The editor requests :

\begin{quote}
It would be interesting to show that the proposed approach brings an advantage over current SMT technology, i.e., improves lexical translations for an existing SMT system....It would also be interesting to assess whether your results carry over to multiple words and/or sentences. 
\end{quote}

To address these concerns, we incorporate previous work from a workshop publication from our colleague. The workshop publication will be cited appropriately in the final version of the paper, but we omit the citation now so as not to de-anonymize the submission.

In this work, we collect full-sentence translations for six Indian languages which are well-represented on MTurk but for which there are currently no professionally-translated corpora available. We use the collected sentences to train and evaluate an SMT system, and show that the systems achieve decent performance. Furthermore, we add the collected single-word dictionaries to the training of these systems, and show that this produces measurable improvement in performance. Table \ref{dictionary_bleu} highlights these results. Please see sections 3 and 5 for a complete discussion of the data and experiments.

\begin{table}[t]
\centering
\begin{tabular}{l|ccc}
  language  & sentences &  dictionaries & Google \\
  \hline\hline
  Bengali    &  12.03 & 17.29 & 20.01 \\
  Hindi      & 16.19 & 18.10 & 25.21\\  
  Malayalam    &  6.65 & 9.72 & - \\      
  Tamil      & 8.08 & 9.66 & 13.51\\  
  Telugu     & 11.94 & 13.70 & 16.03\\  
  Urdu        & 19.22 & 21.98 & 23.09\\   
\end{tabular}
\caption{BLEU scores for translating into English using full sentence translations alone, and with the addition of single-word dictionaries. Scores are calculated using four reference translations and represent the mean of three MERT runs.}
\label{dictionary_bleu}
\end{table}

\section{Affect of time of day when HIT was posted: Reviewer F}

You raised an interesting question about the affect of time of day on Turker activity :

\begin{quote}
Did the authors take into account time of day, when the HIT was posted etc. to get a sense of whether one time of day is more optimal than others for each language? Does it matter at all?
\end{quote}
Figure \ref{time} shows the activity over a 24 hour day for 23 languages with greater than 100 turkers each. The plot shows that activity does vary across time zones, and suggests that choosing the release time intelligently based on the HIT language is likely to affect how quickly it is completed. We include this analysis here for the interest of the reviewer. We do not include it in the paper, however, as we do not feel it meaningfully changes the analysis presented there.

\begin{figure}
\centering
\includegraphics[height=.8\linewidth, angle=270]{figures/times.png}
\caption{Number of HITs completed during each hour of the day for languages with \textgreater 100 turkers.}
\label{time}
\end{figure}

\section{Changes in results if study continued over time: Reviewer B}

You asked : 
\begin{quote}
The authors ran an experiment over 3.5 months, but I wonder how the demographics change over time. Are there seasonal effects in the workforce? Has it changed over the past year? And more importantly, will it change substantially in the future? I'm somewhat skeptical that these demographics will remain constant, especially as Amazon rolls out changes to the service.
\end{quote}

While we agree that the questions posed are very interesting, we feel that answering these questions is the subject of another study. It is true that the current demongraphic makeup of MTurk workers is likely to shift, but we cannot currently take on the expense of conducting a long term study (the study presented here cost ~40K). We have updated the text of the paper to emphasize this limitation in our results by adding the following sentences to our Overview: 
\begin{quote}
While the demographics reported are likely to shift overtime, as Amazon expands its methods of payments and reaches new countries, the data presented provides a 
valuable snapshot of the current state of MTurk, and the methods used can be applied generally in future research.
\end{quote}

\section{Accuracy of Geolocation: Reviewers B and E}

We understand that geolocation is not perfect, which is why we propose the use of location data as just one of several criteria by which to identify likely qualified translators. The trends that we observe in our analysis, where we show that turkers geolocated within a region likely to speak the source language being translated tend to perform better on our controls, coincide with what we would expect to see if geolcation were accurate. Additionally, of the turkers who responded to our survey questions, 95\% of their self-reported locations agreed with our geolocations. These facts reassure us that, on average, the geolocation is performing sufficiently well.

\end{document}

### 2013-11-25 writeup/version1/paper.tex
updates to reviewer response

@@
 \usepackage{multirow}
+\usepackage{colortbl}
 \usepackage{dblfloatfix}
@@
 \usepackage{subfloat}
+\usepackage{booktabs}
 \usepackage{subcaption}
@@
 
+While the demographics reported are likely to shift overtime, as Amazon expands its methods of payments and reaches new countries, the data presented provides a valuable snapshot of the current state of MTurk, and the methods used can be applied generally in future research.
+
 %%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
@@
 \newcite{Zbib-etal:2012:NAACL} used crowdsourcing to construct a 1.5 million word parallel corpus of dialect Arabic and English, training a statistical machine translation system that produced higher quality translations of dialect Arabic than a system a trained on 100 times more Modern Standard Arabic-English parallel data.
-\textbf{??
+
+%\textbf{??
 \newcite{post-callisonburch-osborne:2012:WMT} used MTurk to build parallel corpora between English and six Indian languages, ranging from .5M to 1.5M words, and use them to demonstrate the efficacy of syntactic machine translation on verb-final languages.
 ??}
+
 Several researchers have examined cost optimization using active learning techniques to select the most useful sentences or fragments to translate \cite{ambati_naacl,bloodgood-callisonburch:2010:ACL,AmbatiThesis}.
@@
 
+%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
+\begin{figure}[h]
+\includegraphics[height=\linewidth,angle=270]{../final-figures/completetime}
+%\includegraphics[width=\linewidth]{../final-figures/completetime}
+\caption{Days to complete the translation HITs for 40 of the languages. Tick marks represent the completion of individual assignments. }
+\label{completion-time}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \paragraph{Gold standard translations} 
@@
 
+%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
+\begin{figure*}[h]
+\begin{center}
+\includegraphics[width=\linewidth]{../version1-figures/quality_bar.png}
+\caption{Translation quality for languages with at least 50 Turkers.
+The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms.
+Error bars show the 95\% confidence intervals for each language.}
+\label{hitlangqual} 
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Measuring Translation Quality}
 
-We calculate the quality of translations on the level of individual assignments and aggregated over workers and languages.
+For single word translations, we calculate the quality of translations on the level of individual assignments and aggregated over workers and languages.
 We define an assignment's quality as the proportion of controls that are correct in a given assignment, where correct means exactly correct or judged to be synonymous.
@@
 When a turker completed assignments in more than one language, their quality was computed separately for each language.
-
 Figure \ref{hitlangqual} shows the translation quality for languages with contributions from at least 50 workers.
-
-%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
-\begin{figure*}[h]
-\begin{center}
-\includegraphics[width=\linewidth]{../version1-figures/quality_bar.png}
-\caption{Translation quality for languages with at least 50 Turkers.
-The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms.
-Error bars show the 95\% confidence intervals for each language.}
-\label{hitlangqual} 
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-\centering
-\begin{subfigure}[b]{\linewidth}
-%\includegraphics[width=\textwidth]{../version1-figures/turker-googmatch-distribution.png}
-\includegraphics[width=\linewidth]{../version1-figures/turker-googmatch-distribution.png}
-\caption{Individual turker overlap with Google Translate.
-We remove the 500 workers with the highest overlap (shaded region on the left) from our analysis, as it is reasonable to assume these workers are cheating by submitting translations from Google.
-We believe the workers with no overlap (shaded region on the right) are also likely to be cheating, e.g.
-by submitting random text, and we target these workers through our embedded quality controls.}
-\label{dist}
-\end{subfigure}
-\begin{subfigure}[b]{\linewidth}
-%\includegraphics[width=\textwidth]{../version1-figures/google-cdf-googlangs.png}
-\includegraphics[width=\linewidth]{../version1-figures/google-cdf-googlangs.png}
-\caption{Cumulative distribution of overlap with Google translate for workers and translations.
-We see that eliminating all workers with \textgreater 70\% overlap with google translate still preserves 90\% of translations and \textgreater 90\% of workers.}
-\label{cdf}
-\end{subfigure}
-\caption{}\label{cheaters}
-\end{figure}
 
@@
 It seems likely that those with very high overlap are cheating, but it is also reasonable to assume that honest turkers will overlap with Google with some regularity.
-We therefore divide the workers into three groups : those with very high overlap with Google (likely cheating by using Google to translate words), those with reasonable overlap, and those with no overlap (likely cheating by other means, e.g.
+We divide the workers into three groups: those with very high overlap with Google (likely cheating by using Google to translate words), those with reasonable overlap, and those with no overlap (likely cheating by other means, e.g.
 submitting random text).
@@
 Quality scores reported throughout the paper reflect only translations from turkers whose overlap with Google falls below this 70\% threshold.
+
+\begin{figure}[h!]
+\centering
+\begin{subfigure}[b]{\linewidth}
+%\includegraphics[width=\textwidth]{../version1-figures/turker-googmatch-distribution.png}
+\includegraphics[width=\linewidth]{../version1-figures/turker-googmatch-distribution.png}
+\caption{Individual turker overlap with Google Translate.
+We remove the 500 workers with the highest overlap (shaded region on the left) from our analysis, as it is reasonable to assume these workers are cheating by submitting translations from Google.
+We believe the workers with no overlap (shaded region on the right) are also likely to be cheating, e.g.
+by submitting random text, and we target these workers through our embedded quality controls.}
+\label{dist}
+\end{subfigure}
+\begin{subfigure}[b]{\linewidth}
+%\includegraphics[width=\textwidth]{../version1-figures/google-cdf-googlangs.png}
+\includegraphics[width=\linewidth]{../version1-figures/google-cdf-googlangs.png}
+\caption{Cumulative distribution of overlap with Google translate for workers and translations.
+We see that eliminating all workers with \textgreater 70\% overlap with google translate still preserves 90\% of translations and \textgreater 90\% of workers.}
+\label{cdf}
+\end{subfigure}
+\caption{}\label{cheaters}
+\end{figure}
 
@@
 Some languages follow the pattern of having a smattering of assignments completed early, with the rate picking up later.
-
-%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
-\begin{figure*}[h]
-%\includegraphics[height=\linewidth,angle=270]{../final-figures/completetime}
-\includegraphics[width=\linewidth]{../final-figures/completetime}
-\caption{Days to complete the translation HITs for 40 of the languages. Tick marks represent the completion of individual assignments. }
-\label{completion-time}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 US workers alone reported 61 native languages.
-Overall, XXXX workers were located in a region likely to speak the language from which they were translating, and XXXX workers were located in countries considered out of region (meaning almost half of our 5,281 Turkers completed HITs in multiple languages).
+Overall, 4,297 workers were located in a region likely to speak the language from which they were translating, and 2,778 workers were located in countries considered out of region (meaning that about a third of our 5,281 Turkers completed HITs in multiple languages).
 
@@
 Given the number of Indian workers on Mechanical Turk, it is unsurprising that they represent majority of out-of-region workers.
-\textbf{For the languages that had more than 80 out of region workers (Malay, Amharic, Afrikaans, Icelandic, and Breton), Indian workers represented 90\% of the out of region workers for all of them aside from Amharic}.
+For the languages that had more than 75 out of region workers (Malay, Amharic, Icelandic, Sicilian, Wolof, and Breton), Indian workers represented at least 70\% of the out of region workers in each language.
 
-%When averaged across all languages, there is no significant quality difference between Turkers in region and out of region (0.504 and 0.496, respectively).
-However, within each language, the effect of location on quality varies greatly (Table \ref{region-summary}).
-
-% CCB - commented out this figure and paragraph.  I'm not sure that this figure adds any new information
-%
-%%%%%%%%%%%%%%%% ASSIGNMENT SCATTER %%%%%%%%%%%
-%\begin{figure*}[h]
-%\centering
-%\includegraphics[width=6in]{final-figures/assign-turk-scatter}
-%\caption{Number of assignments and number of Turkers for each language.
-Each dot represents a language.
-Figure includes only data from Turkers who reported only one native language consistantly across assignments, representing approx.
-3900 Turkers across 139,000 assignments.}
-%\label{ass-scatter}
-%\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%Figure \ref{ass-scatter} shows the volume of HITs completed and the number of workers participating for each language.
-While the bulk (19\%) of bilingual Turkers report English as their native language (see Figure \ref{lang-pie}), Mechanical Turk's capacity to support the Indian languages is apparent.
-Hindi, Tamil, and Malayalam are especially well represented in terms of number of active translators.
-
-%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.78\linewidth]{../final-figures/quality-scatter_joined-1column}
-%\end{center}
-
-%\caption{Estimated quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country. }
-%\label{quality-scatter}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%Figure \ref{quality-scatter} shows the number of assignments completed per country and per-country quality estimates for 4 scenerios: (a) overall, (b) for assignments completed in region, (c) for assignments completed out of region, and (d) for out of region assignments which contained low overlap with GoogleTranslate.
 \paragraph{Validation of controls} 
-Higher overlap with Google Translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.XXX), suggesting that some control translations have already been indexed by Google.
+Higher overlap with Google Translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.27), suggesting that some control translations have already been indexed by Google.
 We therefore investigated the validity of our use of Wikipedia inter-language links as gold standard translations.
@@
 We also see that adding the single-word dictionaries to the training set produces consistent performance gains, ranging from 1 to 5 BLEU points.
-Unfortunately, we do not have professionally translated data against which to compare the resulting performances.
-We do, however, report the BLEU scores achieved by Google Translate, where available.
-Given that the sizes of the data sets used to train Google's system are likely much greater than ours, we find these results encouraging as an indication of the potential of Turkers to provide high quality translations.
+Unfortunately, we do not have professionally translated data against which to compare the resulting performances, but we find the outcomes encouraging as an indication of the potential of Turkers to provide high quality translations.
 
@@
 \begin{tabular}{l|ccc}
-  language  & sentences &  dictionaries & Google \\
+  language  & sentences &  dictionaries\\
   \hline\hline
-  Bengali    &  12.03 & 17.29 & 20.01 \\
-  Hindi      & 16.19 & 18.10 & 25.21\\  
-  Malayalam    &  6.65 & 9.72 & - \\      
-  Tamil      & 8.08 & 9.66 & 13.51\\  
-  Telugu     & 11.94 & 13.70 & 16.03\\  
-  Urdu        & 19.22 & 21.98 & 23.09\\   
+  Bengali    &  12.03 & 17.29 \\
+  Hindi      & 16.19 & 18.10\\  
+  Malayalam    &  6.65 & 9.72\\      
+  Tamil      & 8.08 & 9.66\\  
+  Telugu     & 11.94 & 13.70\\  
+  Urdu        & 19.22 & 21.98\\   
 \end{tabular}
@@
 
-%\begin{table}[t]
-%\centering
-%\begin{tabular}{l|rr}
- % language  & SAMT &  Google \\
-  %\hline\hline
- % Bengali    & 13.53  &  20.01 \\
- % Hindi      & 17.29  & 25.21 \\  
- % Malayalam    & 14.28  & - \\      
- % Tamil      &  9.85  &  13.51 \\  
- % Telugu     & 12.61  & 16.03  \\  
- % Urdu        & 20.99  & 23.09 \\   
-%\end{tabular}
-%\caption{BLEU scores translating into English (four references).  BLEU scores are the mean of three MERT runs.}
-%\label{table:bleu}
-%\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+\centering
+\scriptsize
+\begin{tabular}{|p{.1\linewidth}|p{.1\linewidth}|p{.1\linewidth}|p{0.5\linewidth}|}
+\hline
+workers & quality & speed & \\\hline
+many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5} bs de es fr gu hr it kn mk ml ms nl pt ro sh sr te tl\\\cline{3-4}
+&&slow&af bg cy da fi ga gl he ht hu id ja lv no pa sk sv tr\\\cline{2-4}
+&low &fast&hi mr ta ur\\\cline{3-4}
+&&slow&am ar az bcl be bn bo bpy br ca ceb cs el eo is jv ka ko lb lt ne new nn pl ps ru scn sd so su sw uz vi wo zh\\\cline{1-4}
+few &high  &fast&--\\\cline{3-4}
+&&slow&an pms sl sq uk\\\cline{2-4}
+&low  &fast&--\\\cline{3-4}
+&&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}ast diq eu fa fy hy ilo io kk ku mg nap nds pam qu th tt wa war yo\\\hline
+\end{tabular}
+\caption{The green box shows the languages which we have found most supported by MTurk in terms of worker population, worker ability, and speed of completion.
+Languages have ``many'' workers if we recorded more than 50 active turkers.
+Languages are ``high'' quality if they average greater than 70\% accuracy on our controls.
+Languages are ``fast'' if all of our translations (approx.
+10,000 words each) were completed in within two weeks.}
+\label{recommendations}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Mechanical Turk gives researchers access to a diverse set of bilingual workers, making it a promising resource for researchers and developers of multilingual systems.
-Although unfiltered data can contain large amounts of noise, 
-a variety of techniques can be incorporated into crowdsourcing pipelines to ensure high quality data.
-Based on our study, we suggest restricting workers to countries that plausibly speak the foreign language of interest, and embedding gold standard controls where possible, rather than relying solely on self-reported language skills.
+Based on our study, we can confidently recommend 18 languages as good candidates for future research: Bosnian, German, Spanish, French, Gujarati, Croatian, Italian, Kannada, Macedonian, Malayalam, Malay, Dutch, Portuguese, Romanian, Serbo-Croatian, Serbian, Telugu, and Tagalog.
+These languages have large Turker populations who complete tasks quickly and accurately.
+Table \ref{recommendations} summarizes the strengths and weaknesses of all 100 languages covered in our study.
+
+Unfiltered data can contain large amounts of noise, a variety of techniques can be incorporated into crowdsourcing pipelines to ensure high quality data.
+As a best practice, we suggest restricting workers to countries that plausibly speak the foreign language of interest, and embedding gold standard controls where possible, rather than relying solely on self-reported language skills.
 

### 2013-11-25 code/src/20130905/paper-rewrite/figures/code/quality_bar.py

@@ -20,7 +20,7 @@ for row in csv.DictReader(open('results/data/quality.turkers.txt'), delimiter = 
 graph_data = [] 
 t = 0 
 for lang in sorted(data.keys()) : 
-	if lang not in goog_langs : continue
+#	if lang not in goog_langs : continue
 	x1 = [d[0] for d in data[lang]]
 	x2 = [d[1] for d in data[lang]]
 	n1, (smin1, smax1), m1, v1, ss1, sk1 = stats.describe(x1)
@@ -33,6 +33,8 @@ for lang in sorted(data.keys()) :
 
 print "total turkers,", t
 
+print '\n'.join([d[3] for d in graph_data])
+exit(0)
 graph_data = sorted(graph_data, key=operator.itemgetter(1), reverse=True) 
 
 w = .5

### 2013-11-26 writeup/initial submission/paper.tex
renamed folders

--- 2013-03-31 writeup/paper.tex
@@
 %%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
-\begin{figure*}[h]
+\begin{figure}
 \begin{center}
-\includegraphics[width=0.8\linewidth]{final-figures/quality-scatter_joined}
+\includegraphics[width=0.78\linewidth]{final-figures/quality-scatter_joined-1column}
 \end{center}
 
-\caption{Estimated quality of translations by country.
-Each circle is a country, sized proportional to the number of active Turkers from that country.
-Quality is calculated as the average number of control words which were correct translations of the source word, where ”correct” means that the provided translation was judged to be synonymous with the known translation by workers in a second-pass HIT.
-Figure represents data from approx.
-295,000 assignments for which geolocation was known.}
+\caption{Estimated quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country. }
 \label{quality-scatter}
-\end{figure*}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-11-26 writeup/revision 1/paper.tex
renamed folders

--- 2013-11-25 writeup/version1/paper.tex
@@
 Rather than posting a one-off survey, we posted paid tasks consisting of 1,000 assignments to translate a total of 10,000 words in each of 100 languages.
-Our study ran for several weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilingual workers would complete it.
+Our study ran for several months, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilingual workers would complete it.
 Our study was useful both to create bilingual dictionaries and to act as census of the bilingual speakers on MTurk.
@@
 \centering
-\includegraphics[width=\linewidth]{../version1-figures/map.png}
+\includegraphics[width=\linewidth]{figures/map.png}
 \caption{The number of workers per country.
@@
 \begin{figure}[h]
-\includegraphics[height=\linewidth,angle=270]{../final-figures/completetime}
-%\includegraphics[width=\linewidth]{../final-figures/completetime}
+\includegraphics[height=\linewidth,angle=270]{figures/completetime}
+%\includegraphics[width=\linewidth]{figures/completetime}
 \caption{Days to complete the translation HITs for 40 of the languages. Tick marks represent the completion of individual assignments. }
@@
   \centering
-  \includegraphics[width=\textwidth]{../version1-figures/tamil.png}
+  \includegraphics[width=\textwidth]{figures/tamil.png}
   \begin{tabular}{l}
@@
 \begin{center}
-\includegraphics[width=\linewidth]{../version1-figures/quality_bar.png}
+\includegraphics[width=\linewidth]{figures/quality_bar.png}
 \caption{Translation quality for languages with at least 50 Turkers.
@@
 \end{align}	
-When a turker completed assignments in more than one language, their quality was computed separately for each language.
+When a Turker completed assignments in more than one language, their quality was computed separately for each language.
 Figure \ref{hitlangqual} shows the translation quality for languages with contributions from at least 50 workers.
@@
 
-We quantified each turker's overlap with the Google translations so that we could identify and remove workers that appeared to be misusing Google Translate.
+We quantified each Turker's overlap with the Google translations so that we could identify and remove workers that appeared to be misusing Google Translate.
 We used Google to translate all 10,000 words for the 51 foreign languages that Google Translate covered at the time of the study.
@@
 %\begin{center}
-%\includegraphics[width=1\linewidth]{../version1-figures/google_bar.png}
+%\includegraphics[width=1\linewidth]{figures/google_bar.png}
 %\caption{Average proportion of Turker translations matching GoogleTranslate, per assignment. Overall average overlap was 0.37.}
@@
 
-We found that while overall overlap is high (the average turker's overlap was 41\%), it is not consistently high across all turkers.
-Figure \ref{dist} shows that while a small number of turkers have a very high amount of overlap with Google (near 80\%) the majority overlap less than half of the time.
-It seems likely that those with very high overlap are cheating, but it is also reasonable to assume that honest turkers will overlap with Google with some regularity.
+We found that while overall overlap is high (the average Turker's overlap was 41\%), it is not consistently high across all Turkers.
+Figure \ref{dist} shows that while a small number of Turkers have a very high amount of overlap with Google (near 80\%) the majority overlap less than half of the time.
+It seems likely that those with very high overlap are cheating, but it is also reasonable to assume that honest Turkers will overlap with Google with some regularity.
 We divide the workers into three groups: those with very high overlap with Google (likely cheating by using Google to translate words), those with reasonable overlap, and those with no overlap (likely cheating by other means, e.g.
@@
 Our controls are designed to identify workers that fall into the third group (those who are spamming or providing useless translations), but they will not effectively flag workers who are cheating with Google Translate.
-We therefore remove the 500 turkers with the highest overlap with Google.
+We therefore remove the 500 Turkers with the highest overlap with Google.
 This equates to removing all workers with greater than 70\% overlap.
@@
 
-Quality scores reported throughout the paper reflect only translations from turkers whose overlap with Google falls below this 70\% threshold.
+Quality scores reported throughout the paper reflect only translations from Turkers whose overlap with Google falls below this 70\% threshold.
 
@@
 \begin{subfigure}[b]{\linewidth}
-%\includegraphics[width=\textwidth]{../version1-figures/turker-googmatch-distribution.png}
-\includegraphics[width=\linewidth]{../version1-figures/turker-googmatch-distribution.png}
-\caption{Individual turker overlap with Google Translate.
+%\includegraphics[width=\textwidth]{figures/turker-googmatch-distribution.png}
+\includegraphics[width=\linewidth]{figures/turker-googmatch-distribution.png}
+\caption{Individual Turker overlap with Google Translate.
 We remove the 500 workers with the highest overlap (shaded region on the left) from our analysis, as it is reasonable to assume these workers are cheating by submitting translations from Google.
@@
 \begin{subfigure}[b]{\linewidth}
-%\includegraphics[width=\textwidth]{../version1-figures/google-cdf-googlangs.png}
-\includegraphics[width=\linewidth]{../version1-figures/google-cdf-googlangs.png}
+%\includegraphics[width=\textwidth]{figures/google-cdf-googlangs.png}
+\includegraphics[width=\linewidth]{figures/google-cdf-googlangs.png}
 \caption{Cumulative distribution of overlap with Google translate for workers and translations.
@@
 \caption{The green box shows the languages which we have found most supported by MTurk in terms of worker population, worker ability, and speed of completion.
-Languages have ``many'' workers if we recorded more than 50 active turkers.
+Languages have ``many'' workers if we recorded more than 50 active Turkers.
 Languages are ``high'' quality if they average greater than 70\% accuracy on our controls.

### 2013-11-26 writeup/revision 1/reviewer-response/acl2012.tex
renamed folders

%
% File acl2012.tex
%
% Contact: Maggie Li (cswjli@comp.polyu.edu.hk), Michael White (mwhite@ling.osu.edu)
%%
%% Based on the style files for ACL2008 by Joakim Nivre and Noah Smith
%% and that of ACL2010 by Jing-Shin Chang and Philipp Koehn

\documentclass[11pt]{article}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

\title{Instructions for ACL2012 Proceedings}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  This document contains the instructions for preparing a camera-ready manuscript for the proceedings of ACL2012. The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like. These instructions should be used for both papers submitted for review and for final versions of accepted papers. Authors are asked to conform to all the directions reported in this document.
\end{abstract}

\section{Credits}

This document has been adapted from the instructions for earlier ACL proceedings, including those for ACL-2008 by Johanna D. Moore, Simone Teufel, James Allan, and Sadaoki Furui, those for ACL-2005 by Hwee Tou Ng and Kemal Oflazer, those for ACL-2002 by Eugene Charniak and Dekang Lin, and earlier ACL and EACL formats. Those versions were written by several people, including John Chen, Henry S. Thompson and Donald Walker. Additional elements were taken from the formatting instructions of the {\em International Joint Conference on Artificial Intelligence}.

\section{Introduction}

The following instructions are directed to authors of papers submitted to ACL2012 or accepted for publication in its proceedings. All authors are required to adhere to these specifications. Authors are required to provide a Portable Document Format (PDF)
% das: removed reference to PostScript
% and PostScript
version of their papers. \textbf{The proceedings will be printed on
  US-Letter paper}. Authors from countries in which access to
word-processing systems is limited should contact the publication
chairs Maggie Li ({\tt cswjli@comp.polyu.edu.hk}) and Michael White
({\tt mwhite@ling.osu.edu}) as soon as possible.

\section{General Instructions}

Manuscripts must be in two-column format. Exceptions to the two-column format include the title, 
authors' names and complete addresses, which must be centered at the top of the first page, 
and any full-width figures or tables (see the guidelines in Subsection~\ref{ssec:first}). {\bf Type single-spaced}. 
Start all pages directly under the top margin. See the guide-lines later regarding formatting the first page. Do not number the pages.

\subsection{Electronically-available resources}

ACL2012 provides this description in \LaTeX2e (acl2012.tex) and PDF format (acl2012.pdf), along with the LATEX2e style file used to format it (acl2012.sty) and an ACL bibliography style (acl.bst). These files are all available at \url{http://www.acl2012.org}.  A Microsoft Word template file (acl2012.dot) is also available at the same URL. We strongly recommend the use of these style files, which have been appropriately tailored for the ACL2012 proceedings. If you have an option, we recommend that you use the \LaTeX2e version. \textbf{If you will be using the Microsoft Word template, we suggest that you anonymize your source file so that the pdf produced does not retain your identity.} This can be done by removing any personal information from your source
document properties.

\subsection{Format of Electronic Manuscript}
\label{sect:pdf}

For the production of the electronic manuscript you must use Adobe's
Portable Document Format (PDF). This format can be generated from
postscript files: on Linux/Unix systems, you can use {\tt ps2pdf} for this
purpose; under Microsoft Windows, you can use Adobe's Distiller, or
if you have {\tt cygwin} installed, you can use {\tt dvipdf} or
{\tt ps2pdf}.  Note
that some word processing programs generate PDF which may not include
all the necessary fonts (esp. tree diagrams, symbols). When you print
or create the PDF file, there is usually an option in your printer
setup to include none, all or just non-standard fonts.  Please make
sure that you select the option of including ALL the fonts.  {\em Before sending it, test your PDF by printing it from a computer different from the one where it was created}. Moreover,
some word processor may generate very large postscript/PDF files,
where each page is rendered as an image. Such images may reproduce
poorly.  In this case, try alternative ways to obtain the postscript
and/or PDF.  One way on some systems is to install a driver for a
postscript printer, send your document to the printer specifying
``Output to a file'', then convert the file to PDF.

Additionally, it is of utmost importance to specify the {\bf US-Letter format} (8.5in $\times$ 11in) when formatting the paper. When working with {\tt dvips}, for instance, one should specify {\tt -t letter}.

Print-outs of the PDF file on US-Letter paper should be identical to the
hardcopy version.  If you cannot meet the above requirements about the
production of your electronic submission, please contact the
publication chair above as soon as possible.

\subsection{Layout}
\label{ssec:layout}

Format manuscripts two columns to a page, in the manner these
instructions are formatted. The exact dimensions for a page on US-letter
paper are:

\begin{itemize}
\item Left and right margins: 1in
\item Top margin:1in
\item Bottom margin: 1in
\item Column width: 3.15in
\item Column height: 9in
\item Gap between columns: 0.2in
\end{itemize}

\noindent Papers should not be submitted on any other paper size. If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chair above as soon as possible.

\subsection{Fonts}

For reasons of uniformity, Adobe's {\bf Times Roman} font should be
used. In \LaTeX2e{} this is accomplished by putting

\begin{quote}
\begin{verbatim}
\usepackage{times}
\usepackage{latexsym}
\end{verbatim}
\end{quote}
in the preamble. If Times Roman is unavailable, use {\bf Computer
  Modern Roman} (\LaTeX2e{}'s default).  Note that the latter is about
  10\% less dense than Adobe's Times Roman font.

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|rl|}
\hline \bf Type of Text & \bf Font Size & \bf Style \\ \hline
paper title & 15 pt & bold \\
author names & 12 pt & bold \\
author affiliation & 12 pt & \\
the word ``Abstract'' & 12 pt & bold \\
section titles & 12 pt & bold \\
document text & 11 pt  &\\
captions & 11 pt & \\
abstract text & 10 pt & \\
bibliography & 10 pt & \\
footnotes & 9 pt & \\
\hline
\end{tabular}
\end{center}
\caption{\label{font-table} Font guide. }
\end{table}

\subsection{The First Page}
\label{ssec:first}

Center the title, author's name(s) and affiliation(s) across both
columns. Do not use footnotes for affiliations.  Do not include the
paper ID number assigned during the submission process.
Use the two-column format only when you begin the abstract.

{\bf Title}: Place the title centered at the top of the first page, in
a 15 point bold font.  (For a complete guide to font sizes and styles, see Table~\ref{font-table}.)
Long title should be typed on two lines without
a blank line intervening. Approximately, put the title at 1in from the
top of the page, followed by a blank line, then the author's names(s),
and the affiliation on the following line.  Do not use only initials
for given names (middle initials are allowed). Do not format surnames
in all capitals (e.g., ``Zhou,'' not ``ZHOU'').  The affiliation should
contain the author's complete address, and if possible an electronic
mail address. Leave about 0.75in between the affiliation and the body
of the first page. The title, author names and addresses should be completely identical to those entered to the electronic paper submission website in order to maintain the consistency of author information among all publications of the conference.

{\bf Abstract}: Type the abstract at the beginning of the first
column.  The width of the abstract text should be smaller than the
width of the columns for the text in the body of the paper by about
0.25in on each side.  Center the word {\bf Abstract} in a 12 point
bold font above the body of the abstract. The abstract should be a
concise summary of the general thesis and conclusions of the paper.
It should be no longer than 200 words. The abstract text should be in 10 point font.

{\bf Text}: Begin typing the main body of the text immediately after
the abstract, observing the two-column format as shown in
the present document. Do not include page numbers.

{\bf Indent} when starting a new paragraph. For reasons of uniformity,
use Adobe's {\bf Times Roman} fonts, with 11 points for text and
subsection headings, 12 points for section headings and 15 points for
the title.  If Times Roman is unavailable, use {\bf Computer Modern
  Roman} (\LaTeX2e's default; see section \ref{sect:pdf} above).
Note that the latter is about 10\% less dense than Adobe's Times Roman
font.

\subsection{Sections}

{\bf Headings}: Type and label section and subsection headings in the
style shown on the present document.  Use numbered sections (Arabic
numerals) in order to facilitate cross references. Number subsections
with the section number and the subsection number separated by a dot,
in Arabic numerals. Do not number subsubsections.

{\bf Citations}: Citations within the text appear
in parentheses as~\cite{Gusfield:97} or, if the author's name appears in
the text itself, as Gusfield~\shortcite{Gusfield:97}. Append lowercase letters to the year in cases of ambiguities. Treat double authors as in~\cite{Aho:72}, but write as in~\cite{Chandra:81} when more than two authors are involved. Collapse multiple citations as in~\cite{Gusfield:97,Aho:72}. Also refrain from using full citations as sentence constituents. We suggest that instead of
\begin{quote}
  ``\cite{Gusfield:97} showed that ...''
\end{quote}
you use
\begin{quote}
``Gusfield \shortcite{Gusfield:97}   showed that ...''
\end{quote}

If you are using the provided \LaTeX{} and Bib\TeX{} style files, you
can use the command \verb|\newcite| to get ``author (year)'' citations.

As reviewing will be double-blind, the submitted version of the papers should not include the
authors' names and affiliations. Furthermore, self-references that
reveal the author's identity, e.g.,
\begin{quote}
``We previously showed \cite{Gusfield:97} ...''
\end{quote}
should be avoided. Instead, use citations such as
\begin{quote}
``Gusfield \shortcite{Gusfield:97}
previously showed ... ''
\end{quote}

Please do not  use anonymous
citations and  do not include acknowledgements when submitting your papers. Papers that do not conform
to these requirements may be rejected without review.

\textbf{References}: Gather the full set of references together under
the heading {\bf References}; place the section before any Appendices,
unless they contain references. Arrange the references alphabetically
by first author, rather than by order of occurrence in the text.
Provide as complete a citation as possible, using a consistent format,
such as the one for {\em Computational Linguistics\/} or the one in the
{\em Publication Manual of the American
Psychological Association\/}~\cite{APA:83}.  Use of full names for
authors rather than initials is preferred.  A list of abbreviations
for common computer science journals can be found in the ACM
{\em Computing Reviews\/}~\cite{ACM:83}.

The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
American Psychological Association format, allowing regular citations,
short citations and multiple citations as described above.

{\bf Appendices}: Appendices, if any, directly follow the text and the
references (but see above).  Letter them in sequence and provide an
informative title: {\bf Appendix A. Title of Appendix}.

\textbf{Acknowledgment} sections should go as a last section immediately
before the references. Do not number the acknowledgement section.

\subsection{Footnotes}

{\bf Footnotes}: Put footnotes at the bottom of the page. They may
be numbered or referred to by asterisks or other
symbols.\footnote{This is how a footnote should appear.} Footnotes
should be separated from the text by a line.\footnote{Note the
line separating the footnotes from the text.}  Footnotes should be in 9 point font.

\subsection{Graphics}

{\bf Illustrations}: Place figures, tables, and photographs in the
paper near where they are first discussed, rather than at the end, if
possible.  Wide illustrations may run across both columns and should be placed at
the top of a page. Color illustrations are discouraged, unless you have verified that
they will be understandable when printed in black ink.

{\bf Captions}: Provide a caption for every illustration; number each one
sequentially in the form:  ``Figure 1. Caption of the Figure.'' ``Table 1.
Caption of the Table.''  Type the captions of the figures and
tables below the body, using 10 point text.

\section{Translation of non-English Terms}

It is also advised to supplement non-English characters and terms
with appropriate transliterations and/or translations
since not all readers understand all such characters and terms.

Inline transliteration or translation can be represented in
the order of: original-form transliteration ``translation''.

\section{Length of Submission}
\label{sec:length}

Long papers may consist of up to eight (8) pages of content and an
an unlimited number of reference pages, and short papers may consist
of up to four (4) pages of content and an unlimited number of reference pages.
Papers that do not conform to the specified length and
formatting requirements are subject to re-submission.

\section{Other Issues}

Those papers that had software and/or dataset submitted for the review process, should also submit it 
with the camera-ready paper. Besides, the software and/or dataset should not be anonymous.

Please note that the publications of ACL2012 will be publicly available at ACL Anthology 
(http://aclweb.org/anthology-new/) on July 2nd, 2012, one week before the start of the conference. 
Since some of the authors may have plans to file patents related to their papers in the conference, 
we are sending this reminder that July 2nd, 2012 may be considered to be the official publication date, 
instead of the opening day of the conference.

\section*{Acknowledgments}

Do not number the acknowledgment section. Do not include this section when submitting your paper for review.

\begin{thebibliography}{}

\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
Alfred~V. Aho and Jeffrey~D. Ullman.
\newblock 1972.
\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
\newblock Prentice-{Hall}, Englewood Cliffs, NJ.

\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
{American Psychological Association}.
\newblock 1983.
\newblock {\em Publications Manual}.
\newblock American Psychological Association, Washington, DC.

\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
{Association for Computing Machinery}.
\newblock 1983.
\newblock {\em Computing Reviews}, 24(11):503--512.

\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
\newblock 1981.
\newblock Alternation.
\newblock {\em Journal of the Association for Computing Machinery},
  28(1):114--133.

\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
Dan Gusfield.
\newblock 1997.
\newblock {\em Algorithms on Strings, Trees and Sequences}.
\newblock Cambridge University Press, Cambridge, UK.

\end{thebibliography}

\end{document}

### 2013-11-27 writeup/revision 1/reviewer-response/reviewer-response.tex
pdfs and other minor edits

--- 2013-11-25 writeup/reviewer-response/reviewer-response.tex
@@
 \begin{figure}[ht]
-\includegraphics[width=\linewidth]{figures/turker-googmatch-distribution.png}
+\includegraphics[width=\linewidth]{figures/turker-googmatch-distribution.pdf}
 \caption{Individual turker overlap with Google Translate.
@@
 \centering
-\includegraphics[width=\linewidth]{figures/google-cdf-googlangs.png}
+\includegraphics[width=\linewidth]{figures/google-cdf-googlangs.pdf}
 \caption{Cumulative distribution of overlap with Google translate for workers and translations.
@@
 \begin{subfigure}[b]{1\linewidth}
-\includegraphics[width=\textwidth]{figures/quality-all.png}
+\includegraphics[width=\textwidth]{figures/quality-all.pdf}
 \caption{All turkers.}                
@@
 \begin{subfigure}[b]{1\linewidth}
-\includegraphics[width=\textwidth]{figures/quality-filtered.png}
+\includegraphics[width=\textwidth]{figures/quality-filtered.pdf}
 \caption{Turkers with \textless 70\% overlap with Google Translate.}
@@
 \begin{figure}
-\includegraphics[height=1\linewidth, angle=270]{figures/quality_compare.png}
+\includegraphics[width=1\linewidth]{figures/quality_compare.pdf}
 \caption{Quality scores of languages computed as averages over assignments (red) and over turkers (blue).
@@
 Table \ref{dictionary_bleu} highlights these results.
-Please see sections 3 and 5 for a complete discussion of the data and experiments.
+Please see sections 3 and 5 of the revised paper for a complete discussion of the data and experiments.
 
@@
 \centering
-\begin{tabular}{l|ccc}
-  language  & sentences &  dictionaries & Google \\
+\begin{tabular}{l|cc}
+  language  & sentences &  dictionaries \\
   \hline\hline
-  Bengali    &  12.03 & 17.29 & 20.01 \\
-  Hindi      & 16.19 & 18.10 & 25.21\\  
-  Malayalam    &  6.65 & 9.72 & - \\      
-  Tamil      & 8.08 & 9.66 & 13.51\\  
-  Telugu     & 11.94 & 13.70 & 16.03\\  
-  Urdu        & 19.22 & 21.98 & 23.09\\   
+  Bengali    &  12.03 & 17.29\\
+  Hindi      & 16.19 & 18.10\\  
+  Malayalam    &  6.65 & 9.72\\      
+  Tamil      & 8.08 & 9.66 \\  
+  Telugu     & 11.94 & 13.70\\  
+  Urdu        & 19.22 & 21.98\\   
 \end{tabular}

### 2013-11-27 writeup/revision 1/paper.tex
pdfs and other minor edits

@@
 %Language&\# Turkers\\
-\hline
 English & 689 & Tamil & 253 & Malayalam & 219 \\
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/tamil.png}
+  \includegraphics[width=\textwidth]{figures/tamil.pdf}
   \begin{tabular}{l}
@@
 \begin{center}
-\includegraphics[width=\linewidth]{figures/quality_bar.png}
+\includegraphics[width=\linewidth]{figures/quality_bar.pdf}
 \caption{Translation quality for languages with at least 50 Turkers.
@@
 %\includegraphics[width=\textwidth]{figures/turker-googmatch-distribution.png}
-\includegraphics[width=\linewidth]{figures/turker-googmatch-distribution.png}
+\includegraphics[width=\linewidth]{figures/turker-googmatch-distribution.pdf}
 \caption{Individual Turker overlap with Google Translate.
@@
 %\includegraphics[width=\textwidth]{figures/google-cdf-googlangs.png}
-\includegraphics[width=\linewidth]{figures/google-cdf-googlangs.png}
+\includegraphics[width=\linewidth]{figures/google-cdf-googlangs.pdf}
 \caption{Cumulative distribution of overlap with Google translate for workers and translations.
@@
 \hline\hline
-Hindi & 0.635 (296) & \textbf{0.695} (7) & India (284) Uae (5) Uk (3)  & Saudiarabia (2) Russia (1) Oman (1) \\
-Tamil & \textbf{0.653} (273) * & 0.250 (2) & India (266) Unitedstates (3) Canada (2)  & Tunisia (1) Egypt (1)  \\
-Malayalam & 0.764 (234) & \textbf{0.827} (2) & India (223) Uae (6) Unitedstates (3)  & Saudiarabia (1) Maldives (1) \\
-Spanish & 0.814 (191) & \textbf{0.837} (18) & Unitedstates (122) Mexico (16) Spain (14)  & India (15) Newzealand (1) Brazil (1) \\
-French & 0.750 (170) & \textbf{0.816} (11) & India (62) Unitedstates (45) France (23)  & Greece (2) Netherlands (1) Japan (1) \\
-Chinese & \textbf{0.601} (116) & 0.552 (21) & Unitedstates (75) Singapore (13) China (9)  & Hongkong (6) Australia (3) Germany (2)  \\
-German & \textbf{0.825} (91) & 0.768 (41) & Germany (48) Unitedstates (25) Austria (7)  & India (34) Netherlands (1) Greece (1)  \\
-Italian & \textbf{0.863} (90) & 0.796 (42) & Italy (42) Unitedstates (29) Romania (7)  & India (33) Ireland (2) Spain (2)  \\
-Amharic & \textbf{0.136} (16) * & 0.009 (99) & Unitedstates (14) Ethiopia (2)  & India (70) Georgia (9) Macedonia (5)  \\
+Hindi & 0.635 (296) & \textbf{0.695} (7) & India (284) UAE (5) UK (3)  & Saudi Arabia (2) Russia (1) Oman (1) \\
+Tamil & \textbf{0.653} (273) * & 0.250 (2) & India (266) US (3) Canada (2)  & Tunisia (1) Egypt (1)  \\
+Malayalam & 0.764 (234) & \textbf{0.827} (2) & India (223) UAE (6) US (3)  & Saudi Arabia (1) Maldives (1) \\
+Spanish & 0.814 (191) & \textbf{0.837} (18) & US (122) Mexico (16) Spain (14)  & India (15) Newzealand (1) Brazil (1) \\
+French & 0.750 (170) & \textbf{0.816} (11) & India (62) US (45) France (23)  & Greece (2) Netherlands (1) Japan (1) \\
+Chinese & \textbf{0.601} (116) & 0.552 (21) & US (75) Singapore (13) China (9)  & Hongkong (6) Australia (3) Germany (2)  \\
+German & \textbf{0.825} (91) & 0.768 (41) & Germany (48) US (25) Austria (7)  & India (34) Netherlands (1) Greece (1)  \\
+Italian & \textbf{0.863} (90) & 0.796 (42) & Italy (42) US (29) Romania (7)  & India (33) Ireland (2) Spain (2)  \\
+Amharic & \textbf{0.136} (16) * & 0.009 (99) & US (14) Ethiopia (2)  & India (70) Georgia (9) Macedonia (5)  \\
 Kannada & 0.704 (105) & NA (0) & India (105)  & \\
-Arabic & \textbf{0.741} (60) * & 0.604 (45) & Egypt (19) Jordan (16) Morocco (9)  & Unitedstates (19) India (11) Canada (3)  \\
-Sindhi & \textbf{0.190} (96) & 0.062 (9) & India (58) Pakistan (37) Unitedstates (1)  & Macedonia (4) Georgia (2) Indonesia (2)  \\
-Portuguese & 0.869 (101) & \textbf{0.963} (3) & Brazil (44) Portugal (31) Unitedstates (15)  & Romania (1) Japan (1) Israel (1) \\
-Turkish & 0.759 (76) & \textbf{0.804} (27) & Turkey (38) Unitedstates (18) Macedonia (8)  & India (19) Pakistan (4) Taiwan (1) \\
-Telugu & \textbf{0.799} (102) & 0.500 (1) & India (98) Unitedstates (3) Uae (1)  & Saudiarabia (1)  \\
-Irish & \textbf{0.742} (54) & 0.709 (47) & Unitedstates (39) Ireland (13) Uk (2)  & India (36) Romania (5) Macedonia (2)  \\
-Swedish & \textbf{0.734} (54) & 0.711 (45) & Unitedstates (25) Sweden (22) Finland (3)  & India (23) Macedonia (6) Croatia (2)  \\
-Czech & \textbf{0.706} (45) & 0.612 (50) & Unitedstates (17) Czechrepublic (14) Serbia (5)  & Macedonia (22) India (10) Uk (5)  \\
-Russian & \textbf{0.146} (67) & 0.119 (27) & Unitedstates (36) Moldova (7) Russia (6)  & India (14) Macedonia (4) Uk (3)  \\
-Breton & 0.167 (3) & \textbf{0.178} (89) & Unitedstates (3)  & India (83) Macedonia (2) China (1) \\
-
+Arabic & \textbf{0.741} (60) * & 0.604 (45) & Egypt (19) Jordan (16) Morocco (9)  & US (19) India (11) Canada (3)  \\
+Sindhi & \textbf{0.190} (96) & 0.062 (9) & India (58) Pakistan (37) US (1)  & Macedonia (4) Georgia (2) Indonesia (2)  \\
+Portuguese & 0.869 (101) & \textbf{0.963} (3) & Brazil (44) Portugal (31) US (15)  & Romania (1) Japan (1) Israel (1) \\
+Turkish & 0.759 (76) & \textbf{0.804} (27) & Turkey (38) US (18) Macedonia (8)  & India (19) Pakistan (4) Taiwan (1) \\
+Telugu & \textbf{0.799} (102) & 0.500 (1) & India (98) US (3) UAE (1)  & Saudi Arabia (1)  \\
+Irish & \textbf{0.742} (54) & 0.709 (47) & US (39) Ireland (13) UK (2)  & India (36) Romania (5) Macedonia (2)  \\
+Swedish & \textbf{0.734} (54) & 0.711 (45) & US (25) Sweden (22) Finland (3)  & India (23) Macedonia (6) Croatia (2)  \\
+Czech & \textbf{0.706} (45) & 0.612 (50) & US (17) Czech Republic (14) Serbia (5)  & Macedonia (22) India (10) UK (5)  \\
+Russian & \textbf{0.146} (67) & 0.119 (27) & US (36) Moldova (7) Russia (6)  & India (14) Macedonia (4) UK (3)  \\
+Breton & 0.167 (3) & \textbf{0.178} (89) & US (3)  & India (83) Macedonia (2) China (1) \\
 \hline\hline
@@
 workers & quality & speed & \\\hline
-many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5} bs de es fr gu hr it kn mk ml ms nl pt ro sh sr te tl\\\cline{3-4}
-&&slow&af bg cy da fi ga gl he ht hu id ja lv no pa sk sv tr\\\cline{2-4}
-&low &fast&hi mr ta ur\\\cline{3-4}
-&&slow&am ar az bcl be bn bo bpy br ca ceb cs el eo is jv ka ko lb lt ne new nn pl ps ru scn sd so su sw uz vi wo zh\\\cline{1-4}
-few &high  &fast&--\\\cline{3-4}
-&&slow&an pms sl sq uk\\\cline{2-4}
+many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5} de es fr gu it kn ml nl pt ro sr te tl \\\cline{3-4}
+&&slow& ar ga he pa sv tr\\\cline{2-4}
+&low &fast& hi mr ta ur \\\cline{3-4}
+&&slow&bn bo bpy ceb ne new pl ru sd zh\\\cline{1-4}
+few &high  &fast& bs hr mk ms sh\\\cline{3-4}
+&&slow&af an ast bcl be bg cs da el eu fi fy gl ht hu id ilo is ja jv kk ko lt mg nds no pam scn sk sl sq th uk uz war yo\\\cline{2-4}
 &low  &fast&--\\\cline{3-4}
-&&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}ast diq eu fa fy hy ilo io kk ku mg nap nds pam qu th tt wa war yo\\\hline
+&&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}am az br ca cy hy ka lb lv nap nn pms ps so su sw tt vi wa \\\hline
+none&low&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}diq eo fa io ku qu wo \\\hline
 \end{tabular}
 \caption{The green box shows the languages which we have found most supported by MTurk in terms of worker population, worker ability, and speed of completion.
-Languages have ``many'' workers if we recorded more than 50 active Turkers.
+Languages have ``many'' workers if we recorded more than 50 active in-region Turkers.
 Languages are ``high'' quality if they average greater than 70\% accuracy on our controls.
 Languages are ``fast'' if all of our translations (approx.
-10,000 words each) were completed in within two weeks.}
+10,000 words each) were completed within two weeks.}
 \label{recommendations}
@@
 Mechanical Turk gives researchers access to a diverse set of bilingual workers, making it a promising resource for researchers and developers of multilingual systems.
-Based on our study, we can confidently recommend 18 languages as good candidates for future research: Bosnian, German, Spanish, French, Gujarati, Croatian, Italian, Kannada, Macedonian, Malayalam, Malay, Dutch, Portuguese, Romanian, Serbo-Croatian, Serbian, Telugu, and Tagalog.
+Based on our study, we can confidently recommend 13 languages as good candidates for future research: German, Spanish, French, Gujarati, Italian, Kannada, Malayalam, Dutch, Portuguese, Romanian, Serbian, Telugu, and Tagalog.
 These languages have large Turker populations who complete tasks quickly and accurately.

### 2013-11-27 code/src/20130905/paper-rewrite/figures/code/goog-cheaters.py

@@ -65,5 +65,6 @@ plt.xlabel('% overlap with Google Translate')
 
 plt.legend(loc=4)
 
-plt.show()
+#plt.show()
+plt.savefig('google-cdf-googlangs.pdf')
 

### 2013-11-27 code/src/20130905/paper-rewrite/figures/code/quality_bar.py

@@ -19,30 +19,37 @@ for row in csv.DictReader(open('results/data/quality.turkers.txt'), delimiter = 
 	
 graph_data = [] 
 t = 0 
+name_order = ['pt', 'it', 'ms', 'sr', 'ro', 'es', 'de', 'af', 'te', 'sk', 'hr', 'sq', 'fi', 'tr', 'nl', 'id', 'he', 'gu', 'fr', 'da', 'sl', 'bg', 'ja', 'cy', 'gl', 'lv', 'sv', 'kn', 'az', 'hu', 'sw', 'lt', 'ko', 'eu', 'pl', 'ca', 'eo', 'ar', 'cs', 'ta', 'el', 'zh', 'vi', 'is', 'ur', 'ru']
 for lang in sorted(data.keys()) : 
-#	if lang not in goog_langs : continue
+	if lang not in goog_langs : continue
 	x1 = [d[0] for d in data[lang]]
 	x2 = [d[1] for d in data[lang]]
 	n1, (smin1, smax1), m1, v1, ss1, sk1 = stats.describe(x1)
 	n2, (smin2, smax2), m2, v2, ss2, sk2 = stats.describe(x2)
 	t += n1
-	if n1 < 50 : continue
-	graph_data.append((m1,m2,1.96*(math.sqrt(v2) / math.sqrt(n2)),lang))
+	if lang not in name_order : continue #if n1 < 50 : continue
+	graph_data.append((m1,m2,1.96*(math.sqrt(v2) / math.sqrt(n2)),lang, name_order.index(lang)))
 #	tstat, pval = stats.ttest_1samp(x, am)
 #	print '%s\t%.02f\t%.02f\t%.02f\t'%(lang, m, v, pval)
 
 print "total turkers,", t
 
-print '\n'.join([d[3] for d in graph_data])
-exit(0)
-graph_data = sorted(graph_data, key=operator.itemgetter(1), reverse=True) 
+def sort_order(s) : return name_order.index(s)
 
-w = .5
+print '\n'.join([d[3] for d in graph_data])
+#graph_data = sorted(graph_data, key=operator.itemgetter(1), reverse=True) 
+graph_data = sorted(graph_data, key=operator.itemgetter(4)) 
+
+w = 1 
+
 p1 = plt.bar(np.arange(len(graph_data)), [d[1] for d in graph_data], width=w, color='#6699FF', yerr=[d[2] for d in graph_data], ecolor='black')
[…]

### 2013-11-27 code/src/20130905/paper-rewrite/figures/code/time_of_day.py

@@ -60,8 +60,10 @@ def graph(langtimes):
 	plt.xlabel('Time of day')
 	plt.xlim(-1,24)
 	plt.ylim(0,langnum+1)
-	plt.show()
-	
+	#plt.show()
+	plt.savefig("times.pdf")
+
+write_all_times()
 times = time_map()
 
 langtimes = {}

### 2013-11-28 writeup/revision 1/paper.tex
Cropped map
Updated paper

@@
 We use this data to recommend languages with the largest speaker populations as good candidates for other researchers who want to  develop crowdsourced, multilingual technologies.
+To further demonstrate the value of creating data via crowdsourcing, we hire workers to create bilingual parallel corpora in six Indian languages, and use them to train statistical machine translation systems.
 
@@
 
-Surveying thousands of workers allows us to analyze current speaker populations for 100 languages.  The data also allows us to answer questions like: 
-How quickly is work completed in a given language? 
-Are crowdsourced translations reliably good? 
-How often do workers misrepresent their language abilities to obtain financial rewards?
-
-While the demographics reported are likely to shift overtime, as Amazon expands its methods of payments and reaches new countries, the data presented provides a valuable snapshot of the current state of MTurk, and the methods used can be applied generally in future research.
-
 %%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
@@
 \centering
-\includegraphics[width=\linewidth]{figures/map.png}
+\includegraphics[width=\linewidth]{figures/map.pdf}
 \caption{The number of workers per country.
@@
 
+Surveying thousands of workers allows us to analyze current speaker populations for 100 languages.  The data also allows us to answer questions like: 
+How quickly is work completed in a given language? 
+Are crowdsourced translations reliably good? 
+How often do workers misrepresent their language abilities to obtain financial rewards?
+
 \section{Background and Related Work}
-Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost, workforce.
+Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost workforce.
 MTurk allows employers to provide micro-payments in return for workers completing micro-tasks.
@@
 \newcite{Zbib-etal:2012:NAACL} used crowdsourcing to construct a 1.5 million word parallel corpus of dialect Arabic and English, training a statistical machine translation system that produced higher quality translations of dialect Arabic than a system a trained on 100 times more Modern Standard Arabic-English parallel data.
+\newcite{zbib-EtAl:2013:NAACL-HLT} conducted a systematic study that showed that training an MT system on crowdsourced translations resulted in the same performance as training on professional translations, at $\frac{1}{5}$ the cost.
+\newcite{Hu:2010,Hu:2011} performed crowdsourced translation by having monolingual speakers collaborate and iteratively improve MT output.
 
@@
 To contrast our research with previous work, the main contributions of this paper are: (1) a robust methodology for assessing the bilingual  skills of anonymous workers, (2) the largest-scale census to date of language skills of workers on MTurk, and (3) a detailed analysis of the data gathered in our study.
+
+\section{Experimental Design}
+The central task in this study was to investigate Mechanical Turk's bilingual population.
+We accomplished this through self-reported surveys combined with a HIT to translate individual words for 100 languages.
+We evaluate the accuracy of the workers' translations against known translations.
+In cases where these were not exact matches, we used a second pass monolingual HIT, which asked English speakers to evaluate if a worker-provided translation was a synonym of the known translation.
 
@@
 
-\section{Experimental Design}
-The central task in this study was to investigate Mechanical Turk's bilingual population.
-We accomplished this through self-reported surveys combined with a HIT to translate individual words for 100 languages.
-We evaluate the accuracy of the workers' translations against known translations.
-In cases where these were not exact matches, we used a second pass monolingual HIT, which asked English speakers to evaluate if a worker-provided translation was a synonym of the known translation.
-
 \paragraph{Demographic questionnaire}
@@
 We drew our data from the different language versions of Wikipedia.
-We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} (Table \ref{wikipedia-buckets}).
+We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} (Table \ref{Wikipedia-buckets}).
 For each language, we chose the 1,000 most viewed articles over a 1 year period,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and extracted the 10,000 most frequent words from them.
@@
 Each language's code is given in parentheses.
-These language codes are used in other figures throughout this paper.}\label{wikipedia-buckets}
+These language codes are used in other figures throughout this paper.}\label{Wikipedia-buckets}
 \end{table}%
@@
 Each set of 10 words was independently translated by three separate workers.
-5,281 workers completed 256,604 translations assignments, totaling more than 3 million words, over a period of three and a half months.
+5,281 workers completed 256,604 translation assignments, totaling more than 3 million words, over a period of three and a half months.
 
@@
 We used Wikipedia's inter-language links to pair titles of English articles with their corresponding foreign article's title.
-To get a more translatable set of pairs, we excluded any pairs where: (1) the English word was not present in the WordNet ontology  \cite{miller1995wordnet}, (2) either article title was longer than a single word, (3) the English wikipedia page was a subcategory of person or place, or (4) the English and the foreign titles were identical or a substring of the other.
+To get a more translatable set of pairs, we excluded any pairs where: (1) the English word was not present in the WordNet ontology  \cite{miller1995wordnet}, (2) either article title was longer than a single word, (3) the English Wikipedia page was a subcategory of person or place, or (4) the English and the foreign titles were identical or a substring of the other.
 
@@
 
-\begin{figure*}[t]
+\begin{figure}[t]
   \centering
-  \includegraphics[width=\textwidth]{figures/tamil.pdf}
-  \begin{tabular}{l}
+  \includegraphics[width=1.05\linewidth]{figures/hindi.pdf}
+  \footnotesize
+  \begin{tabular}{p{\linewidth}}
     \hline
-    In March 15,2007 Wiki got a place in Oxford English dictionary. \\
-    On March 15, 2007 wiki was included in the Oxford English
-    dictionary. \\
-    ON MARCH 15, 2007, WIKI FOUND A PLACE IN THE OXFORD ENGLISH
-    DICTIONARY \\
-    March 15, 2007 oxford english index of wiki's place. \\ \\
-
+In retribution pakistan also did six nuclear tests on 28 may 1998.\\
+On 28 May Pakistan also conducted six nuclear tests as an act of redressal.\\
+Retaliating on this 'Pakistan' conducted Six(6) Nuclear Tests on 28 May, 1998.\\
+pakistan also did 6 nuclear test in retribution on 28 may, 1998 \\ \\
   \end{tabular}
-  \caption{An example of the variance in translation quality for the
-    human translations of a Tamil sentence; the formatting of the
-    translations has been preserved exactly.}
+  \normalsize
+  \caption{An example of the Turkers' translations of a Hindi sentence. The translations are unedited and contain fixable spelling, capitalization and grammatical errors.}
   \label{figure:variance}
-\end{figure*}
-
-\paragraph{Full sentence translations}
-In addition to the bilingual dictionaries, we are interested in Turkers' ability to translate complete sentences.
-Because the Indian subcontinent is so well represented among our workers, we chose six Indian languages for which to gather translations of full sentences.
-We selected Bengali, Malyalam, Hindi, Tamil, Telugu, and Urdu as good candidates for our study : these languages have large native speaker populations and are well represented on Wikipedia but they are currently not covered by any professionally translated corpora.
-
-Each of the sentence translation HITs contained ten sequential sentences from a source-language Wikipedia article and asked the worker to enter a free-form translation for each.
-We collected four translations from different translators for each source sentence.
-Workers were paid \$0.70 per HIT.
-
-Since there is no gold-standard data available for our chosen languages, and it could not be mined in a straight-forward way as in the single word case, we were unable to embed controls into our HITs.
-We instead accepted or rejected translations based on a review of each worker's submissions, which included a comparison of the translations to a monotonic gloss (produced with a dictionary), and metadata such as the amount of time the worker took to complete the HIT and their geographic location.
-
-Figure~\ref{figure:variance} contains some hand-picked examples of the sorts of translations we obtained.
-While the lack of a gold-standard data set prevented us from evaluating the collected translations in terms of BLEU scores, as in \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we evaluate the quality of the data by using it to train an SMT system.
-We present results in section \ref{sec:data-analysis}.
+\end{figure}
 
@@
 \begin{center}
-\includegraphics[width=\linewidth]{figures/quality_bar.pdf}
+\includegraphics[width=.7\linewidth]{figures/quality_bar.pdf}
 \caption{Translation quality for languages with at least 50 Turkers.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\paragraph{Full sentence translations}
+To demonstrate the feasibility of using crowdsourcing to create multilingual technologies, we hire Turkers to construct bilingual parallel corpora from scratch for six Indian languages.
+\newcite{Germann2001} attempted to build a Tamil-English translation system from scratch by hiring professional translators, but found the cost prohibitive.
+We created parallel corpora by translating the 100 most viewed Wikipedia pages in Bengali, Malyalam, Hindi, Tamil, Telugu, and Urdu into English.
+We collected four translations from different Turkers for each source sentence.
+
+%Embedding gold-standard translations into our full-sentence translation HITs was problematic for two reasons: (1) few public bilingual parallel corpora exist for our chosen languages, and (2) Google could have trained its translation system on them already, resulting in high quality translations when Turkers used MT to translate the gold standard sentences.
+and it could not be mined in a straight-forward way as in the single word case, we were unable to embed controls into our HITs.
+Workers were paid \$0.70 per HIT to translate 10 sentences.  
+ We  accepted or rejected translations based on a manual review of each worker's submissions, which included a comparison of the translations to a monotonic gloss (produced with a dictionary), and metadata such as the amount of time the worker took to complete the HIT and their geographic location.
+
+Figure~\ref{figure:variance} shows an example of the translations we obtained.
+The lack of a professionally translated reference sentences prevented us from doing a systematic comparison between the quality of profession and non-professional translations as  \newcite{zaidan-callisonburch:2011:ACL-HLT2011a} did.
+Instead we evaluate the quality of the data by using it to train SMT systems.
+We present results in section \ref{sec:data-analysis}.
 
@@
 \begin{align}	
-	\text{Quality}(t_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}\text{Quality}(a_j)}}{\mid \texttt{assigns[$i$]} \mid}
+	\text{Quality}(t_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}}\text{Quality}(a_j)}{\mid \texttt{assigns[$i$]} \mid}
 \end{align}	
@@
 \begin{align}	
-	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{turkers[$i$]}\text{Quality}(t_j)}}{\mid \texttt{turkers[$i$]} \mid}
+	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{turkers[$i$]}}\text{Quality}(t_j)}{\mid \texttt{turkers[$i$]} \mid}
 \end{align}	
@@
 
-\paragraph{Use of machine translation}
+\paragraph{Cheating using machine translation}
 
-One obvious way for dishonest workers to shortcut is to use available online translation tools.
+One obvious way for workers to cheat is to use available online translation tools.
 Although we followed best practices to deter copying-and-pasting into online MT systems  by  rendering words and sentences as images \cite{zaidan-callisonburch:2011:ACL-HLT2011a}, this strategy does not prevent workers from typing the words into an MT system if they are able to type in the language's script.
 
-We quantified each Turker's overlap with the Google translations so that we could identify and remove workers that appeared to be misusing Google Translate.
+To identify and remove workers who appeared to be cheating by using Google Translate, we calculated each worker's overlap with the Google translations.
 We used Google to translate all 10,000 words for the 51 foreign languages that Google Translate covered at the time of the study.
@@
 %\begin{center}
-%\includegraphics[width=1\linewidth]{figures/google_bar.png}
+%\includegraphics[width=1\linewidth]{figures/google_bar.pdf}
 %\caption{Average proportion of Turker translations matching GoogleTranslate, per assignment. Overall average overlap was 0.37.}
@@
 
-We found that while overall overlap is high (the average Turker's overlap was 41\%), it is not consistently high across all Turkers.
-Figure \ref{dist} shows that while a small number of Turkers have a very high amount of overlap with Google (near 80\%) the majority overlap less than half of the time.
-It seems likely that those with very high overlap are cheating, but it is also reasonable to assume that honest Turkers will overlap with Google with some regularity.
-We divide the workers into three groups: those with very high overlap with Google (likely cheating by using Google to translate words), those with reasonable overlap, and those with no overlap (likely cheating by other means, e.g.
-submitting random text).
-
-Our controls are designed to identify workers that fall into the third group (those who are spamming or providing useless translations), but they will not effectively flag workers who are cheating with Google Translate.
-We therefore remove the 500 Turkers with the highest overlap with Google.
-This equates to removing all workers with greater than 70\% overlap.
-Figure \ref{cdf} shows that removing workers at or above the 70\% threshold retains 90\% of the collected translations and over 90\% of the workers.
-
-Quality scores reported throughout the paper reflect only translations from Turkers whose overlap with Google falls below this 70\% threshold.
-
 \begin{figure}[h!]
@@
 \begin{subfigure}[b]{\linewidth}
-%\includegraphics[width=\textwidth]{figures/turker-googmatch-distribution.png}
+%\includegraphics[width=\textwidth]{figures/turker-googmatch-distribution.pdf}
 \includegraphics[width=\linewidth]{figures/turker-googmatch-distribution.pdf}
-\caption{Individual Turker overlap with Google Translate.
-We remove the 500 workers with the highest overlap (shaded region on the left) from our analysis, as it is reasonable to assume these workers are cheating by submitting translations from Google.
-We believe the workers with no overlap (shaded region on the right) are also likely to be cheating, e.g.
-by submitting random text, and we target these workers through our embedded quality controls.}
+\caption{Individual workers' overlap with Google Translate.
+We removed the 500 workers with the highest overlap (shaded region on the left) from our analyses, as it is reasonable to assume these workers are cheating by submitting translations from Google.
+Workers with no overlap (shaded region on the right) are also likely to be cheating, e.g.
+by submitting random text.
+}
+%, and we target these workers through our embedded quality controls.}                
 \label{dist}
@@
 \begin{subfigure}[b]{\linewidth}
-%\includegraphics[width=\textwidth]{figures/google-cdf-googlangs.png}
+%\includegraphics[width=\textwidth]{figures/google-cdf-googlangs.pdf}
 \includegraphics[width=\linewidth]{figures/google-cdf-googlangs.pdf}
@@
 
-\section{Data Analysis} \label{sec:data-analysis}
+%We found that while overall overlap is high (the average worker's overlap was 41\%), it is not consistently high across all workers. 
+Figure \ref{dist} shows overlap between Turkers's translations and Google Translate.
+When overlap is high, it seems likely that those with very high overlap are cheating.
+It is also reasonable to assume that honest workers will overlap with Google some amount of the time as Google's translations are usually accurate.
+We divide the workers into three groups: those with very high overlap with Google (likely cheating by using Google to translate words), those with reasonable overlap, and those with no overlap (likely cheating by other means, for instance, by submitting random text).
 
-We performed an analysis of our data to address the following questions:
-\begin{itemize}
-\item How quickly can we expect work to be completed in a particular language? 
-\item Do workers accurately represent their language abilities?  Should we constrain tasks by region? 
-\item Are our gold standard translations valid? 
-\item Can Turkers' translations be used to train an MT system? 
-\end{itemize}
+Our gold-standard controls are designed to identify workers that fall into the third group (those who are spamming or providing useless translations), but they will not effectively flag workers who are cheating with Google Translate.
+We therefore remove the 500 Turkers with the highest overlap with Google.
+This equates to removing all workers with greater than 70\% overlap.
+Figure \ref{cdf} shows that removing workers at or above the 70\% threshold retains 90\% of the collected translations and over 90\% of the workers.
 
-\paragraph{Speed of completion}
-
-Figure \ref{completion-time} gives the completion times for 40 languages.  
-The 10 languages to finish in the shortest amount of time were: Tamil, Malayalam, Telugu, Hindi, Macedonian, Spanish, Serbian, Romanian, Gujarati, and Marathi.
-Seven of the ten fastest languages are from India, which is unsurprising given the geographic distribution of workers.
-Some languages follow the pattern of having a smattering of assignments completed early, with the rate picking up later.
+Quality scores reported throughout the paper reflect only translations from Turkers whose overlap with Google falls below this 70\% threshold.
 
@@
 \hline\hline
-Hindi & 0.635 (296) & \textbf{0.695} (7) & India (284) UAE (5) UK (3)  & Saudi Arabia (2) Russia (1) Oman (1) \\
-Tamil & \textbf{0.653} (273) * & 0.250 (2) & India (266) US (3) Canada (2)  & Tunisia (1) Egypt (1)  \\
-Malayalam & 0.764 (234) & \textbf{0.827} (2) & India (223) UAE (6) US (3)  & Saudi Arabia (1) Maldives (1) \\
-Spanish & 0.814 (191) & \textbf{0.837} (18) & US (122) Mexico (16) Spain (14)  & India (15) Newzealand (1) Brazil (1) \\
-French & 0.750 (170) & \textbf{0.816} (11) & India (62) US (45) France (23)  & Greece (2) Netherlands (1) Japan (1) \\
-Chinese & \textbf{0.601} (116) & 0.552 (21) & US (75) Singapore (13) China (9)  & Hongkong (6) Australia (3) Germany (2)  \\
-German & \textbf{0.825} (91) & 0.768 (41) & Germany (48) US (25) Austria (7)  & India (34) Netherlands (1) Greece (1)  \\
-Italian & \textbf{0.863} (90) & 0.796 (42) & Italy (42) US (29) Romania (7)  & India (33) Ireland (2) Spain (2)  \\
-Amharic & \textbf{0.136} (16) * & 0.009 (99) & US (14) Ethiopia (2)  & India (70) Georgia (9) Macedonia (5)  \\
-Kannada & 0.704 (105) & NA (0) & India (105)  & \\
-Arabic & \textbf{0.741} (60) * & 0.604 (45) & Egypt (19) Jordan (16) Morocco (9)  & US (19) India (11) Canada (3)  \\
-Sindhi & \textbf{0.190} (96) & 0.062 (9) & India (58) Pakistan (37) US (1)  & Macedonia (4) Georgia (2) Indonesia (2)  \\
-Portuguese & 0.869 (101) & \textbf{0.963} (3) & Brazil (44) Portugal (31) US (15)  & Romania (1) Japan (1) Israel (1) \\
-Turkish & 0.759 (76) & \textbf{0.804} (27) & Turkey (38) US (18) Macedonia (8)  & India (19) Pakistan (4) Taiwan (1) \\
-Telugu & \textbf{0.799} (102) & 0.500 (1) & India (98) US (3) UAE (1)  & Saudi Arabia (1)  \\
-Irish & \textbf{0.742} (54) & 0.709 (47) & US (39) Ireland (13) UK (2)  & India (36) Romania (5) Macedonia (2)  \\
-Swedish & \textbf{0.734} (54) & 0.711 (45) & US (25) Sweden (22) Finland (3)  & India (23) Macedonia (6) Croatia (2)  \\
-Czech & \textbf{0.706} (45) & 0.612 (50) & US (17) Czech Republic (14) Serbia (5)  & Macedonia (22) India (10) UK (5)  \\
-Russian & \textbf{0.146} (67) & 0.119 (27) & US (36) Moldova (7) Russia (6)  & India (14) Macedonia (4) UK (3)  \\
-Breton & 0.167 (3) & \textbf{0.178} (89) & US (3)  & India (83) Macedonia (2) China (1) \\
+Hindi & 0.64 (296) & \textbf{0.70} (7) & India (284) UAE (5) UK (3)  & Saudi Arabia (2) Russia (1) Oman (1) \\
+Tamil & \textbf{0.65} (273) * & 0.25 (2) & India (266) US (3) Canada (2)  & Tunisia (1) Egypt (1)  \\
+Malayalam & 0.76 (234) & \textbf{0.83} (2) & India (223) UAE (6) US (3)  & Saudi Arabia (1) Maldives (1) \\
+Spanish & 0.81 (191) & \textbf{0.84} (18) & US (122) Mexico (16) Spain (14)  & India (15) Newzealand (1) Brazil (1) \\
+French & 0.75 (170) & \textbf{0.82} (11) & India (62) US (45) France (23)  & Greece (2) Netherlands (1) Japan (1) \\
+Chinese & \textbf{0.60} (116) & 0.55 (21) & US (75) Singapore (13) China (9)  & Hongkong (6) Australia (3) Germany (2)  \\
+German & \textbf{0.83} (91) & 0.77 (41) & Germany (48) US (25) Austria (7)  & India (34) Netherlands (1) Greece (1)  \\
+Italian & \textbf{0.86} (90) & 0.80 (42) & Italy (42) US (29) Romania (7)  & India (33) Ireland (2) Spain (2)  \\
+Amharic & \textbf{0.14} (16) * & 0.01 (99) & US (14) Ethiopia (2)  & India (70) Georgia (9) Macedonia (5)  \\
+Kannada & 0.70 (105) & N/A (0) & India (105)  & \\
+Arabic & \textbf{0.74} (60) * & 0.60 (45) & Egypt (19) Jordan (16) Morocco (9)  & US (19) India (11) Canada (3)  \\
+Sindhi & \textbf{0.19} (96) & 0.06 (9) & India (58) Pakistan (37) US (1)  & Macedonia (4) Georgia (2) Indonesia (2)  \\
+Portuguese & 0.87 (101) & \textbf{0.96} (3) & Brazil (44) Portugal (31) US (15)  & Romania (1) Japan (1) Israel (1) \\
+Turkish & 0.76 (76) & \textbf{0.80} (27) & Turkey (38) US (18) Macedonia (8)  & India (19) Pakistan (4) Taiwan (1) \\
+Telugu & \textbf{0.80} (102) & 0.50 (1) & India (98) US (3) UAE (1)  & Saudi Arabia (1)  \\
+Irish & \textbf{0.74} (54) & 0.71 (47) & US (39) Ireland (13) UK (2)  & India (36) Romania (5) Macedonia (2)  \\
+Swedish & \textbf{0.73} (54) & 0.71 (45) & US (25) Sweden (22) Finland (3)  & India (23) Macedonia (6) Croatia (2)  \\
+Czech & \textbf{0.71} (45) & 0.61 (50) & US (17) Czech Republic (14) Serbia (5)  & Macedonia (22) India (10) UK (5)  \\
+Russian & \textbf{0.15} (67) & 0.12 (27) & US (36) Moldova (7) Russia (6)  & India (14) Macedonia (4) UK (3)  \\
+Breton & 0.17 (3) & \textbf{0.18} (89) & US (3)  & India (83) Macedonia (2) China (1) \\
 \hline\hline
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Data Analysis} \label{sec:data-analysis}
+
+We performed an analysis of our data to address the following questions:
+\begin{itemize}
+\item Do workers accurately represent their language abilities?  Should we constrain tasks by region? 
+\item How quickly can we expect work to be completed in a particular language? 
+%\item Are our gold standard translations valid? 
+\item Can Turkers' translations be used to train MT systems? 
+\item Do our dictionaries improve MT quality?
+\end{itemize}
 
@@
 
-\paragraph{Validation of controls} 
-Higher overlap with Google Translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.27), suggesting that some control translations have already been indexed by Google.
-We therefore investigated the validity of our use of Wikipedia inter-language links as gold standard translations.
+\paragraph{Speed of translation}
 
-As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
-We had external bilingual dictionaries for 24 of the 100 languages examined in this study.\footnote{The bilingual dictionaries were between English and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz.
-}  We used each of these bilingual dictionaries to compute language-level quality scores, using the dictionary's translation as a gold standard translation for any of the 10,000 foreign words in our study.
-In some cases, the overlap of words was low, since dictionaries list root forms of words and we translated inflected forms.
+Figure \ref{completion-time} gives the completion times for 40 languages.  
+The 10 languages to finish in the shortest amount of time were: Tamil, Malayalam, Telugu, Hindi, Macedonian, Spanish, Serbian, Romanian, Gujarati, and Marathi.
+Seven of the ten fastest languages are from India, which is unsurprising given the geographic distribution of workers.
+Some languages follow the pattern of having a smattering of assignments completed early, with the rate picking up later.
 
-We ranked the 24 languages based on their translation quality scores according to the external dictionaries, and calculated correlation when compared to the ranking produced by our gold standard control.
-The Pearson correlation was $\rho=0.53$.
-We computed a correlation coefficient of $\rho=0.37$ for ranking of the translation quality of individual Turkers using the two sources of reference translations.
+Figure \ref{figure:volume-of-data-by-language} gives the throughput of the full-sentence translation task for the six Indian languages.
+The fastest language was Malayalam, for we collected half a million words of translations in just under a week.
+Table \ref{table:data-size} gives the size of the data set that we created for each of these languages.
 
-Given the strong positive correlation, we are satisfied that the trends reported in this paper hold when using either our gold standard translations or external bilingual dictionaries.
-
-\paragraph{Quality improvements for SMT systems}
-Using the full sentence translations we gathered for the six Indian languages, we were able to train a statistical machine translation system.
-Table \ref{table:data-size} gives the size of the data set for each of these languages.
-Table \ref{dictionary_bleu} shows that the sentences alone produce decent translation performance, with BLEU scores as high as 19.22 for Urdu.
-We also see that adding the single-word dictionaries to the training set produces consistent performance gains, ranging from 1 to 5 BLEU points.
-Unfortunately, we do not have professionally translated data against which to compare the resulting performances, but we find the outcomes encouraging as an indication of the potential of Turkers to provide high quality translations.
+\begin{figure}[t]
+  \includegraphics[width=\linewidth]{figures/volume}
+  \caption{The total volume of translations (measured in English words)
+    as a function of elapsed days. }
+  \label{figure:volume-of-data-by-language}
+\end{figure}
 
@@
   \small
-  \begin{tabular}{l|rr}
-    language & full sentences & dictionaries \\
+  \begin{tabular}{l|rrr}
+    		 & sentence   &  English + & dictionary  \\
+    language &  pairs  & foreign words &  entries \\
     \hline\hline
-    Bengali & 732k (22k)  & 22k \\
-    Hindi   & 1,488k (40k) & 22k \\
-    Malayalam & 863k (32k) & 23k \\
-    Tamil & 916k (38k) & 25k \\
-    Telugu & 1,097k (46k) & 21k \\
-    Urdu & 1,356k (35k) & 20k \\
+    Bengali & 22k & 732k   & 22k \\
+    Hindi   &  40k & 1,488k & 22k \\
+    Malayalam & 32k & 863k & 23k \\
+    Tamil & 38k & 916k & 25k \\
+    Telugu & 46k & 1,097k & 21k \\
+    Urdu & 35k & 1,356k & 20k \\
   \end{tabular}
-  \caption{Size of data set (number of words) collected for each language. For full sentences, number of parallel sentences is shown in parentheses.}
+  \caption{Size of parallel corpora and bilingual dictionaries collected for each language. }
   \label{table:data-size}
@@
 \centering
-\begin{tabular}{l|ccc}
-  language  & sentences &  dictionaries\\
+  \small
+\begin{tabular}{l|cc|c}
+  		  & trained on  &  bitext + & BLEU \\
+  language  & bitexts alone &  dictionaries & $\Delta$ \\
   \hline\hline
-  Bengali    &  12.03 & 17.29 \\
-  Hindi      & 16.19 & 18.10\\  
-  Malayalam    &  6.65 & 9.72\\      
-  Tamil      & 8.08 & 9.66\\  
-  Telugu     & 11.94 & 13.70\\  
-  Urdu        & 19.22 & 21.98\\   
+  Bengali    &  12.03 & 17.29 & 5.26 \\
+  Hindi      & 16.19 & 18.10 & 1.91 \\  
+  Malayalam    &  6.65 & 9.72 & 3.07 \\      
+  Tamil      & 8.08 & 9.66 & 1.58 \\  
+  Telugu     & 11.94 & 13.70 & 1.76 \\  
+  Urdu        & 19.22 & 21.98 & 2.76 \\   
 \end{tabular}
-\caption{BLEU scores for translating into English using full sentence translations alone, and with the addition of single-word dictionaries.
+\caption{BLEU scores for translating into English using bilingual parallel corpora by themselves, and with the addition of single-word dictionaries.
 Scores are calculated using four reference translations and represent the mean of three MERT runs.}
@@
 \end{table}
+
+\paragraph{Training SMT systems}
+We trained statistical translation models from the parallel corpora that we created for the six Indian languages using the Joshua machine translation system \cite{post-EtAl:2013:WMT}.
+Table \ref{dictionary_bleu} shows the translation performance when trained on the bitexts alone, and when incorporating the bilingual dictionaries created in our earlier HIT.
+Adding the dictionaries to the training set produces consistent performance gains, ranging from 1 to 5 BLEU points.
+This represents a substantial improvement, but there is overlap between the source materials for both sets, since both the dictionaries and the bitext source sentences were drawn from Wikipedia.
+
+%Unfortunately, we do not have professionally translated data against which to compare the resulting performances, but we find the outcomes encouraging as an indication of the potential of Turkers to provide high quality translations.
 
@@
 workers & quality & speed & \\\hline
-many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5} de es fr gu it kn ml nl pt ro sr te tl \\\cline{3-4}
-&&slow& ar ga he pa sv tr\\\cline{2-4}
-&low &fast& hi mr ta ur \\\cline{3-4}
-&&slow&bn bo bpy ceb ne new pl ru sd zh\\\cline{1-4}
+%many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5} de es fr gu it kn ml nl pt ro sr te tl \\\cline{3-4}
+%&&slow& ar ga he pa sv tr\\\cline{2-4}
+%& low or medium &fast& hi mr ta ur \\\cline{3-4}
+%&&slow&bn bo bpy ceb ne new pl ru sd zh\\\cline{1-4}
+many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5}   Dutch, French, German, Gujarati, Italian, Kannada, Malayalam, Portuguese, Romanian, Serbian, Spanish, Tagalog, Telugu \\\cline{3-4}
+&&slow& Arabic,  Hebrew, Irish, Punjabi, Swedish, Turkish\\\cline{2-4}
+& low or  &fast& Hindi, Marathi, Tamil, Urdu \\\cline{3-4}
+&medium&slow&Bengali,  Bishnupriya Manipuri, Cebuano,  Chinese, Nepali, Newar, Polish, Russian, Sindhi, Tibetan\\\cline{1-4}
 few &high  &fast& bs hr mk ms sh\\\cline{3-4}
 &&slow&af an ast bcl be bg cs da el eu fi fy gl ht hu id ilo is ja jv kk ko lt mg nds no pam scn sk sl sq th uk uz war yo\\\cline{2-4}
-&low  &fast&--\\\cline{3-4}
-&&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}am az br ca cy hy ka lb lv nap nn pms ps so su sw tt vi wa \\\hline
-none&low&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}diq eo fa io ku qu wo \\\hline
+&low or  &fast&--\\\cline{3-4}
+&medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}am az br ca cy hy ka lb lv nap nn pms ps so su sw tt vi wa \\\hline
+none&low or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}diq eo fa io ku qu wo \\\hline
 \end{tabular}
@@
 
+%\paragraph{Validation of controls} 
+%Higher overlap with Google Translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.27), suggesting that some control translations have already been indexed by Google.
+We therefore investigated the validity of our use of Wikipedia inter-language links as gold standard translations.
+%
+%As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
+We had external bilingual dictionaries for 24 of the 100 languages examined in this study.\footnote{The bilingual dictionaries were between English and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz.
+}  We used each of these bilingual dictionaries to compute language-level quality scores, using the dictionary's translation as a gold standard translation for any of the 10,000 foreign words in our study.
+In some cases, the overlap of words was low, since dictionaries list root forms of words and we translated inflected forms.
+%
+%We ranked the 24 languages based on their translation quality scores according to the external dictionaries, and calculated correlation when compared to the ranking produced by our gold standard control.
+The Pearson correlation was $\rho=0.53$.
+We computed a correlation coefficient of $\rho=0.37$ for ranking of the translation quality of individual Turkers using the two sources of reference translations.
+%
+%Given the strong positive correlation, we are satisfied that the trends reported in this paper hold when using either our gold standard translations or external bilingual dictionaries.
+
 \section{Discussion}
-Mechanical Turk gives researchers access to a diverse set of bilingual workers, making it a promising resource for researchers and developers of multilingual systems.
-Based on our study, we can confidently recommend 13 languages as good candidates for future research: German, Spanish, French, Gujarati, Italian, Kannada, Malayalam, Dutch, Portuguese, Romanian, Serbian, Telugu, and Tagalog.
+Crowdsourcing platforms like Mechanical Turk give researchers instant access to a diverse set of bilingual workers.
+This opens up exciting new avenues for researchers to develop new multilingual systems.
+The demographics reported in this study are likely to shift over time.
+Amazon may change its expand its payments to new currencies.
+Posting long-running HITs in other languages may recruit more speakers of those languages.
+New crowdsourcing platforms may emerge.
+The data presented here provides a valuable snapshot of the current state of MTurk, and the methods used can be applied generally in future research.
+
+Based on our study, we can confidently recommend 13 languages as good candidates for research now: Dutch, French, German, Gujarati, Italian, Kannada, Malayalam, Portuguese, Romanian, Serbian, Spanish, Tagalog, and Telugu.
 These languages have large Turker populations who complete tasks quickly and accurately.
 Table \ref{recommendations} summarizes the strengths and weaknesses of all 100 languages covered in our study.
+Several other languages are viable candidates provided adequate quality control mechanisms are used to select good workers.
 
-Unfiltered data can contain large amounts of noise, a variety of techniques can be incorporated into crowdsourcing pipelines to ensure high quality data.
-As a best practice, we suggest restricting workers to countries that plausibly speak the foreign language of interest, and embedding gold standard controls where possible, rather than relying solely on self-reported language skills.
+Since Mechanical Turk provides financial incentives for participation, many workers attempt to complete tasks even if they do not have the language skills necessary to do so.
+Since MTurk does not provide any information about workers demographics, including their language competencies, it can be hard to exclude such workers.
+As a result naive data collection on MTurk may result in noisy data.
+A variety of techniques should be incorporated into crowdsourcing pipelines to ensure high quality data.
+As a best practice, we suggest: (1) restricting workers to countries that plausibly speak the foreign language of interest, (2) embedding gold standard controls or administering language pretests, rather than relying solely on self-reported language skills, and (3) and excluding workers whose translations have high overlap with online machine translation systems like Google translate.
 
@@
 
-We plan to release all data and code used in this study upon publication of this paper.
-Our data release will include the raw data, along with bilingual dictionaries that are filtered to be high quality.
+With the publication of this paper, we are releasing all data and code used in this study.
+Our data release includes the raw data, along with bilingual dictionaries that are filtered to be high quality.
 It will include 256,604 translation assignments from 5,281 Turkers and 20,952 synonym assignments from 1,005 Turkers, along with meta information like geolocation and time submitted, plus external dictionaries used for validation.
 The dictionaries will contain 1.5M total translated words in 100 languages, along with code to filter the dictionaries based on different criteria.
+The data also includes parallel corpora for six Indian languages, ranging in size between 700,000 to 1.5 million words
 

### 2013-11-29 code/src/20130905/paper-rewrite/figures/code/quality_bar.py
updated bar graphs

@@ -21,7 +21,7 @@ graph_data = []
 t = 0 
 name_order = ['pt', 'it', 'ms', 'sr', 'ro', 'es', 'de', 'af', 'te', 'sk', 'hr', 'sq', 'fi', 'tr', 'nl', 'id', 'he', 'gu', 'fr', 'da', 'sl', 'bg', 'ja', 'cy', 'gl', 'lv', 'sv', 'kn', 'az', 'hu', 'sw', 'lt', 'ko', 'eu', 'pl', 'ca', 'eo', 'ar', 'cs', 'ta', 'el', 'zh', 'vi', 'is', 'ur', 'ru']
 for lang in sorted(data.keys()) : 
-	if lang not in goog_langs : continue
+#	if lang not in goog_langs : continue
 	x1 = [d[0] for d in data[lang]]
 	x2 = [d[1] for d in data[lang]]
 	n1, (smin1, smax1), m1, v1, ss1, sk1 = stats.describe(x1)
@@ -37,10 +37,10 @@ print "total turkers,", t
 def sort_order(s) : return name_order.index(s)
 
 print '\n'.join([d[3] for d in graph_data])
-#graph_data = sorted(graph_data, key=operator.itemgetter(1), reverse=True) 
-graph_data = sorted(graph_data, key=operator.itemgetter(4)) 
+graph_data = sorted(graph_data, key=operator.itemgetter(1), reverse=True) 
+#graph_data = sorted(graph_data, key=operator.itemgetter(4)) 
 
-w = 1 
+w = .5
 
 p1 = plt.bar(np.arange(len(graph_data)), [d[1] for d in graph_data], width=w, color='#6699FF', yerr=[d[2] for d in graph_data], ecolor='black')
 p1 = plt.bar(np.arange(len(graph_data)), [d[0] for d in graph_data], width=w, color='#0000FF')

### 2013-11-29 writeup/revision 1/paper.tex

@@
 &medium&slow&Bengali,  Bishnupriya Manipuri, Cebuano,  Chinese, Nepali, Newar, Polish, Russian, Sindhi, Tibetan\\\cline{1-4}
-few &high  &fast& bs hr mk ms sh\\\cline{3-4}
-&&slow&af an ast bcl be bg cs da el eu fi fy gl ht hu id ilo is ja jv kk ko lt mg nds no pam scn sk sl sq th uk uz war yo\\\cline{2-4}
+few &high  &fast& Bosnia, Croatian  Macedonian  Malay  Serbo-Croatian\\\cline{3-4}
+&&slow&Afrikaans, Albanian, Aragonese, Asturian, Basque, Belarusian, Bulgarian, Central Bicolano, Czech, Danish, Finnish, Galacian, Greek, Haitian, Hungarian, Icelandic, Ilokano, Indonesian, Japanese, Javanese, Kapampangan, Kazakh, Korean, Lithuanian, Low Saxon, Malagasy, Norwegian (Bokmal), Sicilian, Slovak, Slovenian, Thai, Ukranian, Uzbek, Waray-Waray, West Frisian, Yoruba\\\cline{2-4}
 &low or  &fast&--\\\cline{3-4}
-&medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}am az br ca cy hy ka lb lv nap nn pms ps so su sw tt vi wa \\\hline
-none&low or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}diq eo fa io ku qu wo \\\hline
+&medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}Amharic,  Armenian, Azerbaijani, Breton, Catalan, Georgian, Latvian, Luxembourgish, Neapolitian, Norwegian (Nynorsk), Pashto, Piedmontese, Somali, Sudanese, Swahili, Tatar, Vietnamese, Walloon, Welsh \\\hline
+none&low or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}  Esperanto, Ido, Kurdish, Persian, Quechua, Wolof, Zazaki\\\hline
 \end{tabular}

### 2013-11-29 writeup/revision 1/paper.tex
significance in table 3

--- 2013-11-28 writeup/revision 1/paper.tex
@@
 \hline
-{\sc 100k-500k articles:} Arabic (ar), Bulgarian (bg), Catalan (ca), Czech (cs), Danish (da), Esperanto (eo), Basque (eu), Persian (fa), Finnish (fi), Hebrew (he), Hindi (hi), Croatian (hr), Hungarian (hu), Indonesian (id), Korean (ko), Lithuanian (lt), Malay (ms), Norwegian (Bokmal) (no), Romanian (ro), Slovak (sk), Slovenian (sl), Serbian (sr), Swedish (sv), Turkish (tr), Ukrainian (uk), Vietnamese (vi), Waray-Waray (war), Chinese (zh)\\
+{\sc 100k-500k articles:} Arabic (ar), Bulgarian (bg), Catalan (ca), Czech (cs), Danish (da), Esperanto (eo), Basque (eu), Persian (fa), Finnish (fi), Hebrew (he), Hindi (hi), Croatian (hr), Hungarian (hu), Indonesian (id), Korean (ko), Lithuanian (lt), Malay (ms), Norwegian (Bokmal) (no), Romanian (ro), Slovak (sk), Slovenian (sl), Serbian (sr), Swedish (sv), Turkish (tr), UKrainian (UK), Vietnamese (vi), Waray-Waray (war), Chinese (zh)\\
 \hline
@@
 \hline\hline
-Hindi & 0.64 (296) & \textbf{0.70} (7) & India (284) UAE (5) UK (3)  & Saudi Arabia (2) Russia (1) Oman (1) \\
-Tamil & \textbf{0.65} (273) * & 0.25 (2) & India (266) US (3) Canada (2)  & Tunisia (1) Egypt (1)  \\
-Malayalam & 0.76 (234) & \textbf{0.83} (2) & India (223) UAE (6) US (3)  & Saudi Arabia (1) Maldives (1) \\
-Spanish & 0.81 (191) & \textbf{0.84} (18) & US (122) Mexico (16) Spain (14)  & India (15) Newzealand (1) Brazil (1) \\
-French & 0.75 (170) & \textbf{0.82} (11) & India (62) US (45) France (23)  & Greece (2) Netherlands (1) Japan (1) \\
-Chinese & \textbf{0.60} (116) & 0.55 (21) & US (75) Singapore (13) China (9)  & Hongkong (6) Australia (3) Germany (2)  \\
-German & \textbf{0.83} (91) & 0.77 (41) & Germany (48) US (25) Austria (7)  & India (34) Netherlands (1) Greece (1)  \\
-Italian & \textbf{0.86} (90) & 0.80 (42) & Italy (42) US (29) Romania (7)  & India (33) Ireland (2) Spain (2)  \\
-Amharic & \textbf{0.14} (16) * & 0.01 (99) & US (14) Ethiopia (2)  & India (70) Georgia (9) Macedonia (5)  \\
-Kannada & 0.70 (105) & N/A (0) & India (105)  & \\
-Arabic & \textbf{0.74} (60) * & 0.60 (45) & Egypt (19) Jordan (16) Morocco (9)  & US (19) India (11) Canada (3)  \\
-Sindhi & \textbf{0.19} (96) & 0.06 (9) & India (58) Pakistan (37) US (1)  & Macedonia (4) Georgia (2) Indonesia (2)  \\
-Portuguese & 0.87 (101) & \textbf{0.96} (3) & Brazil (44) Portugal (31) US (15)  & Romania (1) Japan (1) Israel (1) \\
-Turkish & 0.76 (76) & \textbf{0.80} (27) & Turkey (38) US (18) Macedonia (8)  & India (19) Pakistan (4) Taiwan (1) \\
-Telugu & \textbf{0.80} (102) & 0.50 (1) & India (98) US (3) UAE (1)  & Saudi Arabia (1)  \\
-Irish & \textbf{0.74} (54) & 0.71 (47) & US (39) Ireland (13) UK (2)  & India (36) Romania (5) Macedonia (2)  \\
-Swedish & \textbf{0.73} (54) & 0.71 (45) & US (25) Sweden (22) Finland (3)  & India (23) Macedonia (6) Croatia (2)  \\
-Czech & \textbf{0.71} (45) & 0.61 (50) & US (17) Czech Republic (14) Serbia (5)  & Macedonia (22) India (10) UK (5)  \\
-Russian & \textbf{0.15} (67) & 0.12 (27) & US (36) Moldova (7) Russia (6)  & India (14) Macedonia (4) UK (3)  \\
-Breton & 0.17 (3) & \textbf{0.18} (89) & US (3)  & India (83) Macedonia (2) China (1) \\
+Hindi & 0.635 (296) & \textbf{0.695} (7) & India (284) UAE (5) UK (3)  & Saudi Arabia (2) Russia (1) Oman (1) \\
+Tamil & \textbf{0.653} (273) ** & 0.250 (2) & India (266) US (3) Canada (2)  & Tunisia (1) Egypt (1)  \\
+Malayalam & 0.764 (234) & \textbf{0.827} (2) & India (223) UAE (6) US (3)  & Saudi Arabia (1) Maldives (1) \\
+Spanish & 0.814 (191) & \textbf{0.837} (18) & US (122) Mexico (16) Spain (14)  & India (15) New Zealand (1) Brazil (1) \\
+French & 0.750 (170) & \textbf{0.816} (11) & India (62) US (45) France (23)  & Greece (2) Netherlands (1) Japan (1) \\
+Chinese & \textbf{0.601} (116) & 0.552 (21) & US (75) Singapore (13) China (9)  & Hong Kong (6) Australia (3) Germany (2)  \\
+German & \textbf{0.825} (91) & 0.768 (41) & Germany (48) US (25) Austria (7)  & India (34) Netherlands (1) Greece (1)  \\
+Italian & \textbf{0.863} (90) * & 0.796 (42) & Italy (42) US (29) Romania (7)  & India (33) Ireland (2) Spain (2)  \\
+Amharic & \textbf{0.136} (16) ** & 0.009 (99) & US (14) Ethiopia (2)  & India (70) Georgia (9) Macedonia (5)  \\
+Kannada & 0.704 (105) & NA (0) & India (105)  & \\
+Arabic & \textbf{0.741} (60) ** & 0.604 (45) & Egypt (19) Jordan (16) Morocco (9)  & US (19) India (11) Canada (3)  \\
+Sindhi & \textbf{0.190} (96) & 0.062 (9) & India (58) Pakistan (37) US (1)  & Macedonia (4) Georgia (2) Indonesia (2)  \\
+Portuguese & 0.869 (101) & \textbf{0.963} (3) & Brazil (44) Portugal (31) US (15)  & Romania (1) Japan (1) Israel (1) \\
+Turkish & 0.759 (76) & \textbf{0.804} (27) & Turkey (38) US (18) Macedonia (8)  & India (19) Pakistan (4) Taiwan (1) \\
+Telugu & \textbf{0.799} (102) & 0.500 (1) & India (98) US (3) UAE (1)  & Saudi Arabia (1)  \\
+Irish & \textbf{0.742} (54) & 0.709 (47) & US (39) Ireland (13) UK (2)  & India (36) Romania (5) Macedonia (2)  \\
+Swedish & \textbf{0.734} (54) & 0.711 (45) & US (25) Sweden (22) Finland (3)  & India (23) Macedonia (6) Croatia (2)  \\
+Czech & \textbf{0.706} (45) * & 0.612 (50) & US (17) Czech Republic (14) Serbia (5)  & Macedonia (22) India (10) UK (5)  \\
+Russian & \textbf{0.146} (67) * & 0.119 (27) & US (36) Moldova (7) Russia (6)  & India (14) Macedonia (4) UK (3)  \\
+Breton & 0.167 (3) & \textbf{0.178} (89) & US (3)  & India (83) Macedonia (2) China (1) \\
 \hline\hline
@@
 In general, in-region Turkers provide higher quality translations.
-(*) indicates differences significant at p=0.05.} \label{region-summary}
+(*) indicates differences significant at p=0.05, (**) at p=0.10.} \label{region-summary}
 \end{table*}
@@
 &medium&slow&Bengali,  Bishnupriya Manipuri, Cebuano,  Chinese, Nepali, Newar, Polish, Russian, Sindhi, Tibetan\\\cline{1-4}
-few &high  &fast& bs hr mk ms sh\\\cline{3-4}
-&&slow&af an ast bcl be bg cs da el eu fi fy gl ht hu id ilo is ja jv kk ko lt mg nds no pam scn sk sl sq th uk uz war yo\\\cline{2-4}
+few &high  &fast& Bosnia, Croatian  Macedonian  Malay  Serbo-Croatian\\\cline{3-4}
+&&slow&Afrikaans, Albanian, Aragonese, Asturian, Basque, Belarusian, Bulgarian, Central Bicolano, Czech, Danish, Finnish, Galacian, Greek, Haitian, Hungarian, Icelandic, Ilokano, Indonesian, Japanese, Javanese, Kapampangan, Kazakh, Korean, Lithuanian, Low Saxon, Malagasy, Norwegian (Bokmal), Sicilian, Slovak, Slovenian, Thai, UKranian, Uzbek, Waray-Waray, West Frisian, Yoruba\\\cline{2-4}
 &low or  &fast&--\\\cline{3-4}
-&medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}am az br ca cy hy ka lb lv nap nn pms ps so su sw tt vi wa \\\hline
-none&low or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}diq eo fa io ku qu wo \\\hline
+&medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}Amharic,  Armenian, Azerbaijani, Breton, Catalan, Georgian, Latvian, Luxembourgish, Neapolitian, Norwegian (Nynorsk), Pashto, Piedmontese, Somali, Sudanese, Swahili, Tatar, Vietnamese, Walloon, Welsh \\\hline
+none&low or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}  Esperanto, Ido, Kurdish, Persian, Quechua, Wolof, Zazaki\\\hline
 \end{tabular}
@@
 %As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
-We had external bilingual dictionaries for 24 of the 100 languages examined in this study.\footnote{The bilingual dictionaries were between English and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz.
+We had external bilingual dictionaries for 24 of the 100 languages examined in this study.\footnote{The bilingual dictionaries were between English and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, UK, ur, and uz.
 }  We used each of these bilingual dictionaries to compute language-level quality scores, using the dictionary's translation as a gold standard translation for any of the 10,000 foreign words in our study.

### 2013-11-29 code/src/20130905/paper-rewrite/figures/code/region_table.py

@@ -27,10 +27,12 @@ def print_table(lang_counts) :
 		params = (lmap[l].capitalize(),inavg,incnt,outavg,outcnt,topinstr,topoutstr)
 		try : 
 			if inavg > outavg : 
-				if sig : print '%s & \\textbf{%.03f} (%d) * & %.03f (%d) & %s & %s \\\\'%params
+				if sig == '5' : print '%s & \\textbf{%.03f} (%d) ** & %.03f (%d) & %s & %s \\\\'%params
+				elif sig == '10' : print '%s & \\textbf{%.03f} (%d) * & %.03f (%d) & %s & %s \\\\'%params
 				else : print '%s & \\textbf{%.03f} (%d) & %.03f (%d) & %s & %s \\\\'%params
 			else: 
-				if sig : print '%s & %.03f (%d) & \\textbf{%.03f} (%d) * & %s & %s\\\\'%params
+				if sig == '5' : print '%s & %.03f (%d) & \\textbf{%.03f} (%d) ** & %s & %s\\\\'%params
+				elif sig == '10' : print '%s & %.03f (%d) & \\textbf{%.03f} (%d) * & %s & %s\\\\'%params
 				else : print '%s & %.03f (%d) & \\textbf{%.03f} (%d) & %s & %s\\\\'%params
 		except : 
 			try : print '%s & %s (%d) & %.03f (%d) & %s & %s\\\\'%params
@@ -96,7 +98,9 @@ for l in region_data :
 	is_significant = False
 	try : 
 		t,p = ttest_ind(region_data[l]['in'], region_data[l]['out'])
-		is_significant = (p < 0.05)	
+		if p < 0.05 : is_significant = '5'
+		elif p < 0.10 : is_significant = '10'
+		else : is_significant = 'X'
 	except ZeroDivisionError: pass
 
 	lang_counts.append((l, inavg, incnt, outavg, outcnt, loc_data[l], incnt+outcnt, is_significant))

### 2013-11-29 writeup/revision 1/paper.tex
significance in table 3
Moving table around

--- 2013-11-29 writeup/revision 1/paper.tex
@@
 
+%\paragraph{Validation of controls} 
+%Higher overlap with Google Translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.27), suggesting that some control translations have already been indexed by Google.
+We therefore investigated the validity of our use of Wikipedia inter-language links as gold standard translations.
+%
+%As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
+We had external bilingual dictionaries for 24 of the 100 languages examined in this study.\footnote{The bilingual dictionaries were between English and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz.
+}  We used each of these bilingual dictionaries to compute language-level quality scores, using the dictionary's translation as a gold standard translation for any of the 10,000 foreign words in our study.
+In some cases, the overlap of words was low, since dictionaries list root forms of words and we translated inflected forms.
+%
+%We ranked the 24 languages based on their translation quality scores according to the external dictionaries, and calculated correlation when compared to the ranking produced by our gold standard control.
+The Pearson correlation was $\rho=0.53$.
+We computed a correlation coefficient of $\rho=0.37$ for ranking of the translation quality of individual Turkers using the two sources of reference translations.
+%
+%Given the strong positive correlation, we are satisfied that the trends reported in this paper hold when using either our gold standard translations or external bilingual dictionaries.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[t]
+\begin{table}
 \centering
-\scriptsize
+\small
+\footnotesize
 \begin{tabular}{|p{.1\linewidth}|p{.1\linewidth}|p{.1\linewidth}|p{0.5\linewidth}|}
 \hline
-workers & quality & speed & \\\hline
+\footnotesize workers & \footnotesize  quality & \footnotesize speed & \\\hline
 %many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5} de es fr gu it kn ml nl pt ro sr te tl \\\cline{3-4}
@@
 \end{tabular}
-\caption{The green box shows the languages which we have found most supported by MTurk in terms of worker population, worker ability, and speed of completion.
-Languages have ``many'' workers if we recorded more than 50 active in-region Turkers.
-Languages are ``high'' quality if they average greater than 70\% accuracy on our controls.
-Languages are ``fast'' if all of our translations (approx.
-10,000 words each) were completed within two weeks.}
+\normalsize
+\caption{The green box shows the best languages to target on MTurk.
+These languages have many workers who generate high quality results quickly.
+We defined {\it many} workers as 50 or more active in-region workers, {\it high} quality as $\geq$70\% accuracy on the gold standard controls, and {\it fast} if all of the 10,000 words were completed within two weeks.}
 \label{recommendations}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\paragraph{Validation of controls} 
-%Higher overlap with Google Translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.27), suggesting that some control translations have already been indexed by Google.
-We therefore investigated the validity of our use of Wikipedia inter-language links as gold standard translations.
-%
-%As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.
-We had external bilingual dictionaries for 24 of the 100 languages examined in this study.\footnote{The bilingual dictionaries were between English and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz.
-}  We used each of these bilingual dictionaries to compute language-level quality scores, using the dictionary's translation as a gold standard translation for any of the 10,000 foreign words in our study.
-In some cases, the overlap of words was low, since dictionaries list root forms of words and we translated inflected forms.
-%
-%We ranked the 24 languages based on their translation quality scores according to the external dictionaries, and calculated correlation when compared to the ranking produced by our gold standard control.
-The Pearson correlation was $\rho=0.53$.
-We computed a correlation coefficient of $\rho=0.37$ for ranking of the translation quality of individual Turkers using the two sources of reference translations.
-%
-%Given the strong positive correlation, we are satisfied that the trends reported in this paper hold when using either our gold standard translations or external bilingual dictionaries.
 
@@
 The dictionaries will contain 1.5M total translated words in 100 languages, along with code to filter the dictionaries based on different criteria.
-The data also includes parallel corpora for six Indian languages, ranging in size between 700,000 to 1.5 million words
+The data also includes parallel corpora for six Indian languages, ranging in size between 700,000 to 1.5 million words.
 

### 2013-11-29 writeup/revision 1/paper.tex

--- 2013-11-29 writeup/revision 1/paper.tex
@@
 In general, in-region Turkers provide higher quality translations.
-(*) indicates differences significant at p=0.05, (**) at p=0.10.} \label{region-summary}
+(**) indicates differences significant at p=0.05, (*) at p=0.10.} \label{region-summary}
 \end{table*}

### 2013-11-29 writeup/revision 1/paper.tex

@@
 \begin{center}
-\includegraphics[width=.7\linewidth]{figures/quality_bar.pdf}
+\includegraphics[width=.9\linewidth]{figures/quality_bar.pdf}
 \caption{Translation quality for languages with at least 50 Turkers.
@@
 \centering
+\footnotesize
 \small
-\footnotesize
 \begin{tabular}{|p{.1\linewidth}|p{.1\linewidth}|p{.1\linewidth}|p{0.5\linewidth}|}
@@
 &&slow& Arabic,  Hebrew, Irish, Punjabi, Swedish, Turkish\\\cline{2-4}
-& low or  &fast& Hindi, Marathi, Tamil, Urdu \\\cline{3-4}
-&medium&slow&Bengali,  Bishnupriya Manipuri, Cebuano,  Chinese, Nepali, Newar, Polish, Russian, Sindhi, Tibetan\\\cline{1-4}
+& low   &fast& Hindi, Marathi, Tamil, Urdu \\\cline{3-4}
+&or medium&slow&Bengali,  Bishnupriya Manipuri, Cebuano,  Chinese, Nepali, Newar, Polish, Russian, Sindhi, Tibetan\\\cline{1-4}
 few &high  &fast& Bosnia, Croatian  Macedonian  Malay  Serbo-Croatian\\\cline{3-4}
 &&slow&Afrikaans, Albanian, Aragonese, Asturian, Basque, Belarusian, Bulgarian, Central Bicolano, Czech, Danish, Finnish, Galacian, Greek, Haitian, Hungarian, Icelandic, Ilokano, Indonesian, Japanese, Javanese, Kapampangan, Kazakh, Korean, Lithuanian, Low Saxon, Malagasy, Norwegian (Bokmal), Sicilian, Slovak, Slovenian, Thai, UKranian, Uzbek, Waray-Waray, West Frisian, Yoruba\\\cline{2-4}
-&low or  &fast&--\\\cline{3-4}
-&medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}Amharic,  Armenian, Azerbaijani, Breton, Catalan, Georgian, Latvian, Luxembourgish, Neapolitian, Norwegian (Nynorsk), Pashto, Piedmontese, Somali, Sudanese, Swahili, Tatar, Vietnamese, Walloon, Welsh \\\hline
+&low   &fast&--\\\cline{3-4}
+&or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}Amharic,  Armenian, Azerbaijani, Breton, Catalan, Georgian, Latvian, Luxembourgish, Neapolitian, Norwegian (Nynorsk), Pashto, Piedmontese, Somali, Sudanese, Swahili, Tatar, Vietnamese, Walloon, Welsh \\\hline
 none&low or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}  Esperanto, Ido, Kurdish, Persian, Quechua, Wolof, Zazaki\\\hline

### 2013-11-29 writeup/revision 1/reviewer-response/reviewer-response.tex
Updated reviewer response document.

@@
 
+\usepackage{colortbl}
+
 \setlength\titlebox{5cm}    % Expanding the titlebox
@@
 
-\title{The Language Demographics of  Amazon Mechanical Turk : Response  to Reviewers}
+\title{Response  to Reviewers: The Language Demographics of  Amazon Mechanical Turk}
 
-\author{Ellie Pavlick\affliationPenn \ \ \ \ \ Ann Irvine\affliationJHU  \ \ \ \ \ Dmitry Kachaev\affliationJHU  \ \ \ \ \  Chris Callison-Burch\affliationPenn$^{,}$\affliationJHU \\
+\author{Ellie Pavlick\affliationPenn \ \ \ \ \ Matt Post\affliationJHU \ \ \ \ \ Ann Irvine\affliationJHU  \ \ \ \ \ Dmitry Kachaev\affliationJHU  \ \ \ \ \  Chris Callison-Burch\affliationPenn$^{,}$\affliationJHU \\
 \affliationPenn Computer and Information Science Department, University of Pennsylvania \\
@@
 
-%\begin{figure}
-%\centering
-%\begin{subfigure}[b]{1\linewidth}
-%\includegraphics[width=\textwidth]{figures/turker-googmatch-distribution.png}
-%\caption{Individual turker overlap with Google Translate.
-We remove the 500 workers with the highest overlap (shaded region on the left) from our analysis, as it is reasonable to assume these workers are cheating by submitting translations from Google.
-We believe the workers with no overlap (shaded region on the right) are also likely to be cheating, e.g.
-by submitting random text, and we target these workers through our embedded quality controls.}
-%\label{dist}
-%\end{subfigure}
-%\begin{subfigure}[b]{1\linewidth}
-%\includegraphics[width=\textwidth]{figures/google-cdf-googlangs.png}
-%\caption{Cumulative distribution of overlap with Google translate for workers and translations.
-We see that eliminating all workers with \textgreater 70\% overlap with google translate still preserves 90\% of translations and \textgreater 90\% of workers.}
-%\label{cdf}
-%\end{subfigure}
-%\caption{}\label{cheaters}
-%\end{figure}
+This document describes the changes that we made in response to the reviewers' suggestions.
+Mirella Lapata, the Action Editor for this submission, distilled the reviews' suggestions into three critical action items:
+\begin{enumerate}
+\item All reviewers had issues with the amount of cheating taking place among
+Turkers. It would be useful to quantify/detect this and remove such
+participants from your results. 
+%Reviewers F and G provide interesting
+%suggestions on how to do this.
+\item Provide additional analysis showing that translation accuracy is not due
+to a few individuals who happened to do most of your tasks
+% (e.g., using random effects models)
+\item  It would also be interesting to assess
+whether your results carry over to sentences and to show that the proposed approach brings an
+advantage over current SMT technology.  Do the lexical translations improve
+ SMT systems? 
+\end{enumerate}
 
-\section{Use of Google Translate : Editor and all reviewers}
+\section{Cheating with Google Translate}
 
-The primary concern across reviewers was the high amount of overlap between workers' translations and translations available through online resources, i.e. Google Translate. The editor summarized : 
+The primary concern across reviewers was that the experimental methodology was flawed since it failed to prevent workers from using online resources like.
+Google Translate to create the translations, and therefore may not reflect the true language abilities of workers on Mechanical Turk.
+Although our gold-standard controls do a good job at detecting workers who cheated by submitting random words in place of actual translations, it did a poor job at detecting users who simply typed the words into Google Translate.
+Since Google likely includes WIkipedia inter-language links as part of its training data for Google Translate, the translations that it produces would likely count as correct translations.
+This would result in us over-estimating the translation quality per-language, and in the number of proficient speakers for the languages that Google covers.
+
+Our initial overlap were inconclusive.  As reviewer E points out: 
 \begin{quote}
-All reviewers had issues with the amount of cheating taking place among Turkers. It would be useful to quantify/detect this and remove such participants from your results.
+The problem with this design is that workers can easily find
+these highly frequent words in a dictionary or translation system. The
+authors test this possibility by comparing the workers' translations with
+that of Google Translate, and show that there is 42\% overlap between these
+two sets of answers. But this cannot be taken as evidence that almost half
+of the workers cheated, since it is quite possible that a fluent speaker of
+a language provides the same translation as Google Translate for a given
+word. In other words, the performance results are inconclusive.
+\end{quote}
+Reviewer G echoed this, saying
+\begin{quote}
+The evidence of widespread cheating on the task, and the apparent
+effectiveness of machine translation at solving the task, means that it is
+hard to evaluate which responses were generated by native speakers.
 \end{quote}
@@
 
-We took at closer look at the amount of overlap with Google translate in our collected translations in order to address this issue.
-We found that while overall overlap is high, it is not consistantly high across all turkers.
-Figure \ref{dist} shows that while a small number of turkers have a very high amount of overlap with Google (near 80\%) the majority overlap less than half of the time.
+We have re-done our analysis to address this issue.
+We compute the overlap between individual Turkers and Google translate (across all items, not just our controls).
+Figure \ref{dist} plots the overlap, ranking from the Turker with the most overlap to the Turker with the least overlap.
+To address the reviewers' concerns, we exclude the 500 Turkers with the highest overlap with Google translate, and remove them from all subsequent analyses in the paper.
+This is equivalent to choosing a threshold value of approximately 70\% overlap, and excluding all Turkers whose translations overlap with Google at that rate or higher.
+Figure \ref{cdf} shows that removing workers at or above the 70\% threshold retains 90\% of the collected translations and over 90\% of the workers.
 
-%As Reviewer E noted :
+Our methodology now catches two types of cheating that can be done by Turkers who do not truly speak the language: 
+\begin{enumerate}
+\item Submitting random words -- detected by low accuracy on our gold standard controls.
+\item Using online MT systems or dictionaries (approximated with Google Translate) -- detected by high overlap with Google on all items.
+\end{enumerate}
 
-%\begin{quote}
-%..it is quite possible that a fluent speaker of a language provides the same translation as Google Translate for a given word.  In other words, the performance results are inconclusive.
-%\end{quote}
+This modification to our experimental design excludes the Indian workers who were producing good Afrikaans-English translations, which Reviewer B highlighted as problematic.
 
-It seems likely that those with very high overlap are cheating, but it is also reasonable to assume that honest turkers will overlap with Google with some regularity.
-We therefore divide the workers into three groups : those with very high overlap with Google (likely cheating by using Google to translate words), those with reasonable overlap, and those with no overlap (likely cheating by other means, e.g.
-submitting random text).
-Our controls are designed to identify workers that fall into the third group (those who are spamming or providing useless translations), but they will not effectively flag workers who are cheating with Google Translate.
+Figure \ref{qual} shows how the overall quality estimates for each language have changed between the initial submission of the paper (top graph) and this revised version (bottom graph).
 
-We chose to remove the 500 turkers with the highest overlap with Google.
-This equates to removing all workers with greater than 70\% overlap.
-Figure \ref{cdf} shows that removing workers at or above the 70\% threshold retains 90\% of the collected translations and over 90\% of the workers.
+%\begin{figure}
+%\includegraphics[width=\linewidth]{figures/quality-all.png}
+%\caption{All turkers.}                
+%\label{quality-all}
+%\end{figure}
+%\begin{figure}
+%\includegraphics[width=\linewidth]{figures/quality-filtered.png}
+%\caption{Turkers with \textless 70\% overlap with Google Translate.}
+%\label{quality-filtered}
+%\caption{Qualities for languages with \textgreater 50 turkers.
+Dark blue shows quality measured by perfect match on the control translation.
+Light blue indicates quality measured by included synonymous translations.}\label{qual}
+%\end{figure}
+
+Reviewer E also had an interesting suggestion on an alternate way that this problem could have been addressed:
+\begin{quote}
+This problem could have been avoided if the assignments were more suitable
+for measuring real language proficiency. For example, unlike single-word
+translations which can be solely conducted using a language resource,
+phrase- or sentence-level translations are a more realistic indication of
+the translator's knowledge of language. The challenge here would be to
+devise the control set, i.e., to come up with gold standard translations of
+such multi-word units. 
+\end{quote}
+At the outset of the study we considered asking workers to translate full sentences instead of individual words.
+As the reviewer notes, it is quite challenging to find good controls for such a broad range of languages.
+Ideally, we would have liked to have re-created Zaidan and Callison-Burch (2011)'s comparison of Turker translations of Urdu to professional translations, and applied it to 100 languages.
+Unfortunately, finding a good set of test sentences for each language proved impossible.
+While there are some documents which have been translated into all languages, like the Bible or the Universal Declaration of Human Rights, it is probable that Google already includes them in its training data.
+
+Instead of attempting all languages, and systematically comparing the quality of professionals against non-professionals, we create sentential translations for 6 languages, and train machine translation systems from the resulting parallel corpora.
+This is described in section \ref{smt-results}.
+
+\section{Are the results robust, or do a few big contributors dominate?}
+
+The Action Editor and Reviewer G highlighted the possibility that the quality results are due to a few large players, and may not be robust if the experiment were rerun with a different group of workers:
+\begin{quote}
+Provide additional analysis showing that translation accuracy is not due to a few individuals who happened to do most of your tasks.
+\end{quote}
+
+We agree that this is a valid concern since many languages followed the pattern of having a small number of very active Turkers complete the majority of assignments.
+In the new version of the paper, we account for this by defining our per-language accuracy as an average over {\it Turker qualities}, rather than over {\it assignment qualities}.
+With this method, each Turker contributes equally to the language's average quality, regardless of the number of HITs that that Turker submitted.
+Section 4 of the paper has been updated to reflect this change.
+
+Figure \ref{qual_dots} shows the quality scores for languages computed over assignments and over Turkers, and the change in each when the 10 most active Turkers in each language are removed.
+We can see that the per-Turker quality measure is robust to the exclusion of these highly-contributing Turkers.
+
+For completeness, we have also updated our reported quality scores in the paper to include confidence intervals and p-values, where appropriate.
+We hope this helps to reduce concern about the robustness of these measures.
 
@@
 
-We have rerun the quality analysis in the paper, omitting workers with \textgreater 70\% overlap with Google Translate.
-The quality scores and rankings do not change substantially.
-For reference, figure \ref{qual} shows the quality scores for languages when computed over all Turkers as in the original draft of the paper (figure \ref{quality-all}) and computed over only Turkers with less than 70\% overlap with Google (figure \ref{quality-filtered}).
-In our new draft of the paper, we have omitted Tukers with more than 70\% overlap from all of our quality computations.
-
-%\begin{figure}
-%\includegraphics[width=\linewidth]{figures/quality-all.png}
-%\caption{All turkers.}                
-%\label{quality-all}
-%\end{figure}
-%\begin{figure}
-%\includegraphics[width=\linewidth]{figures/quality-filtered.png}
-%\caption{Turkers with \textless 70\% overlap with Google Translate.}
-%\label{quality-filtered}
-%\caption{Qualities for languages with \textgreater 50 turkers.
-Dark blue shows quality measured by perfect match on the control translation.
-Light blue indicates quality measured by included synonymous translations.}\label{qual}
-%\end{figure}
-
-\section{Robustness of results to removing few big players: Editor and all reviewers}
-
-The editor and reviewer G highlighted the possibility that the quality results are due to a few large players, and may not be robust if the experiment were rerun with a different group of workers : 
-\begin{quote}
-Provide additional analysis showing that translation accuracy is not due to a few individuals who happened to do most of your tasks.
-\end{quote}
-
-We agree that this is a valid concern since many languages followed the pattern of having a small number of very active Turkers complete the majority of assignments.
-We account of this by reporting qualities of each language as an average over Turker qualities, rather than over assignment qualities.
-By this method, each Turker contributes equally to the language's average quality, regardless of the number of HITs that that Turker submitted.
-Section 4 of the paper has been updated to reflect this change.
-Figure \ref{qual_dots} shows the quality scores for languages computed over assignments and over Turkers, and the change in each when the 10 most active Turkers in each language are removed.
-We can see that the per-Turker quality measure is robust to the exclusion of these highly-contributing Turkers.
-
-For completeness, we have also updated our reported quality scores in the paper to include confidence intervals and p-values, where appropriate.
-We hope this helps to reduce concern about the robustness of these measures.
-
 %\begin{figure}
@@
 
+\section{Using crowdsourced data to train SMT systems, and evaluating the improvements due to dictionaries}\label{smt-results}
+
+All the reviewers expressed desire for further evidence of the usefulness of the Turker-provided translations for statistical machine translation, and the possibility of extending the demonstrated methods to multiple word translations.
+To address these suggestions, we have added a new set of experiments to the paper.
+In the new experiments, we collect full-sentence translations for six Indian languages which are well-represented on MTurk but for which there are currently no professionally-translated corpora available.
+We use the collected sentences to train and evaluate an SMT system, and show that the systems achieve decent performance.
+Furthermore, we add the collected single-word dictionaries to the training of these systems, and show that this produces measurable improvement in performance.
+Table \ref{dictionary_bleu} highlights these results.
+Please see sections 3 and 5 of the revised paper for a complete discussion of the data and experiments.
+
+{\bf NB: We previously published experiments using this Indian language data, but the work has only appeared in an ACL workshop paper and not in a main conference paper nor a journal article.
+We hope that it is therefore allowable for inclusion here.}.
+The workshop publication will be cited appropriately in the final version of the paper, but we omit the citation now so as not to de-anonymize the submission.
+
 \begin{figure}
@@
 \end{figure}
-
-\section{Extrinsic evalutation of mturk data for SMT: Editor and all reviewers}
-
-All the reviewers expressed desire for further evidence of the usefulness of the Turker-provided translations for statistical machine translation, and the possibility of extending the demonstrated methods to multiple word translations.
-The editor requests :
-
-\begin{quote}
-It would be interesting to show that the proposed approach brings an advantage over current SMT technology, i.e., improves lexical translations for an existing SMT system....It would also be interesting to assess whether your results carry over to multiple words and/or sentences.
-\end{quote}
-
-To address these concerns, we incorporate previous work from a workshop publication from our colleague.
-The workshop publication will be cited appropriately in the final version of the paper, but we omit the citation now so as not to de-anonymize the submission.
-
-In this work, we collect full-sentence translations for six Indian languages which are well-represented on MTurk but for which there are currently no professionally-translated corpora available.
-We use the collected sentences to train and evaluate an SMT system, and show that the systems achieve decent performance.
-Furthermore, we add the collected single-word dictionaries to the training of these systems, and show that this produces measurable improvement in performance.
-Table \ref{dictionary_bleu} highlights these results.
-Please see sections 3 and 5 of the revised paper for a complete discussion of the data and experiments.
 
@@
 
-\section{Affect of time of day when HIT was posted: Reviewer F}
+\section{Other suggestions: Does time of day that HIT was posted change the outcome?}
 
-You raised an interesting question about the affect of time of day on Turker activity :
+Reviewer F raised a question about the relation between time of day and Turker activity:
 
@@
 
-\section{Changes in results if study continued over time: Reviewer B}
+\section{Other suggestions: longitudinal study. }
 
-You asked : 
+ Reviewer B asked: 
 \begin{quote}
@@
 While we agree that the questions posed are very interesting, we feel that answering these questions is the subject of another study.
-It is true that the current demongraphic makeup of MTurk workers is likely to shift, but we cannot currently take on the expense of conducting a long term study (the study presented here cost ~40K).
-We have updated the text of the paper to emphasize this limitation in our results by adding the following sentences to our Overview:
+It is true that the current demographic makeup of MTurk workers is likely to shift, but we cannot currently take on the expense of conducting a long term study (the study presented here cost more than \$40K).
+We have updated the text of the paper to emphasize this limitation in our results by adding the following sentences to our Discussion section:
 \begin{quote}
-While the demographics reported are likely to shift overtime, as Amazon expands its methods of payments and reaches new countries, the data presented provides a 
-valuable snapshot of the current state of MTurk, and the methods used can be applied generally in future research.
+The demographics reported in this study are likely to shift over time.
+Amazon may change its expand its payments to new currencies.
+Posting long-running HITs in other languages may recruit more speakers of those languages.
+New crowdsourcing platforms may emerge.
+The data presented here provides a valuable snapshot of the current state of MTurk, and the methods used can be applied generally in future research.
 \end{quote}
 
-\section{Accuracy of Geolocation: Reviewers B and E}
+\section{Other suggestion: Accuracy of Geolocation}
 
+Reviewers B and E were concerned about the accuracy of geolocation. 
 We understand that geolocation is not perfect, which is why we propose the use of location data as just one of several criteria by which to identify likely qualified translators.
@@
 
+\section{Other improvements: Conclusions}
+
+We have strengthened the conclusions to be more clear.
+We have included a table that shows what languages are currently good for researchers to target based on the size of the speaker populations, the quality of the translations, and how fast the translations were completed.
+Table \ref{recommendations} now appears in the Discussion section of the revised submission.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+\centering
+\footnotesize
+\small
+\begin{tabular}{|p{.1\linewidth}|p{.1\linewidth}|p{.1\linewidth}|p{0.5\linewidth}|}
+\hline
+\footnotesize workers & \footnotesize  quality & \footnotesize speed & \\\hline
+%many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5} de es fr gu it kn ml nl pt ro sr te tl \\\cline{3-4}
+%&&slow& ar ga he pa sv tr\\\cline{2-4}
+%& low or medium &fast& hi mr ta ur \\\cline{3-4}
+%&&slow&bn bo bpy ceb ne new pl ru sd zh\\\cline{1-4}
+many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5}    Dutch, French, German, Gujarati, Italian, Kannada, Malayalam, Portuguese, Romanian, Serbian, Spanish, Tagalog, Telugu \\\cline{3-4}
+&&slow& Arabic,  Hebrew, Irish, Punjabi, Swedish, Turkish\\\cline{2-4}
+& low   &fast& Hindi, Marathi, Tamil, Urdu \\\cline{3-4}
+&or medium&slow&Bengali,  Bishnupriya Manipuri, Cebuano,  Chinese, Nepali, Newar, Polish, Russian, Sindhi, Tibetan\\\cline{1-4}
+few &high  &fast& Bosnia, Croatian  Macedonian  Malay  Serbo-Croatian\\\cline{3-4}
+&&slow&Afrikaans, Albanian, Aragonese, Asturian, Basque, Belarusian, Bulgarian, Central Bicolano, Czech, Danish, Finnish, Galacian, Greek, Haitian, Hungarian, Icelandic, Ilokano, Indonesian, Japanese, Javanese, Kapampangan, Kazakh, Korean, Lithuanian, Low Saxon, Malagasy, Norwegian (Bokmal), Sicilian, Slovak, Slovenian, Thai, UKranian, Uzbek, Waray-Waray, West Frisian, Yoruba\\\cline{2-4}
+&low   &fast&--\\\cline{3-4}
+&or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}Amharic,  Armenian, Azerbaijani, Breton, Catalan, Georgian, Latvian, Luxembourgish, Neapolitian, Norwegian (Nynorsk), Pashto, Piedmontese, Somali, Sudanese, Swahili, Tatar, Vietnamese, Walloon, Welsh \\\hline
+none&low or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}  Esperanto, Ido, Kurdish, Persian, Quechua, Wolof, Zazaki\\\hline
+\end{tabular}
+\normalsize
+\caption{The green box shows the best languages to target on MTurk.
+These languages have many workers who generate high quality results quickly.
+We defined {\it many} workers as 50 or more active in-region workers, {\it high} quality as $\geq$70\% accuracy on the gold standard controls, and {\it fast} if all of the 10,000 words were completed within two weeks.}
+\label{recommendations}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2013-11-29 writeup/revision 1/reviewer-response/reviewer-response.tex

@@
 
-This modification to our experimental design excludes the Indian workers who were producing good Afrikaans-English translations, which Reviewer B highlighted as problematic.
+This modification to our experimental design excludes the Indian workers who were producing good Afrikaans-English translations, which Reviewer F highlighted as problematic.
 

### 2013-11-29 writeup/revision 1/reviewer-response/reviewer-response.tex
Updates to reviewer response document.
Minor edit

@@
 The workshop publication will be cited appropriately in the final version of the paper, but we omit the citation now so as not to de-anonymize the submission.
+The analysis of the effect of the dictionaries on the SMT performance is new.
 
@@
 
-\section{Other improvements: Conclusions}
+\section{Other suggestions: specific recommendations}
+
+Reviewer F said:
+\begin{quote}
+I was a little disappointed that the paper does not provide more specific
+recommendations for low-resource languages.
+\end{quote}
 
@@
 few &high  &fast& Bosnia, Croatian  Macedonian  Malay  Serbo-Croatian\\\cline{3-4}
-&&slow&Afrikaans, Albanian, Aragonese, Asturian, Basque, Belarusian, Bulgarian, Central Bicolano, Czech, Danish, Finnish, Galacian, Greek, Haitian, Hungarian, Icelandic, Ilokano, Indonesian, Japanese, Javanese, Kapampangan, Kazakh, Korean, Lithuanian, Low Saxon, Malagasy, Norwegian (Bokmal), Sicilian, Slovak, Slovenian, Thai, UKranian, Uzbek, Waray-Waray, West Frisian, Yoruba\\\cline{2-4}
+&&slow&Afrikaans, Albanian, Aragonese, Asturian, Basque, Belarusian, Bulgarian, Central Bicolano, Czech, Danish, Finnish, Galacian, Greek, Haitian, Hungarian, Icelandic, Ilokano, Indonesian, Japanese, Javanese, Kapampangan, Kazakh, Korean, Lithuanian, Low Saxon, Malagasy, Norwegian (Bokmal), Sicilian, Slovak, Slovenian, Thai, Ukranian, Uzbek, Waray-Waray, West Frisian, Yoruba\\\cline{2-4}
 &low   &fast&--\\\cline{3-4}

### 2013-11-29 writeup/revision 1/paper.tex
Updates to reviewer response document.
Minor edit

@@
 \hline
-{\sc 100k-500k articles:} Arabic (ar), Bulgarian (bg), Catalan (ca), Czech (cs), Danish (da), Esperanto (eo), Basque (eu), Persian (fa), Finnish (fi), Hebrew (he), Hindi (hi), Croatian (hr), Hungarian (hu), Indonesian (id), Korean (ko), Lithuanian (lt), Malay (ms), Norwegian (Bokmal) (no), Romanian (ro), Slovak (sk), Slovenian (sl), Serbian (sr), Swedish (sv), Turkish (tr), UKrainian (UK), Vietnamese (vi), Waray-Waray (war), Chinese (zh)\\
+{\sc 100k-500k articles:} Arabic (ar), Bulgarian (bg), Catalan (ca), Czech (cs), Danish (da), Esperanto (eo), Basque (eu), Persian (fa), Finnish (fi), Hebrew (he), Hindi (hi), Croatian (hr), Hungarian (hu), Indonesian (id), Korean (ko), Lithuanian (lt), Malay (ms), Norwegian (Bokmal) (no), Romanian (ro), Slovak (sk), Slovenian (sl), Serbian (sr), Swedish (sv), Turkish (tr), Ukrainian (UK), Vietnamese (vi), Waray-Waray (war), Chinese (zh)\\
 \hline
@@
 As a best practice, we suggest: (1) restricting workers to countries that plausibly speak the foreign language of interest, (2) embedding gold standard controls or administering language pretests, rather than relying solely on self-reported language skills, and (3) and excluding workers whose translations have high overlap with online machine translation systems like Google translate.
+If cheating using external resources is likely, then also consider (4) recording information like time spent on a HIT (cumulative and on individual items), patterns in keystroke logs, tab/window focus, etc.
 

### 2014-01-26 writeup/revision 1/reviewer-response/reviewer-response.tex
final revision of paper

@@
 
-The primary concern across reviewers was that the experimental methodology was flawed since it failed to prevent workers from using online resources like.
-Google Translate to create the translations, and therefore may not reflect the true language abilities of workers on Mechanical Turk.
+The primary concern across reviewers was that the experimental methodology was flawed since it failed to prevent workers from using online resources like Google Translate to create the translations, and therefore may not reflect the true language abilities of workers on Mechanical Turk.
 Although our gold-standard controls do a good job at detecting workers who cheated by submitting random words in place of actual translations, it did a poor job at detecting users who simply typed the words into Google Translate.
-Since Google likely includes WIkipedia inter-language links as part of its training data for Google Translate, the translations that it produces would likely count as correct translations.
-This would result in us over-estimating the translation quality per-language, and in the number of proficient speakers for the languages that Google covers.
+Since Google likely includes Wikipedia inter-language links as part of its training data for Google Translate, the translations that it produces would likely count as correct translations.
+This would result in us over-estimating the translation quality per-language and the number of proficient speakers for the languages that Google covers.
 
-Our initial overlap were inconclusive.  As reviewer E points out: 
+Our initial overlap calculations were inconclusive.  As reviewer E points out: 
 \begin{quote}
@@
 &or medium&slow&Bengali,  Bishnupriya Manipuri, Cebuano,  Chinese, Nepali, Newar, Polish, Russian, Sindhi, Tibetan\\\cline{1-4}
-few &high  &fast& Bosnia, Croatian  Macedonian  Malay  Serbo-Croatian\\\cline{3-4}
+few &high  &fast& Bosnia, Croatian,  Macedonian,  Malay,  Serbo-Croatian\\\cline{3-4}
 &&slow&Afrikaans, Albanian, Aragonese, Asturian, Basque, Belarusian, Bulgarian, Central Bicolano, Czech, Danish, Finnish, Galacian, Greek, Haitian, Hungarian, Icelandic, Ilokano, Indonesian, Japanese, Javanese, Kapampangan, Kazakh, Korean, Lithuanian, Low Saxon, Malagasy, Norwegian (Bokmal), Sicilian, Slovak, Slovenian, Thai, Ukranian, Uzbek, Waray-Waray, West Frisian, Yoruba\\\cline{2-4}

### 2014-01-26 writeup/final revision/paper.tex
final revision of paper

--- 2013-11-29 writeup/revision 1/paper.tex
@@
 
-\author{Ellie Pavlick\affliationPenn \ \ \ \ \ Ann Irvine\affliationJHU  \ \ \ \ \ Dmitry Kachaev\affliationJHU  \ \ \ \ \  Chris Callison-Burch\affliationPenn$^{,}$\affliationJHU \\
+\author{Ellie Pavlick\affliationPenn \ \ \ \ \ Matt Post\affliationJHU \ \ \ \ \  Ann Irvine\affliationJHU  \ \ \ \ \ Dmitry Kachaev\affliationJHU  \ \ \ \ \  Chris Callison-Burch\affliationPenn$^{,}$\affliationJHU \\
 \affliationPenn Computer and Information Science Department, University of Pennsylvania \\
@@
   }
-
-% Anonymized for submission
-\author{}
 
@@
 We drew our data from the different language versions of Wikipedia.
-We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} (Table \ref{Wikipedia-buckets}).
+We selected the 100 languages with the largest number of articles \footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} (Table \ref{Wikipedia-buckets}).
 For each language, we chose the 1,000 most viewed articles over a 1 year period,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and extracted the 10,000 most frequent words from them.
@@
 Figure \ref{dist} shows overlap between Turkers's translations and Google Translate.
-When overlap is high, it seems likely that those with very high overlap are cheating.
+When overlap is high, it seems likely that those Turkers are cheating.
 It is also reasonable to assume that honest workers will overlap with Google some amount of the time as Google's translations are usually accurate.
@@
 \hline\hline
-Hindi & 0.635 (296) & \textbf{0.695} (7) & India (284) UAE (5) UK (3)  & Saudi Arabia (2) Russia (1) Oman (1) \\
-Tamil & \textbf{0.653} (273) ** & 0.250 (2) & India (266) US (3) Canada (2)  & Tunisia (1) Egypt (1)  \\
-Malayalam & 0.764 (234) & \textbf{0.827} (2) & India (223) UAE (6) US (3)  & Saudi Arabia (1) Maldives (1) \\
-Spanish & 0.814 (191) & \textbf{0.837} (18) & US (122) Mexico (16) Spain (14)  & India (15) New Zealand (1) Brazil (1) \\
-French & 0.750 (170) & \textbf{0.816} (11) & India (62) US (45) France (23)  & Greece (2) Netherlands (1) Japan (1) \\
-Chinese & \textbf{0.601} (116) & 0.552 (21) & US (75) Singapore (13) China (9)  & Hong Kong (6) Australia (3) Germany (2)  \\
-German & \textbf{0.825} (91) & 0.768 (41) & Germany (48) US (25) Austria (7)  & India (34) Netherlands (1) Greece (1)  \\
-Italian & \textbf{0.863} (90) * & 0.796 (42) & Italy (42) US (29) Romania (7)  & India (33) Ireland (2) Spain (2)  \\
-Amharic & \textbf{0.136} (16) ** & 0.009 (99) & US (14) Ethiopia (2)  & India (70) Georgia (9) Macedonia (5)  \\
-Kannada & 0.704 (105) & NA (0) & India (105)  & \\
-Arabic & \textbf{0.741} (60) ** & 0.604 (45) & Egypt (19) Jordan (16) Morocco (9)  & US (19) India (11) Canada (3)  \\
-Sindhi & \textbf{0.190} (96) & 0.062 (9) & India (58) Pakistan (37) US (1)  & Macedonia (4) Georgia (2) Indonesia (2)  \\
-Portuguese & 0.869 (101) & \textbf{0.963} (3) & Brazil (44) Portugal (31) US (15)  & Romania (1) Japan (1) Israel (1) \\
-Turkish & 0.759 (76) & \textbf{0.804} (27) & Turkey (38) US (18) Macedonia (8)  & India (19) Pakistan (4) Taiwan (1) \\
-Telugu & \textbf{0.799} (102) & 0.500 (1) & India (98) US (3) UAE (1)  & Saudi Arabia (1)  \\
-Irish & \textbf{0.742} (54) & 0.709 (47) & US (39) Ireland (13) UK (2)  & India (36) Romania (5) Macedonia (2)  \\
-Swedish & \textbf{0.734} (54) & 0.711 (45) & US (25) Sweden (22) Finland (3)  & India (23) Macedonia (6) Croatia (2)  \\
-Czech & \textbf{0.706} (45) * & 0.612 (50) & US (17) Czech Republic (14) Serbia (5)  & Macedonia (22) India (10) UK (5)  \\
-Russian & \textbf{0.146} (67) * & 0.119 (27) & US (36) Moldova (7) Russia (6)  & India (14) Macedonia (4) UK (3)  \\
-Breton & 0.167 (3) & \textbf{0.178} (89) & US (3)  & India (83) Macedonia (2) China (1) \\
+Hindi & 0.63 (296) & \textbf{0.69} (7) & India (284) UAE (5) UK (3)  & Saudi Arabia (2) Russia (1) Oman (1) \\
+Tamil & \textbf{0.65} (273) ** & 0.25 (2) & India (266) US (3) Canada (2)  & Tunisia (1) Egypt (1)  \\
+Malayalam & 0.76 (234) & \textbf{0.83} (2) & India (223) UAE (6) US (3)  & Saudi Arabia (1) Maldives (1) \\
+Spanish & 0.81 (191) & \textbf{0.84} (18) & US (122) Mexico (16) Spain (14)  & India (15) New Zealand (1) Brazil (1) \\
+French & 0.75 (170) & \textbf{0.82} (11) & India (62) US (45) France (23)  & Greece (2) Netherlands (1) Japan (1) \\
+Chinese & \textbf{0.60} (116) & 0.55 (21) & US (75) Singapore (13) China (9)  & Hong Kong (6) Australia (3) Germany (2)  \\
+German & \textbf{0.82} (91) & 0.77 (41) & Germany (48) US (25) Austria (7)  & India (34) Netherlands (1) Greece (1)  \\
+Italian & \textbf{0.86} (90) * & 0.80 (42) & Italy (42) US (29) Romania (7)  & India (33) Ireland (2) Spain (2)  \\
+Amharic & \textbf{0.14} (16) ** & 0.01 (99) & US (14) Ethiopia (2)  & India (70) Georgia (9) Macedonia (5)  \\
+Kannada & 0.70 (105) & NA (0) & India (105)  & \\
+Arabic & \textbf{0.74} (60) ** & 0.60 (45) & Egypt (19) Jordan (16) Morocco (9)  & US (19) India (11) Canada (3)  \\
+Sindhi & \textbf{0.19} (96) & 0.06 (9) & India (58) Pakistan (37) US (1)  & Macedonia (4) Georgia (2) Indonesia (2)  \\
+Portuguese & 0.87 (101) & \textbf{0.96} (3) & Brazil (44) Portugal (31) US (15)  & Romania (1) Japan (1) Israel (1) \\
+Turkish & 0.76 (76) & \textbf{0.80} (27) & Turkey (38) US (18) Macedonia (8)  & India (19) Pakistan (4) Taiwan (1) \\
+Telugu & \textbf{0.80} (102) & 0.50 (1) & India (98) US (3) UAE (1)  & Saudi Arabia (1)  \\
+Irish & \textbf{0.74} (54) & 0.71 (47) & US (39) Ireland (13) UK (2)  & India (36) Romania (5) Macedonia (2)  \\
+Swedish & \textbf{0.73} (54) & 0.71 (45) & US (25) Sweden (22) Finland (3)  & India (23) Macedonia (6) Croatia (2)  \\
+Czech & \textbf{0.71} (45) * & 0.61 (50) & US (17) Czech Republic (14) Serbia (5)  & Macedonia (22) India (10) UK (5)  \\
+Russian & \textbf{0.15} (67) * & 0.12 (27) & US (36) Moldova (7) Russia (6)  & India (14) Macedonia (4) UK (3)  \\
+Breton & 0.17 (3) & \textbf{0.18} (89) & US (3)  & India (83) Macedonia (2) China (1) \\
 \hline\hline
@@
 
+A few languages standout for having suspiciously strong performance by out of region workers, notably Irish and Swedish, for which out of region workers account for a near equivalent volume and quality of translations to the in region workers.
+This is admittedly implausible, considering the relatively small number of Irish speakers worldwide, and the very low number living in the countries in which our Turkers were based (primarily India).
+Such results highlight the fact that cheating using online translation resources is a real problem, and despite our best efforts to remove workers using Google Translate, some cheating is still evident.
+Restricting to within region workers is an effective way to reduce the prevalence of cheating.
+We discuss the languages which are best supported by true native speakers in section 6.
+
 \paragraph{Speed of translation}
@@
 Figure \ref{figure:volume-of-data-by-language} gives the throughput of the full-sentence translation task for the six Indian languages.
-The fastest language was Malayalam, for we collected half a million words of translations in just under a week.
+The fastest language was Malayalam, for which we collected half a million words of translations in just under a week.
 Table \ref{table:data-size} gives the size of the data set that we created for each of these languages.
@@
 \paragraph{Training SMT systems}
-We trained statistical translation models from the parallel corpora that we created for the six Indian languages using the Joshua machine translation system \cite{post-EtAl:2013:WMT}.
+We trained statistical translation models from the parallel corpora that we created for the six Indian languages using the Joshua machine translation system \cite{post2012constructing}.
 Table \ref{dictionary_bleu} shows the translation performance when trained on the bitexts alone, and when incorporating the bilingual dictionaries created in our earlier HIT.
+The scores reflect the performance when tested on held out sentences from the training data.
 Adding the dictionaries to the training set produces consistent performance gains, ranging from 1 to 5 BLEU points.
-This represents a substantial improvement, but there is overlap between the source materials for both sets, since both the dictionaries and the bitext source sentences were drawn from Wikipedia.
+This represents a substantial improvement.
+It is worth noting, however, that while the source documents for the full sentences used for testing were kept disjoint from those used for training, there is overlap between the source materials for the dictionaries and those from the test set, since both the dictionaries and the bitext source sentences were drawn from Wikipedia.
 
@@
 \footnotesize
-\small
+%\small
 \begin{tabular}{|p{.1\linewidth}|p{.1\linewidth}|p{.1\linewidth}|p{0.5\linewidth}|}
@@
 &or medium&slow&Bengali,  Bishnupriya Manipuri, Cebuano,  Chinese, Nepali, Newar, Polish, Russian, Sindhi, Tibetan\\\cline{1-4}
-few &high  &fast& Bosnia, Croatian  Macedonian  Malay  Serbo-Croatian\\\cline{3-4}
+few &high  &fast& Bosnia, Croatian,  Macedonian,  Malay,  Serbo-Croatian\\\cline{3-4}
 &&slow&Afrikaans, Albanian, Aragonese, Asturian, Basque, Belarusian, Bulgarian, Central Bicolano, Czech, Danish, Finnish, Galacian, Greek, Haitian, Hungarian, Icelandic, Ilokano, Indonesian, Japanese, Javanese, Kapampangan, Kazakh, Korean, Lithuanian, Low Saxon, Malagasy, Norwegian (Bokmal), Sicilian, Slovak, Slovenian, Thai, UKranian, Uzbek, Waray-Waray, West Frisian, Yoruba\\\cline{2-4}
@@
 The demographics reported in this study are likely to shift over time.
-Amazon may change its expand its payments to new currencies.
+Amazon may expand its payments to new currencies.
 Posting long-running HITs in other languages may recruit more speakers of those languages.
@@
 A variety of techniques should be incorporated into crowdsourcing pipelines to ensure high quality data.
-As a best practice, we suggest: (1) restricting workers to countries that plausibly speak the foreign language of interest, (2) embedding gold standard controls or administering language pretests, rather than relying solely on self-reported language skills, and (3) and excluding workers whose translations have high overlap with online machine translation systems like Google translate.
+As a best practice, we suggest: (1) restricting workers to countries that plausibly speak the foreign language of interest, (2) embedding gold standard controls or administering language pretests, rather than relying solely on self-reported language skills, and (3) excluding workers whose translations have high overlap with online machine translation systems like Google translate.
+If cheating using external resources is likely, then also consider (4) recording information like time spent on a HIT (cumulative and on individual items), patterns in keystroke logs, tab/window focus, etc.
 

### 2014-01-26 code/src/20130905/paper-rewrite/figures/code/quality_bar.py

@@ -53,5 +53,6 @@ plt.xlim(0,len(graph_data))
 #print [d[3] for d in graph_data]
 
 plt.xticks(np.arange(len(graph_data)) + w / 2.,[d[3] for d in graph_data], size='x-small', rotation=90)
-#plt.show()
-plt.savefig('quality_bar_filtered.pdf')
+plt.show()
+#plt.set_aspect('equal')
+#plt.savefig('quality_bar_filtered.pdf')

### 2014-01-26 code/src/20130905/paper-rewrite/figures/code/region_table.py

@@ -27,17 +27,17 @@ def print_table(lang_counts) :
 		params = (lmap[l].capitalize(),inavg,incnt,outavg,outcnt,topinstr,topoutstr)
 		try : 
 			if inavg > outavg : 
-				if sig == '5' : print '%s & \\textbf{%.03f} (%d) ** & %.03f (%d) & %s & %s \\\\'%params
-				elif sig == '10' : print '%s & \\textbf{%.03f} (%d) * & %.03f (%d) & %s & %s \\\\'%params
-				else : print '%s & \\textbf{%.03f} (%d) & %.03f (%d) & %s & %s \\\\'%params
+				if sig == '5' : print '%s & \\textbf{%.02f} (%d) ** & %.02f (%d) & %s & %s \\\\'%params
+				elif sig == '10' : print '%s & \\textbf{%.02f} (%d) * & %.02f (%d) & %s & %s \\\\'%params
+				else : print '%s & \\textbf{%.02f} (%d) & %.02f (%d) & %s & %s \\\\'%params
 			else: 
-				if sig == '5' : print '%s & %.03f (%d) & \\textbf{%.03f} (%d) ** & %s & %s\\\\'%params
-				elif sig == '10' : print '%s & %.03f (%d) & \\textbf{%.03f} (%d) * & %s & %s\\\\'%params
-				else : print '%s & %.03f (%d) & \\textbf{%.03f} (%d) & %s & %s\\\\'%params
+				if sig == '5' : print '%s & %.02f (%d) & \\textbf{%.02f} (%d) ** & %s & %s\\\\'%params
+				elif sig == '10' : print '%s & %.02f (%d) & \\textbf{%.02f} (%d) * & %s & %s\\\\'%params
+				else : print '%s & %.02f (%d) & \\textbf{%.02f} (%d) & %s & %s\\\\'%params
 		except : 
-			try : print '%s & %s (%d) & %.03f (%d) & %s & %s\\\\'%params
+			try : print '%s & %s (%d) & %.02f (%d) & %s & %s\\\\'%params
 			except : 
-				try : print '%s & %.03f (%d) & %s (%d) & %s & %s\\\\'%params
+				try : print '%s & %.02f (%d) & %s (%d) & %s & %s\\\\'%params
 				except : print 'BAHHHHHHHHH!'
 	
 #gu	BD,ZM,OM,TZ,KE,CA,ZA,US,MU,other,UK,IN,PK,SG

### 2014-01-26 code/src/completetime.py

@@ -1,177 +1,0 @@
-import re
-import sys
-import csv
-import math
-import json
-import codecs
-import time
-import datetime
-import operator
-import itertools
-import dictionaries
-import numpy as np
-import matplotlib.pyplot as plt
-import compile_data_from_raw as dat
-
-OUTPUT_DIR = 'output'
-RAW_DIR = '/home/steven/Documents/Ellie/Research/demographics/data/dictionary-data-dump-2012-11-13_15:11'
-
-def get_language_dicts(path, filter_list=None):
-	all_dicts = dict()
-	hitmap = dictionaries.hit_map()
-	langids, langcodes = dat.lang_map()
-        hitlangs = dat.hits_language()
-	timemap = time_map()
-	for assign in csv.DictReader(open(path), delimiter='\t'):
-		aid = assign['id']
-		if(aid == ''):
-			continue
-		if(not(filter_list == None) and (aid not in filter_list)):
-			continue
-		alang =  langids[hitlangs[hitmap[aid]]]
-		if not alang in all_dicts:
-			all_dicts[alang] = timemap[aid]
-		tstart, tend = timemap[aid]
-		all_dicts[alang] = (min(all_dicts[alang][0], tstart), max(all_dicts[alang][1], tend))
-	return all_dicts
-
-def time_map():
-	print "Reading data"
-	tdict = dict()
-	for line in open('%s/byassign.times'%OUTPUT_DIR).readlines():
-		aid, start, end = line.split('\t')
-		start_t = datetime.datetime.strptime(start.strip(), "%Y-%m-%d %H:%M:%S")
-		end_t = datetime.datetime.strptime(end.strip(), "%Y-%m-%d %H:%M:%S")
-		tdict[aid] = (start_t, end_t)
-	return tdict
-
-def write_all_times():
-        out = open('%s/byassign.times'%OUTPUT_DIR, 'w')
-        for line in csv.DictReader(open('%s/assignments'%RAW_DIR)):
-                aid = line['id']
-                start = line['accept_time']
-                end = line['submit_time']
-                out.write('%s\t%s\t%s\n'%(aid,start,end,))
-        out.close()
-
-def get_total_time(data):
-	for lang in sorted(data.iteritems(), key=operator.itemgetter(0)):
-		print '%s\t%s'%(lang[0], str(lang[1][1] - lang[1][0]))
-
-def format_for_graph(data):
[…]

### 2014-01-26 writeup/revision 1/paper.tex
Fixed typo
Cropped the quality bar graph to reduce whitespace

--- 2013-11-29 writeup/revision 1/paper.tex
@@
 \begin{center}
-\includegraphics[width=.9\linewidth]{figures/quality_bar.pdf}
+\includegraphics[width=.8\linewidth]{figures/quality_bar.pdf}
 \caption{Translation quality for languages with at least 50 Turkers.
@@
 The demographics reported in this study are likely to shift over time.
-Amazon may change its expand its payments to new currencies.
+Amazon may change its policies about who is eligible to participate or expand its payments to new currencies.
 Posting long-running HITs in other languages may recruit more speakers of those languages.

### 2014-03-10 writeup/final revision/paper.tex
final version

@@
 This facilitates research into human computation, where people can be treated as a function call \cite{vonAhnThesis,Little2009,quinn-bederson:2011}.
-It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge:10,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.
+It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge:10,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP,che.hcomp11}.
 
@@
 
-A few languages standout for having suspiciously strong performance by out of region workers, notably Irish and Swedish, for which out of region workers account for a near equivalent volume and quality of translations to the in region workers.
+A few languages stand out for having suspiciously strong performance by out of region workers, notably Irish and Swedish, for which out of region workers account for a near equivalent volume and quality of translations to the in region workers.
 This is admittedly implausible, considering the relatively small number of Irish speakers worldwide, and the very low number living in the countries in which our Turkers were based (primarily India).
@@
 
+\section{Acknowledgements}
+
+ This material is based on research sponsored by a DARPA Computer Science Study Panel phase 3 award entitled ``Crowdsourcing Translation'' (contract D12PC00368).
+The views and conclusions contained in this publication are those of the authors and should not be interpreted as representing official policies or endorsements by DARPA or the U.S.
+Government.
+This research was supported by the Johns Hopkins University Human Language Technology Center of Excellence and through gifts from Microsoft and Google.
+
+The authors would like to thank the anonymous reviewers for their thoughtful comments, which substantially improved this paper, and of course, our many hard-working Turkers.
+
 \bibliographystyle{acl2012}
